### 2022-02-03 _posts/welcome/welcome.Rmd
2.3.22
1. Recreating 679 SNA Assignment Blog
2. Create GitRepro & Distill Blog
Linberg (2022, Jan. 29). slinberg.net: Distill and Github Pages Setup. Retrieved from https://slinberg.net/meta/distill-and-github-pages-setup/

3. Setup- Publishing to RPubs

---
title: "Welcome to Test: Distill Blog"
description: |
  Welcome to our new blog, Test: Distill Blog. We hope you enjoy 
  reading what we have to say!
author:
  - name: AJW
    url: https://example.com/norajones
    affiliation: Spacely Sprockets
    affiliation_url: https://example.com/spacelysprokets
date: 02-03-2022
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# Learn more about creating blogs with Distill at:
# https://rstudio.github.io/distill/blog.html

```

### 2022-02-03 SetUp_RPubs_PublishBlog.Rmd

---
title: "SetUp_RPubs_PublishBlog"
description: |
  Publishing to RPubs: A new article created using the Distill format.
author:
  - name: 
    url: 
    affiliation: 
    affiliation_url:
date: "`r Sys.Date()`"
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

```

*Publishing to RPubs*

Open RStudio and create a new Rmd file
                            (File > New File > R Markdown).
When you’re ready to publish to RPubs, click Knit.
From your knitted document, click Publish in the top, right-hand corner.
Select Rpubs.

Click Publish. You’ll then be able to create/edit a title, short description and customized slug.

********
Distill is a publication format for scientific and technical writing, native to the web.

Learn more about using Distill for R Markdown at <https://rstudio.github.io/distill>.

### 2022-02-03 Test_ RPubs_Publishing.Rmd

---
title: "Test: RPubs: Publishing"
author: "audra white"
date: "2/3/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2022-02-08 docs/1.SNA-  Templates/SNA-Template_Weekly-Assignments.Rmd

---
title: "Social Network Analysis: Assignment: Week#"
description: " lorum ipsum "
  A new article created using the Distill format.
author:
  - name: "Audra Jamai White" 
    url: 
    affiliation: " DACSS 679: Social Network Analysis"
    affiliation_url: 
date: "`r Sys.Date()`"
output: distill::distill_article
---

```{r setup, Libraries, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# Document Creation
library(knitr)
library(rmarkdown)
library(yaml)
library(distill)
library(blogdown)

# Basic Analysis
library(ggplot2)
library(tidyverse)
library(clipr)
library(dbplyr)
library(data.table)
library(stringr)
library(stringi)
library(tibble)
library(tidyr)

# SNA - Social Network Analysis

library(tergm)
library(ergm)

library(network)
library(networkDynamic)
library(networkDynamicData)

library(statnet)
library(igraph)
library(igraphdata)
library(tsna)
library(sna)

```

*Week \# Assignment*

```{r,Import Data Set,include=FALSE}

```

```{r, Describe Data Set}

```

```{r, Analyze Data Set}

```

Distill is a publication format for scientific and technical writing, native to the web.

Learn more about using Distill for R Markdown at <https://rstudio.github.io/distill>.

### 2022-02-08 docs/2. SNA-Tutorials/Overview-SNA_Tutorials.Rmd

---
title: "SNA Tutorials: Social Overview"
output: html_notebook
---

**[igraph]**
```
```

**[statnet]**
```
```

## Key Terms & Definitions
### Network Structure: Week 2: Key Terms
A *vertex attribute* is a vector (or variable) of additional information about the nodes in a network dataset:
name, location, demographic information about the actors or organizations  comprise the vertices of the network.

In case you have forgotten, we can 
[statnet]
``` print(DataSet.stat) 
```

*edge attribute* is a vector (or variable) of additional information about the edges or relationships in a network dataset. The most common edge attribute is weight, in a weighted dataset.

# Week 1: *Describe Network Data*
## 1. **List and inspect:** 
    List the objects to make sure the datafiles are working properly:
```is()
```

## 2. **Network Size:**
    What is the size of the network?

**[igraph]**
    Count of vertices
```vcount(DataSet.ig)
```
    Count of edges
``` ecount(DataSet.ig)
```
**[statnet]**
    Network Attributes: count vertices and edges 
```print(DataSet.stat)
```

## 3. **Network Features:**

  **[igraph]**    
  Is this a Bipartite or single mode network?
``` is_bipartite(DataSet.ig)
```

  Are edges directed or undirected?
```is_directed(DataSet.ig)
```

  Are edges weighted or unweighted?
```is_weighted(DataSet.ig)
```

  **[statnet]**
    Find network features
```print(DataSet.stat)
```

## 4. **Network Attributes:**
  R commands used with vector objects also work with network attribute data
```sort()
```
```summary()
```

**[igraph]**
```summary(
      E(
      DataSet.ig
      )
      $weight
    )
 ```

**[statnet]**
``` summary(
      DataSet.stat 
      %e% 
      "weight"
    )
```

  *Accessing Attribute Data*
- When we work with an R dataframe object, you can access a specific variable in the dataframe by using the >data$varname< or >$ command<

  **[igraph]**
  access vertex attribute 
```V(
      DataSet.ig
      )
      $name
```
  access edge attribute
```E(
      DataSet.ig
      )
      $weight
```

  **[statnet]**
  access vertex attribute
```head(
      DataSet.stat 
      %v% 
      "vertex.names"
      )
```
  access edge attribute
``` head(
        DataSet.stat 
        %e% 
        "weight"
        )
```

  Generate a list the names of vertex and edge attributes of the network data.
  **[igraph]**
  Names- Vertex Attributes
```igraph::vertex_attr_names(climate.ig)
```
  Names- Edge Attributes
```igraph::edge_attr_names(climate.ig)
````

  **[statnet]**
  Names- Vertex Attributes
```network::list.vertex.attributes(climate.stat)
```
  Names- Edge Attributes
```network::list.edge.attributes(climate.stat)
```

# Week2: *Network Structure: Overview*
- Dyads and Dyad Census
  *dyad census* gives the number of dyads where the relationship is:
    - Reciprocal (mutual), or mut
    - Asymmetric (non-mutual), or asym, and
    - Absent, or null

- Triads and Triad Census
  *triad census* provides a fundamental descriptive insight into the types of triads found in a dataset

- Network Transitivity / Global Clustering
  *Transitivity* is a network-level statistic that captures the proption of connected triads in the network that are complete (all three possible links present)
  *Transitivity* varies between 0 [no connected triads] and 1 [all connected triads are transitive]

- Local Transivity or Clustering
  Local transitivity (*local clustering coefficient*) is the density of an ego network
  *average clustering coefficient* average of local transivity for all vertices in a graph

- Path Length & Geodesic

- Component Structure and Membership

## Dyad Census 
  Classifies all dyads in the network as:
      - Reciprocal (mutual), or mut
      - Asymmetric (non-mutual), or asym, and
      - Absent, or null

  **[igraph]**
```igraph::dyad.census(gotbook.ig)
```  
  **[statnet]**
```sna::dyad.census(gotbook.stat
```

## **Triad Census**
  Classifies all triads in the network

**[igraph]**
``` igraph::triad_census(gotbook.ig)
```
**[statnet]**
  Undirected Network
``` sna::triad.census(gotbook.stat, mode="graph")```
  Directed Detwork
``` sna::triad.census(gotbook.stat, mode=)```

## Transitivity: **Global Clustering**

  network transitivity:
**[igraph]**
``` transitivity(gotbook.ig)
```
  weighted network transitivity:
```igraph::transivity()
```

**[statnet]**
  weighted network transitivity:
``` sna::gtrans()
```
  For Directed Networks - network structure rooted in hierarchy
```gtrans()
```

## Transivity: **Local Clustering**

  **[igraph]**

  1. Retrieve a list of the three vertices we are interested

``` V(gotbook.ig)
      [c(
      "vertex_attr_names",
      "vertex_attr_names",
      "vertex_attr_names"
      )]
```

  2. Check ego network transitivity

```transitivity(
      gotbook.ig,
      type="local",
      vids=V(gotbook.ig)
      [c(
      "vertex_attr_names",
      "vertex_attr_names",
      "vertex_attr_names"
      )]
    ) 
```

  Global clustering cofficient
```transitivity(gotbook.ig,
      type="global"
    )
```

  Average local clustering coefficient
```transitivity(gotbook.ig,
      type="average"
    )
```

# *INCOMPLETE* Advanced [Week 2]
## ADVANCED: Path Length and Geodesic
## ADVANCED Component Structure and Membership

### 2022-02-08 docs/2. SNA-Tutorials/week2-SNA_Tutorial.Rmd

--- 2022-02-08 docs/2. SNA-Tutorials/Overview-SNA_Tutorials.Rmd
@@
 ---
-title: "SNA Tutorials: Social Overview"
+title: "SNA Tutorials: Week 2: Network Structure"
 output: html_notebook
@@
 ## Key Terms & Definitions
-### Network Structure: Week 2: Key Terms
+### Vetex Attribute & Edge Attribute 
 A *vertex attribute* is a vector (or variable) of additional information about the nodes in a network dataset:
@@
 *edge attribute* is a vector (or variable) of additional information about the edges or relationships in a network dataset. The most common edge attribute is weight, in a weighted dataset.
+### Network Structure
+- Dyads and Dyad Census
+  *dyad census* gives the number of dyads where the relationship is:
+    - Reciprocal (mutual), or mut
+    - Asymmetric (non-mutual), or asym, and
+    - Absent, or null
 
-# Week 1: *Describe Network Data*
-## 1. **List and inspect:** 
+- Triads and Triad Census
+  *triad census* provides a fundamental descriptive insight into the types of triads found in a dataset
+
+- Network Transitivity / Global Clustering
+  *Transitivity* is a network-level statistic that captures the proption of connected triads in the network that are complete (all three possible links present)
+  *Transitivity* varies between 0 [no connected triads] and 1 [all connected triads are transitive]
+
+- Local Transivity or Clustering
+  Local transitivity (*local clustering coefficient*) is the density of an ego network
+  *average clustering coefficient* average of local transivity for all vertices in a graph
+
+- Path Length & Geodesic
+
+- Component Structure and Membership
+
+# Network Structure [Week 2]
+aspects of network structure introduced in the Week 2 Lecture:
+- Dyads and Dyad Census
+  *dyad census* gives the number of dyads where the relationship is:
+    - Reciprocal (mutual), or mut
+    - Asymmetric (non-mutual), or asym, and
+    - Absent, or null
+
+- Triads and Triad Census
+  *triad census* provides a fundamental descriptive insight into the types of triads found in a dataset
+
+- Network Transitivity / Global Clustering
+  *Transitivity* is a network-level statistic that captures the proption of connected triads in the network that are complete (all three possible links present)
+  *Transitivity* varies between 0 [no connected triads] and 1 [all connected triads are transitive]
+
+- Local Transivity or Clustering
+  Local transitivity (*local clustering coefficient*) is the density of an ego network
+  *average clustering coefficient* average of local transivity for all vertices in a graph
+
+- Path Length & Geodesic
+
+- Component Structure and Membership
+
+# Describe Network Data 
+## 1. *List and inspect:* 
     List the objects to make sure the datafiles are working properly:
@@
 
-## 2. **Network Size:**
+## 2. *Network Size:*
     What is the size of the network?
@@
 
-## 3. **Network Features:**
+## 3. *Network Features:*
 
@@
 
-## 4. **Network Attributes:**
+## 4. *Network Attributes*
   R commands used with vector objects also work with network attribute data
@@
 
-# Week2: *Network Structure: Overview*
-- Dyads and Dyad Census
-  *dyad census* gives the number of dyads where the relationship is:
-    - Reciprocal (mutual), or mut
-    - Asymmetric (non-mutual), or asym, and
-    - Absent, or null
-
-- Triads and Triad Census
-  *triad census* provides a fundamental descriptive insight into the types of triads found in a dataset
-
-- Network Transitivity / Global Clustering
-  *Transitivity* is a network-level statistic that captures the proption of connected triads in the network that are complete (all three possible links present)
-  *Transitivity* varies between 0 [no connected triads] and 1 [all connected triads are transitive]
-
-- Local Transivity or Clustering
-  Local transitivity (*local clustering coefficient*) is the density of an ego network
-  *average clustering coefficient* average of local transivity for all vertices in a graph
-
-- Path Length & Geodesic
-
-- Component Structure and Membership
-
-## Dyad Census 
+# Dyad Census 
   Classifies all dyads in the network as:
@@
 
-## **Triad Census**
+# Triad Census
   Classifies all triads in the network
@@
 
-## Transitivity: **Global Clustering**
+# Transitivity or Global Clustering
 
@@
 ```
-
-## Transivity: **Local Clustering**
+# Local Transivity or Clustering
 
@@
 
-# *INCOMPLETE* Advanced [Week 2]
+# Advanced [Week 2]
 ## ADVANCED: Path Length and Geodesic

### 2022-02-08 docs/3. SNA - Assignments/DRAFT-week3-Assignment.Rmd

---
title: "Social Network Analysis: Week 3: Degree and Centrality"
description: " "
author:
  - name: "Audra Jamai White" 
    url: 
    affiliation: "Umass Amherst - DACSS 679: Social Network Analysis"
    affiliation_url: 
date: "`r Sys.Date()`"
output: distill::distill_article
---

```{r setup, Libraries, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# Document Creation
library(knitr)
library(markdown)
library(yaml)
library(distill)
library(blogdown)

# Basic Analysis
library(ggplot2)
library(tidyverse)
library(clipr)
library(dbplyr)
library(data.table)
library(stringr)
library(stringi)
library(tibble)
library(tidyr)

# SNA - Social Network Analysis

library(tergm)
library(ergm)
library(network)
library(networkDynamic)
library(networkDynamicData)

library(statnet)
library(igraph)
library(igraphdata)
library(tsna)
library(sna)

```

      *Week 3 Assignment: Degree and Centrality*

Using the tutorial as a guide, 
      *  you may use your own data; 
      *  the data provided in the week 3. Syntax dataset is Correlates of War trade network - you can read more about it online; or
      *  choose another dataset.

## Working from the example R syntax:
1.   calculate network density; 
2.   degree centrality, and 
3.   centralization measures for your network data.

## Write up your results briefly:
*   focus on interpretation of the results. 
*   Don’t list statistics or provide code, 
*  **the goal is to choose a few interesting results and provide an interpretation.**

## Briefly describe the dataset:
1.   identify initial network format; 
2.   describe and identify the nodes 
     including: 
        *  how many nodes are in the dataset; 
3.   what constitutes a tie or edge
     including:
        *  how many ties, 
        *   whether ties are directed/undirected,
        *   whether ties are weighted/binary, 
        *   and how to interpret the value of the tie if any.
        *   Whether or not there are edge attributes 
            that might be used to:
            *   subset data, or 
            *   stack multiple networks. 
Not every feature of the network needs to be described, but **description should orient reader to the network data and provide any necessary context for the results provided.**

## Provide at least two or three noteworthy results, including:
1.   the relevant statistics and interpretation. 
        For example, explaining which node(s) are most central and which are least central. 
2.   Discuss (with any related evidence) whether or not the node(s) behavior is in line with or violates expectations based on the degree centrality measure. 
3.   What do you make of network density and centralization measures?  
4.   What about differences in the binary 100 million threshold network vs valued trade flows network. 
 5.  Check tutorial for other ideas of results to discuss.

##
1.  [**Identify an existing data set.**]{.ul}

| This can be one provided in the course directory, in an R package or library, located online, or some other source.

2.  [**Briefly describe the network dataset.**]{.ul}

| Identify and describe content of nodes and links, and identify format of data set (i.e., matrix or edgelist, directed or not, weighted or not), and whether attribute data are present. 
  Be sure to provide information about network size (e.g., information obtained from network description using week 1 network basics tutorial commands.)

# Week 2: Scripts

```{r Import Data Set, echo=TRUE}

  # install.packages("network")

    data("flo", package = "network")

```

# 2. Briefly describe the network dataset.

-   *Be sure to provide information about network size (e.g., information obtained from network description using week 1 network basics tutorial commands.)*

1.  *Identify and describe content of nodes and links,*

-   each of the 16 Florentine Family Names represent a Node in the network.

```{r Colnames}
 colnames(flo)
```

2.  *Identify format of data set (i.e., matrix or edgelist, directed or not, weighted or not), and*

    -   Flo Format: Size: 16 x 16 square dimmentions indicate a adjacency matrix format

    Network attributes: vertices = 16 directed = TRUE hyper = FALSE loops = FALSE multiple = FALSE bipartite = FALSE total edges= 40 missing edges= 0 non-missing edges= 40

Vertex attribute names: vertex.names

No edge attributes

```{r Dimmentions, echo=TRUE}

  dim(flo)

```

```{r Network Attributes, echo=TRUE}

  network(flo)

```

3.  *Identify whether attribute data are present.*

```{r Summary,echo=TRUE}

  summary(flo,
          print.adj = TRUE
          )
```

## Create & Describe: Directed Adjacency Matrix

*Florentine Families Directed Adjacency Matrix Network Objects:*
    **iGraph** flo.ig 
    **Statnet** flo.stat

iGraph and Statnet both use {r graph4} for Directed Adjacency Matrix Objects

```{r graph4, statnet: Directed: Adjacency Network, echo=TRUE}

    flo.stat<-
        network(
        flo,
        directed=F,
        matrix.type="adjacency"
        )

#     provides a description of several critical network features
    print(flo.stat)

```

```{r graph4, igraph: Directed: Adjacency Network, echo=TRUE}

    flo.ig<-
      graph.adjacency(
      flo,
      mode="undirected"
      ) 
    print(flo.ig)
```

```{r igraph: Network Description, echo=TRUE}

#     Count Vertices
    vcount(flo.ig)

#     Count Edges
    ecount(flo.ig)

# Is this a Bipartite or single mode network?
    is_bipartite(flo.ig)

#  Are edges directed or undirected?
    is_directed(flo.ig)

#Are edges weighted or unweighted?
    is_weighted(flo.ig)

```
 **Vertex and Edge Attributes**

```{r statnet: Attribute Data: Directed: Adjacency Network, echo=TRUE}

#     access vertex attributes
  head(flo.stat %v% "vertex.names")

#      list the names of vertex attributes
  network::list.vertex.attributes(flo.stat)

#     access edge attribute
  head(flo.stat%e% "weight")

#  Generate a list the names of edge attributes
  network::list.edge.attributes(flo.stat)

#   summarize numeric network attribute
  summary(flo.stat  %v% "name")

```

```{r igraph: Attribute Data: Directed: Adjacency Network, echo=TRUE}

#     access vertex attribute 
  V(flo.ig)$name
#     Generate a list the names of vertex attributes
  igraph::vertex_attr_names(flo.ig)

#     access edge attribute
  E(flo.ig)$weight

#   Generate a list the names of edge attributes  
  igraph::edge_attr_names(flo.ig)

#   summarize numeric network attribute
  summary(E(flo.ig)$weight)

```

# 3. Explore the dataset using commands from week 2 tutorial.

5.  *geodesic and path distances,*

## Path Length and Geodesic

```{r iGraph:Nodes: Path: Length, echo=TRUE}

#     Calculate distances between two nodes
    distances(flo.ig,"Bischeri","Ridolfi")

#     Calculate distance between two nodes using unweighted edges
    distances(flo.ig,"Bischeri", "Castellani",weights=NA)

```

We can also find all of the shortest paths between two famalies in this network.
These list the starting node and the ending node with all nodes inbetween for each path. 
The option weights=NA means that any available edge weights are ignored.

```{r iGraph:Nodes: Path: Shortest, echo=TRUE}

#     isolating the distances between specific node
    all_shortest_paths(flo.ig,"Strozzi","Tornabuoni", weights=NA)$res
## Note: manually tell igraph to ignore edge weights.
```

The concept of shortest path to describe the overall network structure can be more useful

```{r iGraph:Network: Path: Shortest, echo=TRUE}

#     find average shortest path for network
    average.path.length(flo.ig,directed=F)

```

6.  *triads or transitivity,*

## Dyad Census

Classifies all dyads in the network as: - Reciprocal (mutual), or mut - Asymmetric (non-mutual), or asym, and - Absent, or null

```{r statnet: Dyad Census , echo=TRUE}

    sna::dyad.census(flo.stat)

```

```{r iGraph: Dyad Census, echo=TRUE}

  igraph::dyad.census(flo.ig)

```

## Triad Census

Classifies all triads in the network. The triad census provides a fundamental descriptive insight into the types of triads found in a particular dataset.

```{r statnet: Triad Census, echo=TRUE}

#     Classify all Triad in the network: Directed Network
  sna::triad.census(flo.stat, mode= )

#     Classify all Triad in the network: Undirected Network
   sna::triad.census(flo.stat, mode="graph")

#     total number of all four triad types returned by triad census
   sum(sna::triad.census(flo.stat, mode="graph"))

```

```{r iGraph: Triad Census, echo=TRUE}
#Classify all Triad in the network
     igraph::triad_census(flo.ig)

```

## Transitivity or Global Clustering

```{r iGraph: weighted/ network transitivity, echo=TRUE}

#     network transitivity:
    transitivity(flo.ig)

#     weighted network transitivity:
#   igraph::transivity(flo.ig)

```

```{r statnet: weighted/ directed network transitivity, echo=TRUE}

#     Directed Networks transitivity:
  gtrans(flo.stat)

#   methods for weighted networks, rank and correlation, along with the relevant references.
#  sna::gtrans()

```

## Local Transivity or Clustering
`Local transitivity` (local clustering coefficient), is a technical description of the density of an ego network.

```{r iGraph:Local transitivity, echo=TRUE}

#     Retrive a list of the vertices we are interested
    V(flo.ig)[c("Bischeri" ,
                "Castellani", 
                "Medici",
                "Ridolfi")]

#     check ego network transitivity
transitivity(flo.ig,
             type="local", 
             vids=V(flo.ig)
             [c("Bischeri",
                "Castellani", 
                "Medici",
                "Ridolfi")]) 
#     get global clustering cofficient
  transitivity(flo.ig, type="global")

#     get average local clustering coefficient
  transitivity(flo.ig, type="average")

```

7.  *connectedness and.or component structure, etc.*

> Distill is a publication format for scientific and technical writing, native to the web.
>
> Learn more about using Distill for R Markdown at <https://rstudio.github.io/distill>.
##

# Week3:    Briefly describe the dataset:
1.   identify initial network format; 
2.   describe and identify the nodes 
     including: 
        *  how many nodes are in the dataset; 
3.   what constitutes a tie or edge
     including:
        *  how many ties, 
        *   whether ties are directed/undirected,
        *   whether ties are weighted/binary, 
        *   and how to interpret the value of the tie if any.
        *   Whether or not there are edge attributes 
            that might be used to:
            *   subset data, or 
            *   stack multiple networks.

#WEEK 3:     Working from the example R syntax:
1.   calculate network density; 
2.   degree centrality, and 
3.   centralization measures for your network data.

#WEEK 3:  Provide at least two or three noteworthy results
1.   the relevant statistics and interpretation. 
        For example, explaining which node(s) are most central and which are least central. 
2.   Discuss (with any related evidence) whether or not the node(s) behavior is in line with or violates expectations based on the degree centrality measure. 
3.   What do you make of network density and centralization measures?  
4.   What about differences in the binary 100 million threshold network vs valued trade flows network. 
 5.  Check tutorial for other ideas of results to discuss.

### 2022-02-08 docs/3. SNA - Assignments/Week3-Assignment.Rmd

--- 2022-02-08 docs/3. SNA - Assignments/DRAFT-week3-Assignment.Rmd
@@
 ```
-
-      *Week 3 Assignment: Degree and Centrality*
-
-Using the tutorial as a guide, 
-      *  you may use your own data; 
-      *  the data provided in the week 3. Syntax dataset is Correlates of War trade network - you can read more about it online; or
-      *  choose another dataset.
-
 ## Working from the example R syntax:
@@
 
-##
-1.  [**Identify an existing data set.**]{.ul}
-
-| This can be one provided in the course directory, in an R package or library, located online, or some other source.
-
-2.  [**Briefly describe the network dataset.**]{.ul}
-
-| Identify and describe content of nodes and links, and identify format of data set (i.e., matrix or edgelist, directed or not, weighted or not), and whether attribute data are present. 
-  Be sure to provide information about network size (e.g., information obtained from network description using week 1 network basics tutorial commands.)
-
-# Week 2: Scripts
-
-```{r Import Data Set, echo=TRUE}
-
-  # install.packages("network")
-
-    data("flo", package = "network")
-
-```
-
-# 2. Briefly describe the network dataset.
-
--   *Be sure to provide information about network size (e.g., information obtained from network description using week 1 network basics tutorial commands.)*
-
-1.  *Identify and describe content of nodes and links,*
-
--   each of the 16 Florentine Family Names represent a Node in the network.
-
-```{r Colnames}
- colnames(flo)
-```
-
-2.  *Identify format of data set (i.e., matrix or edgelist, directed or not, weighted or not), and*
-
-    -   Flo Format: Size: 16 x 16 square dimmentions indicate a adjacency matrix format
-
-    Network attributes: vertices = 16 directed = TRUE hyper = FALSE loops = FALSE multiple = FALSE bipartite = FALSE total edges= 40 missing edges= 0 non-missing edges= 40
-
-Vertex attribute names: vertex.names
-
-No edge attributes
-
-```{r Dimmentions, echo=TRUE}
-
-  dim(flo)
-
-```
-
-```{r Network Attributes, echo=TRUE}
-
-  network(flo)
-
-```
-
-3.  *Identify whether attribute data are present.*
-
-```{r Summary,echo=TRUE}
-
-  summary(flo,
-          print.adj = TRUE
-          )
-```
-
-## Create & Describe: Directed Adjacency Matrix
-
-*Florentine Families Directed Adjacency Matrix Network Objects:*
-    **iGraph** flo.ig 
-    **Statnet** flo.stat
-
-iGraph and Statnet both use {r graph4} for Directed Adjacency Matrix Objects
-
-```{r graph4, statnet: Directed: Adjacency Network, echo=TRUE}
-
-    flo.stat<-
-        network(
-        flo,
-        directed=F,
-        matrix.type="adjacency"
-        )
-
-#     provides a description of several critical network features
-    print(flo.stat)
-
-```
-
-```{r graph4, igraph: Directed: Adjacency Network, echo=TRUE}
-
-    flo.ig<-
-      graph.adjacency(
-      flo,
-      mode="undirected"
-      ) 
-    print(flo.ig)
-```
-
-```{r igraph: Network Description, echo=TRUE}
-
-#     Count Vertices
-    vcount(flo.ig)
-
-#     Count Edges
-    ecount(flo.ig)
-
-# Is this a Bipartite or single mode network?
-    is_bipartite(flo.ig)
-
-#  Are edges directed or undirected?
-    is_directed(flo.ig)
-
-#Are edges weighted or unweighted?
-    is_weighted(flo.ig)
-
-```
- **Vertex and Edge Attributes**
-
-```{r statnet: Attribute Data: Directed: Adjacency Network, echo=TRUE}
-
-#     access vertex attributes
-  head(flo.stat %v% "vertex.names")
-
-#      list the names of vertex attributes
-  network::list.vertex.attributes(flo.stat)
-
-#     access edge attribute
-  head(flo.stat%e% "weight")
-
-#  Generate a list the names of edge attributes
-  network::list.edge.attributes(flo.stat)
-
-#   summarize numeric network attribute
-  summary(flo.stat  %v% "name")
-
-```
-
-```{r igraph: Attribute Data: Directed: Adjacency Network, echo=TRUE}
-
-#     access vertex attribute 
-  V(flo.ig)$name
-#     Generate a list the names of vertex attributes
-  igraph::vertex_attr_names(flo.ig)
-
-#     access edge attribute
-  E(flo.ig)$weight
-
-#   Generate a list the names of edge attributes  
-  igraph::edge_attr_names(flo.ig)
-
-#   summarize numeric network attribute
-  summary(E(flo.ig)$weight)
-
-```
-
-# 3. Explore the dataset using commands from week 2 tutorial.
-
-5.  *geodesic and path distances,*
-
-## Path Length and Geodesic
-
-```{r iGraph:Nodes: Path: Length, echo=TRUE}
-
-#     Calculate distances between two nodes
-    distances(flo.ig,"Bischeri","Ridolfi")
-
-#     Calculate distance between two nodes using unweighted edges
-    distances(flo.ig,"Bischeri", "Castellani",weights=NA)
-
-```
-
-We can also find all of the shortest paths between two famalies in this network.
-These list the starting node and the ending node with all nodes inbetween for each path. 
-The option weights=NA means that any available edge weights are ignored.
-
-```{r iGraph:Nodes: Path: Shortest, echo=TRUE}
-
-#     isolating the distances between specific node
-    all_shortest_paths(flo.ig,"Strozzi","Tornabuoni", weights=NA)$res
-## Note: manually tell igraph to ignore edge weights.
-```
-
-The concept of shortest path to describe the overall network structure can be more useful
-
-```{r iGraph:Network: Path: Shortest, echo=TRUE}
-
-#     find average shortest path for network
-    average.path.length(flo.ig,directed=F)
-
-```
-
-6.  *triads or transitivity,*
-
-## Dyad Census
-
-Classifies all dyads in the network as: - Reciprocal (mutual), or mut - Asymmetric (non-mutual), or asym, and - Absent, or null
-
-```{r statnet: Dyad Census , echo=TRUE}
-
-    sna::dyad.census(flo.stat)
-
-```
-
-```{r iGraph: Dyad Census, echo=TRUE}
-
-  igraph::dyad.census(flo.ig)
-
-```
-
-## Triad Census
-
-Classifies all triads in the network. The triad census provides a fundamental descriptive insight into the types of triads found in a particular dataset.
-
-```{r statnet: Triad Census, echo=TRUE}
-
-#     Classify all Triad in the network: Directed Network
-  sna::triad.census(flo.stat, mode= )
-
-#     Classify all Triad in the network: Undirected Network
-   sna::triad.census(flo.stat, mode="graph")
-
-#     total number of all four triad types returned by triad census
-   sum(sna::triad.census(flo.stat, mode="graph"))
-
-```
-
-```{r iGraph: Triad Census, echo=TRUE}
-#Classify all Triad in the network
-     igraph::triad_census(flo.ig)
-
-```
-
-## Transitivity or Global Clustering
-
-```{r iGraph: weighted/ network transitivity, echo=TRUE}
-
-#     network transitivity:
-    transitivity(flo.ig)
-
-#     weighted network transitivity:
-#   igraph::transivity(flo.ig)
-
-```
-
-```{r statnet: weighted/ directed network transitivity, echo=TRUE}
-
-#     Directed Networks transitivity:
-  gtrans(flo.stat)
-
-#   methods for weighted networks, rank and correlation, along with the relevant references.
-#  sna::gtrans()
-
-```
-
-## Local Transivity or Clustering
-`Local transitivity` (local clustering coefficient), is a technical description of the density of an ego network.
-
-```{r iGraph:Local transitivity, echo=TRUE}
-
-#     Retrive a list of the vertices we are interested
-    V(flo.ig)[c("Bischeri" ,
-                "Castellani", 
-                "Medici",
-                "Ridolfi")]
-
-#     check ego network transitivity
-transitivity(flo.ig,
-             type="local", 
-             vids=V(flo.ig)
-             [c("Bischeri",
-                "Castellani", 
-                "Medici",
-                "Ridolfi")]) 
-#     get global clustering cofficient
-  transitivity(flo.ig, type="global")
-
-#     get average local clustering coefficient
-  transitivity(flo.ig, type="average")
-
-```
-
-7.  *connectedness and.or component structure, etc.*
-
 > Distill is a publication format for scientific and technical writing, native to the web.
@@
 > Learn more about using Distill for R Markdown at <https://rstudio.github.io/distill>.
-##
-
-# Week3:    Briefly describe the dataset:
-1.   identify initial network format; 
-2.   describe and identify the nodes 
-     including: 
-        *  how many nodes are in the dataset; 
-3.   what constitutes a tie or edge
-     including:
-        *  how many ties, 
-        *   whether ties are directed/undirected,
-        *   whether ties are weighted/binary, 
-        *   and how to interpret the value of the tie if any.
-        *   Whether or not there are edge attributes 
-            that might be used to:
-            *   subset data, or 
-            *   stack multiple networks.
-
-#WEEK 3:     Working from the example R syntax:
-1.   calculate network density; 
-2.   degree centrality, and 
-3.   centralization measures for your network data.
-
-#WEEK 3:  Provide at least two or three noteworthy results
-1.   the relevant statistics and interpretation. 
-        For example, explaining which node(s) are most central and which are least central. 
-2.   Discuss (with any related evidence) whether or not the node(s) behavior is in line with or violates expectations based on the degree centrality measure. 
-3.   What do you make of network density and centralization measures?  
-4.   What about differences in the binary 100 million threshold network vs valued trade flows network. 
- 5.  Check tutorial for other ideas of results to discuss.

### 2022-02-08 docs/3. SNA - Assignments/week2-Assignment-Basic_Network_Structure.Rmd

--- 2022-02-08 docs/3. SNA - Assignments/DRAFT-week3-Assignment.Rmd
@@
 ---
-title: "Social Network Analysis: Week 3: Degree and Centrality"
-description: " "
+title: "Social Network Analysis: Week 2: Basic Network Structure"
+description: "use `igraph` and `statnet` tools to describe aspects of network structure introduced in the Week 2 Lecture: Dyads and Dyad Census, Triads and Triad Census, Network Transitivity and Clustering, Path Length & Geodesic"
+
 author:
@@
 
-      *Week 3 Assignment: Degree and Centrality*
+## Social Network Analysis
 
-Using the tutorial as a guide, 
-      *  you may use your own data; 
-      *  the data provided in the week 3. Syntax dataset is Correlates of War trade network - you can read more about it online; or
-      *  choose another dataset.
+# **Week 2 Assignment: Network Structure**
 
-## Working from the example R syntax:
-1.   calculate network density; 
-2.   degree centrality, and 
-3.   centralization measures for your network data.
-
-## Write up your results briefly:
-*   focus on interpretation of the results. 
-*   Don’t list statistics or provide code, 
-*  **the goal is to choose a few interesting results and provide an interpretation.**
-
-## Briefly describe the dataset:
-1.   identify initial network format; 
-2.   describe and identify the nodes 
-     including: 
-        *  how many nodes are in the dataset; 
-3.   what constitutes a tie or edge
-     including:
-        *  how many ties, 
-        *   whether ties are directed/undirected,
-        *   whether ties are weighted/binary, 
-        *   and how to interpret the value of the tie if any.
-        *   Whether or not there are edge attributes 
-            that might be used to:
-            *   subset data, or 
-            *   stack multiple networks. 
-Not every feature of the network needs to be described, but **description should orient reader to the network data and provide any necessary context for the results provided.**
-
-## Provide at least two or three noteworthy results, including:
-1.   the relevant statistics and interpretation. 
-        For example, explaining which node(s) are most central and which are least central. 
-2.   Discuss (with any related evidence) whether or not the node(s) behavior is in line with or violates expectations based on the degree centrality measure. 
-3.   What do you make of network density and centralization measures?  
-4.   What about differences in the binary 100 million threshold network vs valued trade flows network. 
- 5.  Check tutorial for other ideas of results to discuss.
-
-##
 1.  [**Identify an existing data set.**]{.ul}
@@
 
-# Week 2: Scripts
+3.  [**Explore the dataset using commands from week 2 tutorial.**]{.ul}
+
+| Comment on the highlighted aspects of network structure such as geodesic and path distances, triads or transitivity, connectedness and.or component structure, etc. 
+  Be sure to both provide the relevant statistics calculated in R, as well as your own interpretation of these statistics.
+|
+
+# 1. Identify an existing data set.
+
+-   **Data set:** Florentine Families
+
+-   **Description:** This is an adjacency matrix for a small, directed network of the marriages held by the Florentine family and others in Rome.
+
+-   **Package:** [network](https://cran.r-project.org/web/packages/network/network.pdf)
+
+-   **Access:**
+
+    -   [Import Script]{.ul}:
+
+        `>source("./Import Scripts/Florentine Families.R")`
+
+    -   [Orignial Format from Package]{.ul}:
+
+        `>install.packages("network")`
+
+        `>data("flo", package = "network")`
 

### 2022-02-09 docs/1. SNA-DACSS-Import_Scripts/script-NetBasics_ReadData.Rmd

---
title: "Tutorial: Network Creation"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
library(igraph)
library(statnet)
#create a network.rda object
#can also use igraphdata
#load("network.rda")
tutorial_options(exercise.timelimit = 10)
```
##**Introduction**
This tutorial will introduce the basic commands used to create a network data object in R that can be analyzed using a network analysis package. There are three or four major steps required to create a usable network object.

    1. Read raw data into R
    2. Identify critical features of data:
      - edgelist or adjacency matrix format
      - weighted or binary edges
      - single mode or affiliation (bipartite)
      - symmetric or directed
    3. Create a network data object
    4. If required, assign node and edge attributes

We will be using two network analysis packages throughout the course: **igraph** and **statnet**. Each of the packages uses a slightly different network object format, and the network analysis commands in the package will only work on the correct format of network object. Throughout this tutorial, and future tutorials, generic indicators will be appended to the network object name to distinguish between statnet and igraph format:

- *network.ig* - igraph network object
- *network.stat* - statnet network object

##**Loading Raw Data into R**
Typically, reading raw data into R will require a series of steps: setting the working directory and path to the data file, finding the data file name, identifying the raw data type, and then choosing the correct R command to read in the specific file type.

For this course, the required network datasets are all provided in the workspace and only need to be loaded into memory. If you plan to use original network data for weekly assignments, you will need to read the raw data into R and have it available in the workspace to use for analysis each week. An R tutorial, *Reading Data into R*, is available to help you create a custom syntax file to read your original network data in and save it in your course workspace.

```{r load-example, echo=TRUE}
#networkdata<-load("data")
```

```{r load, exercise=TRUE}
##load the network data named "DATA"

```

```{r load-solution}
##load the network data named "DATA"
networkdata<-load("data") 
```

##**Identify Data: Format & Edge Weights**
In order to analyze your network, you'll need to clean up the data and identify it accurately. If you do not already know the four critical features of network data listed in the introduction, the following commands can allow you to identify these features of your network data.

An edgelist is a list of edges between two nodes, and is provided in 2 (binary) or 3 (weighted) columns. Here is an edgelist of men who have invited women on a date.

| Node From | Node To | Edge weight |
| ---------:|:-------:|:------------|
| Bob       | Susan   |      2      |
| John      | Mary    |      5      |

An adjacency matrix is an $n$x$n$ matrix (or $n1$x$n2$ if affiliation data) with the names of nodes as both column and row labels, and either a 0 (if no tie exists) or the weight of the edge.

|           |  Bob  | Susan | John | Mary |
| ---------:|:-----:|:-----:|:----:|:-----|
| Bob       |   -   |   2   |   0  |  0   |
| Susan     |   0   |   -   |   0  |  0   |
| John      |   0   |   0   |   -  |  5   |
| Mary      |   0   |   0   |   0  |  -   |

###`dim()` command

The command `dim()` can be used to tells if your data is an adjacency matrix or an edgelist. If `networkdata` is in the form of a standard adjacency matrix, the dimension will be square ($n$x$n$). If `networkdata` is in the form of an edgelist, the dimension will be $n$x2 (or $n$x3). 
```{r dim-example, echo=TRUE}
#dim(networkdata)
```

```{r quiz1}
quiz(
  question("How would you describe `networkdata`?",
    answer("unweighted adjacency matrix", correct=TRUE),
    answer("weighted adjacency matrix"),
    answer("unweighted edgelist"),
    answer("weighted edgelist")
  )
)
```

##**Identify Data: Affiliation?**

If you have affiliation data (e.g., people who belong to organizations), there are two types of nodes (e.g., people and organizations). Affiliation data can be provided in both edgelist and adjacency matrix format.

Affiliation networks can usually be identified in the previous step if they are in adjacency matrix format. If `networkdata` is an affiliation network in adjacency matrix format, the dimension will be $n1$x$n2$, where $n2$ will typically be substantially more than 3 but not equal to $n1$. For example, here is an affiliation network in adjacency format: men who own dress shirts of different colors. (In this toy example, $n2$=3, but this is not typical.)

|           |  Blue  | White | Other |
| ---------:|:-----:|:------:|:------|
| Bob       |   0   |   8    |   0  |
| Carl      |   4   |   3    |   6  |
| John      |   5   |   3    |   2  |
| George    |   5   |   6    |   3  |

Affiliation data can also be provided in edgelist format. Here is a partial excerpt of the data above on the color of shirts owned by several men.

| Name      | Shirt Color | Num owned |
| ---------:|:-----------:|:----------|
| Bob       | White       |      8    |
| Carl      | Blue        |      4    |
| Carl      | White       |      3    |

###`colnames()` command

If the `dim()` command indicates that your data have more than 2 columns but are not square, the `colnames()` command can be used to confirm whether or not you are working with affiliation data. This command allows you to visually inspect the actual column names as 3rd, 4th, 5th...kth columns of `networkdata` may instead contain edge attributes such as edge weight, type,  etc, or even additional node information.

```{r colnames-example, echo=TRUE}
##need example of two different nxk datasets
##one is affiliation matrix
##one is edgelist with additional info
##can find in weekly examples or in networks list
#dim(networkdata)
#colnames(networkdata)
```

```{r quiz2}
quiz(
  question("Which of the datasets is an affiliation network?",
    answer("networka.data", correct=TRUE),
    answer("networkb.data"),
    answer("both"),
    answer("neither")
  )
)
```

### Other useful commands
It is also possible to provide affiliation network data in edgelist format, but it is more difficult to easily identify whether or not an edgelist captures a traditional one-mode network or a bipartite or affiliation network. Several basic commands that take advantage of the edge names or identifiers provided in the first two columns ("from" and "to") of an edgelist can be used to explore whether or not a network is an affiliation network.

```{r unique-example, echo=TRUE}
#extract a list of unique nodes 
#unique(networkdata[,1])

#Sort the list of unique node identifiers
#sort(unique(networkdata[,1]))

```

Now, try creating a unique list of node identifiers that appear in the second or *TO* column of `networkdata`, and then sort that list.

```{r unique, exercise=TRUE}
#extract a list of unique nodes

#Sort the list of unique node identifiers

```

```{r unique-solution}
#extract a list of unique nodes 
unique(networkdata[,2])

#Sort the list of unique node identifiers
sort(unique(networkdata[,2]))

```

**ADVANCED** If there are many nodes with difficult identifiers, you can use `%in%` to compare the *FROM* and *TO* columns. `%in%` will provide a TRUE or FALSE respond that tells you whether or not each element of the unique node list from column 1 appears in the unique node list from column 2. If you are working with affiliation data, none of the nodes in column 1 (*FROM*) should appear in column 2 (*TO*). In other words, all of the responses to the `%in%` command should be FALSE. Use `table()` to investigate how many responses are TRUE and how many are FALSE.

```{r uniquein-example, echo=TRUE}
#Is a node in column 1 also in column 2?
#unique(networkdata[,1])%in%unique(networkdata[,2])

#tabulate the TRUE/FALSE responses
#table(unique(networkdata[,1])%in%unique(networkdata[,2]))
```

##**Identify Data: Directed or Undirected Ties**
Low priority placeholder.

This need to be filled in - don't remember how I have done this in past - just a placeholder for now. Maybe an example in game of thrones file or other weekly file? Look for symmetric or directed/undirected language. Essentially, check to see if there are reciprocal ties where i,j == j,i. In edgelist, if there is an i, j edge there is either no j,i or if there, i,j==j,i for all i,j. Maybe examples online?

##**Create Network Object from Edgelist**

If data are in edgelist format and are undirected, use one of the following commands:

```{r graph1, echo=TRUE}
##igraph object
#network.ig<-graph.edgelist(as.matrix(networkdata),directed=F)

##statnet object
#network.stat<-network(networkdata, directed=F, matrix.type="edgelist") 
```

If data are in edgelist format and are directed, use the following command:

```{r graph2, echo=TRUE}
#igraph object
#network.ig<-graph.edgelist(as.matrix(networkdata),directed=T)

#statnet object
#network.stat<-network(networkdata, directed=T, matrix.type="edgelist")
```

###Weighted edges

For all of these commands, statnet will automatically read in additional columns (3...k) as edge attributes with attribute names equal to the column name in the rawdata. Thus, weights included in the raw data are automatically read into the network object.

Weighted edgelists will also read in automatically in igraph if third column in the edgelist dataframe is named *weight*. Otherwise, you will need to perform an additional step to assign the weight values to igraph network edges based on the weighted edgelist. All additional edge attribute data in columns 4...k will need to be read in using the same basic command, see Section on Edge attributes below.

```{r weight-edge, echo=TRUE}
#add edge weight to igraph object
#E(network.ig)$weight <- as.numeric(networkdata[,3])
```

###Affiliation data

When reading affiliation or bipartite network data into a statnet object, it is necessary is to include an additional option in the `network()` command: `bipartite=n1` where $n1$ should be replaced with the number of unique actors in the first mode (e.g., length of unique node identifier list created from first column).

When creating an igraph network object, an additional step is needed to indicate that there are two types of nodes.

```{r bipartite-edge, echo=TRUE}
#add node type to igraph object
#the second column of edges is TRUE type
#V(network.ig)$type <- V(network.ig)$name %in% edges[,2] 
```

##**Create Network Object from Adjacency Matrix**

If data are in adjacency format and are undirected, use the following command:

```{r graph3, echo=TRUE}
#igraph object
#network.ig<-graph.adjacency(networkdata,mode="undirected") 
#statnet object
#network.stat<-network(networkdata, directed=F, matrix.type="adjacency") 
```

If data are in adjacency format and are directed, use the following command:

```{r graph4, echo=TRUE}
#igraph object
#network.ig<-graph.adjacency(networkdata,mode="directed")

 #statnet object
#network.stat<-network(networkdata, directed=F, matrix.type="adjacency")
```

###Weighted Edges
This seems messed up - mentions igraph then example is statnet

Weighted adjacency matrices (entries are not 0/1) will read automatically in igraph. Just like the edgelist data, weights from an adjacency matrix require an additional line of code for statnet graphs, using option `ignore.eval` and `names.eval`

```{r graph5, echo=TRUE}
#statnet object
#network.stat<-network(networkdata, directed=F, matrix.type="adjacency", ignore.eval=FALSE, names.eval="weight") 
```

###Bipartite Adjacency Networks

use option `matrix.type="incidence"` in statnet
For igraph, different constructor is used:
graph_from_incidence_matrix(same as adjacency options)

##**Adding and checking Edge Attributes**
If you have edgelist data, edge attributes will often be stored in same data file. Statnet (and iGraph?) will read in all edge attributes automatically. Inspect edge attributes for both packages as follows:

```{r graph6, echo=TRUE}
#display edge attributes for igraph object
#edge_attr(network.ig)`

#display edge attributes for statnet object
#list.edge.attributes(network.stat)`
```

Create new edge attributes if sorted in same order.

```{r graph7, echo=TRUE}
#display edge attributes for igraph object
#E(network.ig)$COLNAME<-edge.attribute$COLNAME

#display edge attributes for statnet object
#set.edge.attribute(network.stat,COLNAME,edge.attribute$COLNAME)
#network.stat %e% "COLNAME"

```

##**Node or Vertex Attributes**

Sometimes, node attributes will be in a separate datafile. Read in the file, replacing "filename" as needed, and then attach the attribute data to the correct nodes.

```{r graph8, echo=TRUE}
#vertex_attributes<-read.csv("vertex_attribute_file.csv",header=T,stringsAsFactors=F)
```

The vertex names in this file must exactly match those in the network. Sometimes this requires using `as.character(x)` to change from factor to character. Now, you can create vertex attributes in igraph

```{r graph9, echo=TRUE}
##add vertex attributes to igraph object
#V(network.ig)[match(V(network)$name,vertex_attributes$VERTEX_NAME)]$COLNAME<-
#  vertex_attributes$COLNAME

##add vertex attributes to statnet object
#network.stat%v%'COLNAME'<- vertex_attributes$COLNAME

```

##**Optional: Convert Affiliation to Single Mode**
This section needs to be updated and decide whether to convert to single mode before or after it is read into network format. Consider whether it is necessary - probably for graduate students.

Next, convert your data to a single mode network in order to analyze. Choose either dimension n1xn1 or n2xn2 (nodes in rows or nodes in columns) If `networkdata` is a matrix of dimension $n1$x$n2$. If it already is, skip to the next step.
```{r five-plus-two, echo=TRUE}
#network_mat<-as.matrix(networkdata)%*%t(as.matrix(networkdata)) #n1xn1 (rows)
#network_mat<-t(as.matrix(networkdata))%*%as.matrix(networkdata) #n2xn2 (columns)
```

### 2022-02-09 docs/1. SNA-DACSS-Import_Scripts/import script- Edgelist.R
2.9.22 wrote general scripts for edgelists and added files
2.9.22
added more script files and imported Cocktail Data

@@ -1,0 +1,166 @@
+#This script imports 
+
+library(statnet)
+library(igraph)
+
+# The import script has created three objects that represent the network:
+#   - sourceEL.net (a dataframe of an edgelist and edge attributes)
+#   - sourceEL.net_ig (an igraph object)
+#   - sourceEL.stat  (a network object compatable with statnet packages like sna & ergm)
+
+
+#######
+      #Lets read the data into the enviroment.
+
+source.df <-cow_alliance
+
+#####
+    #Format DF to become an edgelist
+    
+    # Assign modefied source.df to Edge List variable name 
+sourceEL.net <- 
+  source.df[c( #select column numbers from source.Data in order to be added
+    3,#col-num
+    5,#col-num
+    2,#col-num
+    6:10#col-num:col-num
+    )
+  ]
+
+#####
+###   NOTE: if necessary format Data Types and tidy up source.df
+
+
+#####
+    #**igraph** version of the network
+          # NOTE: igraph automatically adds edge attributes, but not vertices 
+    
+    #First let's create the object. 
+sourceEL.ig <- 
+  graph_from_data_frame(d = sourceEL.net, 
+                        directed = FALSE
+                        )
+
+#####
+    #**statnet** object from our edgelist
+          # Will not have vertex
+          # Will not have edge attributes
+
+    #First we make the eobject. 
+sourceEL.stat <- 
+  network(as.matrix
+          (sourceEL.net[1:2], 
+            matrix.type = 'edgelist')
+          )
+#####     
+      #**statnet** add edge atributes <aka colnames>
+sourceEL.stat%e%"source_ColName" <- 
+  sourceEL.net$source_ColName
+
+sourceEL.stat%e%"source_ColName" <- 
+  sourceEL.net$source_ColName
+
+sourceEL.stat%e%"source_ColName" <- 
+  sourceEL.net$source_ColName
+
+sourceEL.stat%e%"source_Col-isNum" <- 
+  as.character(sourceEL.net$source_Col-isNum)
+
+sourceEL.stat%e%"source_Col-isDate" <- 
+  as.character(sourceEL.net$source_Col-isDate)
+
+#####
+      # Generating the EdgeList
+      
+    ## round 1
+      # from "_netEdge" select "colNames" to be identified with "vertex.names"
+      # future attr: name (v/c), ccode (v/n), state_name1 (e/c), 
+temp<-
+ sourceEL.net[,
+              c("state_name1",
[…]

### 2022-02-09 docs/1. SNA-DACSS-Import_Scripts/import script- Network Objects.R

@@ -1,0 +1,170 @@
+#This script imports 
+
+#Let's load the libraries you need (install them first if you need to)
+if("statnet" %in% rownames(installed.packages()) == FALSE) {install.packages("statnet")}
+if("igraph"  %in% rownames(installed.packages()) == FALSE) {install.packages("igraph")}
+
+library(statnet)
+library(igraph)
+
+# The import script has created three objects that represent the network:
+#   - sourceEL.net (a dataframe of an edgelist and edge attributes)
+#   - sourceEL.net_ig (an igraph object)
+#   - sourceEL.stat  (a network object compatable with statnet packages like sna & ergm)
+
+
+#######
+      #Lets read the data into the enviroment.
+
+source.df <-cow_alliance
+
+#####
+    #Format DF to become an edgelist
+    
+    # Assign modefied source.df to Edge List variable name 
+sourceEL.net <- 
+  source.df[c( #select column numbers from source.Data in order to be added
+    3,#col-num
+    5,#col-num
+    2,#col-num
+    6:10#col-num:col-num
+    )
+  ]
+
+#####
+###   NOTE: if necessary format Data Types and tidy up source.df
+
+
+#####
+    #**igraph** version of the network
+          # NOTE: igraph automatically adds edge attributes, but not vertices 
+    
+    #First let's create the object. 
+sourceEL.ig <- 
+  graph_from_data_frame(d = sourceEL.net, 
+                        directed = FALSE
+                        )
+
+#####
+    #**statnet** object from our edgelist
+          # Will not have vertex
+          # Will not have edge attributes
+
+    #First we make the eobject. 
+sourceEL.stat <- 
+  network(as.matrix
+          (sourceEL.net[1:2], 
+            matrix.type = 'edgelist')
+          )
+#####     
+      #**statnet** add edge atributes <aka colnames>
+sourceEL.stat%e%"source_ColName" <- 
+  sourceEL.net$source_ColName
+
+sourceEL.stat%e%"source_ColName" <- 
+  sourceEL.net$source_ColName
+
+sourceEL.stat%e%"source_ColName" <- 
+  sourceEL.net$source_ColName
+
+sourceEL.stat%e%"source_Col-isNum" <- 
+  as.character(sourceEL.net$source_Col-isNum)
+
+sourceEL.stat%e%"source_Col-isDate" <- 
+  as.character(sourceEL.net$source_Col-isDate)
+
+#####
+      # Generating the EdgeList
+      
[…]

### 2022-02-09 docs/3. SNA - Assignments/IMPORT_cocktail-datasets.R

@@ -8,22 +8,20 @@ library(readr)
 #     _Recip variables contain complete recipies, with measurements in a 
 #     classic spreadsheet Rows contain = individual cases / Columns contain attribute data
 
-leConRecip <- 
-  read_csv("C:/Users/white/iCloudDrive/Documents/1_DACSS_UMassAmherst/Dacss_RProjects/3. Sp22_rProjects/Dacss_679- Coursework/GIT-ajw_Learning-SocialNetworkAnalysis/docs/3. SNA-Data/cocktail_recipies_(by bartender)-le cocktail connoisseur.csv")
-      # le Cocktail Connoisseur webscrape. Unique because it includes Bartenders and Bars drinks are attributed to
+      # le Cocktail Connoisseur webscrape.
+        ## Unique because it includes Bartenders and Bars drinks are attributed to
+leConRecip <- read_csv("C:/Users/white/iCloudDrive/Documents/1_DACSS_UMassAmherst/Dacss_RProjects/3. Sp22_rProjects/Dacss_679- Coursework/GIT-ajw_Learning-SocialNetworkAnalysis/docs/3. SNA-Data/cocktail_recipies_(by bartender)-le cocktail connoisseur.csv")
+View(leConRecip)
 
-
-deathCoRecip <-
-  read_csv("C:/Users/white/iCloudDrive/Documents/1_DACSS_UMassAmherst/Dacss_RProjects/3. Sp22_rProjects/Dacss_679- Coursework/GIT-ajw_Learning-SocialNetworkAnalysis/docs/3. SNA-Data/cocktail_recipies-DeathAndCo.csv")
       # Death & Company's cocktail recipie book
-      # It's really long because all each column class of ingredients <Spirits, Liqueur, Juice, Garnish, Bitters, et al>
+        # It's really long because all each column class of ingredients <Spirits, Liqueur, Juice, Garnish, Bitters, et al>
+deathCoRecip <- read_csv("C:/Users/white/iCloudDrive/Documents/1_DACSS_UMassAmherst/Dacss_RProjects/3. Sp22_rProjects/Dacss_679- Coursework/GIT-ajw_Learning-SocialNetworkAnalysis/docs/3. SNA-Data/cocktail_recipies-DeathAndCo.csv")
 
-pdtDrinks <-
[…]

### 2022-02-09 docs/3. SNA - Assignments/SNA Assignment Scripts/Week 3- Basic Network Creation.R

@@ -1,0 +1,156 @@
+############## Basic Network Creation and Selection  ##############
+
+###################################################################
+#Step 1: Set Working Directory
+getwd()
+setwd()
+
+###################################################################
+#Step 2: Read raw data into R
+#Different approaches to reading into R, depending on file format
+
+###################################################################
+#Step 3: clean network_data into edgelist or adjacency matrix format
+
+#check for adjacency vs edgelist 
+dim(network_data)
+
+#if your data are in the form of an edgelist, network data is nx2 (or more with edge attributes)
+#first column of network_data should be "From", second column should be "To"
+##inspect column names as 3rd-kth columns of network_data may include network attributes
+colnames(network_data)
+
+###################################################################
+#Step 4: Generating a graph object (igraph) or network object (statnet)
+
+        ##If data are in edgelist format (A) and are undirected (B), use the following command:#
+
+#igraph object 
+network.ig<-
+  graph.edgelist(as.matrix(network_data),
+                 directed=F) 
+#statnet object 
+network.stat<-
+  network(network.data[,1:2], 
+          directed=F, 
+          matrix.type="edgelist") 
+
+        ##If data are in edgelist format (A) and are directed (B), use the following command:#
+
+#igraph object 
+network.ig<-
+  graph.edgelist(as.matrix(network_data),
+                 directed=T) 
+              ##weighted edgelists will read in automatically if third column is "weights" in igraph
+
+#statnet object 
+network.stat<-
+  network(network.data[,1:2], 
+          directed=T, 
+          matrix.type="edgelist") 
+                ##weighted edgelist values can be read in statnet in Step 5
+
+        ##If data are in adjacency format (A) and are undirected (B), use the following command:#
+
+#igraph object 
+network.ig<-
+  graph.adjacency(network_data,
+                  mode="undirected") 
+
+#statnet object 
+network.stat<-
+  network(network.data, 
+          directed=F, 
+          matrix.type="adjacency") 
+
+
+        ##If data are in adjacency format (A) and are directed (B), use the following command:#
+
+#igraph object 
+network.ig<-
+  graph.adjacency(network_data,
+                  mode="directed") 
+              ##weighted adjacency matrix (entries are not 0/1) will read automatically in igraph
+
+#statnet object 
+network.stat<-
+  network(network.data, 
+          directed=F, 
[…]

### 2022-02-09 docs/3. SNA - Assignments/SNA Assignment Scripts/import script- Edgelist.R

@@ -1,0 +1,170 @@
+#This script imports 
+
+#Let's load the libraries you need (install them first if you need to)
+if("statnet" %in% rownames(installed.packages()) == FALSE) {install.packages("statnet")}
+if("igraph"  %in% rownames(installed.packages()) == FALSE) {install.packages("igraph")}
+
+library(statnet)
+library(igraph)
+
+# The import script has created three objects that represent the network:
+#   - sourceEL.net (a dataframe of an edgelist and edge attributes)
+#   - sourceEL.net_ig (an igraph object)
+#   - sourceEL.stat  (a network object compatable with statnet packages like sna & ergm)
+
+
+#######
+      #Lets read the data into the enviroment.
+
+source.df <-cow_alliance
+
+#####
+    #Format DF to become an edgelist
+    
+    # Assign modefied source.df to Edge List variable name 
+sourceEL.net <- 
+  source.df[c( #select column numbers from source.Data in order to be added
+    3,#col-num
+    5,#col-num
+    2,#col-num
+    6:10#col-num:col-num
+    )
+  ]
+
+#####
+###   NOTE: if necessary format Data Types and tidy up source.df
+
+
+#####
+    #**igraph** version of the network
+          # NOTE: igraph automatically adds edge attributes, but not vertices 
+    
+    #First let's create the object. 
+sourceEL.ig <- 
+  graph_from_data_frame(d = sourceEL.net, 
+                        directed = FALSE
+                        )
+
+#####
+    #**statnet** object from our edgelist
+          # Will not have vertex
+          # Will not have edge attributes
+
+    #First we make the eobject. 
+sourceEL.stat <- 
+  network(as.matrix
+          (sourceEL.net[1:2], 
+            matrix.type = 'edgelist')
+          )
+#####     
+      #**statnet** add edge atributes <aka colnames>
+sourceEL.stat%e%"source_ColName" <- 
+  sourceEL.net$source_ColName
+
+sourceEL.stat%e%"source_ColName" <- 
+  sourceEL.net$source_ColName
+
+sourceEL.stat%e%"source_ColName" <- 
+  sourceEL.net$source_ColName
+
+sourceEL.stat%e%"source_Col-isNum" <- 
+  as.character(sourceEL.net$source_Col-isNum)
+
+sourceEL.stat%e%"source_Col-isDate" <- 
+  as.character(sourceEL.net$source_Col-isDate)
+
+#####
+      # Generating the EdgeList
+      
[…]

### 2022-02-09 docs/4. SNA Libraries.r

@@ -1,5 +1,35 @@
-# SNA - Social Network Analysis
+# GitHub
+library(askpass)
+library(githubinstall)
+library(gitcreds)
 
+# R Tools
+library(devtools)
+library(installr)
+library(magrittr)
+library(sourcetools)
+
+# Document Creation
+library(knitr)
+library(markdown)
+library(rmarkdown)
+library(yaml)
+library(distill)
+library(blogdown)
+
+
+# Basic Analysis
+library(ggplot2)
+library(tidyverse)
+library(clipr)
+library(dbplyr)
+library(data.table)
+library(stringr)
+library(stringi)
+library(tibble)
+library(tidyr)
+
+# SNA - Social Network Analysis
 library(tergm)
 library(ergm)
 
@@ -25,33 +55,3 @@ library(quanteda.textplots)
 library(quanteda.textstats)
 library(stopwords)
 
-# Basic Analysis
-library(ggplot2)
-library(tidyverse)
-library(clipr)
-library(dbplyr)
-library(data.table)
-library(stringr)
-library(stringi)
-library(tibble)
-library(tidyr)
-
-# Document Creation
-library(knitr)
-library(markdown)
-library(rmarkdown)
-library(yaml)
-library(distill)
-library(blogdown)
-
-# GitHub
-library(askpass)
-library(githubinstall)
-library(gitcreds)
-
-# R Tools
-library(devtools)
-library(installr)
-library(magrittr)
-library(roxygen2)
-library(sourcetools)

### 2022-02-10 docs/3. SNA - Assignments/sna_Week3/DRAFT-week3-Assignment.Rmd
2.9.22 1) Spin up the FML Drive!!!
Getting into the hard part of creating network data

FORMATING SOURCE DATA

2) Only 4 hours of work and 2 committs

--- 2022-02-08 docs/3. SNA - Assignments/DRAFT-week3-Assignment.Rmd
@@
 ---
-title: "Social Network Analysis: Week 3: Degree and Centrality"
+title: "DRAFT: Week 3: Degree and Centrality"
 description: " "
@@
 
-      *Week 3 Assignment: Degree and Centrality*
-
-Using the tutorial as a guide, 
-      *  you may use your own data; 
-      *  the data provided in the week 3. Syntax dataset is Correlates of War trade network - you can read more about it online; or
-      *  choose another dataset.
-
-## Working from the example R syntax:
-1.   calculate network density; 
-2.   degree centrality, and 
-3.   centralization measures for your network data.
-
-## Write up your results briefly:
-*   focus on interpretation of the results. 
-*   Don’t list statistics or provide code, 
-*  **the goal is to choose a few interesting results and provide an interpretation.**
-
 ## Briefly describe the dataset:
@@
             *   stack multiple networks.
-Not every feature of the network needs to be described, but **description should orient reader to the network data and provide any necessary context for the results provided.**
-
-## Provide at least two or three noteworthy results, including:
-1.   the relevant statistics and interpretation. 
-        For example, explaining which node(s) are most central and which are least central. 
-2.   Discuss (with any related evidence) whether or not the node(s) behavior is in line with or violates expectations based on the degree centrality measure. 
-3.   What do you make of network density and centralization measures?  
-4.   What about differences in the binary 100 million threshold network vs valued trade flows network. 
- 5.  Check tutorial for other ideas of results to discuss.
-
-##
-1.  [**Identify an existing data set.**]{.ul}
-
-| This can be one provided in the course directory, in an R package or library, located online, or some other source.
-
-2.  [**Briefly describe the network dataset.**]{.ul}
-
-| Identify and describe content of nodes and links, and identify format of data set (i.e., matrix or edgelist, directed or not, weighted or not), and whether attribute data are present. 
-  Be sure to provide information about network size (e.g., information obtained from network description using week 1 network basics tutorial commands.)
 
 # Week 2: Scripts
+1.  [**Identify an existing data set.**]{.ul}
+```{r Set Working Directory, include=FALSE}
+getwd()
 
-```{r Import Data Set, echo=TRUE}
-
-  # install.packages("network")
-
-    data("flo", package = "network")
+setwd("C:/Users/white/iCloudDrive/Documents/1_DACSS_UMassAmherst/Dacss_RProjects/3. Sp22_rProjects/Dacss_679- Coursework/GIT-ajw_Learning-SocialNetworkAnalysis/docs/3. SNA - Assignments")
 
@@
 
-# 2. Briefly describe the network dataset.
+```{r Read raw data into R}
+
+library(readr)
+
+index_by_name_Smuggler_Cove_cocktail_recipies <- read_csv("C:/Users/white/iCloudDrive/Documents/1_DACSS_UMassAmherst/Dacss_RProjects/3.
+Sp22_rProjects/Dacss_679- Coursework/GIT-ajw_Learning-SocialNetworkAnalysis/docs/3.
+SNA-Data/index-by_name-Smuggler_Cove-cocktail_recipies.csv",
+    col_names = FALSE, col_types = cols(X1 = col_skip(), 
+        X4 = col_skip()), na = "empty")
+
+View(index_by_name_Smuggler_Cove_cocktail_recipies)
+
+summary(index_by_name_Smuggler_Cove_cocktail_recipies)
+
+ # Smuggler's Cove
+
+```
+
+2. Briefly describe the network dataset.
+```{r Identify critical features of data:, echo=FALSE}
+
+dim(smugDrink_Indx.df)
+colnames(smugDrink_Indx.df)
+
+```
 
@@
 ```{r Colnames}
- colnames(flo)
+
 ```
@@
 
-    -   Flo Format: Size: 16 x 16 square dimmentions indicate a adjacency matrix format
-
-    Network attributes: vertices = 16 directed = TRUE hyper = FALSE loops = FALSE multiple = FALSE bipartite = FALSE total edges= 40 missing edges= 0 non-missing edges= 40
-
 Vertex attribute names: vertex.names
-
-No edge attributes
 
@@
 
-  dim(flo)
+  dim(smugDrink_Indx.df)
 
@@
 
-  network(flo)
+  network(smugDrink_Indx.df)
 
@@
 
-  summary(flo,
+  summary(smugDrink_Indx.df,
           print.adj = TRUE
@@
 *Florentine Families Directed Adjacency Matrix Network Objects:*
-    **iGraph** flo.ig 
-    **Statnet** flo.stat
+    **iGraph** smugDrink_Indx.df.ig 
+    **Statnet** smugDrink_Indx.df.stat
 
@@
 
-    flo.stat<-
+    smugDrink_Indx.df.stat<-
         network(
-        flo,
+        smugDrink_Indx.df,
         directed=F,
@@
 ##
-
-# Week3:    Briefly describe the dataset:
-1.   identify initial network format; 
-2.   describe and identify the nodes 
-     including: 
-        *  how many nodes are in the dataset; 
-3.   what constitutes a tie or edge
-     including:
-        *  how many ties, 
-        *   whether ties are directed/undirected,
-        *   whether ties are weighted/binary, 
-        *   and how to interpret the value of the tie if any.
-        *   Whether or not there are edge attributes 
-            that might be used to:
-            *   subset data, or 
-            *   stack multiple networks.
-
-#WEEK 3:     Working from the example R syntax:
-1.   calculate network density; 
-2.   degree centrality, and 
-3.   centralization measures for your network data.
-
-#WEEK 3:  Provide at least two or three noteworthy results
-1.   the relevant statistics and interpretation. 
-        For example, explaining which node(s) are most central and which are least central. 
-2.   Discuss (with any related evidence) whether or not the node(s) behavior is in line with or violates expectations based on the degree centrality measure. 
-3.   What do you make of network density and centralization measures?  
-4.   What about differences in the binary 100 million threshold network vs valued trade flows network. 
- 5.  Check tutorial for other ideas of results to discuss.

### 2022-02-10 docs/3. SNA - Assignments/sna_Week3/Week3_Notebook.Rmd
2.9.22 1) Spin up the FML Drive!!!
Getting into the hard part of creating network data

FORMATING SOURCE DATA

2) Only 4 hours of work and 2 committs

--- 2022-02-10 docs/3. SNA - Assignments/sna_Week3/DRAFT-week3-Assignment.Rmd
@@
 ---
-title: "DRAFT: Week 3: Degree and Centrality"
-description: " "
-author:
-  - name: "Audra Jamai White" 
-    url: 
-    affiliation: "Umass Amherst - DACSS 679: Social Network Analysis"
-    affiliation_url: 
-date: "`r Sys.Date()`"
-output: distill::distill_article
+title: "R Notebook"
+output: html_notebook
 ---
@@
 ```{r setup, Libraries, include=FALSE}
+
 knitr::opts_chunk$set(echo = FALSE)
@@
 ## Briefly describe the dataset:
+
 1.  identify initial network format;
-2.   describe and identify the nodes 
-     including: 
-        *  how many nodes are in the dataset; 
-3.   what constitutes a tie or edge
-     including:
-        *  how many ties, 
-        *   whether ties are directed/undirected,
-        *   whether ties are weighted/binary, 
-        *   and how to interpret the value of the tie if any.
-        *   Whether or not there are edge attributes 
+
+2.  describe and identify the nodes including:
+
+    -   how many nodes are in the dataset;
+
+3.  what constitutes a tie or edge including:
+
+    -   how many ties,
+
+    -   whether ties are directed/undirected,
+
+    -   whether ties are weighted/binary,
+
+    -   and how to interpret the value of the tie
+        if any.
+
+    -   Whether or not there are edge attributes
         that might be used to:
-            *   subset data, or 
-            *   stack multiple networks.
+
+        -   subset data, or
+        -   stack multiple networks.
 
 # Week 2: Scripts
+
 1.  [**Identify an existing data set.**]{.ul}
+
 ```{r Set Working Directory, include=FALSE}
@@
 
-index_by_name_Smuggler_Cove_cocktail_recipies <- read_csv("C:/Users/white/iCloudDrive/Documents/1_DACSS_UMassAmherst/Dacss_RProjects/3.
+indx_SmugglerCove_recip <- read_csv("C:/Users/white/iCloudDrive/Documents/1_DACSS_UMassAmherst/Dacss_RProjects/3.
 Sp22_rProjects/Dacss_679- Coursework/GIT-ajw_Learning-SocialNetworkAnalysis/docs/3.
@@
 
-View(index_by_name_Smuggler_Cove_cocktail_recipies)
-
-summary(index_by_name_Smuggler_Cove_cocktail_recipies)
+View(indx_SmugglerCove_recip)
+summary(indx_SmugglerCove_recip)
 
  # Smuggler's Cove
+
+smugDnkIdx_df <- indx_SmugglerCove_recip
 
@@
 2.  Briefly describe the network dataset.
-```{r Identify critical features of data:, echo=FALSE}
 
-dim(smugDrink_Indx.df)
-colnames(smugDrink_Indx.df)
+```{r Getting Information on a Dataset:, echo=FALSE}
+
+# list the structure of smugDnkIdx_df
+str(smugDnkIdx_df)
+
+# class of an object (numeric, matrix, data frame, etc)
+class(smugDnkIdx_df)
+
+# list the variables in smugDnkIdx_df
+names(smugDnkIdx_df)
+
+# dimensions of an object
+dim(smugDnkIdx_df)
+```
+#### list the structure of smugDnkIdx_df
+$ X2: chr [1:785]
+$ X3: chr [1:785]
+$ X5: chr [1:785]
+$ X6: num [1:785]
+
+cols(
+  ..   X1 = col_skip(),
+  ..   X2 = col_character(),
+  ..   X3 = col_character(),
+  ..   X4 = col_skip(),
+  ..   X5 = col_character(),
+  ..   X6 = col_double()
+  .. )
+
+#### class of an object
+class(smugDnkIdx_df)
+  [1] "spec_tbl_df" 
+      "tbl_df"      
+      "tbl"         
+      "data.frame"
+
+#### list the variables in smugDnkIdx_df
+ names(smugDnkIdx_df)
+[1] "X2" 
+    "X3" 
+    "X5" 
+    "X6"
+#### dimensions of an object
+ dim(smugDnkIdx_df)
+[1] Rows: 785   
+    Cols:   4
+
+# DATA Cleaning
+-   rename column names to something memorable
+```{r Rename columns}
+
+   # Rename column names
+
+names(smugDnkIdx_df)[1] <- "Drink_Name"
+names(smugDnkIdx_df)[2] <- "Ingredient"
+names(smugDnkIdx_df)[3] <- "Ingredient_ClassType"
+names(smugDnkIdx_df)[4] <- "Drink_Code"
+
+```
+-   Drop rows without values 
+```{r Remove missing values}
+
+#One-column based criteria: Extract rows where
+
+testData <- smugDnkIdx_df
+
+testData  %>% filter(is.na(Drink_Code))
 
@@
 
--   *Be sure to provide information about network size (e.g., information obtained from network description using week 1 network basics tutorial commands.)*
+-   Col X5
+    Drop All together
+    split varriables into new columns
 
-1.  *Identify and describe content of nodes and links,*
+#
+## 1.  *Identify and describe content of nodes and
+    links,*
 
--   each of the 16 Florentine Family Names represent a Node in the network.
+-   each of the 16 Florentine Family Names
+    represent a Node in the network.
 
@@
 
-2.  *Identify format of data set (i.e., matrix or edgelist, directed or not, weighted or not), and*
+##2.  *Identify format of data set (i.e., matrix or
+    edgelist, directed or not, weighted or not),
+    and*
 
@@
 
-  dim(smugDrink_Indx.df)
+  dim(smugDnkIdx_df)
 
@@
 
-  network(smugDrink_Indx.df)
+  network(smugDnkIdx_df)
 
@@
 
-  summary(smugDrink_Indx.df,
+  summary(smugDnkIdx_df,
           print.adj = TRUE
@@
 
-*Florentine Families Directed Adjacency Matrix Network Objects:*
-    **iGraph** smugDrink_Indx.df.ig 
-    **Statnet** smugDrink_Indx.df.stat
+*Florentine Families Directed Adjacency Matrix
+Network Objects:* **iGraph** smugDnkIdx_df.ig
+**Statnet** smugDnkIdx_df.stat
 
-iGraph and Statnet both use {r graph4} for Directed Adjacency Matrix Objects
+iGraph and Statnet both use {r graph4} for
+Directed Adjacency Matrix Objects
 
@@
 
-    smugDrink_Indx.df.stat<-
+    smugDnkIdx_df.stat<-
         network(
-        smugDrink_Indx.df,
+        smugDnkIdx_df,
         directed=F,
@@
 ```
+
 **Vertex and Edge Attributes**
@@
 
-We can also find all of the shortest paths between two famalies in this network.
-These list the starting node and the ending node with all nodes inbetween for each path. 
-The option weights=NA means that any available edge weights are ignored.
+We can also find all of the shortest paths between
+two famalies in this network. These list the
+starting node and the ending node with all nodes
+inbetween for each path. The option weights=NA
+means that any available edge weights are ignored.
 
@@
 
-The concept of shortest path to describe the overall network structure can be more useful
+The concept of shortest path to describe the
+overall network structure can be more useful
 
@@
 
-Classifies all dyads in the network as: - Reciprocal (mutual), or mut - Asymmetric (non-mutual), or asym, and - Absent, or null
+Classifies all dyads in the network as: -
+Reciprocal (mutual), or mut - Asymmetric
+(non-mutual), or asym, and - Absent, or null
 
@@
 
-Classifies all triads in the network. The triad census provides a fundamental descriptive insight into the types of triads found in a particular dataset.
+Classifies all triads in the network. The triad
+census provides a fundamental descriptive insight
+into the types of triads found in a particular
+dataset.
 
@@
 ## Local Transivity or Clustering
-`Local transitivity` (local clustering coefficient), is a technical description of the density of an ego network.
+
+`Local transitivity` (local clustering
+coefficient), is a technical description of the
+density of an ego network.
 
@@
 
-7.  *connectedness and.or component structure, etc.*
+7.  *connectedness and.or component structure,
+    etc.*
 
-> Distill is a publication format for scientific and technical writing, native to the web.
+> Distill is a publication format for scientific
+> and technical writing, native to the web.
 >
-> Learn more about using Distill for R Markdown at <https://rstudio.github.io/distill>.
-##
+> Learn more about using Distill for R Markdown at
+> <https://rstudio.github.io/distill>. ##

### 2022-02-10 docs/3. SNA - Assignments/SNA Assignment Scripts/Week 3- Basic Network Creation.R

@@ -9,16 +9,31 @@ setwd()
 #Step 2: Read raw data into R
 #Different approaches to reading into R, depending on file format
 
+
+## possible adjacency matrix
+
+## possible edgelists
+
+
 ###################################################################
 #Step 3: clean network_data into edgelist or adjacency matrix format
 
 #check for adjacency vs edgelist 
-dim(network_data)
 
-#if your data are in the form of an edgelist, network data is nx2 (or more with edge attributes)
-#first column of network_data should be "From", second column should be "To"
-##inspect column names as 3rd-kth columns of network_data may include network attributes
-colnames(network_data)
+dim(deathCo_Recip.df)
+dim(leConRecip.df)
+dim(smugDrink_Indx.df)
+
+
+
+          #if your data are in the form of an edgelist, network data is nx2 (or more with edge attributes)
+          #first column of network_data should be "From", second column should be "To"
+
+  ##inspect column names as 3rd-kth columns of network_data may include network attributes
+colnames( )
+# lol need to find readable human format
+
+
 
 ###################################################################
 #Step 4: Generating a graph object (igraph) or network object (statnet)
@@ -27,7 +42,7 @@ colnames(network_data)
 
 #igraph object 
 network.ig<-
-  graph.edgelist(as.matrix(network_data),
+  graph.edgelist(as.matrix(deathCo_recip.df),
                  directed=F) 
 #statnet object 
 network.stat<-
@@ -39,7 +54,7 @@ network.stat<-
 
 #igraph object 
 network.ig<-
-  graph.edgelist(as.matrix(network_data),
+  graph.edgelist(as.matrix(deathCo_recip.df),
                  directed=T) 
               ##weighted edgelists will read in automatically if third column is "weights" in igraph
 

### 2022-02-10 docs/3. SNA - Assignments/sna_Week3/Week3_Notebook.Rmd
2.9.22
Spin up the FML Drive!!!

Getting into the hard part of creating network data

FORMATING SOURCE DATA

@@
 
-# DATA Cleaning
--   rename column names to something memorable
-```{r Rename columns}
+```{r}
 
-   # Rename column names
+colnames(smugDnkIdx_df)
 
-names(smugDnkIdx_df)[1] <- "Drink_Name"
-names(smugDnkIdx_df)[2] <- "Ingredient"
-names(smugDnkIdx_df)[3] <- "Ingredient_ClassType"
-names(smugDnkIdx_df)[4] <- "Drink_Code"
+head(smugDnkIdx_df, n=10)
 
-```
--   Drop rows without values 
-```{r Remove missing values}
-
-#One-column based criteria: Extract rows where
-
-testData <- smugDnkIdx_df
-
-testData  %>% filter(is.na(Drink_Code))
+head(smugDnkIdx_df, n=10)
 
@@
 
--   Col X5
-    Drop All together
-    split varriables into new columns
+> dim() smugDnkIdx_df
+>
+> rows: 785
+>
+> columns: 4
+>
+> column names: "X2" "X3" "X5" "X6"
 
-#
-## 1.  *Identify and describe content of nodes and
+-   *need to rename column names to something
+    memorable*
+
+    ```{r}
+
+    # example of melt function
+    library(reshape)
+
+    mdata <- 
+      melt(smugDnkIdx_df,
+           id=c(
+             "id",
+             "time")
+           )
+    ```
+
+1.  *Identify and describe content of nodes and
     links,*
@@
 
-##2.  *Identify format of data set (i.e., matrix or
+2.  *Identify format of data set (i.e., matrix or
     edgelist, directed or not, weighted or not),

### 2022-02-10 docs/3. SNA - Assignments/IMPORT_cocktail-datasets.R

@@ -1,35 +1,0 @@
-# 1. Read raw data into R
-# Load csv files directly into R Files and use auto-import function
-
-#Load your dataset into the environment#
-
-library(readr)
-
-#     _Recip variables contain complete recipies, with measurements in a 
-#     classic spreadsheet Rows contain = individual cases / Columns contain attribute data
-
-      # le Cocktail Connoisseur webscrape.
-        ## Unique because it includes Bartenders and Bars drinks are attributed to
-leConRecip <- read_csv("C:/Users/white/iCloudDrive/Documents/1_DACSS_UMassAmherst/Dacss_RProjects/3. Sp22_rProjects/Dacss_679- Coursework/GIT-ajw_Learning-SocialNetworkAnalysis/docs/3. SNA-Data/cocktail_recipies_(by bartender)-le cocktail connoisseur.csv")
-View(leConRecip)
-
-      # Death & Company's cocktail recipie book
-        # It's really long because all each column class of ingredients <Spirits, Liqueur, Juice, Garnish, Bitters, et al>
-deathCoRecip <- read_csv("C:/Users/white/iCloudDrive/Documents/1_DACSS_UMassAmherst/Dacss_RProjects/3. Sp22_rProjects/Dacss_679- Coursework/GIT-ajw_Learning-SocialNetworkAnalysis/docs/3. SNA-Data/cocktail_recipies-DeathAndCo.csv")
-
-      # Please Don't Tell
-pdtRecipies <- read_csv("C:/Users/white/iCloudDrive/Documents/1_DACSS_UMassAmherst/Dacss_RProjects/3. Sp22_rProjects/Dacss_679- Coursework/GIT-ajw_Learning-SocialNetworkAnalysis/docs/3. SNA-Data/index-by_name-Please_Dont_Tell-cocktail_recipies.csv")
-
-      # Smuggler's Cove
-smugDrinkIndex <- read_csv("C:/Users/white/iCloudDrive/Documents/1_DACSS_UMassAmherst/Dacss_RProjects/3. Sp22_rProjects/Dacss_679- Coursework/GIT-ajw_Learning-SocialNetworkAnalysis/docs/3. SNA-Data/index-by_name-Smuggler_Cove-cocktail_recipies.csv")
-
-      
-# 2. Identify critical features of data:
-      #- edgelist or adjacency matrix format
-      #- weighted or binary edges
-      #- single mode or affiliation (bipartite)
-      #- symmetric or directed
-
[…]

### 2022-02-10 docs/3. SNA - Assignments/SNA Assignment Scripts/WEEK3-fimport script- Edgelist.R

@@ -1,12 +1,3 @@
-#This script imports 
-
-#Let's load the libraries you need (install them first if you need to)
-if("statnet" %in% rownames(installed.packages()) == FALSE) {install.packages("statnet")}
-if("igraph"  %in% rownames(installed.packages()) == FALSE) {install.packages("igraph")}
-
-library(statnet)
-library(igraph)
-
 # The import script has created three objects that represent the network:
 #   - sourceEL.net (a dataframe of an edgelist and edge attributes)
 #   - sourceEL.net_ig (an igraph object)
@@ -14,9 +5,11 @@ library(igraph)
 
 
 #######
-      #Lets read the data into the enviroment.
+#Lets read the data into the environment.
 
-source.df <-cow_alliance
+## possible edgelists
+
+######
 
 #####
     #Format DF to become an edgelist

### 2022-02-10 docs/3. SNA - Assignments/sna_Week3/IMPORT_cocktail-datasets.R

@@ -1,0 +1,64 @@
+
+
+
+# 1. Read raw data into R
+# Load csv files directly into R Files and use auto-import function
+
+#Load your dataset into the environment#
+## 1.  [**Identify an existing data set.**]{.ul}
+
+
+```{r Set Working Directory, include=FALSE}
+getwd()
+
+setwd("C:/Users/white/iCloudDrive/Documents/1_DACSS_UMassAmherst/Dacss_RProjects/3. Sp22_rProjects/Dacss_679- Coursework/GIT-ajw_Learning-SocialNetworkAnalysis/docs/3. SNA - Assignments")
+
+```
+#Lets read the data into the environment.
+
+```{r Read raw data into R}
+
+library(readr)
+
+indx_SmugglerCove_recip <- read_csv("C:/Users/white/iCloudDrive/Documents/1_DACSS_UMassAmherst/Dacss_RProjects/3. Sp22_rProjects/Dacss_679- Coursework/GIT-ajw_Learning-SocialNetworkAnalysis/docs/3. SNA-Data/index-by_name-Smuggler_Cove-cocktail_recipies.csv", 
+                                    col_names = FALSE, col_types = cols(X1 = col_skip(), 
+                                                                        X4 = col_skip()), na = "empty")
+
+View(indx_SmugglerCove_recip)
+summary(indx_SmugglerCove_recip)
+
+# Smuggler's Cove
+
+smugDnkIdx_df <- indx_SmugglerCove_recip
+
+problems(smugDnkIdx_df)
+```
+
+#     _Recip variables contain complete recipies, with measurements in a 
+#     classic spreadsheet Rows contain = individual cases / Columns contain attribute data
+
+      # le Cocktail Connoisseur webscrape.
+        ## Unique because it includes Bartenders and Bars drinks are attributed to
+
+      # Death & Company's cocktail recipie book
+        # It's really long because all each column class of ingredients <Spirits, Liqueur, Juice, Garnish, Bitters, et al>
+
+      # Please Don't Tell
+
+      # Smuggler's Cove
+
+
+## possible adjacency matrix
+
+
+## possible edgelists
+
+# 2. Identify critical features of data:
+      #- edgelist or adjacency matrix format
+      #- weighted or binary edges
+      #- single mode or affiliation (bipartite)
+      #- symmetric or directed
+
+# 3. Create a network data object
+
+# 4. If required, assign node and edge attributes

### 2022-02-11 docs/3. SNA - Assignments/sna_Week3/Week3_Notebook.Rmd

@@
 
-```{r}
+#
+## Basic R: Import & Clean Data
+```{r Import }
+library(tidyr)
+library(readr)
 
-colnames(smugDnkIdx_df)
+smugCovIdx <- read_csv("C:/Users/white/iCloudDrive/Documents/1_DACSS_UMassAmherst/Dacss_RProjects/3.
+Sp22_rProjects/Dacss_679- Coursework/GIT-ajw_Learning-SocialNetworkAnalysis/docs/3.
+SNA-Data/index-by_name-Smuggler_Cove-cocktail_recipies.csv",
+                       col_names = FALSE, 
+                       col_types = cols(X1 = col_skip(), 
+                                                        X4 = col_skip()))
+```
 
-head(smugDnkIdx_df, n=10)
+```{r & Clean Data}
+      # Drop NA rows
+smugCovIdx <- na.omit(smugCovIdx)
 
-head(smugDnkIdx_df, n=10)
+# DATA Cleaning
+
+#     Extract variables
+#####
+library(stringr)
+          # extract first word of the column, adds values in new Column at the end of DF
+
+                    #1st pastIt
+passIt <- smugCovIdx
+
+                    #2nd passIt
+passIt$substring_first <-     
+  str_extract(
+    passIt$X5,
+    "(\\w+)")
+
+#####
+
+#####
+#     Drop it like...
+#####
+      # DROP COLUMNS FROM DATA FRAME
+
+                      #3rd PassIt
+passIt = subset(passIt, 
+                       select = -c(3)
+                       )
+#####
+
+#####
+#     Give Variables a human name
+#####
+
+# rename column names with human language
+
+                      # Return it
+smugCovIdx <- passIt
+
+names(smugCovIdx )[1] <- "dnkName"
+names(smugCovIdx )[2] <- "dnkIng"
+names(smugCovIdx )[3] <- "dnkCode"   
+names(smugCovIdx )[4] <- "classIng"
 
@@
 
-> dim() smugDnkIdx_df
->
-> rows: 785
->
-> columns: 4
->
-> column names: "X2" "X3" "X5" "X6"
+## Basic R: Brief Dataset Description
+```{r Identify critical features of data:, echo=FALSE}
 
--   *need to rename column names to something
-    memorable*
+dim(smugCovIdx)
 
-    ```{r}
+colnames(smugCovIdx)
 
-    # example of melt function
-    library(reshape)
-
-    mdata <- 
-      melt(smugDnkIdx_df,
-           id=c(
-             "id",
-             "time")
-           )
-    ```
-
-1.  *Identify and describe content of nodes and
-    links,*
-
--   each of the 16 Florentine Family Names
-    represent a Node in the network.
-
-```{r Colnames}
+summary(smugCovIdx)
 
@@
 
-2.  *Identify format of data set (i.e., matrix or
+# Network: Creating network Data
+
+# Network: Describe Network Data
+## 1.  *Identify and describe content of nodes and
+    links,*
+
+##2.  *Identify format of data set (i.e., matrix or
     edgelist, directed or not, weighted or not),
@@
 Vertex attribute names: vertex.names
-
-```{r Dimmentions, echo=TRUE}
-
-  dim(smugDnkIdx_df)
-
-```
 

### 2022-02-11 docs/3. SNA - Assignments/sna_Week3/Week3_Notebook.Rmd
2.11.22
UP and at it

@@
 
-## Briefly describe the dataset:
-
-1.  identify initial network format;
-
-2.  describe and identify the nodes including:
-
-    -   how many nodes are in the dataset;
-
-3.  what constitutes a tie or edge including:
-
-    -   how many ties,
-
-    -   whether ties are directed/undirected,
-
-    -   whether ties are weighted/binary,
-
-    -   and how to interpret the value of the tie
-        if any.
-
-    -   Whether or not there are edge attributes
-        that might be used to:
-
-        -   subset data, or
-        -   stack multiple networks.
-
-# Week 2: Scripts
-
-1.  [**Identify an existing data set.**]{.ul}
-
 ```{r Set Working Directory, include=FALSE}
@@
 ```
+
+## Basic R: Import & Clean Data
 
@@
 SNA-Data/index-by_name-Smuggler_Cove-cocktail_recipies.csv",
-    col_names = FALSE, col_types = cols(X1 = col_skip(), 
-        X4 = col_skip()), na = "empty")
+    col_names = FALSE, 
+    col_types = cols(X1 = col_skip(),
+                     X4 = col_skip()), 
+                    na = "empty")
 
@@
 
-smugDnkIdx_df <- indx_SmugglerCove_recip
+smugCovIdx <- indx_SmugglerCove_recip
 
@@
 
-2.  Briefly describe the network dataset.
-
 ```{r Getting Information on a Dataset:, echo=FALSE}
 
-# list the structure of smugDnkIdx_df
-str(smugDnkIdx_df)
+# list the structure of smugCovIdx
+str(smugCovIdx)
 
 # class of an object (numeric, matrix, data frame, etc)
-class(smugDnkIdx_df)
+class(smugCovIdx)
 
-# list the variables in smugDnkIdx_df
-names(smugDnkIdx_df)
+# list the variables in smugCovIdx
+names(smugCovIdx)
 
 # dimensions of an object
-dim(smugDnkIdx_df)
-```
-#### list the structure of smugDnkIdx_df
-$ X2: chr [1:785]
-$ X3: chr [1:785]
-$ X5: chr [1:785]
-$ X6: num [1:785]
-
-cols(
-  ..   X1 = col_skip(),
-  ..   X2 = col_character(),
-  ..   X3 = col_character(),
-  ..   X4 = col_skip(),
-  ..   X5 = col_character(),
-  ..   X6 = col_double()
-  .. )
-
-#### class of an object
-class(smugDnkIdx_df)
-  [1] "spec_tbl_df" 
-      "tbl_df"      
-      "tbl"         
-      "data.frame"
-
-#### list the variables in smugDnkIdx_df
- names(smugDnkIdx_df)
-[1] "X2" 
-    "X3" 
-    "X5" 
-    "X6"
-#### dimensions of an object
- dim(smugDnkIdx_df)
-[1] Rows: 785   
-    Cols:   4
-
-#
-## Basic R: Import & Clean Data
-```{r Import }
-library(tidyr)
-library(readr)
-
-smugCovIdx <- read_csv("C:/Users/white/iCloudDrive/Documents/1_DACSS_UMassAmherst/Dacss_RProjects/3.
-Sp22_rProjects/Dacss_679- Coursework/GIT-ajw_Learning-SocialNetworkAnalysis/docs/3.
-SNA-Data/index-by_name-Smuggler_Cove-cocktail_recipies.csv",
-                       col_names = FALSE, 
-                       col_types = cols(X1 = col_skip(), 
-                                                        X4 = col_skip()))
+dim(smugCovIdx)
 ```
@@
 
+# Network: Creating network Data
 ## Basic R: Brief Dataset Description
-```{r Identify critical features of data:, echo=FALSE}
+```{r Network: Identify critical features, echo=FALSE}
+#### dimensions of an object
+dim()
 
-dim(smugCovIdx)
+#### class of an object
+class()
 
-colnames(smugCovIdx)
+# list the structure of smugCovIdx
+str()
 
-summary(smugCovIdx)
+# class of an object (numeric, matrix, data frame, etc)
+class()
+
+# list the variables in smugCovIdx
+names()
+
+colnames( )
+
+summary( )
 
@@
 
-# Network: Creating network Data
-
-# Network: Describe Network Data
-## 1.  *Identify and describe content of nodes and
-    links,*
-
-##2.  *Identify format of data set (i.e., matrix or
-    edgelist, directed or not, weighted or not),
-    and*
-
-Vertex attribute names: vertex.names
-
-```{r Network Attributes, echo=TRUE}
-
-  network(smugDnkIdx_df)
-
-```
-
-3.  *Identify whether attribute data are present.*
-
-```{r Summary,echo=TRUE}
-
-  summary(smugDnkIdx_df,
-          print.adj = TRUE
-          )
-```
-
-## Create & Describe: Directed Adjacency Matrix
-
-*Florentine Families Directed Adjacency Matrix
-Network Objects:* **iGraph** smugDnkIdx_df.ig
-**Statnet** smugDnkIdx_df.stat
+## Directed Adjacency Matrix: Create & Describe
 
@@
 
-    smugDnkIdx_df.stat<-
+    smugCovIdx.stat<-
         network(
-        smugDnkIdx_df,
+        smugCovIdx,
         directed=F,
@@
 
-# 3. Explore the dataset using commands from week 2 tutorial.
+#   Week 2: Scripts
+##    Network: Describe Network Data
+##    *Identify and describe content of nodes and
+    links,*
+
+##    *Identify format of data set (i.e., matrix or
+    edgelist, directed or not, weighted or not),
+    and*
+
+Vertex attribute names: vertex.names
+
+```{r Network Attributes, echo=TRUE}
+
+  network(smugCovIdx)
+
+```
+
+3.  *Identify whether attribute data are present.*
+
+```{r Summary,echo=TRUE}
+
+  summary(smugCovIdx,
+          print.adj = TRUE
+          )
+```
+
+#       Explore the dataset using commands from week 2 tutorial.
 

### 2022-02-11 docs/3. SNA - Assignments/sna_Week3/Week3_Notebook.Rmd
2.11.22
UP and at it

getting somewhere

@@
 ```{r & Clean Data}
+
+  library(stringr)
       # Drop NA rows
@@
 #####
-library(stringr)
+
           # extract first word of the column, adds values in new Column at the end of DF
@@
 # Network: Creating network Data
+
 ## Basic R: Brief Dataset Description

### 2022-02-11 docs/1. SNA-DACSS-Import_Scripts/Load Data -grad_script_template.R

@@ -8,15 +8,26 @@ setwd("") #For example: C:/Users/Tim/Google Drive/Political Networks Course/Data
 library()
 
 #Load your dataset into the environment#
-networkData <- read.csv("",header = T,stringsAsFactors = F) #For example: imf_cpis.csv#
+networkData <- 
+  read.csv("",header = T,stringsAsFactors = F) 
+#For example: imf_cpis.csv#
 
 #Depending on the data structure, create a network object from the dataset loaded#
 #If it's an edgelist...#
-network <- graph.data.frame(networkData[,1:2],directed = T/F) #Only include T or F, not both#
-E(network)$weight <- networkData$'weight' #Include the column name of the weights vector#
+
+network <- 
+  graph.data.frame(networkData[,1:2],
+                   directed = T/F) #Only include T or F, not both#
+
+E(network)$weight <- 
+  networkData$'weight' #Include the column name of the weights vector#
+
 #If it's an adjacency matrix...#
-network <- graph.adjacency(networkData, mode = "directed", weighted = T)
-#Change to undirected if applicable, change 'weighted' to NULL if values are binary#
+network <- 
+  graph.adjacency(networkData, 
+                  mode = "directed", 
+                  weighted = T)
+                  #Change to undirected if applicable, change 'weighted' to NULL if values are binary#
 
 #Check it out!#
 plot(network)

### 2022-02-11 docs/3. SNA - Assignments/SNA Assignment Scripts/import script- Edgelist.R

@@ -18,6 +18,25 @@ library(igraph)
 
 source.df <-cow_alliance
 
+
+      # Basic Info on Object}
+#### list the structure of smugCovIdx
+
+#### class of an object
+class()
+
+#### list the variables in smugCovIdx
+names()
+
+#### dimensions of an object
+dim()
+
+
+colnames(smugCovIdx)
+
+summary(smugCovIdx)
+
+# ```
 #####
     #Format DF to become an edgelist
     

### 2022-02-11 docs/3. SNA - Assignments/sna_Week3/scripts_Week3_NetworkFormation.R

@@ -1,18 +1,45 @@
-# Network Formation 
+library(network)
+
+#           Network Formation 
+        #### check for adjacency vs edgelist 
+#####
+passIt <- smugCovIdx
+dim(passIt)
+  #####
+        #### Edgelist: Network Formation
+            ## NOTE: Edgelist Format
+#####
+            ## network data is nx2 (or more with edge attributes)
+            ## first column is "From", 
+            ## second column is "To"
+  #####
+          ### Edgelist: inspect column names
+              ## inspect column names as 3rd-kth columns of network_data may include network attributes
+colnames(passIt)
+  #####
 
 #####
 #       Format DF to become an edgelist
 #####
+      ###
+      passIt
+#     rows: 4
+#     columns: 672
+#     colnames: 
+              c("dnkName",#c1
+              "dnkIng", #c2
+              "dnkCode",#c3
+              "classIng") #c4 
       # Assign modified source.df to Edge List variable name 
-smugCovIdx_net <- 
-  smugCovIdx[c( #select column numbers from source.Data in order to be added
-    3,# dnkCode
-    1,# dnkName
-    2,# dnkIng
-    4)# classIng
-  ]
+        passIt <- 
+        passIt[c( #select column numbers from source.Data in order to be added
+                2,# dnkIng 
+                3,# dnkCode
+                1,# dnkName
+                4)# classIng
+              ]
 
-summary(smugCovIdx_net)
+summary(passIt)
 #####
 
 

### 2022-02-14 docs/3. SNA - Assignments/sna_Week3/Week3_Notebook.Rmd
2.14.22
so much fuckery

plotting
plot(dr_smug_ntWrk)
plot(tst_ntwrk)

from Rmd yeilds same error message

plotting from rScript is fine >.<

# it's a bloody statnet edgelist

@@
 
-View(indx_SmugglerCove_recip)
+# View(indx_SmugglerCove_recip)
 summary(indx_SmugglerCove_recip)
@@
 
+colnames(passIt)
                     #2nd passIt
 passIt$substring_first <- 
-  str_extract(
-    passIt$X5,
-    "(\\w+)")
+  str_extract(passIt$X5,"(\\w+)")
 
+colnames(passIt)
 #####
@@
 passIt = subset(passIt, 
-                       select = -c(3)
+                       select = -c(3,4)
                        )
+colnames(passIt)
 #####
@@
 names(smugCovIdx )[2] <- "dnkIng"
-names(smugCovIdx )[3] <- "dnkCode"   
-names(smugCovIdx )[4] <- "classIng"
+names(smugCovIdx )[3] <- "ingType"
+
+colnames(smugCovIdx)
+```
+
+# Network: Creating network Data
+```{r NETWORK: Network Formation}
+passIt <- smugCovIdx
+dim(passIt)
+  #####
+        #### Edgelist: Network Formation
+            ## NOTE: Edgelist Format
+#####
+            ## network data is nx2 (or more with edge attributes)
+            ## first column is "From", 
+            ## second column is "To"
+  #####
+          ### Edgelist: inspect column names
+              ## inspect column names as 3rd-kth columns of network_data may include network attributes
+
+colnames(passIt)
 
@@
 
-# Network: Creating network Data
+```{r EDGELIST: IGRAPH: create a network object from the dataset, echo=TRUE}
 
+ smug_unrIg <- smugCovIdx
+
+smug_unrIg <-
+  graph.data.frame(
+    smug_unrIg[,1:3],
+    directed = F)
+
+summary(smug_unrIg)
+
+##### Summary Output
+#####
+      # IGRAPH c6de075 UN-- 274 672 -- 
+      # + attr: name (v/c), ingType (e/c)
+
+```
+
+```{r Edgelist: Statnet Network Object}
+
+#Lets read the data into the enviroment.
+#This will import it formatted as an edgelist
+
+source_netEdge <- smugCovIdx
+
+# Identify Edge Vertices and Edge Attributes
+
+colnames(source_netEdge)
+# dnkName <- "dnkName" 
+# dnkIng <- "dnkIng"  
+# edgeAT <- "ingType"
+
+#Lets create an statnet object from our edgelist
+#First we make the object. It will have no vertex or edge attributes
+sourceEL_sn <- 
+  network(as.matrix(source_netEdge[1:2], 
+                    matrix.type = 'edgelist')
+  )
+
+#**%e%** Let's add edge atributes, do not include the colNames for edge vertex
+
+sourceEL_sn%e%"ingType" <- source_netEdge$ingType
+sourceEL_sn%e%"dnkIng" <- source_netEdge$dnkIng
+
+# Generating the EdgeList
+
+##**round 1**
+          # from "_netEdge" select "colNames" to be identified with "vertex.names"
+
+temp <- source_netEdge[,c("dnkName")]
+
+##**round 2**
+            # code still selecting from "_netEdge", add "colNames"
+
+colnames(temp)<- c("dnkIng")
+
+##**round 3**
+            # "rBind" selects "colnames" from "_netEdge" and BINDS them to temp
+
+temp<- rbind(temp, source_netEdge[, c("dnkIng")])
+
+##**final round** !!! is being used as variable in generating an edgelist object
+                # temp contains
+
+sourceEL_sn%v%"dnkName"<- 
+  temp$dnkIng[match(sourceEL_sn%v%"vertex.names",
+                    temp$dnkIng)]
+
+print(sourceEL_sn)
+
+# it's a bloody statnet edgelist 
+```
+
+# Network Info
 ## Basic R: Brief Dataset Description

### 2022-02-14 docs/1. SNA-DACSS-Import_Scripts/import script_Sn-Ig_Network Objects.R

@@ -1,0 +1,54 @@
+
+#Lets read the data into the enviroment.
+#This will import it formatted as an edgelist
+source_netEdge <- sourceData
+source_netEdge <- source_netEdge[c(3,5,2,4,1,6:19)]
+
+
+#Lets create an statnet object from our edgelist
+#First we make the object. It will have no vertex or edge attributes
+sourceEL_sn <- 
+  network(as.matrix(source_netEdge[1:2], 
+                    matrix.type = 'edgelist')
+  )
+
+#**%e%** Let's add edge atributes, do not include the colNames for edge vertex
+sourceEL_sn%e%"source_edgeAt"      <- source_netEdge$source_edgeAt
+sourceEL_sn%e%"source_edgeAt"     <- source_netEdge$source_edgeAt
+sourceEL_sn%e%"source_edgeAt"    <- source_netEdge$source_edgeAt
+sourceEL_sn%e%"source_edgeAt_date"    <- as.character(source_netEdge$source_edgeAt_date)
+sourceEL_sn%e%"source_edgeAt_end_date"   <- as.character(source_netEdge$source_edgeAt_date)
+
+
+# Generating the EdgeList
+
+##**round**
+          # from "_netEdge" select "colNames" to be identified with "vertex.names"
+
+temp <- source_netEdge[,c("vertex_1", "vCode1")]
+
+
+
+##**round 2**
+            # code still selecting from "_netEdge", add "colNames"
+
+colnames(temp)<- c("vertex_2", "vCode2")
+
+
+##**round 3**
+            # "rBind" selects "colnames" from "_netEdge" and BINDS them to temp
+
+temp<- rbind(temp, source_netEdge[, c("vertex_2" ,"vCode2")])
+print(temp)
+
+
+##**final round** !!! is being used as variable in generating an edgelist object
+                # temp contains 
+        
+
+sourceEL_sn%v%"vCode1"<- 
+  temp$vCode2[match(sourceEL_sn%v%"vertex.names",
+                    temp$vertex_2)]
+
+summary(sourceEL_sn)
+# it's a bloody statnet edgelist 

### 2022-02-14 docs/3. SNA - Assignments/SNA Assignment Scripts/import script- Edgelist.R

@@ -108,7 +108,7 @@ print(temp)
             # round 1 TOTAL: n-rows x 2 
 
 
-      ## round 2
+      ##**round 2**
         # code still selecting from "_netEdge", add "colNames"
         # future attr: state_name2 (e/c), ccode2 (e/n)
 colnames(temp)<-
@@ -125,9 +125,11 @@ print(temp)
 temp<-
   rbind(temp,
        sourceEL.net[,
-                         c("state_name2"
-                           ,"ccode2"
-                         )])
+                         c("state_name2",
+                           "ccode2")
+                    ]
+       )
+
 print(temp)
           # A tibble: n-rows x 2 <selected colmns>
           # round 3 TOTAL: (round 1 n-rows) + (round 2 n-rows) x 2

### 2022-02-14 docs/3. SNA - Assignments/sna_Week3/scripts_Week3_NetworkFormation.R

@@ -1,5 +1,4 @@
 library(network)
-
 #           Network Formation 
         #### check for adjacency vs edgelist 
 #####
@@ -16,10 +15,8 @@ dim(passIt)
           ### Edgelist: inspect column names
               ## inspect column names as 3rd-kth columns of network_data may include network attributes
 colnames(passIt)
-  #####
-
-#####
-#       Format DF to become an edgelist
+  ####
+#       Edgelist: Format DF to become a Network Obkect
 #####
       ###
       passIt
@@ -28,18 +25,202 @@ colnames(passIt)
 #     colnames: 
               c("dnkName",#c1
               "dnkIng", #c2
-              "dnkCode",#c3
-              "classIng") #c4 
-      # Assign modified source.df to Edge List variable name 
-        passIt <- 
-        passIt[c( #select column numbers from source.Data in order to be added
-                2,# dnkIng 
-                3,# dnkCode
-                1,# dnkName
-                4)# classIng
-              ]
+              "ingType") #c3
 
-summary(passIt)
+#Depending on the data structure, create a network object from the dataset loaded#
+  #####
+              
+#             IGRAPH:  Network Formation  
+        ##### IGRAPH: edgelist 
 #####
+tst_ntwrk <- 
+  graph.data.frame(passIt[,3:2,1],
+                   directed = T)
+summary(tst_ntwrk)
+
+plot(tst_ntwrk)
+plot(tst_ntwrk, vertex.cex = .5)
+plot(dr_smugCov, vertex.cex =2, mode = "circle")
+plot(unDr_smugCov, vertex.cex =2, mode = "circle")
+  #####
+
+#             Statnet:  Network Formation  
+        ##### Statnet: edgelist 
+#####
+            #**statnet** object from our edgelist
+# Will not have vertex
+# Will not have edge attributes
+
+          # First we make the network object. 
+#####  
+colnames(passIt)
+# [1] "dnkName" "dnkIng"  "ingType"
+
+
+sourceEL_stat <- 
+  network(as.matrix
+          (passIt[1:3], 
+            matrix.type = 'edgelist')
+  )
+ 
+      #####
+            #**statnet** add edge atributes <aka colnames>
[…]

### 2022-02-14 docs/3. SNA - Assignments/sna_Week3/scripts_Week3_NetworkFormation.R
2.14.22
so much fuckery

plotting
plot(dr_smug_ntWrk)
plot(tst_ntwrk)

from Rmd yeilds same error message

plotting from rScript is fine >.<

@@ -19,7 +19,7 @@ colnames(passIt)
   #####
 
 #####
-#       Format DF to become an edgelist
+#       Edgelist: Format DF to become a Network Obkect
 #####
       ###
       passIt
@@ -28,18 +28,123 @@ colnames(passIt)
 #     colnames: 
               c("dnkName",#c1
               "dnkIng", #c2
-              "dnkCode",#c3
-              "classIng") #c4 
-      # Assign modified source.df to Edge List variable name 
-        passIt <- 
-        passIt[c( #select column numbers from source.Data in order to be added
-                2,# dnkIng 
-                3,# dnkCode
-                1,# dnkName
-                4)# classIng
-              ]
+              "ingType") #c3
 
-summary(passIt)
-#####
+#Depending on the data structure, create a network object from the dataset loaded#
+#If it's an edgelist...#
+
+tst_ntwrk <- 
+  graph.data.frame(passIt[,3:2,1],
+                   directed = T)
+summary(tst_ntwrk)
+
+plot(tst_ntwrk)
+plot(tst_ntwrk, vertex.cex = .5)
+
+plot(tst_ntwrk, vertex.cex =2, mode = "circle")
+###################################################################
+#Step 4: Generating a graph object (igraph) or network object (statnet)
+
+##If data are in edgelist format (A) and are undirected (B), use the following command:#
+
+#igraph object 
+network.ig<-
+  graph.edgelist(as.matrix(deathCo_recip.df),
+                 directed=F) 
+
+
+
+
+
+##### FUCK IT 
+      #####
+            #####
+            ##### FOR REAL
+# Node List: as Matrix
+
+mtrxIt <- 
+  as.matrix(
+    passIt[c(
+      "dnkName", # Node
+      "dnkCode") # # Unique ID for each Node
+      ]
+    )
+
+class(mtrxIt)
+summary(mtrxIt)
+
+nodes_mtrx <- 
+  mtrxIt
+class(nodes_mtrx)
+summary(nodes_mtrx)
+
+# Edge Attributes : As Matrix
+
+mtrxIt <- 
+  as.matrix(
+    passIt[c(
+      "ingType", # Edge attributes
+      "dnkIng")
+    ]
+  )
+
+edgeAt_mtrx <- 
+  mtrxIt
[…]

### 2022-02-14 docs/3. SNA - Assignments/sna_Week3/Week3_Notebook.Rmd

@@
 ---
+
+```{r}
+vectordata=as.vector(mtrxIt)
+print(smugCov_ntWrk)
+```
 
@@
 
-# View(indx_SmugglerCove_recip)
+View(indx_SmugglerCove_recip)
 summary(indx_SmugglerCove_recip)
@@
 
-colnames(passIt)
 #####
@@
 passIt = subset(passIt, 
-                       select = -c(3,4)
+                       select = -c(3)
                        )
@@
 # Network: Creating network Data
-```{r NETWORK: Network Formation}
-passIt <- smugCovIdx
-dim(passIt)
-  #####
-        #### Edgelist: Network Formation
-            ## NOTE: Edgelist Format
-#####
-            ## network data is nx2 (or more with edge attributes)
-            ## first column is "From", 
-            ## second column is "To"
-  #####
-          ### Edgelist: inspect column names
-              ## inspect column names as 3rd-kth columns of network_data may include network attributes
+```{r HOLD: EDGELIST: IGRAPH: create a network object from the dataset, eval=FALSE, include=FALSE}
+colnames(smugCovIdx )
 
-colnames(passIt)
+# [1] "dnkName" "dnkIng"  "ingType"
+# V1 <- "dnkName" 
+# V2 <- "dnkIng"  
+# EA <- "ingType"
+dr_smugCov <- smugCovIdx
+
+ ##If data are in edgelist format (A) and are undirected (B), use the following command:#
+
+#igraph object 
+network_ig<- graph.edgelist(as.matrix(smugCovIdx[1:2]), directed=F)
+
+#  Adding edge and node attributes to network/graph object
+
+#If you have edgelist data, edge attributes will often be stored in same data file
+#iGraph will read in all edge attributes automatically, inspect as follows
+edge_attr(network_ig)
+
+##but to create new edge attribute if edges sorted correctly
+# E(network_ig)$COLNAME<-edge.attribute$COLNAME
+
+#The vertex names in this file must exactly match those in the network#
+#sometimes this requires using as.character(x) to change from factor to character
+#create vertex attributes in igraph
+# V(network_ig)[match(V(network)$name,vertex_attributes$VERTEX_NAME)]$COLNAME<-
+#  vertex_attributes$COLNAME
 
@@
 
-```{r EDGELIST: IGRAPH: create a network object from the dataset, echo=TRUE}
-
- smug_unrIg <- smugCovIdx
-
-smug_unrIg <-
-  graph.data.frame(
-    smug_unrIg[,1:3],
-    directed = F)
-
-summary(smug_unrIg)
-
-##### Summary Output
-#####
-      # IGRAPH c6de075 UN-- 274 672 -- 
-      # + attr: name (v/c), ingType (e/c)
-
-```
-
-```{r Edgelist: Statnet Network Object}
-
+```{r NETWORK EDGELIST: Statnet & Igraph, include=FALSE}
 #Lets read the data into the enviroment.
@@
 colnames(source_netEdge)
-# dnkName <- "dnkName" 
-# dnkIng <- "dnkIng"  
-# edgeAT <- "ingType"
+# [1] "dnkName" "dnkIng"  "ingType"
+# V1 <- "dnkName" 
+# V2 <- "dnkIng"  
+# EA <- "ingType"
 
-#Lets create an statnet object from our edgelist
+# Lets create an statnet object from our edgelist
+#####
 #First we make the object. It will have no vertex or edge attributes
@@
                     temp$dnkIng)]
+      #####
+            summary(sourceEL_sn)
+dim(sourceEL_sn)
 
-print(sourceEL_sn)
+              # it's a bloody statnet edgelist !!!
 
-# it's a bloody statnet edgelist 
+#**igraph** version of the network
+#####
+          # NOTE: igraph automatically adds edge attributes, but not vertices
+
+    #First let's create the object.
+
+sourceEL_ig <- smugCovIdx
+
+sourceEL_ig <- graph_from_data_frame(d = sourceEL_ig, directed = FALSE)
+
+ #**igraph** Generate Edgelist
+
+V(sourceEL_ig)$dnkName<-
+  temp$dnkIng[
+    match(V
+          (sourceEL_ig)$name,
+          temp$dnkIng)
+  ]
+print(sourceEL_ig )
+edge_attr(sourceEL_ig)
+
+#########
+########
+          smugEL_sn  <- sourceEL_sn
+          smugEL_ig <- sourceEL_ig
+dim(smug_sn)
 ```
@@
 ```{r Network: Identify critical features, echo=FALSE}
-#### dimensions of an object
-dim()
 
+#**Statnet EdgeList**   smugEL_sn
+#####
 #### class of an object
-class()
+class(smugEL_sn )
+class(smugEL_ig )
 
 # list the structure of smugCovIdx
-str()
+str(smugEL_sn )
+str(smugEL_ig )
 
-# class of an object (numeric, matrix, data frame, etc)
-class()
-
-# list the variables in smugCovIdx
-names()
-
-colnames( )
-
-summary( )
-
+View(smug_sn)
+View(smug_ig)
 ```
@@
 #     provides a description of several critical network features
-    print(flo.stat)
+    print(source.stat)
 
@@
 
-    flo.ig<-
+    source.ig<-
       graph.adjacency(
@@
       ) 
-    print(flo.ig)
+    print(source.ig)
 ```
@@
 #     Count Vertices
-    vcount(flo.ig)
+    vcount(source.ig)
 
 #     Count Edges
-    ecount(flo.ig)
+    ecount(source.ig)
 
 # Is this a Bipartite or single mode network?
-    is_bipartite(flo.ig)
+    is_bipartite(source.ig)
 
 #  Are edges directed or undirected?
-    is_directed(flo.ig)
+    is_directed(source.ig)
 
 #Are edges weighted or unweighted?
-    is_weighted(flo.ig)
+    is_weighted(source.ig)
 
@@
 #     access vertex attributes
-  head(flo.stat %v% "vertex.names")
+  head(source.stat %v% "vertex.names")
 
 #      list the names of vertex attributes
-  network::list.vertex.attributes(flo.stat)
+  network::list.vertex.attributes(source.stat)
 
 #     access edge attribute
-  head(flo.stat%e% "weight")
+  head(source.stat%e% "weight")
 
 #  Generate a list the names of edge attributes
-  network::list.edge.attributes(flo.stat)
+  network::list.edge.attributes(source.stat)
 
 #   summarize numeric network attribute
-  summary(flo.stat  %v% "name")
+  summary(source.stat  %v% "name")
 
@@
 #     access vertex attribute 
-  V(flo.ig)$name
+  V(source.ig)$name
 #     Generate a list the names of vertex attributes
-  igraph::vertex_attr_names(flo.ig)
+  igraph::vertex_attr_names(source.ig)
 
 #     access edge attribute
-  E(flo.ig)$weight
+  E(source.ig)$weight
 
 #   Generate a list the names of edge attributes  
-  igraph::edge_attr_names(flo.ig)
+  igraph::edge_attr_names(source.ig)
 
 #   summarize numeric network attribute
-  summary(E(flo.ig)$weight)
+  summary(E(source.ig)$weight)
 
@@
 #     Calculate distances between two nodes
-    distances(flo.ig,"Bischeri","Ridolfi")
+    distances(source.ig,"node 1","node 2")
 
 #     Calculate distance between two nodes using unweighted edges
-    distances(flo.ig,"Bischeri", "Castellani",weights=NA)
+    distances(source.ig,"node 1", "node 5",weights=NA)
 
@@
 #     isolating the distances between specific node
-    all_shortest_paths(flo.ig,"Strozzi","Tornabuoni", weights=NA)$res
+    all_shortest_paths(source.ig,"node 3","node 4", weights=NA)$res
 ## Note: manually tell igraph to ignore edge weights.
@@
 #     find average shortest path for network
-    average.path.length(flo.ig,directed=F)
+    average.path.length(source.ig,directed=F)
 
@@
 
-    sna::dyad.census(flo.stat)
+    sna::dyad.census(source.stat)
 
@@
 
-  igraph::dyad.census(flo.ig)
+  igraph::dyad.census(source.ig)
 
@@
 #     Classify all Triad in the network: Directed Network
-  sna::triad.census(flo.stat, mode= )
+  sna::triad.census(source.stat, mode= )
 
 #     Classify all Triad in the network: Undirected Network
-   sna::triad.census(flo.stat, mode="graph")
+   sna::triad.census(source.stat, mode="graph")
 
 #     total number of all four triad types returned by triad census
-   sum(sna::triad.census(flo.stat, mode="graph"))
+   sum(sna::triad.census(source.stat, mode="graph"))
 
@@
 #Classify all Triad in the network
-     igraph::triad_census(flo.ig)
+     igraph::triad_census(source.ig)
 
@@
 #     network transitivity:
-    transitivity(flo.ig)
+    transitivity(source.ig)
 
 #     weighted network transitivity:
-#   igraph::transivity(flo.ig)
+#   igraph::transivity(source.ig)
 
@@
 #     Directed Networks transitivity:
-  gtrans(flo.stat)
+  gtrans(source.stat)
 
@@
 #     Retrive a list of the vertices we are interested
-    V(flo.ig)[c("Bischeri" ,
-                "Castellani", 
-                "Medici",
-                "Ridolfi")]
+    V(source.ig)[c("node 1" ,
+                "node 5", 
+                "node 6",
+                "node 2")]
 
 #     check ego network transitivity
-transitivity(flo.ig,
+transitivity(source.ig,
              type="local", 
-             vids=V(flo.ig)
-             [c("Bischeri",
-                "Castellani", 
-                "Medici",
-                "Ridolfi")]) 
+             vids=V(source.ig)
+             [c("node 1",
+                "node 5", 
+                "node 6",
+                "node 2")]) 
 #     get global clustering cofficient
-  transitivity(flo.ig, type="global")
+  transitivity(source.ig, type="global")
 
 #     get average local clustering coefficient
-  transitivity(flo.ig, type="average")
+  transitivity(source.ig, type="average")
 
@@
 
-> Distill is a publication format for scientific
-> and technical writing, native to the web.
+Distill is a publication format for scientific
+and technical writing, native to the web.
 >
-> Learn more about using Distill for R Markdown at
-> <https://rstudio.github.io/distill>. ##
+Learn more about using Distill for R Markdown at
+<https://rstudio.github.io/distill>. ##

### 2022-02-14 docs/3. SNA - Assignments/sna_Week3/Week3_Notebook.Rmd

--- 2022-02-11 docs/3. SNA - Assignments/sna_Week3/Week3_Notebook.Rmd
@@
 
+colnames(passIt)
                     #2nd passIt
 passIt$substring_first <- 
-  str_extract(
-    passIt$X5,
-    "(\\w+)")
+  str_extract(passIt$X5,"(\\w+)")
 
@@
                        )
+colnames(passIt)
 #####
@@
 names(smugCovIdx )[2] <- "dnkIng"
-names(smugCovIdx )[3] <- "dnkCode"   
-names(smugCovIdx )[4] <- "classIng"
+names(smugCovIdx )[3] <- "ingType"
+
+colnames(smugCovIdx)
+```
+
+# Network: Creating network Data
+```{r EDGELIST: IGRAPH: create a network object from the dataset, echo=TRUE}
+
+ dr_smugCov <- smugCovIdx
+
+dr_smugCov <-
+  graph.data.frame(smugCovIdx[,3:2,1],
+                   directed = T)
+summary(dr_smugCov)
+
+plot(dr_smug_ntWrk)
+plot(tst_ntwrk)
+unDr_smug_ntWrk
 
@@
 
-# Network: Creating network Data
-
+# Network Info
 ## Basic R: Brief Dataset Description

### 2022-02-15 docs/3. SNA - Assignments/sna_Week3/Week3_Notebook.Rmd
2.15.22
opswdefopajwfgjQ"pfnetwork_statnetEA

--- 2022-02-14 docs/3. SNA - Assignments/sna_Week3/Week3_Notebook.Rmd
@@
 ---
-
-```{r}
-vectordata=as.vector(mtrxIt)
-print(smugCov_ntWrk)
-```
 
@@
 
-setwd("C:/Users/white/iCloudDrive/Documents/1_DACSS_UMassAmherst/Dacss_RProjects/3. Sp22_rProjects/Dacss_679- Coursework/GIT-ajw_Learning-SocialNetworkAnalysis/docs/3. SNA - Assignments")
+setwd("C:/Users/white/iCloudDrive/Documents/1_DACSS_UMassAmherst/Dacss_RProjects/3. Sp22_rProjects/Dacss_679- Coursework/GIT-ajw_Learning-SocialNetworkAnalysis/docs/3. SNA - Assignments/sna_Week3")
 
@@
 ```{r HOLD: EDGELIST: IGRAPH: create a network object from the dataset, eval=FALSE, include=FALSE}
+
 colnames(smugCovIdx )
@@
   ]
-print(sourceEL_ig )
-edge_attr(sourceEL_ig)
+# print(sourceEL_ig )
+# edge_attr(sourceEL_ig)
 
@@
           smugEL_ig <- sourceEL_ig
-dim(smug_sn)
+
 ```
@@
 # Network Info
-## Basic R: Brief Dataset Description
+  Network Objects: EDGE LIST
+                  STATNET: smugEL_sn
+                  IGRAPH: smugEL_ig
+
+## Smuggler's Cove Index- NETWORK: EDGELIST: Features & Descriptions
 ```{r Network: Identify critical features, echo=FALSE}
@@
 #####
-#### class of an object
+
+```
+
+```{r STATNET: Network Description}
+
+      # class of an object
 class(smugEL_sn )
-class(smugEL_ig )
 
@@
 str(smugEL_sn )
-str(smugEL_ig )
 
-View(smug_sn)
-View(smug_ig)
-```
-
-## Directed Adjacency Matrix: Create & Describe
-
-iGraph and Statnet both use {r graph4} for
-Directed Adjacency Matrix Objects
-
-```{r graph4, statnet: Directed: Adjacency Network, echo=TRUE}
-
-    smugCovIdx.stat<-
-        network(
-        smugCovIdx,
-        directed=F,
-        matrix.type="adjacency"
-        )
-
-#     provides a description of several critical network features
-    print(source.stat)
-
-```
-
-```{r graph4, igraph: Directed: Adjacency Network, echo=TRUE}
-
-    source.ig<-
-      graph.adjacency(
-      flo,
-      mode="undirected"
-      ) 
-    print(source.ig)
+      ## Network Attributes
+ print(smugEL_sn)
+          # Vertices =  
+          # Directed = 
+          # hyper = 
+          # loops = 
+          # multiple = 
+          # bipartite = 
+          # total edges = 
+                # missing edges =
+                # non-missing edges = 
+          # Vertex attribute names:
+          # Edge Attribute Names: 
 ```
@@
 
+      # class of an object
+    class(smugEL_ig )
+
+        # list the structure of smugCovIdx
+    str(smugEL_ig )
+
+## Network Size
       # Count Vertices
-    vcount(source.ig)
+    vcount(smugEL_ig)
 
       # Count Edges
-    ecount(source.ig)
+    ecount(smugEL_ig)
 
-# Is this a Bipartite or single mode network?
-    is_bipartite(source.ig)
+## Network Mode
+    # Bipartitie / Unimodal
+    is_bipartite(smugEL_ig)
 
-#  Are edges directed or undirected?
-    is_directed(source.ig)
+## Edges    
+    # Un/directed 
+    is_directed(smugEL_ig)
 
-#Are edges weighted or unweighted?
-    is_weighted(source.ig)
+    # weighted or unweighted?
+    is_weighted(smugEL_ig)
 
@@
 
+# class of an object
+    class(smugEL_sn)
+
 #     access vertex attributes
-  head(source.stat %v% "vertex.names")
+  head(smugEL_sn %v% "vertex.names")
 
 #      list the names of vertex attributes
-  network::list.vertex.attributes(source.stat)
+  network::list.vertex.attributes(smugEL_sn)
 
 #     access edge attribute
-  head(source.stat%e% "weight")
+#  head(smugEL_sn%e% "weight")
 
 #  Generate a list the names of edge attributes
-  network::list.edge.attributes(source.stat)
+  network::list.edge.attributes(smugEL_sn)
 
 #   summarize numeric network attribute
-  summary(source.stat  %v% "name")
+  summary(smugEL_sn  %v% "name")
 
@@
 #     access vertex attribute 
-  V(source.ig)$name
+  V(smugEL_ig)$name
 #     Generate a list the names of vertex attributes
-  igraph::vertex_attr_names(source.ig)
+  igraph::vertex_attr_names(smugEL_ig)
 
 #     access edge attribute
-  E(source.ig)$weight
+  E(smugEL_ig)$weight
 
 #   Generate a list the names of edge attributes  
-  igraph::edge_attr_names(source.ig)
-
-#   summarize numeric network attribute
-  summary(E(source.ig)$weight)
+  igraph::edge_attr_names(smugEL_ig)
 
@@
 
-##    *Identify format of data set (i.e., matrix or
-    edgelist, directed or not, weighted or not),
-    and*
-
 Vertex attribute names: vertex.names
-
-```{r Network Attributes, echo=TRUE}
-
-  network(smugCovIdx)
-
-```
 
@@
 #     Calculate distances between two nodes
-    distances(source.ig,"node 1","node 2")
+    distances(smugEL_ig,"node 1","node 2")
 
 #     Calculate distance between two nodes using unweighted edges
-    distances(source.ig,"node 1", "node 5",weights=NA)
+    distances(smugEL_ig,"node 1", "node 5",weights=NA)
 
@@
 #     isolating the distances between specific node
-    all_shortest_paths(source.ig,"node 3","node 4", weights=NA)$res
+    all_shortest_paths(smugEL_ig,"node 3","node 4", weights=NA)$res
 ## Note: manually tell igraph to ignore edge weights.
@@
 #     find average shortest path for network
-    average.path.length(source.ig,directed=F)
+    average.path.length(smugEL_ig,directed=F)
 
@@
 Classifies all dyads in the network as: -
-Reciprocal (mutual), or mut - Asymmetric
-(non-mutual), or asym, and - Absent, or null
+Reciprocal (mutual), or 
+mut - Asymmetric (non-mutual), or 
+asym, and - 
+Absent, or null
 
@@
 
-    sna::dyad.census(source.stat)
+    sna::dyad.census(smugEL_sn)
 
@@
 
-  igraph::dyad.census(source.ig)
+  igraph::dyad.census(smugEL_ig)
 
@@
 into the types of triads found in a particular
-dataset.
+smugEL_
 
@@
 #     Classify all Triad in the network: Directed Network
-  sna::triad.census(source.stat, mode= )
+
+  sna::triad.census(smugEL_sn, mode= )
 
 #     Classify all Triad in the network: Undirected Network
-   sna::triad.census(source.stat, mode="graph")
+   sna::triad.census(smugEL_sn, mode="graph")
 
 #     total number of all four triad types returned by triad census
-   sum(sna::triad.census(source.stat, mode="graph"))
+   sum(sna::triad.census(smugEL_sn, mode="graph"))
 
@@
 #Classify all Triad in the network
-     igraph::triad_census(source.ig)
+     igraph::triad_census(smugEL_ig)
 
@@
 #     network transitivity:
-    transitivity(source.ig)
+    transitivity(smugEL_ig)
 
 #     weighted network transitivity:
-#   igraph::transivity(source.ig)
+#   igraph::transivity(smugEL_ig)
 
@@
 #     Directed Networks transitivity:
-  gtrans(source.stat)
+  gtrans(smugEL_sn)
 
@@
 #     Retrive a list of the vertices we are interested
-    V(source.ig)[c("node 1" ,
+    V(smugEL_ig)[c("node 1" ,
                 "node 5", 
@@
 #     check ego network transitivity
-transitivity(source.ig,
+transitivity(smugEL_ig,
              type="local", 
-             vids=V(source.ig)
+             vids=V(smugEL_ig)
              [c("node 1",
@@
 #     get global clustering cofficient
-  transitivity(source.ig, type="global")
+  transitivity(smugEL_ig, type="global")
 
 #     get average local clustering coefficient
-  transitivity(source.ig, type="average")
+  transitivity(smugEL_ig, type="average")
 

### 2022-02-15 docs/3. SNA - Assignments/sna_Week3/week3_AssignmentNotes.R

@@ -1,0 +1,916 @@
+# [697: Week 3 Assignment: Degree and Centrality](https://docs.google.com/document/d/1vE7ICJVbqq6PrLQqg-ix77Y3kC1jz0UuziJOw0v0et0/edit)
+######
+### Using the tutorial as a guide, 
+*  you may use your own data; 
+*  the data provided in the week 3. Syntax dataset is Correlates of War trade network - you can read more about it online; or
+*  choose another dataset.
+
+## Working from the example R syntax:
+1.   calculate network density; 
+2.   degree centrality, and 
+3.   centralization measures for your network data. 
+
+
+## Write up your results briefly:
+*   focus on interpretation of the results. 
+*   Don’t list statistics or provide code, 
+*  **the goal is to choose a few interesting results and provide an interpretation.**
+  
+  ## Briefly describe the dataset:
+  1.   identify initial network format; 
+2.   describe and identify the nodes 
+including: 
+  *  how many nodes are in the dataset; 
+3.   what constitutes a tie or edge
+including:
+  *  how many ties, 
+*   whether ties are directed/undirected,
+*   whether ties are weighted/binary, 
+*   and how to interpret the value of the tie if any.
+*   Whether or not there are edge attributes 
+that might be used to:
+  *   subset data, or 
+*   stack multiple networks. 
+Not every feature of the network needs to be described, but **description should orient reader to the network data and provide any necessary context for the results provided.**
+  
+  ## Provide at least two or three noteworthy results, including:
+  1.   the relevant statistics and interpretation. 
+For example, explaining which node(s) are most central and which are least central. 
+2.   Discuss (with any related evidence) whether or not the node(s) behavior is in line with or violates expectations based on the degree centrality measure. 
+3.   What do you make of network density and centralization measures?  
+  4.   What about differences in the binary 100 million threshold network vs valued trade flows network. 
+5.  Check tutorial for other ideas of results to discuss.
+
+  ######
+#####
+      ##### Tutorial: Network Degree, Week 3
+#####
+      ### Statnet Getting Started
+#####
+library(statnet)
+
+data-EXAMPLE <- read.csv("EXAMPLE.csv", header=T, row.names=1, check.names=FALSE)
+#include header = T and row.names = 1 to account for the node labels
+
+att-EXAMPLE = read.csv("EXAMPLE_Attributes.csv", header=T)
+
+data-EXAMPLE
+head(att-EXAMPLE)
+
+
[…]

### 2022-02-15 docs/3. SNA - Assignments/sna_Week3/Week3_Notebook.Rmd
2.15.22

@@
 ```{r HOLD: EDGELIST: IGRAPH: create a network object from the dataset, eval=FALSE, include=FALSE}
-
 colnames(smugCovIdx )
@@
 # Network Info
-  Network Objects: EDGE LIST
-                  STATNET: smugEL_sn
-                  IGRAPH: smugEL_ig
-
-## Smuggler's Cove Index- NETWORK: EDGELIST: Features & Descriptions
+## Basic R: Brief Dataset Description
 ```{r Network: Identify critical features, echo=FALSE}
@@
 #####
+#### class of an object
+class(smugEL_sn )
+class(smugEL_ig )
+
+# list the structure of smugCovIdx
+str(smugEL_sn )
+str(smugEL_ig )
 
@@
 
-```{r STATNET: Network Description}
-
-      # class of an object
-class(smugEL_sn )
-
-      # list the structure of smugCovIdx
-str(smugEL_sn )
-
-      ## Network Attributes
- print(smugEL_sn)
-          # Vertices =  
-          # Directed = 
-          # hyper = 
-          # loops = 
-          # multiple = 
-          # bipartite = 
-          # total edges = 
-                # missing edges =
-                # non-missing edges = 
-          # Vertex attribute names:
-          # Edge Attribute Names: 
-```
+## EDGELIST: Describe
 
 ```{r igraph: Network Description, echo=TRUE}
+# class of an object
 
-      # class of an object
     class(smugEL_ig )
@@
 # list the structure of smugCovIdx
+
     str(smugEL_ig )
-
-## Network Size
 #     Count Vertices
@@
 
-## Network Mode
-    # Bipartitie / Unimodal
+# Is this a Bipartite or single mode network?
     is_bipartite(smugEL_ig)
 
-## Edges    
-    # Un/directed 
+#  Are edges directed or undirected?
     is_directed(smugEL_ig)
 
-    # weighted or unweighted?
+#Are edges weighted or unweighted?
     is_weighted(smugEL_ig)
@@
 into the types of triads found in a particular
-smugEL_
+dataset.
 

### 2022-02-15 docs/3. SNA - Assignments/sna_Week3/Week3_Notebook.Rmd

--- 2022-02-15 docs/3. SNA - Assignments/sna_Week3/Week3_Notebook.Rmd
@@
   network(as.matrix(source_netEdge[1:2], 
-                    matrix.type = 'edgelist')
+                    matrix.type = 'edgelist',
+                    loops=T,
+                    hyper=T)
   )
+print(sourceEL_sn)
 
@@
 
+print(sourceEL_sn)
+
+sourceEL_sn%v%"dnkName"<- sourceEL_sn%v%"vertex.names",source_netEdge$dnkName
+
+print(sourceEL_sn)
 # Generating the EdgeList
-
+#####
 ##**round 1**
@@
 
+View(temp)
 ##**round 2**
@@
  colnames(temp)<- c("dnkIng")
+# View(temp)
 
@@
 
-temp<- rbind(temp, source_netEdge[, c("dnkIng")])
+temp <- rbind(temp,source_netEdge[, c("dnkIng")])
+
+View(temp)
+#######
 
@@
 sourceEL_sn%v%"dnkName"<- 
-  temp$dnkIng[match(sourceEL_sn%v%"vertex.names",
-                    temp$dnkIng)]
+  temp$dnkName[match(sourceEL_sn%v%"vertex.names",
+                    temp$dnkName)]
       #####
             summary(sourceEL_sn)
-dim(sourceEL_sn)
+View(sourceEL_sn)
+
+#####
+
+#     access edge attribute
+#  head(smugEL_sn%e% "weight")
+
+#####
 
@@
 
+#####
       #**igraph** Generate Edgelist
+######
 
@@
 
+            # list the structure of smugCovIdx
+    str(smugEL_ig )
+    str(smug_sn)
+
 ```
@@
                   IGRAPH: smugEL_ig
+
+```{r}
+
+colnames(smugCovIdx)
+#Lets make some network objects
+
+smugCovIdx_igraph <- graph_from_data_frame(smugCovIdx)
+print(smugCovIdx_igraph)
+
+#Now let's create a statnet object
+
+network_edgelist <- smugCovIdx
+
+network_statnet <- network(as.matrix(network_edgelist[,c("dnkName")]), 
+                             directed = FALSE, matrix.type = "edgelist")
+
+  network_statnet%e%'dnkIng'  <- smugCovIdx$dnkIng
+  network_statnet%e%'ingType' <- smugCovIdx$ingType
+
+  network_statnet%v%'dnkName'<-
+    as.character(smugCovIdx$dnkName[match(smugCovIdx,network_statnet%v%'vertex.names')])
+
+print(network_statnet)
+
+                                 #     access vertex attributes
+  view(network_statnet%v% "vertex.names")
+            # list the names of vertex attributes
+  network::list.vertex.attributes(network_statnet)
+            #  Generate a list the names of edge attributes
+  network::list.edge.attributes(network_statnet)
+            #   summarize numeric network attribute
+  summary(network_statnet%v%"dnkName")
+
+```
 
@@
 
-        # list the structure of smugCovIdx
-    str(smugEL_ig )
-
 ## Network Size
@@
 #     access vertex attributes
-  head(smugEL_sn %v% "vertex.names")
+  view(smugEL_sn %v% "vertex.names")
 

### 2022-02-15 docs/3. SNA - Assignments/sna_Week3/Week3_Notebook.Rmd

--- 2022-02-15 docs/3. SNA - Assignments/sna_Week3/Week3_Notebook.Rmd
@@
 
-# Network: Creating network Data
-```{r HOLD: EDGELIST: IGRAPH: create a network object from the dataset, eval=FALSE, include=FALSE}
-
-colnames(smugCovIdx )
-
-# [1] "dnkName" "dnkIng"  "ingType"
-# V1 <- "dnkName" 
-# V2 <- "dnkIng"  
-# EA <- "ingType"
-dr_smugCov <- smugCovIdx
-
- ##If data are in edgelist format (A) and are undirected (B), use the following command:#
-
-#igraph object 
-network_ig<- graph.edgelist(as.matrix(smugCovIdx[1:2]), directed=F)
-
-#  Adding edge and node attributes to network/graph object
-
-#If you have edgelist data, edge attributes will often be stored in same data file
-#iGraph will read in all edge attributes automatically, inspect as follows
-edge_attr(network_ig)
-
-##but to create new edge attribute if edges sorted correctly
-# E(network_ig)$COLNAME<-edge.attribute$COLNAME
-
-#The vertex names in this file must exactly match those in the network#
-#sometimes this requires using as.character(x) to change from factor to character
-#create vertex attributes in igraph
-# V(network_ig)[match(V(network)$name,vertex_attributes$VERTEX_NAME)]$COLNAME<-
-#  vertex_attributes$COLNAME
-
-```
-
-```{r NETWORK EDGELIST: Statnet & Igraph, include=FALSE}
-#Lets read the data into the enviroment.
-#This will import it formatted as an edgelist
-
-source_netEdge <- smugCovIdx
-
-# Identify Edge Vertices and Edge Attributes
-
-colnames(source_netEdge)
-# [1] "dnkName" "dnkIng"  "ingType"
-# V1 <- "dnkName" 
-# V2 <- "dnkIng"  
-# EA <- "ingType"
-
-# Lets create an statnet object from our edgelist
-#####
-#First we make the object. It will have no vertex or edge attributes
-sourceEL_sn <- 
-  network(as.matrix(source_netEdge[1:2], 
-                    matrix.type = 'edgelist')
-  )
-
-#**%e%** Let's add edge atributes, do not include the colNames for edge vertex
-
-sourceEL_sn%e%"ingType" <- source_netEdge$ingType
-sourceEL_sn%e%"dnkIng" <- source_netEdge$dnkIng
-
-# Generating the EdgeList
-
-##**round 1**
-          # from "_netEdge" select "colNames" to be identified with "vertex.names"
-
-temp <- source_netEdge[,c("dnkName")]
-
-##**round 2**
-            # code still selecting from "_netEdge", add "colNames"
-
-colnames(temp)<- c("dnkIng")
-
-##**round 3**
-            # "rBind" selects "colnames" from "_netEdge" and BINDS them to temp
-
-temp<- rbind(temp, source_netEdge[, c("dnkIng")])
-
-##**final round** !!! is being used as variable in generating an edgelist object
-                # temp contains
-
-sourceEL_sn%v%"dnkName"<- 
-  temp$dnkIng[match(sourceEL_sn%v%"vertex.names",
-                    temp$dnkIng)]
-      #####
-            summary(sourceEL_sn)
-dim(sourceEL_sn)
-
-              # it's a bloody statnet edgelist !!!
-
-#**igraph** version of the network
-#####
-          # NOTE: igraph automatically adds edge attributes, but not vertices
-
-    #First let's create the object.
-
-sourceEL_ig <- smugCovIdx
-
-sourceEL_ig <- graph_from_data_frame(d = sourceEL_ig, directed = FALSE)
-
- #**igraph** Generate Edgelist
-
-V(sourceEL_ig)$dnkName<-
-  temp$dnkIng[
-    match(V
-          (sourceEL_ig)$name,
-          temp$dnkIng)
-  ]
-# print(sourceEL_ig )
-# edge_attr(sourceEL_ig)
-
-#########
-########
-          smugEL_sn  <- sourceEL_sn
-          smugEL_ig <- sourceEL_ig
-
-```
-
 # Network Info
@@
                   IGRAPH: smugEL_ig
+
+```{r EDGELIST: Network Objects}
+
+#Lets make some network objects
+
+colnames(smugCovIdx) 
+# tell R data should be understood as a matrix
+smug_matrix = as.matrix(smugCovIdx,
+                        matrix.type="edgelist",
+                        directed=FALSE) 
+head.matrix(smug_matrix)
+
+network_edgelist <- smug_matrix
+
+  network_nodes <- smugCovIdx 
+    network_nodes<- 
+      select(network_nodes,
+             dnkName)
+
+    View(network_nodes)
+######
+      ######**igraph** 
+######
+        #igraph object 
+network_ig <- 
+  graph.edgelist(
+    as.matrix(
+      smugCovIdx), 
+    directed=F)
+                ## create new edge attribute
+  E(network_ig)$dnkIng<-smugCovIdx$dnkIng
+  E(network_ig)$ingType<-smugCovIdx$ingType
+  #create vertex attributes in igraph
+ V(network_ig)[match(V(smug_matrix)$dnkName,network_nodes$dnkName)]$dnkName<-
+   network_nodes$dnkName
+
+  V(network.ig)[match(V(network_edgelist)$name,network_nodes$VERTEX_NAME)]$dnkName <- network_nodes$dnkName
+      summary(edge_attr(network_ig))
+
+head(network_ig)
+summary(network_ig)
+      ######
+
+#####
+      #####**statnet** 
+#####    
+  network_edgelist <- smugCovIdx
+
+  network_nodes <- smugCovIdx 
+  network_nodes<- 
+    select(network_nodes,
+           dnkName)
+summary(network_nodes)
+View(network_nodes)
+
+  #Now let's create a statnet object
+  network_statnet <- network(network_edgelist, 
+                             matrix.type = "edgelist",
+                             vertex.attr = network_nodes,
+                             multiple = T)
+
+  network_statnet%e%'dnkIng'  <-
+    network_edgelist$dnkIng
+
+  network_statnet%e%'ingType'<- 
+    network_edgelist$ingType
+
+summary(network_statnet)
+
+                                 #     access vertex attributes
+  view(network_statnet%v% "vertex.names")
+            # list the names of vertex attributes
+  network::list.vertex.attributes(network_statnet)
+            #  Generate a list the names of edge attributes
+  network::list.edge.attributes(network_statnet)
+            #   summarize numeric network attribute
+  summary(network_statnet%v%"dnkName")
+
+```
 

### 2022-02-16 docs/3. SNA - Assignments/sna_Week3/Week3_Notebook.Rmd
whelp, there's data in the statnet and igraph object, but sure if it's meaningful though

@@
 
+#   Project Varriables
+
+    Raw Data:
+  indx_SmugglerCove_recip
+
+    DataFrame:
+  smugCovIdx
+  network_nodes <- smugCovIdx << "dnkName"
+
+    Matrix:
+  smug_matrix
+  network_edgelist <- smug_matrix
+
+    Network Objects: EDGE LIST
+  STATNET: smugEL_sn
+  IGRAPH: smugEL_ig
+
 # Network Info
@@
 
-```{r EDGELIST: Network Objects}
+```{r EDGELIST: Network Objects: statnet & igraph, include=FALSE}
 
@@
 
-    View(network_nodes)
+        ### View(network_nodes)
+
 ######
@@
     as.matrix(
-      smugCovIdx), 
+      smugCovIdx[1:2]), 
     directed=F)
@@
   #create vertex attributes in igraph
- V(network_ig)[match(V(smug_matrix)$dnkName,network_nodes$dnkName)]$dnkName<-
+ V(network_ig)[match(V(network_ig)$dnkName,network_nodes$dnkName)]$dnkName<-
    network_nodes$dnkName
 
-  V(network.ig)[match(V(network_edgelist)$name,network_nodes$VERTEX_NAME)]$dnkName <- network_nodes$dnkName
       summary(edge_attr(network_ig))
 
-head(network_ig)
-summary(network_ig)
+  # head(network_ig)
+  # summary(network_ig)
       ######
@@
 
+       # list the names: vertex attributes
+  view(network_statnet%v% "vertex.names")
+
 summary(network_statnet)
+        #####
 
-                                 #     access vertex attributes
-  view(network_statnet%v% "vertex.names")
-            # list the names of vertex attributes
-  network::list.vertex.attributes(network_statnet)
-            #  Generate a list the names of edge attributes
-  network::list.edge.attributes(network_statnet)
-            #   summarize numeric network attribute
-  summary(network_statnet%v%"dnkName")
+ ## Network Objects: EDGE LIST
+              ##**STATNET:**
+  smugEL_sn <- network_statnet
+
+                ##**IGRAPH:** 
+  smugEL_ig <- network_ig
 
@@
 ## Smuggler's Cove Index- NETWORK: EDGELIST: Features & Descriptions
-```{r Network: Identify critical features, echo=FALSE}
 
-#**Statnet EdgeList**   smugEL_sn
-#####
-
-```
-
-```{r STATNET: Network Description}
+```{r STATNET: Network Description, include=FALSE}
 
@@
 
-      # list the structure of smugCovIdx
-str(smugEL_sn )
+## access vertex attributes
+            # list the names:  vertex attributes
+  network::list.vertex.attributes(smugEL_sn)
+
+            # list the names:  edge attributes
+  network::list.edge.attributes(smugEL_sn)
+      #   summarize: numeric network attribute
+  summary(smug_sn%v%"dnkName")
 
@@
           # Edge Attribute Names:
+
+##**NOTE** large quantity of output
+
+  # list the structure of smugCovIdx
+# str(smugEL_sn)
 ```
+
+smugEL_sn
+
+[1] "network"
+
+Network attributes:
+  vertices = 274 
+  directed = TRUE 
+  hyper = FALSE 
+  loops = FALSE 
+  multiple = TRUE 
+  bipartite = FALSE 
+  total edges= 672 
+    missing edges= 0 
+    non-missing edges= 672
+
+ Vertex attribute names: 
+    dnkName vertex.names
+
+ Edge attribute names: 
+    dnkIng ingType
 
@@
 ## Network Size
+
       # Count Vertices
@@
 
-```
+    # edge weights
+    E(smugEL_ig)$weight
 
-**Vertex and Edge Attributes**
+## access vertex attributes
 
-```{r statnet: Attribute Data: Directed: Adjacency Network, echo=TRUE}
+    # Generate a list the names of vertex attributes
+  V(smugEL_ig)$name
 
-# class of an object
-    class(smugEL_sn)
-
-#     access vertex attributes
-  view(smugEL_sn %v% "vertex.names")
-
-#      list the names of vertex attributes
-  network::list.vertex.attributes(smugEL_sn)
-
-#     access edge attribute
-#  head(smugEL_sn%e% "weight")
-
-#  Generate a list the names of edge attributes
-  network::list.edge.attributes(smugEL_sn)
-
-#   summarize numeric network attribute
-  summary(smugEL_sn  %v% "name")
-
-```
-
-```{r igraph: Attribute Data: Directed: Adjacency Network, echo=TRUE}
-
-#     access vertex attribute 
-  V(smugEL_ig)$name
-#     Generate a list the names of vertex attributes
+    # access edge attribute  names
   igraph::vertex_attr_names(smugEL_ig)
-
-#     access edge attribute
-  E(smugEL_ig)$weight
 
@@
 
+## Network Attributes
+ summary(smugEL_ig)
+          # Vertices =  
+          # Directed = 
+          # hyper = 
+          # loops = 
+          # multiple = 
+          # bipartite = 
+          # total edges = 
+                # missing edges =
+                # non-missing edges = 
+          # Vertex attribute names:
+          # Edge Attribute Names: 
 ```
+smugEL_ig
 
-#   Week 2: Scripts
-##    Network: Describe Network Data
-##    *Identify and describe content of nodes and
-    links,*
+[1] "igraph"
 
-Vertex attribute names: vertex.names
+Network attributes:
+  vertices = 274 
+  directed = FALSE
+  hyper = FALSE 
+  loops = FALSE 
+  multiple = TRUE 
+  bipartite = FALSE 
+  total edges= 672 
+    missing edges= 0 
+    non-missing edges= 672
 
-3.  *Identify whether attribute data are present.*
+ Vertex attribute names: 
+    dnkName vertex.names
 
-```{r Summary,echo=TRUE}
+ Edge attribute names: 
+    dnkIng ingType
 
-  summary(smugCovIdx,
-          print.adj = TRUE
-          )
-```
-
-#       Explore the dataset using commands from week 2 tutorial.
-
-5.  *geodesic and path distances,*
+#   Week 2: Basic Network Structure: Smuggler's Cove Drink Index
 
 ## Path Length and Geodesic
-
-```{r iGraph:Nodes: Path: Length, echo=TRUE}
-
-#     Calculate distances between two nodes
-    distances(smugEL_ig,"node 1","node 2")
-
-#     Calculate distance between two nodes using unweighted edges
-    distances(smugEL_ig,"node 1", "node 5",weights=NA)
-
-```
-
-We can also find all of the shortest paths between
-two famalies in this network. These list the
-starting node and the ending node with all nodes
-inbetween for each path. The option weights=NA
-means that any available edge weights are ignored.
-
-```{r iGraph:Nodes: Path: Shortest, echo=TRUE}
-
-#     isolating the distances between specific node
-    all_shortest_paths(smugEL_ig,"node 3","node 4", weights=NA)$res
-## Note: manually tell igraph to ignore edge weights.
-```
-
-The concept of shortest path to describe the
-overall network structure can be more useful
 
@@
 
-6.  *triads or transitivity,*
+```{r iGraph: Specific Nodes: Path: Shortest, echo=TRUE}
+
+#     isolating the distances between specific node
+    all_shortest_paths(smugEL_ig,"Strozzi","Tornabuoni", weights=NA)$res
+## Note: manually tell igraph to ignore edge weights.
+```
+
+```{r iGraph: Specific Nodes: Path: Length, echo=TRUE}
+
+#     Calculate distances between two nodes
+    distances(smugEL_ig,"Bischeri","Ridolfi")
+
+#     Calculate distance between two nodes using unweighted edges
+    distances(smugEL_ig,"Bischeri", "Castellani",weights=NA)
+
+```
 
 ## Dyad Census
-
 Classifies all dyads in the network as: - 
-Reciprocal (mutual), or 
-mut - Asymmetric (non-mutual), or 
-asym, and - 
-Absent, or null
+Reciprocal (mutual), 
+or mut - Asymmetric (non-mutual), 
+or asym, 
+and - Absent, or null
 
@@
 
-Classifies all triads in the network. The triad
-census provides a fundamental descriptive insight
-into the types of triads found in a particular
-smugEL_
+Classifies all triads in the network. 
+The triad census provides a fundamental descriptive insight into the types of triads found in a particular dataset.
 
 ```{r statnet: Triad Census, echo=TRUE}
-
-#     Classify all Triad in the network: Directed Network
-
-  sna::triad.census(smugEL_sn, mode= )
 
@@
 
-#     weighted network transitivity:
-#   igraph::transivity(smugEL_ig)
-
 ```
@@
 ## Local Transivity or Clustering
-
-`Local transitivity` (local clustering
-coefficient), is a technical description of the
-density of an ego network.
+`Local transitivity` (local clustering coefficient), is a technical description of the density of an ego network.
 
@@
 #     Retrive a list of the vertices we are interested
-    V(smugEL_ig)[c("node 1" ,
-                "node 5", 
-                "node 6",
-                "node 2")]
+    V(smugEL_ig)[c("Bischeri" ,
+                "Castellani", 
+                "Medici",
+                "Ridolfi")]
 
@@
              vids=V(smugEL_ig)
-             [c("node 1",
-                "node 5", 
-                "node 6",
-                "node 2")]) 
+             [c("Bischeri",
+                "Castellani", 
+                "Medici",
+                "Ridolfi")]) 
 #     get global clustering cofficient
@@
 
-7.  *connectedness and.or component structure,
-    etc.*
+## Component Structure and Isolates
+
+```{r Statnet: Isolates, echo=TRUE}
+
+              ## Isolates:
+
+ #List the isolates
+ isolates(smugEL_sn)
+
+ # Returns a list of the isolates in the graph or graph set
+ isolates(smugEL_sn, diag=FALSE)
+
+ # Is Ego an Isolate?
+ is.isolate(smugEL_sn, ego, g=1, diag=FALSE)
+
+ # Adds n isolates to the graph (or graphs)
+ add.isolates(smugEL_sn, n, return.as.edgelist = FALSE)
+
+```
+
+```{r igraph: Component Structure, echo=TRUE}
+                ## Component Structure:
+
+    # Number of components
+ igraph::components(smugEL_ig)$no
+
+  # Size of each component
+ igraph::components(smugEL_ig)$csize
+
+```
+
+## Network Density
+
+ The density of a network is defined as the proportion of ties present out of all possible ties in a network.
+
+ **Note:**
+
+ the network density command ignores edge values at present.
+
+ If loops are present or there are multiple edges between two nodes, then the results may not make sense.
+
+```{r Statnet, echo=TRUE}
+
+# get network density: with possible loops
+ network.density(smugEL_sn)
+
+ # get network density without loops: statnet
+ gden(smugEL_sn, diag=FALSE)
+
+```
+
+ **Igraph** provides an incorrect density calculation as the default assumes  that loops are not included but does not remove them.
+
+ Therefore, the default calculation includes the loops in the numerator but not the denominator of the density calculation.
+
+```{r igraph: network density, echo=TRUE}
+#get network density without loops: igraph
+ network.density(smugEL_ig,loops=TRUE)
+
+ # get network density
+ network.density(smugEL_ig)
+ # provides an incorrect density calculation as the default assumes that loops are not included but does not remove them
+
+```
+
+## Vertex Degree
+ **Vertex degree** is a description of an individual node; each vertex in a network may have a different node degree.
+
+ *Node Degree:*
+   node degree is one measure of node centrality or popularity; 
+ Node degree cis a count of the relationships that a node is involved in or the count of the edges that are incident to a vertex
+
+ **use the network degree command to:**
+   *  compute network summary statistics (such as average network degree);
+ *  graph the network degree distribution; or
+ *  identify particular nodes (such as the five nodes with the most contacts).
+
+```{r Statnet: Vertex Degree, echo=TRUE}
+
+      # statnet: Calculate average network degree
+
+  sna::degree(smugEL_sn)
+          # ignores loops or self-nominations
+
+```
+
+```{r igraph: Vertex Degree, echo=TRUE}
+# igraph: Calculate average network degree
+ # provides node name along with node degree
+
+ # includes loops
+ igraph::degree(smugEL_ig)
+
+```
+
+## Network Degree Summary Statistics
+
+```{r Statnet: , echo=TRUE}
+      # Basic R: get summary statistics for node attributes
+ summary(network_nodes)
+      # provides range, mean, median and standard deviation of a vector.
+
+ # get summary statistics for node degree for the binary network degree
+
+ summary(data.frame(
+   name=smugEL_sn%v%"vertex.names",
+   totdegree=sna::degree(smugEL_sn),
+   indegree=sna::degree(smugEL_sn, cmode="indegree"),
+   outdegree=sna::degree(smugEL_sn, cmode="outdegree")
+ ))
+
+```
+
+#Visualizations
+
+## igraph Visualizations
+igraph provides three different ways for visualization.
+```{r igraph: , echo=TRUE}
+
+plot.igraph(smugEL_ig)
+
+ # uses regular R graphics and can be used with any R device.
+
+#  (Tk is quite resource hungry, so don't try this for very large graphs.)
+
+ tkplot(smugEL_ig)
+
+```
+
+```{r Statnet: Visualization, echo=TRUE}
+
+ # add in vertex labels and change the size and color of these labels
+ gplot(smugEL_sn, 
+       displaylabels=TRUE,
+       label.cex=.75, 
+       label.col="black"
+ )
+
+ # For directed graphs, you can turn off the arrows
+ gplot(smugCovIdx, 
+       displaylabels=TRUE, 
+       label.cex=.75, 
+       label.col="black", 
+       usearrows = FALSE)
+
+ # differentiate nodes based on their attributes
+ gplot(smugEL_sn, 
+       displaylabels=TRUE,
+       label.cex=.75,
+       label.col="black",
+       vertex.col=att$dnkName
+ )
+
+ legend("bottomleft",
+        fill=0:4,
+        legend=paste("DEPT",0:4),
+        cex=0.75
+ )
+
+ # changed the shape of the nodes based on the level of their positions. 
+ ## You change the shape of the nodes by specifying the number of sides you want the shape to have using the vertex.sides argument. 
+ gplot(smugEL_sn, 
+       displaylabels=TRUE,
+       label.cex=.75,
+       label.col="black",
+       vertex.cex = 2,
+       vertex.sides=(att$LEVEL+2)
+ )
+
+```
+
+```{r Statnet: , echo=TRUE}
+
+```
+
+## Visualization: ggplot2
+```{r Visualization: ggplot2}
+
+# Dependencies
+ library(network)
+ library(sna)
+ library(ggplot2)
+
+library(visNetwork)
+library(threejs)
+ library(networkD3)
+ library(ndtv)
+ # ggnetwork - This package allows to pass network objects to ggplot2 and provides geometries to plot their elements.
+
+ library(ggnetwork)
+
+  # visualize your network graphs 
+ library(GGally)
+
+## [network visualization with ggplot2]
+
+```
+
+#
+```{r Statnet: , echo=TRUE}
+
+```
+
+```{r igraph: , echo=TRUE}
+
+```
 

### 2022-02-16 docs/3. SNA - Assignments/sna_Week3/week3_AssignmentNotes.R

@@ -229,9 +229,9 @@ summary.network(network-EXAMPLEet,print.adj = FALSE)
  
  print()
  
- 
- # Dyad Census:
- 
+ ######
+          # Dyad Census:
+ ######
  #Classify all dyads in the network: igraph
  igraph::dyad.census(EXAMPLE.ig)
  
@@ -525,6 +525,8 @@ summary.network(network-EXAMPLEet,print.adj = FALSE)
  
  groupby()%>%
    group_indices(.data, ...))
+######
+ 
  
  ### Plotting Distributions
  
@@ -820,95 +822,4 @@ summary.network(network-EXAMPLEet,print.adj = FALSE)
  install.packages("networkD3")
  install.packages("ndtv")
  #######
-        ###### Statnet: Visualization
- #######
- The statnet package also allows for you to easily visualize your network graphs with the gplot function.
- 
- ```{r}
- 
- # visualize your network graphs 
- gplot(network-EXAMPLE)
- 
- # add in vertex labels and change the size and color of these labels
- gplot(network-EXAMPLE, 
-       displaylabels=TRUE,
-       label.cex=.75, 
-       label.col="black"
- )
- 
- # For directed graphs, you can turn off the arrows
- gplot(network-EXAMPLE, 
-       displaylabels=TRUE, 
-       label.cex=.75, 
-       label.col="black", 
-       usearrows = FALSE
- )
- 
- # differentiate nodes based on their attributes
- gplot(network-EXAMPLE, 
-       displaylabels=TRUE,
-       label.cex=.75,
-       label.col="black",
-       vertex.col=att$DEPT
- )
- 
- legend("bottomleft",
-        fill=0:4,
-        legend=paste("DEPT",0:4),
-        cex=0.75
- )
- 
- # changed the shape of the nodes based on the level of their positions. 
- ## You change the shape of the nodes by specifying the number of sides you want the shape to have using the vertex.sides argument. 
- gplot(network-EXAMPLE, 
-       displaylabels=TRUE,
-       label.cex=.75,
-       label.col="black",
-       vertex.cex = 2,
-       vertex.sides=(att$LEVEL+2)
- )
- 
- ```
- 
- 
- 
- graph provides three different ways for visualization
- ```{r}
- # igraph Visualizations
- 
- plot.igraph()
[…]

### 2022-02-16 docs/3. SNA - Assignments/sna_Week3/week3_Scrap.R

@@ -1,5 +1,6 @@
 
 # Week 1: *Describe Network Data*
+######
 ## 1. **List and inspect:** 
 List the objects to make sure the datafiles are working properly:
   ```is()
@@ -115,9 +116,7 @@ Names- Edge Attributes
 Names- Edge Attributes
 ```network::list.edge.attributes(climate.stat)
 ```
-
-
-
+#######
 
 # Week2: *Network Structure: Overview*
 - Dyads and Dyad Census
@@ -152,80 +151,79 @@ Classifies all dyads in the network as:
 ```  
 **[statnet]**
   ```sna::dyad.census(gotbook.stat
-                      ```
-                      
-                      ## **Triad Census**
-                      Classifies all triads in the network
-                      
-                      **[igraph]**
-                        ``` igraph::triad_census(gotbook.ig)
-                      ```
-                      **[statnet]**
-                        Undirected Network
-                      ``` sna::triad.census(gotbook.stat, mode="graph")```
-                      Directed Detwork
-                      ``` sna::triad.census(gotbook.stat, mode=)```
-                      
-                      ## Transitivity: **Global Clustering**
-                      
-                      network transitivity:
-                        **[igraph]**
-                        ``` transitivity(gotbook.ig)
-                      ```
-                      weighted network transitivity:
-                        ```igraph::transivity()
-                      ```
-                      
-                      **[statnet]**
-                        weighted network transitivity:
-                        ``` sna::gtrans()
-                      ```
-                      For Directed Networks - network structure rooted in hierarchy
-                      ```gtrans()
-                      ```
-                      
-                      
-                      ## Transivity: **Local Clustering**
-                      
-                      **[igraph]**
-                        
-                        1. Retrieve a list of the three vertices we are interested  
-                      
-                      ``` V(gotbook.ig)
-                      [c(
-                        "vertex_attr_names",
-                        "vertex_attr_names",
-                        "vertex_attr_names"
-                      )]
-                      ```
-                      
-                      2. Check ego network transitivity
-                      
-                      ```transitivity(
-                        gotbook.ig,
-                        type="local",
-                        vids=V(gotbook.ig)
-                        [c(
[…]

### 2022-02-16 docs/3. SNA - Assignments/sna_Week3/Week3_Notebook.Rmd
2.16.22
graph's n stuff

@@
                     #2nd passIt
-passIt$substring_first <- 
-  str_extract(passIt$X5,"(\\w+)")
+passIt$substring_first <- str_extract(passIt$X5,"(\\w+)")
 
@@
   smugCovIdx
+            colname: "dnkName" "dnkIng"  "ingType"
   network_nodes <- smugCovIdx << "dnkName"
@@
   IGRAPH: smugEL_ig
+
+  Edge Vetex:
+              dnkName
+  Edge Attributes:
+                  dnkIng
+                  ingType
 
@@
       #   summarize: numeric network attribute
-  summary(smug_sn%v%"dnkName")
+  summary(smugEL_sn%v%"dnkName")
 
@@
 
+## igraph: Exploring Network
+
+```{r}
+library("igraph")
+
+```
+IGRAPH 574c3d4 UN-- 274 672 -- 
++ attr: name (v/c), 
+        dnkName (v/c), 
+        dnkIng (e/c),
+      | ingType (e/c)
++ edges from 574c3d4 (vertex names):
+
 #   Week 2: Basic Network Structure: Smuggler's Cove Drink Index
+We can break large social networks down into their constituent parts.
+These constituent parts are referred to as “motifs”.
+The most basic motif consists of two nodes and is called a dyad.
+Edges in a network signify the presence or absence of dyadic relations.
+It follows that a dyad in an undirected network can have two unique configurations: connected or disconnected; and three unique configurations in a directed network (mutual, assymetric, and null)
 
@@
 ## Dyad Census
+
 Classifies all dyads in the network as: - 
@@
 
-  igraph::dyad.census(smugEL_ig)
+graph.density(smugEL_ig)
+    ## Density captures, at the macro-level, the proportion of dyads that are present over the possible total number of dyads in the network
+
+      # Generating a random graph for comparison
+# ?erdos.renyi.game
+      ## In an erdos.renyi.graph, each edge has the same probability of being created.
+We determine the probability and it returns a random graph with a density that equals (in expectation) this probability.
+
+smugEL_igNod <- vcount(smugEL_ig)
+
+smugEL_igDen <- graph.density(smugEL_ig)
+
+smugEL_igRandoG <- 
+  erdos.renyi.game(
+    n = smugEL_igNod, 
+    p.or.m = smugEL_igDen, 
+    directed = F) 
+      # where n is the number of nodes, 
+      # p.or.m is the probability of drawing an edge, 
+      #directed is whether the network is directed or not
+
+#**plot(smugEL_igRandoG, ...** in .R notebook  
+     # vertex.size = 5, 
+     # vertex.label = 1, 
+     # edge.curved = .1, 
+     # vertex.color = "tomato", 
+     # edge.arrow.size = .1, 
+     # edge.width = .5, 
+     # edge.color = "grey60")
 
@@
 `Local transitivity` (local clustering coefficient), is a technical description of the density of an ego network.
+```{r iGraph: Transitivity: Network}
+#     get global clustering cofficient
+  transitivity(smugEL_ig, type="global")
 
-```{r iGraph:Local transitivity, echo=TRUE}
+#     get average local clustering coefficient
+  transitivity(smugEL_ig, type="average")
+
+```
+
+```{r iGraph:Local transitivity: Node List & Ego Network, echo=TRUE}
 
@@
                 "Ridolfi")]) 
-#     get global clustering cofficient
-  transitivity(smugEL_ig, type="global")
-
-#     get average local clustering coefficient
-  transitivity(smugEL_ig, type="average")
-
 ```
@@
  # Is Ego an Isolate?
- is.isolate(smugEL_sn, ego, g=1, diag=FALSE)
+ is.isolate(smugEL_sn, ego_exp, g=1, diag=FALSE)
 
  # Adds n isolates to the graph (or graphs)
- add.isolates(smugEL_sn, n, return.as.edgelist = FALSE)
+ add.isolates(smugEL_sn, n_umber, return.as.edgelist = FALSE)
 
@@
  igraph::components(smugEL_ig)$no 
+      ##**NOTE:** $no prevents a list of comonents from being printed
 
@@
 
-```{r Statnet, echo=TRUE}
+```{r Statnet: Network Density, echo=TRUE}
 
@@
    network.density(smugEL_sn)
+          ##**WARNING: Network is multiplex - no general way to define density.**
 
- # get network density without loops: statnet
- gden(smugEL_sn, diag=FALSE)
+ # get network density **with** loops: statnet
+ gden(smugEL_sn, diag=F)
 
@@
 ```{r igraph: network density, echo=TRUE}
-#get network density without loops: igraph
- network.density(smugEL_ig,loops=TRUE)
 
- # get network density
+    #get network density **with** loops
  network.density(smugEL_ig)
- # provides an incorrect density calculation as the default assumes that loops are not included but does not remove them
+ class(smugEL_ig)
+          ##**NOTE** provides an incorrect density calculation 
+          ## as the default assumes that loops are not included but does not remove them
 

### 2022-02-16 docs/3. SNA - Assignments/sna_Week3/week3_Plots.R

@@ -1,0 +1,121 @@
+
+###############
+              ##### Plotting: iGraph
+###############
+library(igraph)
+#####
+#####
+          #  read a summary of it by typing its name into R
+smugEL_ig
+
+          # View values in “name” attribute with the V()$ function.
+ print(V(smugEL_ig)$name)
+
+ #####
+      ### plot: basic R 
+      plot(smugEL_ig)
+ 
+      #####
+        ###**Plot Name: smugIG_plot-R_blue-curved-small*
+#####
+plot(smugEL_ig, 
+     vertex.size=3,
+     vertex.color = "blue",
+     vertex.frame.color = NA,
+     vertex.label = NA,
+     edge.curved = 1.7,
+     edge.arrow.size = .3, 
+     edge.width = .5)
+      #####
+        ###**Plot: Kamada Kawai **
+            ###**Plot Name** igraph_kamadaLayout_smug
+######
+      # run the layout function on our graph
+ 
+ kamadaLayout <-
+   layout.kamada.kawai(smugEL_ig)
+ 
+        # change the default layout setting to equal the layout we generated above
+ plot(smugEL_ig, 
+      layout = kamadaLayout, 
+      vertex.size = 3, 
+      vertex.color = "black", 
+      vertex.frame.color = NA, 
+      vertex.label.cex = .7,  
+      vertex.label = NA, 
+      edge.curved = .3, 
+      edge.arrow.size = .1, 
+      edge.width = .5)
+ 
+    ##### 
+      ###**Plot: Frucherman-Reingold **
+   ###**Plot Name** igrap-smugEL_Frucherman-Reingold
+#####
+      # run the layout function on our graph
+ fruchtermanLayout <- 
+   layout.fruchterman.reingold(smugEL_ig)
+ 
+ # and then we change the default layout setting to equal the layout we generated above
+ plot(smugEL_ig,
+      layout = fruchtermanLayout, 
+      vertex.size = 2, 
+      vertex.color = "green", 
+      vertex.frame.color = NA, 
+      vertex.label.cex = 1,  
+      vertex.label = NA, 
+      edge.curved = 5, 
+      edge.arrow.size = .1, 
+      edge.width = .1)
+  
+    #####
+   
+###############
[…]

### 2022-02-19 docs/3. SNA - Assignments/Week3-Distill-Blog_Degree-and-Centrality.Rmd
11.??.22
I took a break

---
title: "Social Network Analysis: Week 3: Degree and Centrality"
description: " "
author:
  - name: "Audra Jamai White" 
    url: 
    affiliation: "Umass Amherst - DACSS 679: Social Network Analysis"
    affiliation_url: 
date: "`r Sys.Date()`"
output: distill::distill_article
---

```{r setup, Libraries, include=FALSE}
knitr::opts_chunk$set(include = FALSE)
# Document Creation
library(knitr)
library(markdown)
library(yaml)
library(distill)
library(blogdown)
```

## *Briefly describe Smuggler's Cove Drink Index dataset:*

[Smuggler's Cove](https://www.smugglerscovesf.com/#about-section)

:   is a legendary cocktail bar in San Francisco.
    Since opening in 2009, this Tiki Bar has
    developed a dedicated following and received
    many awards. What do people in the restaurant
    industry do when they receive any modicum of
    celebrity?

    *Release a recipe book - of course !*

    It's not like a bar boasting about" featuring
    the largest rum selection in the United
    States, and cocktails from over three
    centuries of rum history" has to worry about
    one of their customers (or competitors) being
    able to replicate their [highly specialized
    bar
    menu](https://www.smugglerscovesf.com/menu).

    The [Smuggler's Cove: Exotic Cocktails, Rum,
    and the Cult of
    Tiki](https://www.smugglerscovesf.com/#book-section)
    book does provide cocktail aficionados and
    home-mixologists with an education in the
    history of rum and "tiki drinks"; along with
    over 80 recipes to inspire our #HomeBarGoals

[Smuggler's Cove Recipe Book Index](https://docs.google.com/spreadsheets/d/1W5eaejaZ9MOu3I36R9TZIus7xlHhkX7JonmBzGHXnTI/edit#gid=942764477)

:   The overlap between [(tech-bros /
    data-nerds) + ((Eldrich) Millennials,
    X-ennials)) + (high class bar flies) ] isn't a
    perfect circle; But it is a very enmeshed Venn
    Diagram!

    Like, any other group creating a 21st social
    nice by relying on pretentiously inaccessible
    hobbies as the basis of social capitol to
    create a hobby to base one's social identity
    on -- there's a sub reddit to share pictures,
    memes, and datasets with like-minded folks.

    [Thanks
    el_joker1](https://www.reddit.com/r/cocktails/comments/5um8zh/smugglers_cove_tiki_cocktail_book_index/)
    !!! I wonder how many other cocktail+data
    geeks have played around with this CVS?

[Network Dataset: Smuggler's Cove Index](https://docs.google.com/spreadsheets/d/1W5eaejaZ9MOu3I36R9TZIus7xlHhkX7JonmBzGHXnTI/edit#gid=942764477)

:   The CSV is a pretty small data set. The
    source.csv contains 6 columns and hundreds of
    rows.

    My network dataset contains 3 columns: Drink
    Name, Drink Ingredient, and Ingredient Type
    (Juice, Rum, Bitters, Fruit, ect).

    These three categories are used to develop and
    Edge list with a small number of redundant
    edge attributes.

# Does a Recipe Book Contain Network Data?

I like to think so.

The network data contained in a cocktail recipe
book can serve as a proxy for some of the more
traditional elements of social network analysis.

![](https://media.giphy.com/media/3o7TKJhutMCl75fkLm/giphy.gif)

Recipes (and recipe meta data) are all a part of
the the larger super-structure of "things humans
eat". Recipe books can be viewed as a codex of
specific elements of specific food cultures[^1].
The elements of recipes in a cookbook have a
relationship to each other because they're are a
part of a curated collection - but that
relationship is defined more by the social facts
of the author's food culture(s) than the
individual decisions.

> *How do the social facts of and author's food
> culture shape their recipe selection?*
>
> The author's of[Smuggler's
> Cove](https://www.smugglerscovesf.com/#about-section)
> could not have opened their bar in a place where
> the community's alcohol food taboo is codified
> in the law, which could be many places - all of
> which are not San Francisco. Since the authors
> did live in California during the early 21st
> century they were exposed to the 21st century
> cocktail culture revival. The ability for the
> authors to write about [Exotic Cocktails, Rum,
> and the Cult of
> Tiki](https://www.amazon.com/Smugglers-Cove-Exotic-Cocktails-Cult/dp/1607747324)
> is wholly contingent upon recreational
> consumption of the alcohol being a deeply
> ingrained element of San Francisco's food
> culture - which developed a cocktail focused
> sub-culture.
>
> When "Prohibition" was a social fact in the
> early 20th century U.S.A. the legally codified
> alcohol taboo was an element of the larger
> culture's class stratification and racial cast
> system. The perpetrators of Temperance Movement
> restricted alcohol access as a means of social
> control - specifically, the socially
> undesirable. While their social betters enjoyed
> the privileged of maintaining (extra)legal
> access to alcohol. This period's cocktail
> culture being determined by access to alcohol
> could be used as a proxy for examining proximity
> to political power during the Temperance
> Movement. Besides the venn diagram of
> communities target by the Temperance Movement
> and the target populations of nascent eugenics
> movement quite possibly being just one circle -
> elements of cocktail culture can serve as a
> proxy to explore network dynamics of early 20th
> pre-globalized international markets, in
> addition to agricultural products immediately
> before The Dust Bowl and advent of
> refrigeration.

#  So What ?

Every time-period has it's own "cocktail culture",
which can be viewed as a network of period-related
products, technological practices, and culinary
aesthetics manifesting in each element of a
cocktail recipe.

I'm curious to find how Drink Names are linked to
each other by sharing ingredients.

##

1.  <div>

    > -   identify initial network format;
    >
    > -   describe and identify the nodes
    >     including:
    >
    >     -   how many nodes are in the dataset;
    >
    > -   what constitutes a tie or edge
    >     including:
    >
    >     -   how many ties,
    >
    >     -   whether ties are
    >         directed/undirected,
    >
    >     -   whether ties are weighted/binary,
    >
    >     -   and how to interpret the value of
    >         the tie if any.
    >
    >     -   Whether or not there are edge
    >         attributes that might be used to:
    >
    >         -   subset data, or
    >         -   stack multiple networks.

    </div>

## Working from the example R syntax:

1.  calculate network density;

2.  degree centrality, and

3.  centralization measures for your network data.

    | Col1 | Col2 | Col3 |
    |------|------|------|
    |      |      |      |
    |      |      |      |
    |      |      |      |

    : Network Maeasure

## *Write up your results briefly:*

-   focus on interpretation of the results.
-   Don't list statistics or provide code,
-   **the goal is to choose a few interesting
    results and provide an interpretation.**

##

## *Provide at least two or three noteworthy results*, including:

1.  the relevant statistics and interpretation.
    For example, explaining which node(s) are most
    central and which are least central.
2.  Discuss (with any related evidence) whether or
    not the node(s) behavior is in line with or
    violates expectations based on the degree
    centrality measure.
3.  What do you make of network density and
    centralization measures?\
4.  What about differences in the binary 100
    million threshold network vs valued trade
    flows network.
5.  Check tutorial for other ideas of results to
    discuss.

> Distill is a publication format for scientific
> and technical writing, native to the web.
>
> Learn more about using Distill for R Markdown at
> <https://rstudio.github.io/distill>.

[^1]: *sFood Culture?*

    The differentiating elements between food
    cultures are what a community eats, how food
    is prepared, when food is prepared, why it's
    prepared a certain way, who prepares the food,
    and who consumes the food. All of which
    combine to create food taboos and culinary
    traditions - the social facts informing a
    foundational aspect of daily life.

    Humans are wild! Throughout time and space we
    have integrated an assortment of plants,
    animals, insects, fungi, and minerals into
    idiosyncratic food cultures. The consumables
    in food culture are particular while the
    technological methods of preparation and
    preservation are shared. Foods are consumed
    raw or cook. Cooked foods can be boiled,
    roasted, baked, or fried. Food preservation
    methods are equally limited. Perishables are
    dried, cured (salt, smoke, sugar, acid, ect.),
    and fermented.[We love to ferment
    things!](https://fermentationassociation.org/fermentation-in-anthropology/)

    Most of my favorite foods are fermented-
    bread, cheese, pickles, booze. Anything can be
    fermented, but fermenting liquids - grain
    mash, plant juice, milk, honey- into beverages
    seems to be universal. The wildest thing and
    our love of fermentation liquids is that the
    end product usually contains a toxin -
    alcohol!

    I'm sure several someone's have researched why
    humans love to create and imbibe intoxicants
    a.k.a poison -[at least we're not the only
    ones.](https://youtu.be/A0Xsqo-n_AE)

### 2022-02-19 docs/3. SNA - Assignments/sna_Week3/Week3_Notebook.Rmd
11.??.22
I took a break

@@
                   IGRAPH: smugEL_ig
+                          ingTypeEL_Dig
 
-```{r EDGELIST: Network Objects: statnet & igraph, include=FALSE}
+```{r EDGELIST: UNDIRECTED Network Objects: statnet & igraph, include=FALSE}
 
@@
 
+```{r EDGELIST: IGRAPH: DIRECTED Network: ingType, include=FALSE}
+
+#Lets make some network objects
+
+colnames(smugCovIdx) 
+# tell R data should be understood as a matrix
+smug_matrix = as.matrix(smugCovIdx,
+                        matrix.type="edgelist",
+                        directed=FALSE) 
+head.matrix(smug_matrix)
+
+network_edgelist <- smug_matrix
+
+  nodes_ingType <- smugCovIdx 
+    nodes_ingType<- 
+      select(nodes_ingType,ingType)
+view(nodes_ingType)
+        ### View(nodes_ingType)
+
+######
+      ######**igraph** 
+######
+        #igraph object: ingType
+d_network_ig <- 
+  graph.edgelist(
+    as.matrix(
+      smugCovIdx[2:3]), 
+    directed=T)
+
+vertex.attributes(d_network_ig)
+                ## create new edge attribute
+  E(d_network_ig)$dnkIng<-smugCovIdx$dnkIng
+  E(d_network_ig)$dnkName<-smugCovIdx$dnkName
+
+  #create vertex attributes in igraph
+ V(d_network_ig)[match(V(d_network_ig)$ingType,nodes_ingType$ingType)]$ingType<- nodes_ingType$ingType
+
+   View(d_network_ig)
+   head(d_network_ig)
+  summary(d_network_ig)
+  summary(edge_attr(d_network_ig))
+  summary(vertex.attributes(d_network_ig))
+
+   ingTypeEL_Dig <- d_network_ig
+```
+
 ## Smuggler's Cove Index- NETWORK: EDGELIST: Features & Descriptions
@@
 
+```{r STATNET: functions that calculate network-level descriptives}
+library(statnet)
+library(sna)
+
+    #summary of network object, also provides an edge list
+summary(smugEL_sn)$no
+
+    #number of nodes in the network
+network.size(smugEL_sn)
+
+    #number dyads that exist in network (n*(n-1))
+network.dyadcount( smugEL_sn)
+
+    #number of edges present in the network
+network.edgecount( smugEL_sn)
+
+    #network density (edge count/dyad count)
+gden(smugEL_sn)
+  gden(smugEL_sn,
+       diag = T,
+       mode = "graph")
+
+    ##**diag=* 
+    ##boolean indicating whether or not the diagonal should be treated as valid data. 
+        ##*Set this true if and only if the data can contain loops. 
+        ##*diag is FALSE by default.
+    ##**mode="digraph"*
+    ##* string indicating the type of graph being evaluated. 
+    ##* "digraph" indicates that edges should be interpreted as directed; 
+    ##* "graph" indicates that edges are undirected. mode is set to "digraph" by default.
+
+  # grecip calculates the dyadic reciprocity 
+grecip(smugEL_sn) 
+      #proportion of symmetric dyads
+  grecip(smugEL_sn, measure = "dyadic") 
+      # returns the ratio of mutuals to non-null dyads.
+  grecip(smugEL_sn, measure = "dyadic.nonnull") 
+      # the proportion of edges which are reciprocated
+  grecip(smugEL_sn, measure = "edgewise") 
+      # returns the log of the ratio of the edgewise reciprocity to the density
+  grecip(smugEL_sn, measure = "edgewise.lrr") 
+      # The correlation measure may be interpreted as the net tendency for edges of similar relative value (with respect to the mean edge value) to occur within the same dyads. 
+  grecip(smugEL_sn, measure = "correlation")
+
+      # k-path or k-cycle  compute census statistics (respectively) on one or more input graphs
+      ## In addition to aggregate counts of paths or cycles, results may be disaggregated by vertex and co-membership information may be computed.
+
+Usage
+
+  #**kpath* Count paths of length <=3
+kpath.census(smugEL_sn, maxlen=3,
+             tabulate.by.vertex=FALSE) 
+View(kpath.census(smugEL_sn, tabulate.by.vertex=T))
+
+#**kcycle*Count cycles of length <=3
+kcycle.census(smugEL_sn, maxlen=3, tabulate.by.vertex=FALSE) 
+  View(kcycle.census(smugEL_sn, maxlen=3,tabulate.by.vertex=T))
+
+# counts of cliques by size
+clique.census(smugEL_sn, tabulate.by.vertex=F, enumerate=F)
+view(clique.census(smugEL_sn, tabulate.by.vertex=TRUE, enumerate=TRUE))
+
+```
+
+gtrans(smugEL_sn)
+proportion of transitive triads
+
+symmetrize( smugEL_sn, rule = "weak") 
+symmetrize so i<->j iff i->j OR i<-j
+
+symmetrize( smugEL_sn, rule = "strong") 
+symmetrize so i<->j iff i->j OR i<-j
+
+dyad.census(smugEL_sn) 
+MAN dyad census
+
+triad.census(smugEL_sn) 
+standard directed triad census
+
 ```{r igraph: Network Description, echo=TRUE}
-
+library(igraph)
       # class of an object
-    class(smugEL_ig )
+    class(smugEL_ig)
 
@@
 
-## igraph: Exploring Network
+```{r IGRAPH: DIRECTED Network: ingType, echo=TRUE}
 
-```{r}
-library("igraph")
+      # class of an object
+    class(ingTypeEL_Dig)
+
+## Network Size
+
+      # Count Vertices
+    vcount(ingTypeEL_Dig)
+
+      # Count Edges
+    ecount(ingTypeEL_Dig)
+
+## Network Mode
+    # Bipartitie / Unimodal
+    is_bipartite(ingTypeEL_Dig)
+
+## Edges    
+    # Un/directed 
+    is_directed(ingTypeEL_Dig)
+
+    # weighted or unweighted?
+    is_weighted(ingTypeEL_Dig)
+
+    # edge weights
+    E(ingTypeEL_Dig)$weight
+
+## access vertex attributes
+
+    # Generate a list the names of vertex attributes
+  V(ingTypeEL_Dig)$name
+
+    # access edge attribute  names
+  igraph::vertex_attr_names(ingTypeEL_Dig)
+
+    # Generate a list the names of edge attributes  
+  igraph::edge_attr_names(ingTypeEL_Dig)
+
+## Network Attributes
+ summary(ingTypeEL_Dig)
+          # Vertices =  
+          # Directed = 
+          # hyper = 
+          # loops = 
+          # multiple = 
+          # bipartite = 
+          # total edges = 
+                # missing edges =
+                # non-missing edges = 
+          # Vertex attribute names:
+          # Edge Attribute Names:
 
 ```
-IGRAPH 574c3d4 UN-- 274 672 -- 
-+ attr: name (v/c), 
-        dnkName (v/c), 
-        dnkIng (e/c),
-      | ingType (e/c)
-+ edges from 574c3d4 (vertex names):
+
+  # class of an object
+[1] "igraph"
+
+      ## Network Size
+
+  # Count Vertices
+[1] 201
+
+  # Count Edges
+[1] 672
+
+      ## Network Mode
+  # Bipartitie / Unimodal
+     is_bipartite
+[1] FALSE
+
+    ## Edges    
+   # Un/directed 
+     is_directed
+[1] TRUE
+
+  # weighted or unweighted?
+     is_weighted
+[1] FALSE
+
+   # edge weights
+NULL
 
 #   Week 2: Basic Network Structure: Smuggler's Cove Drink Index
-We can break large social networks down into their constituent parts.
-These constituent parts are referred to as “motifs”.
-The most basic motif consists of two nodes and is called a dyad.
-Edges in a network signify the presence or absence of dyadic relations.
-It follows that a dyad in an undirected network can have two unique configurations: connected or disconnected; and three unique configurations in a directed network (mutual, assymetric, and null)
+)
 
@@
 
-```{r iGraph:Network: Path: Shortest, echo=TRUE}
+### Igraph: Undirected
+```{r iGraph: Undirected: Path: Shortest, echo=TRUE}
 
@@
 
-```{r iGraph: Specific Nodes: Path: Shortest, echo=TRUE}
+```{r iGraph: Undirected: Specific Nodes: Path: Shortest, echo=TRUE}
 
@@
 
-```{r iGraph: Specific Nodes: Path: Length, echo=TRUE}
+```{r iGraph: Undirected: Specific Nodes: Path: Length, echo=TRUE}
 
@@
     distances(smugEL_ig,"Bischeri", "Castellani",weights=NA)
+
+```
+### Igraph: Directed
+```{r iGraph: Directed: Path: Shortest, echo=TRUE}
+
+#     find average shortest path for network
+    average.path.length(ingTypeEL_Dig,directed=T)
+
+```
+
+```{r iGraph: Directed:Specific Nodes: Path: Shortest, echo=TRUE}
+
+#     isolating the distances between specific node
+    all_shortest_paths(ingTypeEL_Dig,
+                       "Strozzi","Tornabuoni", 
+                       weights=NA)$res
+## Note: manually tell igraph to ignore edge weights.
+```
+
+```{r iGraph: Directed: Specific Nodes: Path: Length, echo=TRUE}
+
+#     Calculate distances between two nodes
+    distances(ingTypeEL_Dig,"Bischeri","Ridolfi")
+
+#     Calculate distance between two nodes using unweighted edges
+    distances(ingTypeEL_Dig,"Bischeri", "Castellani",weights=NA)
 
@@
 ```
-
-```{r iGraph: Dyad Census, echo=TRUE}
-
+plot(sna::dyad.census(smugEL_sn))
+```{r iGraph: Undirected: GRAPH: Dyad Census, echo=TRUE}
+library(igraph)
 graph.density(smugEL_ig)
@@
 ```
+plot(sna::triad.census(smugEL_sn, mode="graph"))
+plot(sum(sna::triad.census(smugEL_sn, mode="graph")))
 
-```{r iGraph: Triad Census, echo=TRUE}
+```{r iGraph: Undirected: Triad Census: Calculating a triad census, echo=TRUE}
 #Classify all Triad in the network
@@
 
+ plot(igraph::triad_census(smugEL_ig))
+
+```{r iGraph: Undirected:TRIDADS: Banning triads}
+
+```
+
 ## Transitivity or Global Clustering
 
-```{r iGraph: weighted/ network transitivity, echo=TRUE}
+```{r iGraph: Undirected: weighted/ network transitivity, echo=TRUE}
 
@@
 `Local transitivity` (local clustering coefficient), is a technical description of the density of an ego network.
-```{r iGraph: Transitivity: Network}
+```{r iGraph: Undirected: Transitivity: Network}
 #     get global clustering cofficient
@@
 
-```{r iGraph:Local transitivity: Node List & Ego Network, echo=TRUE}
+```{r iGraph: Undirected: Local transitivity: Node List & Ego Network, echo=TRUE}
 
@@
 
-```{r igraph: Component Structure, echo=TRUE}
+```{r iGraph: Undirected: Component Structure, echo=TRUE}
                 ## Component Structure:
@@
 
-```{r igraph: network density, echo=TRUE}
+```{r iGraph: Undirected: network density, echo=TRUE}
 
@@
 
-```{r igraph: Vertex Degree, echo=TRUE}
+```{r iGraph: Undirected: Vertex Degree, echo=TRUE}
 # igraph: Calculate average network degree
@@
       # Basic R: get summary statistics for node attributes
- summary(network_nodes)
+ summary(nodes_ingTypes)
       # provides range, mean, median and standard deviation of a vector.
@@
 
-#Visualizations
+# Centrilization
 
-## igraph Visualizations
-igraph provides three different ways for visualization.
-```{r igraph: , echo=TRUE}
+```{r iGraph: Undirected: DEGREE CENTRALITY: dnkIng}
+library(igraph)
+library(tidyverse)
 
-plot.igraph(smugEL_ig)
+# graph the SMUG network
 
- # uses regular R graphics and can be used with any R device.
+smug_attributes <- smugCovIdx
+smug_edj <- smugCovIdx[2:3]
+View(smug_edj)
+#V1: dnkIng
+#V2: ingType
 
-#  (Tk is quite resource hungry, so don't try this for very large graphs.)
+smugNet <- 
+  graph.edgelist(as.matrix(smug_edj), directed = T)
 
- tkplot(smugEL_ig)
+V(smugNet)$dnkIng <- 
+  smug_attributes$dnkIng[match(V(smugNet)$name, smug_attributes$ingType)]
+
+V(smugNet)$dnkName <- 
+  smug_attributes$dnkName[
+    match(V(
+      smugNet)$name,
+      smug_attributes$dnkIng)
+    ]
+summary(smugNet)
+
+###**PLOT** in .R Doc
+
+```
+
+```{r iGraph: Undirected: DEGREE CENTRALITY: dnkIng}
+library(igraph)
+library(tidyverse)
+
+# graph the SMUG network
+
+smug_attributes <- smugCovIdx
+smug_edj <- smugCovIdx[2:3]
+View(smug_edj)
+#V1: dnkIng
+#V2: ingType
+
+smugNet <- 
+  graph.edgelist(as.matrix(smug_edj), directed = T)
+
+V(smugNet)$ingType <- 
+  smug_attributes$ingType[match(V(smugNet)$name, smug_attributes$ingType)]
+
+V(smugNet)$dnkName <-
+  smug_attributes$dnkName[match(V(smugNet)$name, smug_attributes$dnkName)]
+
+summary(smugNet)
+
+###**PLOT** in .R Doc
+
+```
+
+```{r iGraph: Undirected: DEGREE CENTRALITY: ingType, echo=TRUE}
+# graph the SMUG network
+
+smug_attributes <- smugCovIdx
+smug_edj <- smugCovIdx[2:3]
+View(smug_edj)
+#V1: dnkIng
+#V2: ingType
+
+smugNet <- 
+  graph.edgelist(as.matrix(smug_edj), directed = T)
+
+V(smugNet)$dnkName <-
+  smug_attributes$dnkName[match(V(smugNet)$name, smug_attributes$dnkIng)]
+
+summary(smugNet)
+View(smugNet)
+
+###**PLOT** in .R Doc
 
@@
 and technical writing, native to the web.
->
+
 Learn more about using Distill for R Markdown at
-<https://rstudio.github.io/distill>. ##
+<https://rstudio.github.io/distill. ##
+
+# iGraph Directed Network Object
+
+## Degree Centrality
+We can break large social networks down into their constituent parts.
+These constituent parts are referred to as “motifs”.
+The most basic motif consists of two nodes and is called a dyad.
+Edges in a network signify the presence or absence of dyadic relations.
+It follows that a dyad in an undirected network can have two unique configurations: connected or disconnected; and three unique configurations in a directed network (mutual, assymetric, and null
+
+```{r iGraph: Directed: GRAPH: Dyad Census, echo=TRUE}
+
+graph.density(ingTypeEL_Dig)
+    ## Density captures, at the macro-level, the proportion of dyads that are present over the possible total number of dyads in the network
+
+      # Generating a random graph for comparison
+# ?erdos.renyi.game
+      ## In an erdos.renyi.graph, each edge has the same probability of being created.
+We determine the probability and it returns a random graph with a density that equals (in expectation) this probability.
+
+ingTypeEL_DigNod <- vcount(ingTypeEL_Dig)
+
+ingTypeEL_DigDen <- graph.density(ingTypeEL_Dig)
+
+smugEL_DigRandoG <- 
+  erdos.renyi.game(
+    n = smugEL_igNod, 
+    p.or.m = smugEL_igDen, 
+    directed = T) 
+      # where n is the number of nodes, 
+      # p.or.m is the probability of drawing an edge, 
+      #directed is whether the network is directed or not
+
+#**plot(smugEL_DigRandoG, ...** in .R notebook  
+     # vertex.size = 5, 
+     # vertex.label = 1, 
+     # edge.curved = .1, 
+     # vertex.color = "tomato", 
+     # edge.arrow.size = .1, 
+     # edge.width = .5, 
+     # edge.color = "grey60")
+
+```
+
+```{r iGraph: Directed: Degree Centrality}
+# Degree centrality is calculated using the degree function in R. It returns how many edges each node has.
+view(degree(ingTypeEL_Dig))
+
+ingT_deg <- ingTypeEL_Dig
+V(ingT_deg)$degree <- degree(ingT_deg) # assignment
+
+# plot(ingT_deg, 
+#     vertex.label.cex = .6, 
+#     vertex.label.color = "black", 
+#     vertex.size = V(ingTypeEL_Dig)$degree, 
+#     vertex.label.cex = .2) # sized by degree
+
+```
+
+```{r iGraph: Directed: Betweenness Centrality}
+
+view(betweenness(ingTypeEL_Dig, directed = FALSE))
+
+# view(betweenness(ingTypeEL_Dig, directed = TRUE))
+              # Yeilds 0
+
+ingTypeEL_Between <- ingTypeEL_Dig
+# We can again assign the output of betweenness() to a variable in the network and size the nodes according to it.
+
+V(ingTypeEL_Between)$betweenness <- 
+  betweenness(ingTypeEL_Between, 
+              directed = F)
+
+# plot(ingTypeEL_Between, 
+#     vertex.label.cex = .6, 
+#     vertex.label.color = "black", 
+#     vertex.size = V(ingTypeEL_Between)$betweenness) # sized by betweenness
+
+```
+
+With closeness centrality we again make use of the shortest paths between nodes.
+We measure the distance between two nodes as the length of the shortest path between them.
+Farness, for a given node, is the average distance from that node to all other nodes.
+Closeness is then the reciprocal of farness (1/farness).
+```{r iGraph: UnDirected:  Closeness Centrality}
+
+view(closeness(smugEL_ig))
+
+  # We assign it to a node variable and plot the network, adjusting node size by closeness.
+ingTyp_Cent <- smugEL_ig #**UNDIRECTED **
+
+V(ingTyp_Cent)$closeness <- closeness(ingTyp_Cent)
+
+View(ingTyp_Cent)
+
+# plot(ingTyp_Cent,
+#     vertex.label.cex = .6, 
+#     vertex.label.color = "black", 
+#     vertex.size = V(ingTyp_Cent)$closeness/max(V(ingTyp_Cent)$closeness) * 20)
+
+```
+
+Degree centrality only takes into account the number of edges for each node, but it leaves out information about ego’s alters
+```{r iGraph: Directed: Eigenvector Centrality}
+
+view(evcent(ingTypeEL_Dig)$vector)
+# view(evcent(smugEL_ig)$vector)
+ingTyp_Vector <- ingTypeEL_Dig
+V(ingTyp_Vector)$eigenvector <- evcent(ingTyp_Vector)$vector
+
+# plot(ingTyp_Vector,
+#     vertex.label.cex = .6, 
+#     vertex.label.color = "black", 
+#     vertex.size = V(ingTyp_Vector)$eigenvector/max(V(ingTyp_Vector)$eigenvector) * 20)
+```
+
+ “Interpretively, the Bonacich power measure corresponds to the notion that the power of a vertex is recursively defined by the sum of the power of its alters.
+The nature of the recursion involved is then controlled by the power exponent: positive values imply that vertices become more powerful as their alters become more powerful (as occurs in cooperative relations), while negative values imply that vertices become more powerful only as their alters become weaker (as occurs in competitive or antagonistic relations).”
+```{r iGraph: Directed: Bonacich Centrality}
+
+ingTyp_Cent <- ingTypeEL_Dig
+
+V(ingTyp_Cent)$bonacich <- 
+  power_centrality(ingTyp_Cent, exponent = -2, rescale = T)
+
+V(ingTyp_Cent)$bonacich <- 
+  ifelse(V(ingTyp_Cent)$bonacich < 0, 0, V(ingTyp_Cent)$bonacich)
+```
+
+```{r iGraph: Directed: Page Rank}
+
+ingTyp_Cent <- ingTypeEL_Dig
+
+V(ingTyp_Cent)$page_rank <- page_rank(ingTyp_Cent, directed = TRUE)$vector
+
+```
+
+ plot(ingTyp_Cent,
+     vertex.label.cex = .6, 
+     vertex.label.color = "black", 
+     vertex.size = V(ingTyp_Cent)$page_rank/max(V(ingTyp_Cent)$page_rank) * 20)
+
+```{r FUCK IT: Measure Correlations, eval=FALSE, include=FALSE}
+# extract all the vertex attributes
+all_atts <- 
+  lapply(list.vertex.attributes(ingTyp_Cent),function(x) get.vertex.attribute(ingTyp_Cent,x))
+
+# bind them into a matrix
+all_atts <- 
+  do.call("cbind", all_atts)
+
+# add column nams
+colnames(all_atts) <- 
+  list.vertex.attributes(ingTyp_Cent)
+
+# drop the family variable
+all_atts <- 
+  data.frame(all_atts[,2:ncol(all_atts)])
+
+# convert all to numeric
+all_atts <- 
+  sapply(all_atts, as.numeric)
+
+# produce a correlation matrix
+cormat <- 
+  cor(all_atts)
+
+# melt it using reshape to function melt() to prepare it for ggplot which requires long form data
+setDT(as.data.frame(cormat))
+melted_cormat <- melt(cormat)
+
+ggplot(data = melted_cormat, aes(x=Var1, y=Var2, fill=value)) + 
+  geom_tile() +
+  scale_fill_distiller(palette = "Spectral", direction=-2) +
+  xlab("") +
+  ylab("")
+```
+
+```{r FUCKIT : Centralization and Degree Distributions, eval=FALSE, include=FALSE}
+# extract all the vertex attributes
+all_atts <- lapply(list.vertex.attributes(ingTyp_Cent),function(x) get.vertex.attribute(ingTyp_Cent,x))
+# bind them into a matrix
+all_atts <- do.call("cbind", all_atts)
+# add column nams
+colnames(all_atts) <- list.vertex.attributes(ingTyp_Cent)
+# drop the family variable
+all_atts <- data.frame(all_atts[,2:ncol(all_atts)])
+# convert all to numeric
+all_atts <- sapply(all_atts, as.numeric)
+# produce a correlation matrix
+cormat <- cor(all_atts)
+
+as.data.table(cormat)
+
+view()
+# melt it using reshape to function melt() to prepare it for ggplot which requires long form data
+melted_cormat <- melt(cormat)
+ggplot(data = melted_cormat, aes(x=Var1, y=Var2, fill=value)) + 
+  geom_tile() +
+  scale_fill_distiller(palette = "Spectral", direction=-2) +
+  xlab("") +
+  ylab("")
+```

### 2022-02-19 docs/3. SNA - Assignments/sna_Week3/week3_Dig_Plots.R

@@ -1,0 +1,252 @@
+
+
+
+
+
+
+plotIngType <- ingTypeEL_Dig
+
+######
+      ### iGraph: Directed: Degree Centrality
+######
+ingTypeEL_Dig
+
+plot(ingT_deg, 
+     vertex.size = V(ingT_deg)$degree*2, # sized by degre
+     vertex.color = "PINK",
+     vertex.frame.color = "PURPLE",
+     vertex.label.cex = .75, 
+     vertex.label = NA, 
+     edge.width = 6,
+     edge.color = "blue",
+     edge.arrow.size = .01) 
+
+
+vertex.size=3,
+vertex.color = "blue",
+vertex.frame.color = NA,
+vertex.label = NA,
+edge.curved = 1.7,
+.3, 
+edge.width = .5)
+      ######
+######
+      ### iGraph: Directed: Betweenness Centrality
+######
+
+plot(ingTypeEL_Between, 
+     vertex.size = V(ingTypeEL_Between)$betweenness, # sized by betweenness
+     vertex.color = "blue",
+     vertex.frame.color = "grey",
+     vertex.label.cex = .6, 
+     vertex.label = NA, 
+      edge.width = .5, 
+     edge.color = "orange",
+     edge.arrow.size = .01,
+     edge.curved = 2) 
+
+      #####
+######
+### iGraph: UnDirected: UnDirected:  Closeness Centrality
+######
+plot(ingTyp_Cent,
+     vertex.label.cex = .6,
+     vertex.color = "blue",
+     vertex.frame.color = "purple",
+     vertex.size = V(ingTyp_Cent)$closeness/max(V(ingTyp_Cent)$closeness) * 20,
+     vertex.label = NA, 
+     edge.width = .5, 
+     edge.color = "purple",
+     edge.arrow.size = .01,
+     edge.curved = .75) 
+        ######
+
+######
+### iGraph: Directed: Eigenvector Centrality
+######
+
+plot(ingTyp_Vector,
+     vertex.size = V(ingTyp_Vector)$eigenvector/max(V(ingTyp_Vector)$eigenvector)*100,
+     vertex.label = NA,
+     vertex.color = "pink",
+     vertex.frame.color = "green",
+     edge.width = .5, 
+     edge.color = "black",
+     edge.arrow.size = .5)
+     
+
+######
+### iGraph: Directed: Bonacich Centrality
+######
+
+plot(ingTyp_Cent,
[…]

### 2022-02-19 docs/3. SNA - Assignments/sna_Week3/week3_Plots.R

@@ -14,6 +14,7 @@ smugEL_ig
  #####
       ### plot: basic R 
       plot(smugEL_ig)
+      plot(ingTypeEL_Dig)
  
       #####
         ###**Plot Name: smugIG_plot-R_blue-curved-small*
@@ -46,7 +47,6 @@ plot(smugEL_ig,
       edge.curved = .3, 
       edge.arrow.size = .1, 
       edge.width = .5)
- 
     ##### 
       ###**Plot: Frucherman-Reingold **
    ###**Plot Name** igrap-smugEL_Frucherman-Reingold
@@ -56,17 +56,16 @@ plot(smugEL_ig,
    layout.fruchterman.reingold(smugEL_ig)
  
  # and then we change the default layout setting to equal the layout we generated above
- plot(smugEL_ig,
-      layout = fruchtermanLayout, 
-      vertex.size = 2, 
-      vertex.color = "green", 
-      vertex.frame.color = NA, 
-      vertex.label.cex = 1,  
-      vertex.label = NA, 
-      edge.curved = 5, 
-      edge.arrow.size = .1, 
-      edge.width = .1)
-  
+ 
+ plot(smugNet, 
+      vertex.size = 6, 
+      vertex.color= "orange",
+      vertex.label.cex = .5, 
+      vertex.label.color = "black", 
+      edge.with = .5,
+      edge.curved = 5,
+      edge.arrow.size = 0.1)
+ 
     #####
    
 ###############
@@ -117,5 +116,36 @@ plot(smugEL_ig,
         #####
       
 ###############
-                ##### Plotting:
+                ##### Plotting: igraph: DEGREE CENTRALITY
 ###############
+######
+      ###**Plot: base R *
+      ###**Plot Name: Degree Centrality: dnkIng*
+######      
+      plot(smugNet, 
+           vertex.size = 8, 
+           vertex.label = NA,
+           vertex.color = "orange", 
+           edge.color = "blue",
+           edge.width = 2,
+           edge.arrow.size = 0.5,
+           edge.curved = 1)
+      
+      plot(smugNet, 
+           vertex.size = 4,
+           vertex.label.size = 1,
+           vertex.color = "gray",
+           edge.color = "blue",
+           edge.widtth = 2,
+           edge.arrow.size = 0.25)
+      
+      #####      
+######
+      ###
+######      
+      #####
+######
+      ###
+######
+      
+      

### 2022-02-19 docs/3. SNA - Assignments/Week3-Distill-Blog_Degree-and-Centrality.Rmd
2.22.22 late on this past weekend's committs

@@
 
-I'm curious to find how Drink Names are linked to
-each other by sharing ingredients.
+![](https://tenor.com/brZQ5.gif){width="2474"
+height="255"}
 
-##
+There is not an organization with the self-imposed
+responsibility and authority to standardize the
+recopies and classification of cocktails while
+maintain records attributing a drinks development
+to a specific bar or bartender. Can we use SNA
+methods to suss out anecdotal aspects of
+contemporary cocktail culture?
 
-1.  <div>
+To start: I'm curious to see what sort of
+relationships exists between Tiki Cocktail
+Ingredients? Cocktails are build with specific
+ingredients, methods, and presentations to fit
+contemporary cocktail culture aesthetics.
 
-    > -   identify initial network format;
-    >
-    > -   describe and identify the nodes
-    >     including:
-    >
-    >     -   how many nodes are in the dataset;
-    >
-    > -   what constitutes a tie or edge
-    >     including:
-    >
-    >     -   how many ties,
-    >
-    >     -   whether ties are
-    >         directed/undirected,
-    >
-    >     -   whether ties are weighted/binary,
-    >
-    >     -   and how to interpret the value of
-    >         the tie if any.
-    >
-    >     -   Whether or not there are edge
-    >         attributes that might be used to:
-    >
-    >         -   subset data, or
-    >         -   stack multiple networks.
+*For example:* "gin goes with lime (not lemon);"
+but why is that? *Short answer:* European
+imperialism and systematic wealth extraction of
+the global south. It's the same reason why my
+Jamaican Grandmother said "kidney beans go in rice
+& peas (not English peas)"
 
-    </div>
+*Another example:* The fictional James Bond being
+cited as an authoritative voice on whether a
+proper Martini's should be shaken or stirred.
+*Short answer:* Cocktails with eggs and milk are
+shaken to create foam. Spirit forward drinks tend
+to be stirred to limit dilution. *You can shake a
+drink with carbonated ingredients if you want to.*
 
-## Working from the example R syntax:
+# What makes a Tiki Drink a "Tiki Drink?"
+
+This isn't the "ask 10 people and get 10 different
+answers" sort of question, but all of the answers
+are based on each person's professionally
+(un)informed opinion. As a former bartender - I
+believe in the authority of the published opinions
+of professional bartenders and [cocktail
+historians](https://www.theatlantic.com/health/archive/2010/06/how-to-be-a-drink-historian/58724/).
+Their opinion is based in direct experience and
+observation of the subject in question. Which is
+the sort of thing empiricists do, but since they
+are building cocktails instead of a dataset, their
+answers are given the same consideration of
+qualitative research.
+
+## To start:
+
+## I'm curious to see what sort of relationships exists between Tiki Cocktail Ingredients?
+
+## Cocktails are build with specific ingredients, methods, and presentations to fit contemporary cocktail culture aesthetics.
+
+### *Write up your results briefly:*
+
+-   focus on interpretation of the results.
+-   Don't list statistics or provide code,
+-   **the goal is to choose a few interesting
+    results and provide an interpretation.**
+
+### Working from the example R syntax:
 
@@
 
-    | Col1 | Col2 | Col3 |
-    |------|------|------|
-    |      |      |      |
-    |      |      |      |
-    |      |      |      |
+<div>
 
-    : Network Maeasure
+> -   identify initial network format;
+>
+>     -   **Smuggler's Cove Index was converted
+>         into an edgelist**
+>
+> -   describe and identify the nodes including:
+>
+>     -   **Smuggler's Cove Edgelist**
+>
+>         -   **Nodes: 274**
+>
+>         -   **Edges: 672**
+>
+> -   what constitutes a tie or edge including:
+>
+>     -   Ties
+>
+>         -   Number:
+>
+>         -   Directed
+>
+>         -   Binary
+>
+>     -   interpret the value of the tie if any.
+>
+>     -    edge attributes that might be used to:
+>
+>         -   subset data, or
+>         -   stack multiple networks.
 
-## *Write up your results briefly:*
-
--   focus on interpretation of the results.
--   Don't list statistics or provide code,
--   **the goal is to choose a few interesting
-    results and provide an interpretation.**
-
-##
+</div>
 
@@
 1.  the relevant statistics and interpretation.
-    For example, explaining which node(s) are most
-    central and which are least central.
+
+    -   For example, explaining which **node(s)
+        are most central and which are least
+        central.**
+
 2.  Discuss (with any related evidence) whether or
-    not the node(s) behavior is in line with or
+    not the **node(s) behavior is in line with or
     violates expectations based on the degree
-    centrality measure.
-3.  What do you make of network density and
+    centrality measure.**
+
+    1.  **What do you make of network density and
         centralization measures?\
-4.  What about differences in the binary 100
-    million threshold network vs valued trade
-    flows network.
-5.  Check tutorial for other ideas of results to
-    discuss.
+        **
+
+        +-----------+--------------+--------+-----------+
+        | Analysis  | statnet      | igraph | Plot      |
+        +===========+==============+========+===========+
+        | Dyad      | Mutual: 1    | 0.0179 | yes       |
+        | Census    |              |        |           |
+        |           | A            |        |           |
+        |           | symmetrical: |        |           |
+        |           | 670          |        |           |
+        |           |              |        |           |
+        |           | Null: 36730  |        |           |
+        +-----------+--------------+--------+-----------+
+        | Triad     | 0: 3216391   |        |           |
+        | Census:   |              |        |           |
+        |           | 1: 7879 0    |        |           |
+        | All       |              |        |           |
+        | Triads in | 2 : 166754   |        |           |
+        | Network   |              |        |           |
+        |           | 3:           |        |           |
+        +-----------+--------------+--------+-----------+
+        | Triad     | 3391024      | (undi  | yes       |
+        | Census:   |              | rected |           |
+        |           |              | graph) |           |
+        | total     |              |        |           |
+        | number of |              | [1]    |           |
+        | all four  |              | 3      |           |
+        | triad     |              | 216659 |           |
+        | types     |              |        |           |
+        |           |              | [2]    |           |
+        |           |              | 166486 |           |
+        |           |              |        |           |
+        |           |              | [11]   |           |
+        |           |              | 7879   |           |
+        +-----------+--------------+--------+-----------+
+        | Tra       | undirected   | Undi   |           |
+        | nsitivity |              | rected |           |
+        +-----------+--------------+--------+-----------+
+        | Local     |              |        |           |
+        | tran      |              |        |           |
+        | sitivity: |              |        |           |
+        | Node List |              |        |           |
+        | & Ego     |              |        |           |
+        | Network   |              |        |           |
+        +-----------+--------------+--------+-----------+
+        | Isolates  | no           |        |           |
+        +-----------+--------------+--------+-----------+
+        | Un        |              | n      |           |
+        | directed: |              | umber: |           |
+        | Component |              | 1      |           |
+        | Structure |              |        |           |
+        |           |              | size:  |           |
+        |           |              | 274    |           |
+        +-----------+--------------+--------+-----------+
+        | Directed: |              | 0.01   | yes       |
+        | GRAPH:    |              | 671642 |           |
+        | Dyad      |              |        |           |
+        | Census    |              |        |           |
+        +-----------+--------------+--------+-----------+
+        |           |              |        | yes       |
+        | Directed: |              |        |           |
+        | Degree    |              |        |           |
+        | C         |              |        |           |
+        | entrality |              |        |           |
+        +-----------+--------------+--------+-----------+
+        | Directed: |              |        | yes       |
+        | Be        |              |        |           |
+        | tweenness |              |        |           |
+        | C         |              |        |           |
+        | entrality |              |        |           |
+        +-----------+--------------+--------+-----------+
+        | Directed: |              |        | yes       |
+        | Ei        |              |        |           |
+        | genvector |              |        |           |
+        | C         |              |        |           |
+        | entrality |              |        |           |
+        +-----------+--------------+--------+-----------+
+        | Directed: |              |        |           |
+        | Bonacich  |              |        |           |
+        | Ce        |              |        |           |
+        | ntrality} |              |        |           |
+        +-----------+--------------+--------+-----------+
+        |           |              |        |           |
+        | Directed: |              |        |           |
+        | Page Rank |              |        |           |
+        +-----------+--------------+--------+-----------+
+        |           |              |        |           |
+        +-----------+--------------+--------+-----------+
+        |           |              |        |           |
+        +-----------+--------------+--------+-----------+
 

### 2022-02-19 docs/3. SNA - Assignments/Week3_Degree-and-Centrality.Rmd
2.22.22 late on this past weekend's committs

--- 2022-02-08 docs/3. SNA - Assignments/Week3-Assignment.Rmd
@@
 
-## Write up your results briefly:
+##        *Write up your results briefly: *
 *   focus on interpretation of the results. 
@@
 
-## Briefly describe the dataset:
+##        *Briefly describe the dataset:*
 1.   identify initial network format; 
@@
             *   stack multiple networks.
-Not every feature of the network needs to be described, but **description should orient reader to the network data and provide any necessary context for the results provided.**
 
-## Provide at least two or three noteworthy results, including:
+##        *Provide at least two or three noteworthy results*, including:
 1.   the relevant statistics and interpretation. 

### 2022-02-22 docs/0. Setting UP Project/Week0_About_Distill-Blog.Rmd

--- 2022-02-19 docs/3. SNA - Assignments/Week3-Distill-Blog_Degree-and-Centrality.Rmd
@@
 ---
-title: "Social Network Analysis: Week 3: Degree and Centrality"
+title: "Social Network Analysis: Week 0: About this dataset"
 description: " "
@@
     url: 
-    affiliation: "Umass Amherst - DACSS 679: Social Network Analysis"
+    affiliation: "UMass Amherst: DACSS 679: Social Network Analysis: Assignments"
     affiliation_url: 
@@
 
-## *Briefly describe Smuggler's Cove Drink Index dataset:*
+## *About the Smuggler's Cove Drink Index dataset:*
 
@@
     Since opening in 2009, this Tiki Bar has
-    developed a dedicated following and received
-    many awards. What do people in the restaurant
-    industry do when they receive any modicum of
-    celebrity?
+    developed a dedicated following, received many
+    awards, and is high-key famous among cocktail
+    corps d'elite.
+
+![](https://media.giphy.com/media/l2JJIQmEvS4hBbnjO/giphy.gif)
+
+[Exotic Cocktails, Rum, and the Cult of Tiki](https://www.smugglerscovesf.com/#book-section)
+
+:   What do people in the restaurant industry do
+    when they receive any modicum of celebrity?
 
@@
 
-The network data contained in a cocktail recipe
-book can serve as a proxy for some of the more
-traditional elements of social network analysis.
+Every time-period has it's own "cocktail culture",
+which can be viewed as a network of period-related
+products, technological practices, and culinary
+aesthetics manifesting in each element of a
+cocktail recipe.
+
+Converting the data and metadata in recipe book
+into network data could serve as a proxy to
+reflect on more conventional network datasets.
+Researchers into business and profitability could
+recipe books cum network data to perform
+historical market research - but all of those
+people are not me.
 
@@
 
-> *How do the social facts of and author's food
-> culture shape their recipe selection?*
->
-> The author's of[Smuggler's
-> Cove](https://www.smugglerscovesf.com/#about-section)
-> could not have opened their bar in a place where
-> the community's alcohol food taboo is codified
-> in the law, which could be many places - all of
-> which are not San Francisco. Since the authors
-> did live in California during the early 21st
-> century they were exposed to the 21st century
-> cocktail culture revival. The ability for the
-> authors to write about [Exotic Cocktails, Rum,
-> and the Cult of
-> Tiki](https://www.amazon.com/Smugglers-Cove-Exotic-Cocktails-Cult/dp/1607747324)
-> is wholly contingent upon recreational
-> consumption of the alcohol being a deeply
-> ingrained element of San Francisco's food
-> culture - which developed a cocktail focused
-> sub-culture.
->
-> When "Prohibition" was a social fact in the
-> early 20th century U.S.A. the legally codified
-> alcohol taboo was an element of the larger
-> culture's class stratification and racial cast
-> system. The perpetrators of Temperance Movement
-> restricted alcohol access as a means of social
-> control - specifically, the socially
-> undesirable. While their social betters enjoyed
-> the privileged of maintaining (extra)legal
-> access to alcohol. This period's cocktail
-> culture being determined by access to alcohol
-> could be used as a proxy for examining proximity
-> to political power during the Temperance
-> Movement. Besides the venn diagram of
-> communities target by the Temperance Movement
-> and the target populations of nascent eugenics
-> movement quite possibly being just one circle -
-> elements of cocktail culture can serve as a
-> proxy to explore network dynamics of early 20th
-> pre-globalized international markets, in
-> addition to agricultural products immediately
-> before The Dust Bowl and advent of
-> refrigeration.
+How do the social facts of and author's food culture shape their recipe selection?
+
+:   The author's of[Smuggler's
+    Cove](https://www.smugglerscovesf.com/#about-section)
+    could not have opened their bar in a place
+    where the community's alcohol food taboo is
+    codified in the law, which could be many
+    places - all of which are not San Francisco.
+    Since the authors did live in California
+    during the early 21st century they were
+    exposed to the 21st century cocktail culture
+    revival. The ability for the authors to write
+    about [Exotic Cocktails, Rum, and the Cult of
+    Tiki](https://www.amazon.com/Smugglers-Cove-Exotic-Cocktails-Cult/dp/1607747324)
+    is wholly contingent upon recreational
+    consumption of the alcohol being a deeply
+    ingrained element of San Francisco's food
+    culture - which developed a cocktail focused
+    sub-culture.
+
+    When "Prohibition" was a social fact in the
+    early 20th century U.S.A. the legally codified
+    alcohol taboo was an element of the larger
+    culture's class stratification and racial cast
+    system. The perpetrators of Temperance
+    Movement restricted alcohol access as a means
+    of social control - specifically, the socially
+    undesirable. While their social betters
+    enjoyed the privileged of maintaining
+    (extra)legal access to alcohol. This period's
+    cocktail culture being determined by access to
+    alcohol could be used as a proxy for examining
+    proximity to political power during the
+    Temperance Movement. Besides the venn diagram
+    of communities target by the Temperance
+    Movement and the target populations of nascent
+    eugenics movement quite possibly being just
+    one circle - elements of cocktail culture can
+    serve as a proxy to explore network dynamics
+    of early 20th pre-globalized international
+    markets, in addition to agricultural products
+    immediately before The Dust Bowl and advent of
+    refrigeration.
 
@@
 
-Every time-period has it's own "cocktail culture",
-which can be viewed as a network of period-related
-products, technological practices, and culinary
-aesthetics manifesting in each element of a
-cocktail recipe.
+Cocktails are build with specific ingredients,
+methods, and presentations to fit contemporary
+cocktail culture aesthetics.
 
-![](https://tenor.com/brZQ5.gif){width="2474"
-height="255"}
+![](https://media3.giphy.com/media/zbW5zoQetefZwdBR6Z/200w.webp?cid=ecf05e477of2cy4i1vdat12zy8n4ufrcuuikyv6qxkmwe1z2&rid=200w.webp&ct=g){width="400"}
 
@@
 historians](https://www.theatlantic.com/health/archive/2010/06/how-to-be-a-drink-historian/58724/).
+
 Their opinion is based in direct experience and
@@
 
-## I'm curious to see what sort of relationships exists between Tiki Cocktail Ingredients?
+I'm curious to see what sort of relationships
+exists between cocktail ingredients?
 
-## Cocktails are build with specific ingredients, methods, and presentations to fit contemporary cocktail culture aesthetics.
+![](C:/Users/white/AppData/Local/RStudio/tmp/paste-FF879F11.png){width="500"}
 
-### *Write up your results briefly:*
-
--   focus on interpretation of the results.
--   Don't list statistics or provide code,
--   **the goal is to choose a few interesting
-    results and provide an interpretation.**
-
-### Working from the example R syntax:
-
-1.  calculate network density;
-
-2.  degree centrality, and
-
-3.  centralization measures for your network data.
-
-<div>
-
-> -   identify initial network format;
->
->     -   **Smuggler's Cove Index was converted
->         into an edgelist**
->
-> -   describe and identify the nodes including:
->
->     -   **Smuggler's Cove Edgelist**
->
->         -   **Nodes: 274**
->
->         -   **Edges: 672**
->
-> -   what constitutes a tie or edge including:
->
->     -   Ties
->
->         -   Number:
->
->         -   Directed
->
->         -   Binary
->
->     -   interpret the value of the tie if any.
->
->     -    edge attributes that might be used to:
->
->         -   subset data, or
->         -   stack multiple networks.
-
-</div>
-
-## *Provide at least two or three noteworthy results*, including:
-
-1.  the relevant statistics and interpretation.
-
-    -   For example, explaining which **node(s)
-        are most central and which are least
-        central.**
-
-2.  Discuss (with any related evidence) whether or
-    not the **node(s) behavior is in line with or
-    violates expectations based on the degree
-    centrality measure.**
-
-    1.  **What do you make of network density and
-        centralization measures?\
-        **
-
-        +-----------+--------------+--------+-----------+
-        | Analysis  | statnet      | igraph | Plot      |
-        +===========+==============+========+===========+
-        | Dyad      | Mutual: 1    | 0.0179 | yes       |
-        | Census    |              |        |           |
-        |           | A            |        |           |
-        |           | symmetrical: |        |           |
-        |           | 670          |        |           |
-        |           |              |        |           |
-        |           | Null: 36730  |        |           |
-        +-----------+--------------+--------+-----------+
-        | Triad     | 0: 3216391   |        |           |
-        | Census:   |              |        |           |
-        |           | 1: 7879 0    |        |           |
-        | All       |              |        |           |
-        | Triads in | 2 : 166754   |        |           |
-        | Network   |              |        |           |
-        |           | 3:           |        |           |
-        +-----------+--------------+--------+-----------+
-        | Triad     | 3391024      | (undi  | yes       |
-        | Census:   |              | rected |           |
-        |           |              | graph) |           |
-        | total     |              |        |           |
-        | number of |              | [1]    |           |
-        | all four  |              | 3      |           |
-        | triad     |              | 216659 |           |
-        | types     |              |        |           |
-        |           |              | [2]    |           |
-        |           |              | 166486 |           |
-        |           |              |        |           |
-        |           |              | [11]   |           |
-        |           |              | 7879   |           |
-        +-----------+--------------+--------+-----------+
-        | Tra       | undirected   | Undi   |           |
-        | nsitivity |              | rected |           |
-        +-----------+--------------+--------+-----------+
-        | Local     |              |        |           |
-        | tran      |              |        |           |
-        | sitivity: |              |        |           |
-        | Node List |              |        |           |
-        | & Ego     |              |        |           |
-        | Network   |              |        |           |
-        +-----------+--------------+--------+-----------+
-        | Isolates  | no           |        |           |
-        +-----------+--------------+--------+-----------+
-        | Un        |              | n      |           |
-        | directed: |              | umber: |           |
-        | Component |              | 1      |           |
-        | Structure |              |        |           |
-        |           |              | size:  |           |
-        |           |              | 274    |           |
-        +-----------+--------------+--------+-----------+
-        | Directed: |              | 0.01   | yes       |
-        | GRAPH:    |              | 671642 |           |
-        | Dyad      |              |        |           |
-        | Census    |              |        |           |
-        +-----------+--------------+--------+-----------+
-        |           |              |        | yes       |
-        | Directed: |              |        |           |
-        | Degree    |              |        |           |
-        | C         |              |        |           |
-        | entrality |              |        |           |
-        +-----------+--------------+--------+-----------+
-        | Directed: |              |        | yes       |
-        | Be        |              |        |           |
-        | tweenness |              |        |           |
-        | C         |              |        |           |
-        | entrality |              |        |           |
-        +-----------+--------------+--------+-----------+
-        | Directed: |              |        | yes       |
-        | Ei        |              |        |           |
-        | genvector |              |        |           |
-        | C         |              |        |           |
-        | entrality |              |        |           |
-        +-----------+--------------+--------+-----------+
-        | Directed: |              |        |           |
-        | Bonacich  |              |        |           |
-        | Ce        |              |        |           |
-        | ntrality} |              |        |           |
-        +-----------+--------------+--------+-----------+
-        |           |              |        |           |
-        | Directed: |              |        |           |
-        | Page Rank |              |        |           |
-        +-----------+--------------+--------+-----------+
-        |           |              |        |           |
-        +-----------+--------------+--------+-----------+
-        |           |              |        |           |
-        +-----------+--------------+--------+-----------+
-
-> Distill is a publication format for scientific
+> `D`istill is a publication format for scientific
 > and technical writing, native to the web.

### 2022-02-22 docs/3. SNA - Assignments/DRAFT_Week3-Distill-Blog_Degree-and-Centrality.Rmd

---
title: "Social Network Analysis: Week 3: Degree and Centrality"
description: " "
author:
  - name: "Audra Jamai White" 
    url: 
    affiliation: "Umass Amherst - DACSS 679: Social Network Analysis"
    affiliation_url: 
date: "`r Sys.Date()`"
output: distill::distill_article
---

```{r setup, Libraries, include=FALSE}
knitr::opts_chunk$set(include = FALSE)
# Document Creation
library(knitr)
library(markdown)
library(yaml)
library(distill)
library(blogdown)
```

![](https://media.giphy.com/media/3ornkcUTDQyU4E6kRa/giphy.gif)

![](https://media.giphy.com/media/3ornjK3aalyWAEhxDi/giphy.gif)

![](https://media.giphy.com/media/3o6Yg4Hgd2bt4802xW/giphy.gif)

![](https://media.giphy.com/media/l2JJzfwyTZYUbjQn6/giphy.gif)

# [Research Question:]{.smallcaps}

## Can we use SNA methods to suss out anecdotal aspects of contemporary cocktail culture?

Probably!

The difficulty lies in finding the right type of
data and formatting it in such a way to answer
meaningful questions.

![](https://media.giphy.com/media/l44QthVdK0aN0h0BO/giphy.gif)

[#ButAlso]{.smallcaps} Determining what those
*meaningful questions* are*.*

### Does a Recipe Book Contain Network Data?

The elements of recipes in a cookbook have a
relationship to each other because they're are a
part of a curated collection - but that
relationship is defined more by the social facts
of the author's food culture(s) than the
individual decisions.

![](https://c.tenor.com/lNr4hoGtM3cAAAAC/thomas-jane-josephus-miller.gif)

Recipes (and recipe meta data) are all a part of
the the larger super-structure of "things humans
eat". Each recipe book can serve as a topical
codex for author's food cultures[^1].

[Smuggler's Cove](https://www.smugglerscovesf.com/#about-section)

:   is a legendary cocktail bar in San Francisco.
    Since opening in 2009, this Tiki Bar has
    developed a dedicated following and received
    many awards.

Source Text: [Smuggler's Cove: Exotic Cocktails, Rum, and the Cult of Tiki](https://www.smugglerscovesf.com/#book-section)

:   Fatures 80 cocktail recipes accompanied by the
    history of rum and tiki drinks.

Source Data: [Smuggler's Cove: Recipe Book Index](https://docs.google.com/spreadsheets/d/1W5eaejaZ9MOu3I36R9TZIus7xlHhkX7JonmBzGHXnTI/edit#gid=942764477)

:   [Thanks
    el_joker1](https://www.reddit.com/r/cocktails/comments/5um8zh/smugglers_cove_tiki_cocktail_book_index/)
    for converting the index into a CSV and
    posting on Reddit

    Smuggler's Cove CSV is a pretty small data
    set. The source.csv contains 6 columns and
    several hundred rows.

Network Data: Smuggler's Cove Index

:   My network dataset contains 3 columns:

    -   [Drink Name]{.smallcaps}

    -   [Drink Ingredient]{.smallcaps}
        ^Lime Juice/Rye/Orgeat/Lime Wedge^

    -   [Ingredient Type]{.smallcaps}
        ^Juice/ Whiskey/ Syrup/Fruit^

    These three categories are used to develop and
    Edge list with a small number of redundant
    edge attributes.

# What makes a Tiki Drink a "Tiki Drink?"

This isn't the "ask 10 people and get 10 different
answers" sort of question - but all of the answers
are based on each person's (un)informed opinion
and not a professional organization [issuing
product
standards](https://www.gayot.com/wine/wine-map/france.html)
or establishing professional standards with
data-driven research.

![](https://media.giphy.com/media/3oz8xxBsDMZWcMCHoQ/giphy.gif)

## To start:

### I'm curious to see what sort of relationships exist between the components of [Smuggler's Cove](https://www.smugglerscovesf.com/#about-section) Tiki Cocktail Recipies?

# ## \*Write up your results briefly: \*

\* focus on interpretation of the results.

\* Don't list statistics or provide code,

\* \*\*the goal is to choose a few interesting
results and provide an interpretation.\*\*

## \*Briefly describe the dataset:\*

## \*Provide at least two or three noteworthy

results\*, including:

1\. the relevant statistics and interpretation.

For example, explaining which node(s) are most
central and which are least central.

2\. Discuss (with any related evidence) whether or
not the node(s) behavior is in line with or
violates expectations based on the degree
centrality measure.

3\. What do you make of network density and
centralization measures?

4\. What about differences in the binary 100
million threshold network vs valued trade flows
network.

5.  Check tutorial for other ideas of results to
    discuss.

    *Provide at least two or three noteworthy
    results*, including:

<!-- -->

1.  the relevant statistics and interpretation.

    -   For example, explaining which **node(s)
        are most central and which are least
        central.**

2.  Discuss (with any related evidence) whether or
    not the **node(s) behavior is in line with or
    violates expectations based on the degree
    centrality measure.**

    1.  **What do you make of network density and
        centralization measures?\
        **

        +---+---+---+---+
        | A | s | i | P |
        | n | t | g | l |
        | a | a | r | o |
        | l | t | a | t |
        | y | n | p |   |
        | s | e | h |   |
        | i | t |   |   |
        h       | s|    |   |  |
        +====+===+===+===+
        | D | M | 0 | y |
        | y | u | . | e |
        | a | t |   | s |
        | d | u | 0 |   |
      |  yC | a | 1 |  |
        | e n| l | 7 |   |
        | n | : | 9 |   |
        | s | 1 |   |  | 
        |       | u |
  |   |   |           s | A |   |   |
          | | s |1 7| 9  
        |
  | y |   |   |           | | m |s y| m m
        |   |     | |   |
        |
  | e |   |   |           | | t |t r| i c
        |   | r |     | |
        |
  | i |   |   |           | | c |   |   |
        |   | a |   |   |
        |   | l |     | |
        |
  | : |   |   |           | | 6 |   |    
        |   | 7 |     | |
        |
  | 0 |   |   |           | |   |   |   |
 |      |     N |   |   |
        |
  | u |   |   |           | | l |u l| l :
        |   | l |     | |
        |
  | : |   |   |           | | 3 |6 7| 3 0
        |   | 6 |   |   |
        |   | 7 |   |   |
        |   | 3 |     | |
        |
  | 0 |   |   +-----------+-+---+---+---+
        | T | 0 | \ |   |
        | r | : | | |   |
        | C e n s i | 3 | l |   |
        | a | 2 |   |   |
        | d | 1 |       |
|
        C | 6 |   |       |       e | 3 |   |    
        |       | n | 9 |   |   |
     |    s | 1 |   |  | 1 : 7 8   |u |   |   |    
        | s | 1 |   |   |
        | : | : |  |
   |
     | A    | 7 |   | |  \|        |  | 8 |   |    
        |   | \ |  |
   |
     +------| | |   |--+-----------+--+---+---+| \| l \| l \| 9 \| \| \| \| T \|
        0 \| \| \| \|\|\| r \| \| \|\
        \| \| i \| 2 \| \| 2 \| a \| : \| \| \| \|
        d \| 1 \| \| \| \| \|\| \| s \| \| \| \|
        \| \|i\| 6 \| i 4 \|n 7\|\| \| \|

|    \|\| N \| \| \| N
|  \| \| e \| 4 \| 4 e \| \|\| t \| \| \| \| \| w \| \| 3 \| \|\| \| \| oo \| \| \|\| \| \|r\| r \| \| \|
|      \|\| k \| \| \| \| k +---+---+-----+ \| T \|-- \| ( \| y \| \| r \| 3 \| u \| e \| \| i \| 9 \| n \| s \| \| a \| 1 \| d \| \| \| d \| 0 \| i \| \| \| C \| 2 \| r \| \| \| e \| 4 \| e \| \| \| \| cn \| \| \| \| n \| \|\|d g\| ss s t \| \| u \| \| e \| \| \| s \| \| d \| \| \| : \| \| g \| \| \| \|aph r \| t\| \| \| at \| \| \| \| \| \|\|\| \| \| \| p \| \| \| t \| t\| h \| \| \| )a \| \| \| l \| \| \| \| \| n \| \| [ \| \| \| u \| \| 1 \| \| mber \| m \| \| 2 \|

] \| \| b \| \| 3 \| \|\| \|\|\
\| e e 2 \| \| \| r \| \| 1 \|665\| 9 \| 6\| o \|
\| \| \|\
\| f\| \| 6 \| \| riad t \| \| \| a \|a \| 5 \| l
\| \| 9\
\| \| l \|\| \| \| ypes \| \| [ \| f \| [] \| \|
\|\| 16\| o o \| 2 \| \| \| u \| \| ] \| \| \| r
\| \| 1 \| \| \| t \| \| 6 \| \| \| r \| \| 6 \|
\| \| i \| \| 4 \| \| \| a \| \| 8 \| \| \| d \|
\| \| \| \|6 6 6 \| \|\| t \| t \|\
\| y \| \| [ \| \| \| p \| \| 1 \| \| \| e \| \| 1
\| \| \| s \| \| ] \| \| \| \| \|\| \| \|\
\| [\|11]\| 8 \| \| 8 \| \| \| 7 \|\
\| +-\|- \| \| \| \| +-- -+---+---+---+ \| T \| u
\| U \| \| \| r \| n \| n \| \| \| a \| d \| d \|
\| \| n \| i \| i \| \| \| s \| r \| r \| \| \| i
\| e \| \|\
e e \| e \| \| c t c \| t \| i \| t \| t \| \| \|
v \| e \| e \| \| \| i \| d \| d \| \| \| t \|
\|\| \|--\|\| \| y \|\| \| \|\| +---+---+---+L oal
---+ \| L \|L \| \| \| \| o \| \| \| c \| \| \| \|
\| a \| \| \| \| \| \| \|l \| l \| \| \|t \| \| \|
\| r \| \| \|ran s \| \| \| a \| \| a \| n \|\| \|
\| \| \| \| \| \| \| \| i \| \| \| \| \| t \| \|
\| \| \| i \| \| \| \| \| v \| \| \| \| \| i \| \|
\| \| \| t \| \| \| \| \|\| \| \| \| \|\| \| \| \|
: \| \| \| \| \| N \| \| \| \| \| o \| \| \| \| \|
d \| \| \| \| \| e \| \| \| \| \| L \| \| \| \| \|
i \| \| \|\
\| \| \| \|\|\| s s \| s\
&\| Eg\| t \| \| \| \|

    & &  |

& \| \|E\| \| \|\| \| \| g \| \| \| \| \| o \| \|
\| \| \| N \| \| \| \| \| \| \| e \| \| \| w\|ork
\| \| \| \| \| \|\| w \| \| w \| o \| \|\| \| \|
\|\| \| \| r \| r\| \|\
\|k \| \| \| \| +---+---+---+---+ \| I \| n \| \|
\| \| s \| o \| \| \| \| o \| \| \| \| \| l \| \|
\| \| \| a \| \| \| \| \| t \| \| \| \| \| e \|---
\|\|---\| \| \| \| \| s\| \| \| +---+---+---+---+
\| U \| \| n \| \| \| n \| \| u \| \| \| d \| \| m
\| \| \| i \| \| b \| \| \| r \| \| e \| \| \| e
\| \| r \| \| \| c \| \| : \| \| \| t \| \| 1 \|
\| \| e \| \| \| \| \| d \| \| s \| \| \| : \| \|
i \| \| \| \| \| zC \|C \| C \| \|\| \| o \|\| \|
\|\| \| m \| \| : \| \| \| p \| \| 2 \| \| \| o \|
\| 7 \| \| \| n \| \| 4 \| \| \| e \| \| \| \| n
\|\| S \|\|tru\| \| \| \| t \|\| \| S \| \| \| \|
\| t \| \| \| \| \| r \| \| \| \| \| u \| \|274 \|
\| c \| \| c \| \| c \| \|

    |t |   ||t
    |    |        ||

\| \| +- r \|\| \| \| \|\| e \| \| \| \|
+---+---+rec + \| D \| \| i \| 0 \| y \| \| . \| e
\|\| \| r \| \| 0 \| s \| \| e \| \| 1 \| \| \|
6\|7 \| 6 c \| c \|\| \| d \| \| t \| \| 7 \| \|
\|e e \| \| d \| 6 \| \| \| : \| \| 4 \| \| \| \|
\| \| 2 G \| G 2 \| \|\| 2 R\| \|\| \| \| A \| \|
\| \| \| P \| \| \| \| \| H \| \| \| \| \| : \| \|
\| \| \| D \| \| \| \| \| y \| \| \| \| \| a \| \|
\| \| \|\
d \| C \| \| \| \| \| \| \|\| \| C \| \|\
\| \|\| \| e \| \| \| \| \| \|\| \| s \| \| \| \|
\| \| \| \| \| u \|\| \| s \| \| \| \|
+---+---+---+---+ \| D \| \| \| y \| \| i \| \| \|
e \| \| r \| \| \| s \| \| e \| \| \| \| \| \| \|
c \| \|cy\| cs \|\| \| t \| \| \| t \|\
\| \| \| \| d \| \| \| \| \| : \| \| \| \| \| D \|
\| \| \| \| \| \| \|ee \| e\| \| g \| \| \| \| \|
\| \| r \| \| e \| \| \| \| \| e \| \| \| \| \| C
\| \| \| \| \| e \| \| \| \| \| n \| \| \| \| \| t
\| \| \| \| \| r \| \| \| \| \| a \| \| \| \| \| l
\| \| \| \| \| i \| \| \| \| \| \| \| --- \| t \|
\| \| \| y \| \| \|\| \| +---+---+rec + \| D \| \|
i \| \| y \| \| \| e \|\| \| r \| \| \| s \| \| e
\| \| \| \| \| \| \| c \| \|cy\| cs \|\| t \| \|
\| \| e\
\| \| \| \| d \| \| \| \| \| : \| \| \| \| \| B \|
\| \| \| \| e \| \| \| \| \| t \| \| \| \|

     w |       | | |

\| \|\| \| \| \| \| e \| \| e \| \| \| \| \| n \|
\| \| \| \| n \| \| \| \| \| e \| \| \| \|

     s |       ||  |

\| s \| \| \|\| \| \| C \| \| \| \| \| e \| \| \|
\| \| n \| \| \| \| \| t \| \| \| \| \| \| \| \|\|
rr \| \| \| a \| \| \| \| \| l \| \| \| \| \| i \|
\| \| \| \| \|\| t +-\| --\|-\| \| yy \|\| \|+---
+--+ ----+ --+---+ \| D \| \| y \| \| \| e \| \|
\| r \| \| \| s \| \| e \| \| \| \| \| c \| \| \|
y\| s \| \| \| tedt \| \| \| e \| \|\|\| \|\| \|
\| \| \| \| d \|\
d \| : \| \| \| \| \| E \| \| \| \| \| i \| \| \|
\| \| g \| \| \| \| \| e \| \| \|\| \| \|\| n\| \|
\| \| \| \| v \| \| \| \| \| e \| \| \| \| \| c \|
\| \| \| \| t \| \| \| \|

       o |   C||e |n||

\| \| \| \|\| r \| \| C \| \| \| \| \| e \| \| \|
\| \| n \| \| \| \| \| t \| \| \| \| \| r \| \| \|
\| \| \| a \|\| \|\| \| \| \| \| \| l \| \| \|
\|\| i \| i \| \|t + \|\|\| \|\|\| \| y \| \| \|
\| +---+---+---+---+ \| D \| \| \| \| \| i \| \|
\| \| \| r \| \| \| \| \| \| e \| e\| \| \| \| c
\| \| \|\| \| t \| \| \| \| \| e \| \| \| \| \| d
\| \| \| \| \| : \| \| \| \| \| B \| \| \| \| \| o
\| \| \| \| \| n \| \| \| \| \| a \| \| \| \| \| c
\| \| \| \| \| i \| \| \| \| \| c \| \| \| \| \| h
\| \| \| \| \| C \| \| \| \| \| e \| \| \| \| \| n
\| \| \| \| \| t \| \| \|\| \| \|\| r\| \| \| \|
\| \| a \| \| \| \| \| l \| \| \| \| \| i \| \| \|
\| \| t \| \| \| \|

       y |    ||  | ||
          | 
          |   |   |

} +---+---+---+ \| ------+ +--+ \|\| D \| \|\| i
\| \| \|\| \| \| \| r \| \| \| \| \| \| \| \|\| e
\| \| \| \| \| \| c \|c \|\| c \| \| \|t \| k \|t
\| t \| \| \| \|e \| \| \| \| \| \| \| \| \| \|\|:
\| \| \| \| \| P \| \| \| \| \| \| \| \|\
a \| \| g \|\| \| \| \| \| \| e \| \| \| \| \| R
\| \| \| \| \|a

          | a |   || a||  |

| \| n\| n\| \|n \| \| \| \| \|----- --+ \|

-

    -   ++ + +-+---+ \|+- \| \| +-+ +> Dist+ill+
        \| \| + is+ a publ+ic\| \| \|
        +---+---+---+---+

> Distill is a publicacien is a p ublicanttecnical
> witing, native to the web.
>
> Learn more about using Distill for R Markdown at
> <https://rstudio.github.io/distill>.

[^1]: *sFood Culture?*

    The differentiating elements between food
    cultures are what a community eats, how food
    is prepared, when food is prepared, why it's
    prepared a certain way, who prepares the food,
    and who consumes the food. All of which
    combine to create food taboos and culinary
    traditions - the social facts informing a
    foundational aspect of daily life.

    Humans are wild! Throughout time and space we
    have integrated an assortment of plants,
    animals, insects, fungi, and minerals into
    idiosyncratic food cultures. The consumables
    in food culture are particular while the
    technological methods of preparation and
    preservation are shared. Foods are consumed
    raw or cook. Cooked foods can be boiled,
    roasted, baked, or fried. Food preservation
    methods are equally limited. Perishables are
    dried, cured (salt, smoke, sugar, acid, ect.),
    and fermented.[We love to ferment
    things!](https://fermentationassociation.org/fermentation-in-anthropology/)

    Most of my favorite foods are fermented-
    bread, cheese, pickles, booze. Anything can be
    fermented, but fermenting liquids - grain
    mash, plant juice, milk, honey- into beverages
    seems to be universal. The wildest thing and
    our love of fermentation liquids is that the
    end product usually contains a toxin -
    alcohol!

    I'm sure several someone's have researched why
    humans love to create and imbibe intoxicants
    a.k.a poison -[at least we're not the only
    ones.](https://youtu.be/A0Xsqo-n_AE)

### 2022-02-22 docs/3. SNA - Assignments/Week3_DRAFT_Results.Rmd

--- 2022-02-08 docs/3. SNA - Assignments/DRAFT-week3-Assignment.Rmd
@@
 
-      *Week 3 Assignment: Degree and Centrality*
+## Working from the example R syntax:
 
-Using the tutorial as a guide, 
-      *  you may use your own data; 
-      *  the data provided in the week 3. Syntax dataset is Correlates of War trade network - you can read more about it online; or
-      *  choose another dataset.
-
-## Working from the example R syntax:
 1.  calculate network density;
@@
 
-## Write up your results briefly:
-*   focus on interpretation of the results. 
-*   Don’t list statistics or provide code, 
-*  **the goal is to choose a few interesting results and provide an interpretation.**
+## *Write up your results briefly:*
 
-## Briefly describe the dataset:
-1.   identify initial network format; 
-2.   describe and identify the nodes 
-     including: 
-        *  how many nodes are in the dataset; 
-3.   what constitutes a tie or edge
-     including:
-        *  how many ties, 
-        *   whether ties are directed/undirected,
-        *   whether ties are weighted/binary, 
-        *   and how to interpret the value of the tie if any.
-        *   Whether or not there are edge attributes 
-            that might be used to:
-            *   subset data, or 
-            *   stack multiple networks. 
-Not every feature of the network needs to be described, but **description should orient reader to the network data and provide any necessary context for the results provided.**
+-   focus on interpretation of the results.
+-   Don't list statistics or provide code,
+-   **the goal is to choose a few interesting
+    results and provide an interpretation.**
 
-## Provide at least two or three noteworthy results, including:
-1.   the relevant statistics and interpretation. 
-        For example, explaining which node(s) are most central and which are least central. 
-2.   Discuss (with any related evidence) whether or not the node(s) behavior is in line with or violates expectations based on the degree centrality measure. 
-3.   What do you make of network density and centralization measures?  
-4.   What about differences in the binary 100 million threshold network vs valued trade flows network. 
- 5.  Check tutorial for other ideas of results to discuss.
+## *Briefly describe the dataset:*
 
-##
-1.  [**Identify an existing data set.**]{.ul}
+# 1. identify initial network format
 
-| This can be one provided in the course directory, in an R package or library, located online, or some other source.
+<div>
 
-2.  [**Briefly describe the network dataset.**]{.ul}
+> -   identify initial network format;
+>
+>     -   **Smuggler's Cove Index was converted
+>         into an edgelist**
+>
+> -   what constitutes a tie or edge including:
+>
+>     -   Ties
+>
+>         -   Number:
+>
+>         -   Directed:
+>
+>         -   Binary:
+>
+>     -   interpret the value of the tie if any.
+>
+>     -   edge attributes that might be used to:
+>
+>     <!-- -->
+>
+>         -   subset data, or
+>         -   stack multiple networks.
 
-| Identify and describe content of nodes and links, and identify format of data set (i.e., matrix or edgelist, directed or not, weighted or not), and whether attribute data are present. 
-  Be sure to provide information about network size (e.g., information obtained from network description using week 1 network basics tutorial commands.)
+</div>
 
-# Week 2: Scripts
+# 2. describe and identify the nodes including:
 
-```{r Import Data Set, echo=TRUE}
+<div>
 
-  # install.packages("network")
+**Smuggler's Cove Edge-list contains:**
 
-    data("flo", package = "network")
+> -   Nodes: 274
+>
+>     -   Nodes Values:
+>
+>         -   [Drink Name]{.smallcaps}
+>
+>         -   [Drink Ingredient]{.smallcaps}
+>
+> -   Edges: 672
+>
+>     -   Drink Ingredient Type
 
-```
+</div>
 
-# 2. Briefly describe the network dataset.
+# 3. what constitutes a tie or edge including:
 
--   *Be sure to provide information about network size (e.g., information obtained from network description using week 1 network basics tutorial commands.)*
+-   how many ties,
 
-1.  *Identify and describe content of nodes and links,*
+-   whether ties are directed/undirected,
 
--   each of the 16 Florentine Family Names represent a Node in the network.
+-   whether ties are weighted/binary,
 
-```{r Colnames}
- colnames(flo)
-```
+-   and how to interpret the value of the tie if
+    any.
 
-2.  *Identify format of data set (i.e., matrix or edgelist, directed or not, weighted or not), and*
+-   Whether or not there are edge attributes that
+    might be used to:
 
-    -   Flo Format: Size: 16 x 16 square dimmentions indicate a adjacency matrix format
+    -   subset data, or
+    -   stack multiple networks.
 
-    Network attributes: vertices = 16 directed = TRUE hyper = FALSE loops = FALSE multiple = FALSE bipartite = FALSE total edges= 40 missing edges= 0 non-missing edges= 40
+# *Provide at least two or three noteworthy results*, including:
 
-Vertex attribute names: vertex.names
+## 1. the relevant statistics and interpretation. For example, explaining which node(s) are most central and which are least central.
 
-No edge attributes
+## 2. Discuss (with any related evidence) whether or not the node(s) behavior is in line with or violates expectations based on the degree centrality measure.
 
-```{r Dimmentions, echo=TRUE}
+## 3.What do you make of network density and centralization measures?
 
-  dim(flo)
+## 4. What about differences in the binary 100 million threshold network vs valued trade flows network.
 
-```
+## 5. Check tutorial for other ideas of results to discuss.
 
-```{r Network Attributes, echo=TRUE}
-
-  network(flo)
-
-```
-
-3.  *Identify whether attribute data are present.*
-
-```{r Summary,echo=TRUE}
-
-  summary(flo,
-          print.adj = TRUE
-          )
-```
-
-## Create & Describe: Directed Adjacency Matrix
-
-*Florentine Families Directed Adjacency Matrix Network Objects:*
-    **iGraph** flo.ig 
-    **Statnet** flo.stat
-
-iGraph and Statnet both use {r graph4} for Directed Adjacency Matrix Objects
-
-```{r graph4, statnet: Directed: Adjacency Network, echo=TRUE}
-
-    flo.stat<-
-        network(
-        flo,
-        directed=F,
-        matrix.type="adjacency"
-        )
-
-#     provides a description of several critical network features
-    print(flo.stat)
-
-```
-
-```{r graph4, igraph: Directed: Adjacency Network, echo=TRUE}
-
-    flo.ig<-
-      graph.adjacency(
-      flo,
-      mode="undirected"
-      ) 
-    print(flo.ig)
-```
-
-```{r igraph: Network Description, echo=TRUE}
-
-#     Count Vertices
-    vcount(flo.ig)
-
-#     Count Edges
-    ecount(flo.ig)
-
-# Is this a Bipartite or single mode network?
-    is_bipartite(flo.ig)
-
-#  Are edges directed or undirected?
-    is_directed(flo.ig)
-
-#Are edges weighted or unweighted?
-    is_weighted(flo.ig)
-
-```
- **Vertex and Edge Attributes**
-
-```{r statnet: Attribute Data: Directed: Adjacency Network, echo=TRUE}
-
-#     access vertex attributes
-  head(flo.stat %v% "vertex.names")
-
-#      list the names of vertex attributes
-  network::list.vertex.attributes(flo.stat)
-
-#     access edge attribute
-  head(flo.stat%e% "weight")
-
-#  Generate a list the names of edge attributes
-  network::list.edge.attributes(flo.stat)
-
-#   summarize numeric network attribute
-  summary(flo.stat  %v% "name")
-
-```
-
-```{r igraph: Attribute Data: Directed: Adjacency Network, echo=TRUE}
-
-#     access vertex attribute 
-  V(flo.ig)$name
-#     Generate a list the names of vertex attributes
-  igraph::vertex_attr_names(flo.ig)
-
-#     access edge attribute
-  E(flo.ig)$weight
-
-#   Generate a list the names of edge attributes  
-  igraph::edge_attr_names(flo.ig)
-
-#   summarize numeric network attribute
-  summary(E(flo.ig)$weight)
-
-```
-
-# 3. Explore the dataset using commands from week 2 tutorial.
-
-5.  *geodesic and path distances,*
-
-## Path Length and Geodesic
-
-```{r iGraph:Nodes: Path: Length, echo=TRUE}
-
-#     Calculate distances between two nodes
-    distances(flo.ig,"Bischeri","Ridolfi")
-
-#     Calculate distance between two nodes using unweighted edges
-    distances(flo.ig,"Bischeri", "Castellani",weights=NA)
-
-```
-
-We can also find all of the shortest paths between two famalies in this network.
-These list the starting node and the ending node with all nodes inbetween for each path. 
-The option weights=NA means that any available edge weights are ignored.
-
-```{r iGraph:Nodes: Path: Shortest, echo=TRUE}
-
-#     isolating the distances between specific node
-    all_shortest_paths(flo.ig,"Strozzi","Tornabuoni", weights=NA)$res
-## Note: manually tell igraph to ignore edge weights.
-```
-
-The concept of shortest path to describe the overall network structure can be more useful
-
-```{r iGraph:Network: Path: Shortest, echo=TRUE}
-
-#     find average shortest path for network
-    average.path.length(flo.ig,directed=F)
-
-```
-
-6.  *triads or transitivity,*
-
-## Dyad Census
-
-Classifies all dyads in the network as: - Reciprocal (mutual), or mut - Asymmetric (non-mutual), or asym, and - Absent, or null
-
-```{r statnet: Dyad Census , echo=TRUE}
-
-    sna::dyad.census(flo.stat)
-
-```
-
-```{r iGraph: Dyad Census, echo=TRUE}
-
-  igraph::dyad.census(flo.ig)
-
-```
-
-## Triad Census
-
-Classifies all triads in the network. The triad census provides a fundamental descriptive insight into the types of triads found in a particular dataset.
-
-```{r statnet: Triad Census, echo=TRUE}
-
-#     Classify all Triad in the network: Directed Network
-  sna::triad.census(flo.stat, mode= )
-
-#     Classify all Triad in the network: Undirected Network
-   sna::triad.census(flo.stat, mode="graph")
-
-#     total number of all four triad types returned by triad census
-   sum(sna::triad.census(flo.stat, mode="graph"))
-
-```
-
-```{r iGraph: Triad Census, echo=TRUE}
-#Classify all Triad in the network
-     igraph::triad_census(flo.ig)
-
-```
-
-## Transitivity or Global Clustering
-
-```{r iGraph: weighted/ network transitivity, echo=TRUE}
-
-#     network transitivity:
-    transitivity(flo.ig)
-
-#     weighted network transitivity:
-#   igraph::transivity(flo.ig)
-
-```
-
-```{r statnet: weighted/ directed network transitivity, echo=TRUE}
-
-#     Directed Networks transitivity:
-  gtrans(flo.stat)
-
-#   methods for weighted networks, rank and correlation, along with the relevant references.
-#  sna::gtrans()
-
-```
-
-## Local Transivity or Clustering
-`Local transitivity` (local clustering coefficient), is a technical description of the density of an ego network.
-
-```{r iGraph:Local transitivity, echo=TRUE}
-
-#     Retrive a list of the vertices we are interested
-    V(flo.ig)[c("Bischeri" ,
-                "Castellani", 
-                "Medici",
-                "Ridolfi")]
-
-#     check ego network transitivity
-transitivity(flo.ig,
-             type="local", 
-             vids=V(flo.ig)
-             [c("Bischeri",
-                "Castellani", 
-                "Medici",
-                "Ridolfi")]) 
-#     get global clustering cofficient
-  transitivity(flo.ig, type="global")
-
-#     get average local clustering coefficient
-  transitivity(flo.ig, type="average")
-
-```
-
-7.  *connectedness and.or component structure, etc.*
-
-> Distill is a publication format for scientific and technical writing, native to the web.
+> Distill is a publication format for scientific
+> and technical writing, native to the web.
 >
-> Learn more about using Distill for R Markdown at <https://rstudio.github.io/distill>.
-##
-
-# Week3:    Briefly describe the dataset:
-1.   identify initial network format; 
-2.   describe and identify the nodes 
-     including: 
-        *  how many nodes are in the dataset; 
-3.   what constitutes a tie or edge
-     including:
-        *  how many ties, 
-        *   whether ties are directed/undirected,
-        *   whether ties are weighted/binary, 
-        *   and how to interpret the value of the tie if any.
-        *   Whether or not there are edge attributes 
-            that might be used to:
-            *   subset data, or 
-            *   stack multiple networks.
-
-#WEEK 3:     Working from the example R syntax:
-1.   calculate network density; 
-2.   degree centrality, and 
-3.   centralization measures for your network data.
-
-#WEEK 3:  Provide at least two or three noteworthy results
-1.   the relevant statistics and interpretation. 
-        For example, explaining which node(s) are most central and which are least central. 
-2.   Discuss (with any related evidence) whether or not the node(s) behavior is in line with or violates expectations based on the degree centrality measure. 
-3.   What do you make of network density and centralization measures?  
-4.   What about differences in the binary 100 million threshold network vs valued trade flows network. 
- 5.  Check tutorial for other ideas of results to discuss.
+> Learn more about using Distill for R Markdown at
+> <https://rstudio.github.io/distill>.

### 2022-02-25 docs/3. SNA - Assignments/Week3-Assignment.Rmd
2.24.22
I think I fixed the network objects

Okay, this time I REALLY fixed them AND kinda understand the metadata

@@
 ```
-## Working from the example R syntax:
-1.   calculate network density; 
-2.   degree centrality, and 
-3.   centralization measures for your network data.
 
-## Write up your results briefly:
+#        *Write up your results briefly: *
 *   focus on interpretation of the results. 
@@
 
+#  Working from the example R syntax:
+1.   calculate network density; 
+2.   degree centrality, and 
+3.   centralization measures for your network data. 
+# Import & Describe Network
+
+# 1.   calculate network density
+# 2.   degree centrality
+# 3.   centralization measures for your network data.
+
+# 
 > Distill is a publication format for scientific and technical writing, native to the web.

### 2022-02-25 docs/3. SNA - Assignments/sna_Week3/Week3_Notebook.Rmd
2.22.22 late on this past weekend's committs
2.24.22
I think I fixed the network objects

Okay, this time I REALLY fixed them AND kinda understand the metadata

@@
 ---
-title: "R Notebook"
+title: "Week 3 Notebook"
 output: html_notebook
----
-
-```{r setup, Libraries, include=FALSE}
-
-knitr::opts_chunk$set(echo = FALSE)
-
-# Document Creation
-library(knitr)
-library(markdown)
-library(yaml)
-library(distill)
-library(blogdown)
-
-# Basic Analysis
-library(ggplot2)
-library(tidyverse)
-library(clipr)
-library(dbplyr)
-library(data.table)
-library(stringr)
-library(stringi)
-library(tibble)
-library(tidyr)
-
-# SNA - Social Network Analysis
-
-library(tergm)
-library(ergm)
-library(network)
-library(networkDynamic)
-library(networkDynamicData)
-
-library(statnet)
-library(igraph)
-library(igraphdata)
-library(tsna)
-library(sna)
-
-```
-
-```{r Set Working Directory, include=FALSE}
-getwd()
-
-setwd("C:/Users/white/iCloudDrive/Documents/1_DACSS_UMassAmherst/Dacss_RProjects/3. Sp22_rProjects/Dacss_679- Coursework/GIT-ajw_Learning-SocialNetworkAnalysis/docs/3. SNA - Assignments/sna_Week3")
-
-```
-
-## Basic R: Import & Clean Data
-
-```{r Read raw data into R}
-
-library(readr)
-
-indx_SmugglerCove_recip <- read_csv("C:/Users/white/iCloudDrive/Documents/1_DACSS_UMassAmherst/Dacss_RProjects/3.
-Sp22_rProjects/Dacss_679- Coursework/GIT-ajw_Learning-SocialNetworkAnalysis/docs/3.
-SNA-Data/index-by_name-Smuggler_Cove-cocktail_recipies.csv",
-    col_names = FALSE, 
-    col_types = cols(X1 = col_skip(),
-                     X4 = col_skip()), 
-                    na = "empty")
-
-View(indx_SmugglerCove_recip)
-summary(indx_SmugglerCove_recip)
-
- # Smuggler's Cove
-
-smugCovIdx <- indx_SmugglerCove_recip
-
-```
-
-```{r Getting Information on a Dataset:, echo=FALSE}
-
-# list the structure of smugCovIdx
-str(smugCovIdx)
-
-# class of an object (numeric, matrix, data frame, etc)
-class(smugCovIdx)
-
-# list the variables in smugCovIdx
-names(smugCovIdx)
-
-# dimensions of an object
-dim(smugCovIdx)
-```
-
-```{r & Clean Data}
-
-  library(stringr)
-      # Drop NA rows
-smugCovIdx <- na.omit(smugCovIdx)
-
-# DATA Cleaning
-
-#     Extract variables
-#####
-
-          # extract first word of the column, adds values in new Column at the end of DF
-
-                    #1st pastIt
-passIt <- smugCovIdx
-
-colnames(passIt)
-                    #2nd passIt
-passIt$substring_first <- str_extract(passIt$X5,"(\\w+)")
-
-#####
-
-#####
-#     Drop it like...
-#####
-      # DROP COLUMNS FROM DATA FRAME
-
-                      #3rd PassIt
-passIt = subset(passIt, 
-                       select = -c(3)
-                       )
-colnames(passIt)
-#####
-
-#####
-#     Give Variables a human name
-#####
-
-# rename column names with human language
-
-                      # Return it
-smugCovIdx <- passIt
-
-names(smugCovIdx )[1] <- "dnkName"
-names(smugCovIdx )[2] <- "dnkIng"
-names(smugCovIdx )[3] <- "ingType"
-
-colnames(smugCovIdx)
-```
-
-#   Project Varriables
-
-    Raw Data:
-  indx_SmugglerCove_recip
-
-    DataFrame:
-  smugCovIdx
-            colname: "dnkName" "dnkIng"  "ingType"
-  network_nodes <- smugCovIdx << "dnkName"
-
-    Matrix:
-  smug_matrix
-  network_edgelist <- smug_matrix
-
-    Network Objects: EDGE LIST
-  STATNET: smugEL_sn
-  IGRAPH: smugEL_ig
-
-  Edge Vetex:
-              dnkName
-  Edge Attributes:
-                  dnkIng
-                  ingType
 
 # Network Info
-  Network Objects: EDGE LIST
-                  STATNET: smugEL_sn
-                  IGRAPH: smugEL_ig
-                          ingTypeEL_Dig
-
-```{r EDGELIST: UNDIRECTED Network Objects: statnet & igraph, include=FALSE}
-
-#Lets make some network objects
-
-colnames(smugCovIdx) 
-# tell R data should be understood as a matrix
-smug_matrix = as.matrix(smugCovIdx,
-                        matrix.type="edgelist",
-                        directed=FALSE) 
-head.matrix(smug_matrix)
-
-network_edgelist <- smug_matrix
-
-  network_nodes <- smugCovIdx 
-    network_nodes<- 
-      select(network_nodes,
-             dnkName)
-
-        ### View(network_nodes)
-
-######
-      ######**igraph** 
-######
-        #igraph object 
-network_ig <- 
-  graph.edgelist(
-    as.matrix(
-      smugCovIdx[1:2]), 
-    directed=F)
-                ## create new edge attribute
-  E(network_ig)$dnkIng<-smugCovIdx$dnkIng
-  E(network_ig)$ingType<-smugCovIdx$ingType
-  #create vertex attributes in igraph
- V(network_ig)[match(V(network_ig)$dnkName,network_nodes$dnkName)]$dnkName<-
-   network_nodes$dnkName
-
-      summary(edge_attr(network_ig))
-
-  # head(network_ig)
-  # summary(network_ig)
-      ######
-
-#####
-      #####**statnet** 
-#####    
-  network_edgelist <- smugCovIdx
-
-  network_nodes <- smugCovIdx 
-  network_nodes<- 
-    select(network_nodes,
-           dnkName)
-summary(network_nodes)
-View(network_nodes)
-
-  #Now let's create a statnet object
-  network_statnet <- network(network_edgelist, 
-                             matrix.type = "edgelist",
-                             vertex.attr = network_nodes,
-                             multiple = T)
-
-  network_statnet%e%'dnkIng'  <-
-    network_edgelist$dnkIng
-
-  network_statnet%e%'ingType'<- 
-    network_edgelist$ingType
-
-       # list the names: vertex attributes
-  view(network_statnet%v% "vertex.names")
-
-summary(network_statnet)
-        #####
-
- ## Network Objects: EDGE LIST
-              ##**STATNET:**
-  smugEL_sn <- network_statnet
-
-                ##**IGRAPH:** 
-  smugEL_ig <- network_ig
-
-```
-
-```{r EDGELIST: IGRAPH: DIRECTED Network: ingType, include=FALSE}
-
-#Lets make some network objects
-
-colnames(smugCovIdx) 
-# tell R data should be understood as a matrix
-smug_matrix = as.matrix(smugCovIdx,
-                        matrix.type="edgelist",
-                        directed=FALSE) 
-head.matrix(smug_matrix)
-
-network_edgelist <- smug_matrix
-
-  nodes_ingType <- smugCovIdx 
-    nodes_ingType<- 
-      select(nodes_ingType,ingType)
-view(nodes_ingType)
-        ### View(nodes_ingType)
-
-######
-      ######**igraph** 
-######
-        #igraph object: ingType
-d_network_ig <- 
-  graph.edgelist(
-    as.matrix(
-      smugCovIdx[2:3]), 
-    directed=T)
-
-vertex.attributes(d_network_ig)
-                ## create new edge attribute
-  E(d_network_ig)$dnkIng<-smugCovIdx$dnkIng
-  E(d_network_ig)$dnkName<-smugCovIdx$dnkName
-
-  #create vertex attributes in igraph
- V(d_network_ig)[match(V(d_network_ig)$ingType,nodes_ingType$ingType)]$ingType<- nodes_ingType$ingType
-
-   View(d_network_ig)
-   head(d_network_ig)
-  summary(d_network_ig)
-  summary(edge_attr(d_network_ig))
-  summary(vertex.attributes(d_network_ig))
-
-   ingTypeEL_Dig <- d_network_ig
-```
-
 ## Smuggler's Cove Index- NETWORK: EDGELIST: Features & Descriptions
@@
       #   summarize: numeric network attribute
-  summary(smugEL_sn%v%"dnkName")
+  summary(smugEL_sn%v%"dnkNam")
 
@@
 
-smugEL_sn
-
-[1] "network"
-
-Network attributes:
-  vertices = 274 
-  directed = TRUE 
-  hyper = FALSE 
-  loops = FALSE 
-  multiple = TRUE 
-  bipartite = FALSE 
-  total edges= 672 
-    missing edges= 0 
-    non-missing edges= 672
-
- Vertex attribute names: 
-    dnkName vertex.names
-
- Edge attribute names: 
-    dnkIng ingType
-
 ```{r STATNET: functions that calculate network-level descriptives}
@@
 
-gtrans(smugEL_sn)
-proportion of transitive triads
-
-symmetrize( smugEL_sn, rule = "weak") 
-symmetrize so i<->j iff i->j OR i<-j
-
-symmetrize( smugEL_sn, rule = "strong") 
-symmetrize so i<->j iff i->j OR i<-j
-
-dyad.census(smugEL_sn) 
-MAN dyad census
-
-triad.census(smugEL_sn) 
-standard directed triad census
-
 ```{r igraph: Network Description, echo=TRUE}
@@
     # Generate a list the names of vertex attributes
-  V(smugEL_ig)$name
+  view(V(smugEL_ig)$name)
 
     # access edge attribute  names
-  igraph::vertex_attr_names(smugEL_ig)
+  view(igraph::vertex_attr_names(smugEL_ig))
 
     # Generate a list the names of edge attributes  
-  igraph::edge_attr_names(smugEL_ig)
+  view(igraph::edge_attr_names(smugEL_ig))
 
@@
 ```
-smugEL_ig
-
-[1] "igraph"
-
-Network attributes:
-  vertices = 274 
-  directed = FALSE
-  hyper = FALSE 
-  loops = FALSE 
-  multiple = TRUE 
-  bipartite = FALSE 
-  total edges= 672 
-    missing edges= 0 
-    non-missing edges= 672
-
- Vertex attribute names: 
-    dnkName vertex.names
-
- Edge attribute names: 
-    dnkIng ingType
-
-```{r IGRAPH: DIRECTED Network: ingType, echo=TRUE}
+
+```{r IGRAPH: DIRECTED Network: ingTyp, echo=TRUE}
 
       # class of an object
-    class(ingTypeEL_Dig)
+    class(ingTypEL_Dig)
 
@@
       # Count Vertices
-    vcount(ingTypeEL_Dig)
+    vcount(ingTypEL_Dig)
 
       # Count Edges
-    ecount(ingTypeEL_Dig)
+    ecount(ingTypEL_Dig)
 
@@
     # Bipartitie / Unimodal
-    is_bipartite(ingTypeEL_Dig)
+    is_bipartite(ingTypEL_Dig)
 
@@
     # Un/directed 
-    is_directed(ingTypeEL_Dig)
+    is_directed(ingTypEL_Dig)
 
     # weighted or unweighted?
-    is_weighted(ingTypeEL_Dig)
+    is_weighted(ingTypEL_Dig)
 
     # edge weights
-    E(ingTypeEL_Dig)$weight
+    E(ingTypEL_Dig)$weight
 
@@
     # Generate a list the names of vertex attributes
-  V(ingTypeEL_Dig)$name
+  V(ingTypEL_Dig)$name
 
     # access edge attribute  names
-  igraph::vertex_attr_names(ingTypeEL_Dig)
+  igraph::vertex_attr_names(ingTypEL_Dig)
 
     # Generate a list the names of edge attributes  
-  igraph::edge_attr_names(ingTypeEL_Dig)
+  igraph::edge_attr_names(ingTypEL_Dig)
 
 ## Network Attributes
- summary(ingTypeEL_Dig)
+ summary(ingTypEL_Dig)
           # Vertices =  
@@
 #     find average shortest path for network
-    average.path.length(ingTypeEL_Dig,directed=T)
+    average.path.length(ingTypEL_Dig,directed=T)
 
@@
 #     isolating the distances between specific node
-    all_shortest_paths(ingTypeEL_Dig,
+    all_shortest_paths(ingTypEL_Dig,
                        "Strozzi","Tornabuoni", 
@@
 #     Calculate distances between two nodes
-    distances(ingTypeEL_Dig,"Bischeri","Ridolfi")
+    distances(ingTypEL_Dig,"Bischeri","Ridolfi")
 
 #     Calculate distance between two nodes using unweighted edges
-    distances(ingTypeEL_Dig,"Bischeri", "Castellani",weights=NA)
+    distances(ingTypEL_Dig,"Bischeri", "Castellani",weights=NA)
 
@@
  igraph::components(smugEL_ig)$no 
-      ##**NOTE:** $no prevents a list of comonents from being printed
+      ##**NOTE:** $no prevents a list of components from being printed
 
@@
       # Basic R: get summary statistics for node attributes
- summary(nodes_ingTypes)
+ summary(nodes_ingTyps)
       # provides range, mean, median and standard deviation of a vector.
@@
 #V1: dnkIng
-#V2: ingType
+#V2: ingTyp
 
@@
 V(smugNet)$dnkIng <- 
-  smug_attributes$dnkIng[match(V(smugNet)$name, smug_attributes$ingType)]
-
-V(smugNet)$dnkName <- 
-  smug_attributes$dnkName[
+  smug_attributes$dnkIng[match(V(smugNet)$name, smug_attributes$ingTyp)]
+
+V(smugNet)$dnkNam <- 
+  smug_attributes$dnkNam[
     match(V(
@@
 
-V(smugNet)$ingType <- 
-  smug_attributes$ingType[match(V(smugNet)$name, smug_attributes$ingType)]
-
-V(smugNet)$dnkName <-
-  smug_attributes$dnkName[match(V(smugNet)$name, smug_attributes$dnkName)]
+V(smugNet)$ingTyp <- 
+  smug_attributes$ingTyp[match(V(smugNet)$name, smug_attributes$ingTyp)]
+
+V(smugNet)$dnkNam <-
+  smug_attributes$dnkNam[match(V(smugNet)$name, smug_attributes$dnkNam)]
 
@@
 
-```{r iGraph: Undirected: DEGREE CENTRALITY: ingType, echo=TRUE}
+```{r iGraph: Undirected: DEGREE CENTRALITY: ingTyp, echo=TRUE}
 # graph the SMUG network
@@
 
-V(smugNet)$dnkName <-
-  smug_attributes$dnkName[match(V(smugNet)$name, smug_attributes$dnkIng)]
+V(smugNet)$dnkNam <-
+  smug_attributes$dnkNam[match(V(smugNet)$name, smug_attributes$dnkIng)]
 
@@
        label.col="black",
-       vertex.col=att$dnkName
+       vertex.col=att$dnkNam
  )
@@
 
-graph.density(ingTypeEL_Dig)
+graph.density(ingTypEL_Dig)
     ## Density captures, at the macro-level, the proportion of dyads that are present over the possible total number of dyads in the network
@@
 
-ingTypeEL_DigNod <- vcount(ingTypeEL_Dig)
-
-ingTypeEL_DigDen <- graph.density(ingTypeEL_Dig)
+ingTypEL_DigNod <- vcount(ingTypEL_Dig)
+
+ingTypEL_DigDen <- graph.density(ingTypEL_Dig)
 
@@
 # Degree centrality is calculated using the degree function in R. It returns how many edges each node has.
-view(degree(ingTypeEL_Dig))
-
-ingT_deg <- ingTypeEL_Dig
+view(degree(ingTypEL_Dig))
+
+ingT_deg <- ingTypEL_Dig
 V(ingT_deg)$degree <- degree(ingT_deg) # assignment
@@
 #     vertex.label.color = "black", 
-#     vertex.size = V(ingTypeEL_Dig)$degree, 
+#     vertex.size = V(ingTypEL_Dig)$degree, 
 #     vertex.label.cex = .2) # sized by degree
@@
 
-view(betweenness(ingTypeEL_Dig, directed = FALSE))
-
-# view(betweenness(ingTypeEL_Dig, directed = TRUE))
+view(betweenness(ingTypEL_Dig, directed = FALSE))
+
+# view(betweenness(ingTypEL_Dig, directed = TRUE))
               # Yeilds 0
 
-ingTypeEL_Between <- ingTypeEL_Dig
+ingTypEL_Between <- ingTypEL_Dig
 # We can again assign the output of betweenness() to a variable in the network and size the nodes according to it.
 
-V(ingTypeEL_Between)$betweenness <- 
-  betweenness(ingTypeEL_Between, 
+V(ingTypEL_Between)$betweenness <- 
+  betweenness(ingTypEL_Between, 
               directed = F)
 
-# plot(ingTypeEL_Between, 
+# plot(ingTypEL_Between, 
 #     vertex.label.cex = .6, 
 #     vertex.label.color = "black", 
-#     vertex.size = V(ingTypeEL_Between)$betweenness) # sized by betweenness
+#     vertex.size = V(ingTypEL_Between)$betweenness) # sized by betweenness
 
@@
 
-view(evcent(ingTypeEL_Dig)$vector)
+view(evcent(ingTypEL_Dig)$vector)
 # view(evcent(smugEL_ig)$vector)
-ingTyp_Vector <- ingTypeEL_Dig
+ingTyp_Vector <- ingTypEL_Dig
 V(ingTyp_Vector)$eigenvector <- evcent(ingTyp_Vector)$vector
@@
 
-ingTyp_Cent <- ingTypeEL_Dig
+ingTyp_Cent <- ingTypEL_Dig
 

### 2022-02-25 docs/1. SNA-DACSS-Import_Scripts/CopyOfimport script- Network Objects.R
2.24.22
I think I fixed the network objects

@@ -1,0 +1,89 @@
+#This script imports 
+
+
+library(statnet)
+library(igraph)
+
+# The import script has created three objects that represent the network:
+#   - sourceEL_ig (a dataframe of an edgelist and edge attributes)
+#   - sourceEL_ig_ig (an igraph object)
+#   - snEL  (a network object compatable with statnet packages like sna & ergm)
+
+
+#######
+      #Lets read the data into the enviroment.
+
+source_df<-smugCovIdx
+
+#####
+    #Format DF to become an edgelist
+    
+    # Assign modefied source_dfto Edge List variable name 
+sourceEL <- 
+ source_df[c( #select column numbers from source.Data in order to be added
+   1:4)]
+
+summary(sourceEL)
+
+
+#####
+    #**igraph** version of the network
+          # NOTE: igraph automatically adds edge attributes, but not vertices 
+    
+    #First let's create the object. 
+sourceEL_ig <- graph_from_data_frame(d = sourceEL, 
+                        directed = FALSE)
+
+print(summary(sourceEL_ig))
+#####
+    #**statnet** object from our edgelist
+          # Will not have vertex
+          # Will not have edge attributes
+
+    #First we make and EMPTYobject. 
+snEL <- 
+  network(as.matrix
+          (sourceEL[], 
+            matrix.type = 'edgelist',
+            directed = TRUE))
+
+#######**VERIFY**
+        network::list.vertex.attributes(snEL)
+        network::list.edge.attributes(snEL) 
+
+#**Purge* unwanted attributes
+network::delete.vertex.attribute(snEL,"  ")
+network::delete.edge.attribute(snEL,"  ")
+
+
+#**Assign:**VERTICES atributes <aka colnames>
+snEL%v%"vertex.names"<- sourceEL$intTyp
+snEL%v%"ingNam"<- sourceEL$ingNam
+        
+#**Assign:** edge atributes <aka colnames>        
+        
+snEL%e%"dnkIng" <- sourceEL$dnkIng
+snEL%e%"dnkNam" <- sourceEL$dnkNam
+
+#######**VERIFY**
+print(snEL)
+network::list.vertex.attributes(snEL)
+network::list.edge.attributes(snEL)       
+
+          # it's a bloody statnet edgelist !!!
+
+     
+     
+     
+              #**igraph** Generate Edgelist
+
+V(sourceEL_ig)$ccode<-
+  temp$ccode2[
+    match(V
[…]

### 2022-02-25 docs/1. SNA-DACSS-Import_Scripts/SmugIndx_import script_Network Objects.R

@@ -1,0 +1,163 @@
+      # read the data into Code Block
+
+source_df<-smugCovIdx
+
+#####
+    #Format DF to become an edgelist
+
+sourceEL <- source_df[
+  c( #select column numbers from source.Data in order to be added
+   1:4)]
+
+summary(sourceEL)
+
+#####
+library(statnet)
+#####
+
+#####
+    #**STATNET** object from edgelist
+          # No vertex attribute data
+          # No edge attribute data
+
+    #**Create object.**
+snEL <- 
+  network(as.matrix
+          (sourceEL[1:2], 
+            matrix.type = 'edgelist'))
+
+      #######**VERIFY**
+              print(snEL)               
+              network::list.vertex.attributes(snEL)
+              network::list.edge.attributes(snEL)
+              View(snEL%v%"vertex.names")
+                  
+#**Assign:**VERTICES atributes <aka colnames>
+
+ 
+ snEL%v%"dNam"<- sourceEL$dnkNam
+ snEL%v%"iNam"<- sourceEL$ingNam
+        
+      #######**VERIFY**
+              network::list.vertex.attributes(snEL)
+              summary(snEL%v%"iNam")
+              View(snEL%v%"dNam")
+              View(snEL%v%"iNam")
+              view(snEL%v%"vertex.names")
+              
+#**Assign:** edge atributes <aka colnames>        
+      
+snEL%e%"ingTyp" <- sourceEL$ingTyp
+# snEL%e%"dnkNam" <- sourceEL$dnkNam
+
+        #######**VERIFY**
+                network::list.edge.attributes(snEL)       
+
+#**Purge* unwanted attributes
+          network::delete.vertex.attribute(snEL,"na")
+         # network::delete.vertex.attribute(snEL,"vertex.names")
+          network::delete.edge.attribute(snEL,"na")
+  
+  #######**VERIFY**
+          network::list.vertex.attributes(snEL)
+          network::list.edge.attributes(snEL)
+          class(snEL)
+          print(snEL)
+#
+##          
+###
+###** it's a bloody statnet edgelist !!! **###
+         
+     
+          
+#####
+library(igraph)
+#####
+
+#**IGRAPH**
+          # NOTE: igraph automatically adds edge attributes, but not vertices 
+          #              [1] "dnkNam" "ingNam" "dnkIng" "ingTyp"
+#**Create Edgelist Matrix** 
+
+sourceEL_mx = 
[…]

### 2022-02-25 docs/3. SNA - Assignments/sna_Week3/DRAFT-week3-Assignment.Rmd

@@
 # Week 2: Scripts
-1.  [**Identify an existing data set.**]{.ul}
-```{r Set Working Directory, include=FALSE}
-getwd()
+## Smuggler's Index: Network Attributes  
+  - Edgelist
+  - unweghted
+  - undirected
 
-setwd("C:/Users/white/iCloudDrive/Documents/1_DACSS_UMassAmherst/Dacss_RProjects/3. Sp22_rProjects/Dacss_679- Coursework/GIT-ajw_Learning-SocialNetworkAnalysis/docs/3. SNA - Assignments")
+Network attributes:
+
+*statnet*
+  vertices = 274
+  directed = TRUE
+  hyper = FALSE
+  loops = FALSE
+  multiple = FALSE
+  bipartite = FALSE
+ total edges = 671 
+   missing edges = 0 
+   non-missing edges = 0 
+ density = 0
+
+Edge attributes:
+[1]ingTyp:
+   character valued attribute
+
+Attribute summary:
+  the 10 most common values are:
+  JUICE     RUM   SYRUP LIQUEUR BITTERS    SODA   SPICE     GIN  BRANDY   FRUIT 
+    135     125     115      84      54      28      19      12       9       7
+
+###   IGRAPH:   Network Description
+*igraph*
+- Network Size
+  - Number Vertex: 274
+    - attr: name (v/c)
+  - Number Edges: 672
+    - attr: ingTyp (e/c)
+- Bipartite: FALSE
+- Directed: FALSE
+- Weighted: FALSE
+
+Names
+- Vertex Names: view
+- Edge Attribute Names: [1] "ingTyp"
+```{r igraph: Network Description, echo=TRUE}
+
+summary(igEL)
+#     Count Vertices
+    vcount(igEL)
+
+#     Count Edges
+    ecount(igEL)
+
+# Is this a Bipartite or single mode network?
+    is_bipartite(igEL)
+
+#  Are edges directed or undirected?
+    is_directed(igEL)
+
+#Are edges weighted or unweighted?
+    is_weighted(igEL)
 
@@
 
-```{r Read raw data into R}
+```{r igraph: Vertex & Attribute info, echo=TRUE}
+library(igraph)
 
-library(readr)
+#     access vertex attribute 
+  head(V(igEL)$name,20)
+#     Generate a list the names of vertex attributes
+  print(igraph::vertex_attr_names(igEL))
 
-index_by_name_Smuggler_Cove_cocktail_recipies <- read_csv("C:/Users/white/iCloudDrive/Documents/1_DACSS_UMassAmherst/Dacss_RProjects/3.
-Sp22_rProjects/Dacss_679- Coursework/GIT-ajw_Learning-SocialNetworkAnalysis/docs/3.
-SNA-Data/index-by_name-Smuggler_Cove-cocktail_recipies.csv",
-    col_names = FALSE, col_types = cols(X1 = col_skip(), 
-        X4 = col_skip()), na = "empty")
+#     access edge attribute
+  head(E(igEL)$ingTyp, 20)
 
-View(index_by_name_Smuggler_Cove_cocktail_recipies)
+#   Generate a list the names of edge attributes  
+  igraph::edge_attr_names(igEL)
 
-summary(index_by_name_Smuggler_Cove_cocktail_recipies)
-
- # Smuggler's Cove
+#   summarize numeric network attribute
+  summary(E(igEL)$weight)
 
@@
 
-2. Briefly describe the network dataset.
-```{r Identify critical features of data:, echo=FALSE}
+###   STATNET:   Network Description 
+ *statnet*
+  vertices = 274
+  directed = TRUE
+  hyper = FALSE
+  loops = FALSE
+  multiple = FALSE
+  bipartite = FALSE
+ total edges = 671 
+   missing edges = 0 
+   non-missing edges = 0 
+ density = 0
 
-dim(smugDrink_Indx.df)
-colnames(smugDrink_Indx.df)
+Edge attributes:
+
+ ingTyp:
+   character valued attribute
+   attribute summary:
+   the 10 most common values are:
+  JUICE     RUM   SYRUP LIQUEUR BITTERS    SODA   SPICE     GIN  BRANDY   FRUIT 
+    135     125     115      84      54      28      19      12       9       7 
+```{r statnet: Network Summary & Attribute info, echo=TRUE}
+
+summary(snEL)
+print(snEL)
+#     access vertex attributes
+ head(snEL %v% "vertex.names")
+
+#      list the names of vertex attributes
+  network::list.vertex.attributes(snEL)
+
+#     access edge attribute
+  head(snEL%e% "ingTyp")
+
+#  Generate a list the names of edge attributes
+  network::list.edge.attributes(snEL)
+
+#   summarize numeric network attribute
+  summary(snEL  %v% "name")
 
@@
 
--   *Be sure to provide information about network size (e.g., information obtained from network description using week 1 network basics tutorial commands.)*
+##  Path Length and Geodesic Distance
 
-1.  *Identify and describe content of nodes and links,*
+- Nodes: 
+  - (v/c) Drink Names
+  - (v/c) Drink Ingredients
+- Links: 
+  - (e/c)  Ingredient Type
 
--   each of the 16 Florentine Family Names represent a Node in the network.
+###  Statnet:   Path Length and Geodesic Distance
 
-```{r Colnames}
+    Attribute summary:
+  the 10 most common values are:
+  JUICE     RUM   SYRUP LIQUEUR BITTERS    SODA   SPICE     GIN  BRANDY   FRUIT 
+    135     125     115      84      54      28      19      12       9       7 
+```{r STATNET:Path: Length}
+library(statnet)
 
@@
 
-2.  *Identify format of data set (i.e., matrix or edgelist, directed or not, weighted or not), and*
+ >head(snEL%e% "ingTyp")
 
-Vertex attribute names: vertex.names
+[1] "FRUIT"   "LEAVES"  "JUICE"   "SYRUP"   "LIQUEUR" "RUM"
 
-```{r Dimmentions, echo=TRUE}
+   >head(snEL %v% "vertex.names")
 
-  dim(smugDrink_Indx.df)
+[1] "(1-INCH-SQUARE) CHUNKS PINEAPPLE" "(1-INCH-SQUARE) PINEAPPLE CHUNKS" "2:1 SIMPLE SYRUP"                
+[4] "A WISH FOR GRACE"                 "ABRICOT VIEUX"                    "ABSINTHE BLANC"
+
+###  IGRAPH:   Path Length and Geodesic Distance
+
+```{r iGraph:Nodes: Path: Length, echo=TRUE}
+library(igraph)
+
+# Head
+head(V(igEL)$name,10)
+head(E(igEL)$ingTyp, 10)
+
+#Tail
+tail(V(igEL)$name,10)
+tail(E(igEL)$ingTyp, 10)
 
@@
 
-```{r Network Attributes, echo=TRUE}
+  # 20 Vertex Names
 
-  network(smugDrink_Indx.df)
+      Head, 10 + Tail, 10
+ [1] "AKU AKU"                    
+ [2] "(1-INCH-SQUARE) CHUNKS PINEAPPLE"    
+ [3] "MINT LEAVES"                
+ [4] "LIME JUICE"    
+ [5] "DEMERARA SYRUP"             
+ [6] "PEACH LIQUEUR (SUCH AS MATHILDE, COMBIER, OR GIFFARD)"
+ [7] "BLENDED LIGHTLY AGED RUM"   
+ [8] "PUPULE" 
+ [9] "ORANGE JUICE"               
+ [10] "CINNAMON SYRUP"
+ [1] "SINGAPORE SLING"                     
+      "BENEDICTINE"
+      "HONDO HATTIE'S JUNGLE PUNCH!"    
+  [4] "KAHIKO PUNCH"
+      "PASSION FRUIT HONEY"                 
+      "TRIUMVIRATE PUNCH"   
+  [7] "EUREKA PUNCH"                         
+      "YULETIDAL WAVE"
+      "RUMBUSTION PUNCH"                
+ [10] "PUKA PUNCH"
+
+  The shortest path to describe the overall network structure 
+```{r iGraph:Network: Path: Shortest, echo=TRUE}
+
+#     find average shortest path for network
+    average.path.length(igEL,directed=F)
 
@@
 
-3.  *Identify whether attribute data are present.*
+```{r iGraph:Nodes: Path: Length, echo=TRUE}
+library(igraph)
 
-```{r Summary,echo=TRUE}
+#     Calculate distance between two nodes using unweighted edges
 
-  summary(smugDrink_Indx.df,
-          print.adj = TRUE
-          )
-```
-
-## Create & Describe: Directed Adjacency Matrix
-
-*Florentine Families Directed Adjacency Matrix Network Objects:*
-    **iGraph** smugDrink_Indx.df.ig 
-    **Statnet** smugDrink_Indx.df.stat
-
-iGraph and Statnet both use {r graph4} for Directed Adjacency Matrix Objects
-
-```{r graph4, statnet: Directed: Adjacency Network, echo=TRUE}
-
-    smugDrink_Indx.df.stat<-
-        network(
-        smugDrink_Indx.df,
-        directed=F,
-        matrix.type="adjacency"
-        )
-
-#     provides a description of several critical network features
-    print(flo.stat)
+    distances(igEL,"AKU AKU" ,  "SINGAPORE SLING",weights=NA)
+    distances(igEL,"AKU AKU" ,  "HONDO HATTIE'S JUNGLE PUNCH!",weights=NA)
+    distances(igEL,"AKU AKU" ,"KAHIKO PUNCH" ,weights=NA)
+    distances(igEL,"AKU AKU" , "PASSION FRUIT HONEY"   ,weights=NA)
+    distances(igEL,"AKU AKU" , "TRIUMVIRATE PUNCH"   ,weights=NA)
+    distances(igEL,"AKU AKU" ,"EUREKA PUNCH" ,weights=NA)
+    distances(igEL,"AKU AKU" , "YULETIDAL WAVE" ,weights=NA)
+    distances(igEL,"AKU AKU" ,"RUMBUSTION PUNCH"   ,weights=NA)
+    distances(igEL,"AKU AKU" ,"PUKA PUNCH",weights=NA)
 
@@
 
-```{r graph4, igraph: Directed: Adjacency Network, echo=TRUE}
-
-    flo.ig<-
-      graph.adjacency(
-      flo,
-      mode="undirected"
-      ) 
-    print(flo.ig)
-```
-
-```{r igraph: Network Description, echo=TRUE}
-
-#     Count Vertices
-    vcount(flo.ig)
-
-#     Count Edges
-    ecount(flo.ig)
-
-# Is this a Bipartite or single mode network?
-    is_bipartite(flo.ig)
-
-#  Are edges directed or undirected?
-    is_directed(flo.ig)
-
-#Are edges weighted or unweighted?
-    is_weighted(flo.ig)
-
-```
- **Vertex and Edge Attributes**
-
-```{r statnet: Attribute Data: Directed: Adjacency Network, echo=TRUE}
-
-#     access vertex attributes
-  head(flo.stat %v% "vertex.names")
-
-#      list the names of vertex attributes
-  network::list.vertex.attributes(flo.stat)
-
-#     access edge attribute
-  head(flo.stat%e% "weight")
-
-#  Generate a list the names of edge attributes
-  network::list.edge.attributes(flo.stat)
-
-#   summarize numeric network attribute
-  summary(flo.stat  %v% "name")
-
-```
-
-```{r igraph: Attribute Data: Directed: Adjacency Network, echo=TRUE}
-
-#     access vertex attribute 
-  V(flo.ig)$name
-#     Generate a list the names of vertex attributes
-  igraph::vertex_attr_names(flo.ig)
-
-#     access edge attribute
-  E(flo.ig)$weight
-
-#   Generate a list the names of edge attributes  
-  igraph::edge_attr_names(flo.ig)
-
-#   summarize numeric network attribute
-  summary(E(flo.ig)$weight)
-
-```
-
-# 3. Explore the dataset using commands from week 2 tutorial.
-
-5.  *geodesic and path distances,*
-
-## Path Length and Geodesic
-
-```{r iGraph:Nodes: Path: Length, echo=TRUE}
-
-#     Calculate distances between two nodes
-    distances(flo.ig,"Bischeri","Ridolfi")
-
-#     Calculate distance between two nodes using unweighted edges
-    distances(flo.ig,"Bischeri", "Castellani",weights=NA)
-
-```
-
-We can also find all of the shortest paths between two famalies in this network.
-These list the starting node and the ending node with all nodes inbetween for each path. 
-The option weights=NA means that any available edge weights are ignored.
+Find *all* of the shortest paths between two specific nodes in this network.
 
@@
 #     isolating the distances between specific node
-    all_shortest_paths(flo.ig,"Strozzi","Tornabuoni", weights=NA)$res
+
 ## Note: manually tell igraph to ignore edge weights.
-```
 
-The concept of shortest path to describe the overall network structure can be more useful
+all_shortest_paths(igEL,
+                     "AKU AKU" ,
+                     "SINGAPORE SLING",
+                     weights=NA)$res
 
-```{r iGraph:Network: Path: Shortest, echo=TRUE}
+all_shortest_paths(igEL,
+                   "AKU AKU",
+                   "HONDO HATTIE'S JUNGLE PUNCH!",
+                   weights=NA)$res
 
-#     find average shortest path for network
-    average.path.length(flo.ig,directed=F)
+all_shortest_paths(igEL,
+                   "AKU AKU",
+                   "KAHIKO PUNCH",
+                   weights=NA)$res
 
+all_shortest_paths(igEL,
+                     "AKU AKU", 
+                     "PASSION FRUIT HONEY",
+                     weights=NA)$res
+
+all_shortest_paths(igEL,
+                   "AKU AKU",
+                   "TRIUMVIRATE PUNCH",
+                   weights=NA)$res
+
+  all_shortest_paths(igEL,"AKU AKU",
+                     "EUREKA PUNCH",
+                     weights=NA)$res
+
+  all_shortest_paths(igEL,"AKU AKU", 
+                     "YULETIDAL WAVE" ,
+                     weights=NA)$res
+
+  all_shortest_paths(igEL,
+                     "AKU AKU" ,
+                     "RUMBUSTION PUNCH",
+                     weights=NA)$res
+
+  all_shortest_paths(igEL,
+                     "AKU AKU" ,
+                     "PUKA PUNCH",
+                     weights=NA)$res
 ```
@@
 
-Classifies all dyads in the network as: - Reciprocal (mutual), or mut - Asymmetric (non-mutual), or asym, and - Absent, or null
+Classifies all dyads in the network as:
+- Mutual - Reciprocal (mutual) 
+- Asymmetric -  (non-mutual), 
+- Null - Absent
 
 ```{r statnet: Dyad Census , echo=TRUE}
-
-    sna::dyad.census(flo.stat)
+library(statnet)
+    sna::dyad.census(snEL)
 
 ```
+```{r iGraph: Dyad Census, echo=TRUE}
+library(igraph)
 
-```{r iGraph: Dyad Census, echo=TRUE}
-
-  igraph::dyad.census(flo.ig)
+dyad.census(igEL)
 
@@
 
-Classifies all triads in the network. The triad census provides a fundamental descriptive insight into the types of triads found in a particular dataset.
+Classifies all triads in the network.
 
 ```{r statnet: Triad Census, echo=TRUE}
+library(sna)
+#     Classify all Triad in the network:
 
-#     Classify all Triad in the network: Directed Network
-  sna::triad.census(flo.stat, mode= )
+#Directed Network
+#**triad.census(snEL, mode="digraph")*
 
 #     Classify all Triad in the network: Undirected Network
-   sna::triad.census(flo.stat, mode="graph")
+   sna::triad.census(
+     snEL,
+     mode="graph")
 
 #     total number of all four triad types returned by triad census
-   sum(sna::triad.census(flo.stat, mode="graph"))
+   sum(
+     sna::triad.census(
+       snEL,
+       mode="graph")
+     )
+
+#Davis and Leinhardt classification of the triad classification scheme 
+   # describes each triad by a string of four elements: 
+   # the number of mutual (complete) dyads within the triad; 
+   # the number of asymmetric dyads within the triad; 
+   # the number of null (empty) dyads within the triad; 
+   #and a configuration code for the triads which are not uniquely distinguished by the first three distinctions.
+
+   sna::triad.classify(
+     snEL,
+     tri=c(1,2,3),
+     mode==c("digraph")
+   )
+  #Classify the triads (1,2,3) and (2,3,4)
+
+   triad.classify(snEL,tri=c(1:14))
+   gplot(snEL,c[1:14])
 
@@
 ```{r iGraph: Triad Census, echo=TRUE}
+library(igraph)
 #Classify all Triad in the network
-     igraph::triad_census(flo.ig)
+     igraph::triad_census(igEL)
 
@@
 #     network transitivity:
-    transitivity(flo.ig)
+    transitivity(igEL)
 
 #     weighted network transitivity:
-#   igraph::transivity(flo.ig)
+#   igraph::transivity(igEL)
 
@@
 #     Directed Networks transitivity:
-  gtrans(flo.stat)
+  gtrans(snEL)
 
@@
 #     Retrive a list of the vertices we are interested
-    V(flo.ig)[c("Bischeri" ,
-                "Castellani", 
+    V(igEL)[c("" ,
+                "", 
                 "Medici",
-                "Ridolfi")]
+                "")]
 
 #     check ego network transitivity
-transitivity(flo.ig,
+transitivity(igEL,
              type="local", 
-             vids=V(flo.ig)
-             [c("Bischeri",
-                "Castellani", 
+             vids=V(igEL)
+             [c("",
+                "", 
                 "Medici",
-                "Ridolfi")]) 
+                "")]) 
 #     get global clustering cofficient
-  transitivity(flo.ig, type="global")
+  transitivity(igEL, type="global")
 
 #     get average local clustering coefficient
-  transitivity(flo.ig, type="average")
+  transitivity(igEL, type="average")
 

### 2022-02-25 docs/3. SNA - Assignments/sna_Week3/week3_Plots/Scripts_week3_Plots.Rmd

# IGRAPH
```{r igraph:}

library(igraph)

```

# Plotting: network data

###**Plot Name: smugIG_plot-R_blue-curved-small*
```{r igraph:plot: basic R }

library(igraph)
plot(smugEL_ig, 
     vertex.size=3,
     vertex.color = "blue",
     vertex.frame.color = NA,
     vertex.label = NA,
     edge.curved = 1.7,
     edge.arrow.size = .3, 
     edge.width = .5)

```

###**Plot: Kamada Kawai **
    ###**Plot Name** igraph_kamadaLayout_smug
```{r igraph: Plot: Kamada Kawai}

library(igraph)

 # run the layout function on our graph

 kamadaLayout <-
   layout.kamada.kawai(smugEL_ig)

# change the default layout setting to equal the layout we generated above
 plot(smugEL_ig, 
      layout = kamadaLayout, 
      vertex.size = 3, 
      vertex.color = "black", 
      vertex.frame.color = NA, 
      vertex.label.cex = .7,  
      vertex.label = NA, 
      edge.curved = .3, 
      edge.arrow.size = .1, 
      edge.width = .5)
```

###**Plot: Frucherman-Reingold **
   ###**Plot Name** igrap-smugEL_Frucherman-Reingold
```{r igraph:}

library(igraph)

# run the layout function on our graph
 fruchtermanLayout <- 
   layout.fruchterman.reingold(smugEL_ig)

 # and then we change the default layout setting to equal the layout we generated above

 plot(smugNet, 
      vertex.size = 6, 
      vertex.color= "orange",
      vertex.label.cex = .5, 
      vertex.label.color = "black", 
      edge.with = .5,
      edge.curved = 5,
      edge.arrow.size = 0.1)

```

# Plotting: attribute data
###**Plot: Color & Attribute**
              ###**Plot Name: $Vertex Naame and $color **

```{r igraph:}

library(igraph)
 V(smugEL_ig)$color <- ifelse(V(smugEL_ig)$name == "PUKA PUNCH", "red", "yellow")
  V(smugEL_ig)$color <- NA
  V(smugEL_ig)$color <- ifelse(V(smugEL_ig)$name == "RUMBUSTION PUNCH", "red","yellow")
  V(smugEL_ig)$color <- ifelse(V(smugEL_ig)$name == "TRIUMVIRATE PUNCH", "red", V(smugEL_ig)$color)
  V(smugEL_ig)$color <- ifelse(V(smugEL_ig)$name == "KAHIKO PUNCH", "red", V(smugEL_ig)$color)
  V(smugEL_ig)$color <- ifelse(V(smugEL_ig)$name == , "black", V(smugEL_ig)$color)
  V(smugEL_ig)$color <- ifelse(V(smugEL_ig)$name ==  "DOCTOR FUNK" , "green",V(smugEL_ig)$color)
  V(smugEL_ig)$color <- ifelse(V(smugEL_ig)$name ==  "AKU AKU", "green",V(smugEL_ig)$color)
  V(smugEL_ig)$color <- ifelse(V(smugEL_ig)$name ==  "JET PILOT" , "green",V(smugEL_ig)$color)
  V(smugEL_ig)$color <- ifelse(V(smugEL_ig)$name == "SINGAPORE SLING", "purple", V(smugEL_ig)$color)
  V(smugEL_ig)$color <- ifelse(V(smugEL_ig)$name ==  "SCORPION", "purple", V(smugEL_ig)$color)
  V(smugEL_ig)$color <- ifelse(V(smugEL_ig)$name == "MAI TAI", "purple", V(smugEL_ig)$color)
  V(smugEL_ig)$color <- ifelse(V(smugEL_ig)$name == "MEXICAN EL DIABLO", "black", V(smugEL_ig)$color)

      plot(smugEL_ig, 
           vertex.size = 3, 
           vertex.frame.color =  "black", 
           vertex.label.cex = .7, 
           vertex.label = NA, 
           edge.curved = .5, 
           edge.arrow.size = .3)

```

```{r igraph:}

library(igraph)

```

# Statnet
```{r STATNET:}

library(statnet)
library(sna)

```

# Plotting: network data
# Plotting: attribute data

### 2022-02-25 docs/3. SNA - Assignments/week2-Assignment-Basic_Network_Structure.Rmd

@@
                 "Ridolfi")]
-
 #     check ego network transitivity

### 2022-02-25 docs/3. SNA - Assignments/sna_Week3/Week3_Notebook.Rmd

@@
 output: html_notebook
+---
+
+```{r setup, Libraries, include=FALSE}
+
+knitr::opts_chunk$set(echo = FALSE)
+
+# Document Creation
+library(knitr)
+library(markdown)
+library(yaml)
+library(distill)
+library(blogdown)
+
+# Basic Analysis
+library(ggplot2)
+library(tidyverse)
+library(clipr)
+library(dbplyr)
+library(data.table)
+library(stringr)
+library(stringi)
+library(tibble)
+library(tidyr)
+
+# SNA - Social Network Analysis
+
+library(tergm)
+library(ergm)
+library(network)
+library(networkDynamic)
+library(networkDynamicData)
+
+library(statnet)
+library(igraph)
+library(igraphdata)
+library(tsna)
+library(sna)
+
+```
+
+```{r Set Working Directory, include=FALSE}
+getwd()
+
+setwd("C:/Users/white/iCloudDrive/Documents/1_DACSS_UMassAmherst/Dacss_RProjects/3. Sp22_rProjects/Dacss_679- Coursework/GIT-ajw_Learning-SocialNetworkAnalysis/docs/3. SNA - Assignments/sna_Week3")
+
+```
+
+## Basic R: Import & Clean Data
+
+```{r Read raw data into R}
+
+library(readr)
+
+indx_SmugglerCove_recip <- read_csv("C:/Users/white/iCloudDrive/Documents/1_DACSS_UMassAmherst/Dacss_RProjects/3.
+Sp22_rProjects/Dacss_679- Coursework/GIT-ajw_Learning-SocialNetworkAnalysis/docs/3.
+SNA-Data/index-by_name-Smuggler_Cove-cocktail_recipies.csv",
+    col_names = FALSE, 
+    col_types = cols(X1 = col_skip(),
+                     X4 = col_skip()), 
+                    na = "empty")
+
+View(indx_SmugglerCove_recip)
+summary(indx_SmugglerCove_recip)
+
+ # Smuggler's Cove
+
+smugCovIdx <- indx_SmugglerCove_recip
+
+```
+
+```{r Getting Information on a Dataset:, echo=FALSE}
+
+# list the structure of smugCovIdx
+str(smugCovIdx)
+
+# class of an object (numeric, matrix, data frame, etc)
+class(smugCovIdx)
+
+# list the variables in smugCovIdx
+names(smugCovIdx)
+
+# dimensions of an object
+dim(smugCovIdx)
+```
+
+```{r & Clean Data}
+
+  library(stringr)
+# DATA Cleaning
+
+      # Drop NA rows
+smugCovIdx <- na.omit(smugCovIdx)
+
+#####
+#     Drop it like...
+#####
+      # DROP COLUMNS FROM DATA FRAME
+
+smugCovIdx = subset(smugCovIdx, 
+                       select = -c(4)
+                       )
+
+#####
+
+#     Extract variables
+#####
+
+          # extract first word of the column, adds values in new Column at the end of DF
+
+                    #1st pastIt
+passIt <- smugCovIdx
+
+colnames(passIt)
+                    #2nd passIt
+passIt$substring_first <- str_extract(passIt$X5,"(\\w+)")
+
+#####
+
+#####
+#     Give Variables a human name
+#####
+
+# rename column names with human language
+
+                      # Return it
+colnames(passIt)
+smugCovIdx <- passIt
+
+colnames(smugCovIdx)
+names(smugCovIdx )[1] <- "dnkNam"
+names(smugCovIdx )[2] <- "ingNam"
+names(smugCovIdx )[3] <- "dnkIng"
+names(smugCovIdx )[4] <- "ingTyp"
+colnames(smugCovIdx)
+```
+
+#   Project Varriables
+
+    Raw Data:
+  indx_SmugglerCove_recip
+
+    DataFrame:
+  smugCovIdx
+            "dnkNam" "ingNam" "dnkIng" "ingTyp"
+  network_nodes <- smugCovIdx << "dnkNam"
+
+    Matrix:
+
+    Network Objects: EDGE LIST
 
@@
 
+smugEL_sn
+
+[1] "network"
+
+Network attributes:
+  vertices = 274 
+  directed = TRUE 
+  hyper = FALSE 
+  loops = FALSE 
+  multiple = TRUE 
+  bipartite = FALSE 
+  total edges= 672 
+    missing edges= 0 
+    non-missing edges= 672
+
+ Vertex attribute names: 
+    dnkNam vertex.names
+
+ Edge attribute names: 
+    dnkIng ingTyp
+
 ```{r STATNET: functions that calculate network-level descriptives}
@@
 ```
+
+gtrans(smugEL_sn)
+proportion of transitive triads
+
+symmetrize( smugEL_sn, rule = "weak") 
+symmetrize so i<->j iff i->j OR i<-j
+
+symmetrize( smugEL_sn, rule = "strong") 
+symmetrize so i<->j iff i->j OR i<-j
+
+dyad.census(smugEL_sn) 
+MAN dyad census
+
+triad.census(smugEL_sn) 
+standard directed triad census
 
@@
 ```
+smugEL_ig
+
+[1] "igraph"
+
+Network attributes:
+  vertices = 274 
+  directed = FALSE
+  hyper = FALSE 
+  loops = FALSE 
+  multiple = TRUE 
+  bipartite = FALSE 
+  total edges= 672 
+    missing edges= 0 
+    non-missing edges= 672
+
+ Vertex attribute names: 
+    dnkNam vertex.names
+
+ Edge attribute names: 
+    dnkIng ingTyp
 

### 2022-03-02 docs/3. SNA - Assignments/sna_Week3/DRAFT-week3-Assignment.Rmd
3.2.22
Can you focus a bit more on just doing the assignment and not trying to be so high speed

@@
 
+```{r STATNET: Component Size Distribution}
+library(statnet)
+library(sna)
+
+component.dist(
+  snEL, 
+  connected= c("unilateral")) # c("strong","weak","unilateral","recursive"))
+
+component.largest(
+  snEL, 
+  connected = c("unilateral"), #=c("strong","weak","unilateral" "recursive")
+  result = c("graph"), #c("membership", "graph") 
+  return.as.edgelist = FALSE)
+
+```
+
+##### Details: Component Size Distribution 
+Components are maximal sets of mutually connected vertices; depending on the definition of “connected” one employs, one can arrive at several types of components.
+Those supported here are as follows (in increasing order of restrictiveness):
+
+weak: v_1 is connected to v_2 iff there exists a semi-path from v_1 to v_2 (i.e., a path in the weakly symmetrized graph)
+
+unilateral: v_1 is connected to v_2 iff there exists a directed path from v_1 to v_2 or a directed path from v_2 to v_1
+
+strong: v_1 is connected to v_2 iff there exists a directed path from v_1 to v_2 and a directed path from v_2 to v_1
+
+recursive: v_1 is connected to v_2 iff there exists a vertex sequence v_a,...,v_z such that v_1,v_a,...,v_z,v_2 and v_2,v_z,...,v_a,v_1 are directed paths
+
 ##  Path Length and Geodesic Distance
@@
 
-    Attribute summary:
-  the 10 most common values are:
-  JUICE     RUM   SYRUP LIQUEUR BITTERS    SODA   SPICE     GIN  BRANDY   FRUIT 
-    135     125     115      84      54      28      19      12       9       7 
-```{r STATNET:Path: Length}
+```{r STATNET:Path: Reachability}
 library(statnet)
+library(sna)
 
@@
 
- >head(snEL%e% "ingTyp")
+```{r STATNET:Path: Geodesic number & lengths}
+library(statnet)
+library(sna)
 
-[1] "FRUIT"   "LEAVES"  "JUICE"   "SYRUP"   "LIQUEUR" "RUM"
+summary(geodist(snEL, 
+        inf.replace=Inf, 
+        count.paths=TRUE, # include geodesics 
+        predecessors=FALSE,# include predecessor list
+        ignore.eval=FALSE, # ignore edge values
+        na.omit=FALSE) # remove NA-values edges
+        )
+```
 
-   >head(snEL %v% "vertex.names")
+```{r STATNET:Path: k Path Census}
+library(statnet)
+library(sna)
 
-[1] "(1-INCH-SQUARE) CHUNKS PINEAPPLE" "(1-INCH-SQUARE) PINEAPPLE CHUNKS" "2:1 SIMPLE SYRUP"                
-[4] "A WISH FOR GRACE"                 "ABRICOT VIEUX"                    "ABSINTHE BLANC"
+summary(kpath.census(snEL, 
+             maxlen = 5, 
+             mode = "graph",
+             tabulate.by.vertex = TRUE, 
+             path.comembership = c("none"), # c("none", "sum","bylength"), 
+             dyadic.tabulation = c("none") # c("none", "sum", "bylength"))
+))
+              ##**"sum"* returns a vertex by vertex matrix of source/destination path counts
+             ##**"bylength"* disaggregates these counts by path length. 
+             ##**"none"* disables this computation.
+
+```
+- Aggregate counts of paths/cycles by length (i.e., k).
+
+- Counts of paths/cycles to which each vertex belongs (when tabulate.byvertex==TRUE).
+
+- Counts of path/cycle co-memberships, potentially disaggregated by length (when the appropriate co-membership argument is set to bylength).
+
+- For path.census, counts of the total number of paths from each vertex to each other vertex, possibly disaggregated by length (if dyadic.tabulation=="bylength").
 

### 2022-03-02 docs/3. SNA - Assignments/sna_Week3/week3_Plots/Scripts_week3_Plots.Rmd
3.2.22
Can you focus a bit more on just doing the assignment and not trying to be so high speed

@@
 # IGRAPH
+
 ```{r igraph:}
@@
 
-# Plotting: network data
+## Plotting: network data
 
-###**Plot Name: smugIG_plot-R_blue-curved-small*
+### Plot Name: smugIG_plot-R_blue-curved-small\*
+
 ```{r igraph:plot: basic R }
@@
 
-###**Plot: Kamada Kawai **
-    ###**Plot Name** igraph_kamadaLayout_smug
+### **Plot: Kamada Kawai**
+
+**Plot Name** igraph_kamadaLayout_smug
+
 ```{r igraph: Plot: Kamada Kawai}
@@
 
-###**Plot: Frucherman-Reingold **
-   ###**Plot Name** igrap-smugEL_Frucherman-Reingold
+### **Plot: Frucherman-Reingold**
+
+**Plot Name** igrap-smugEL_Frucherman-Reingold
+
 ```{r igraph:}
@@
 
-# Plotting: attribute data
-###**Plot: Color & Attribute**
-              ###**Plot Name: $Vertex Naame and $color **
+## Plotting: attribute data
+
+### **Plot: Color & Attribute**
+
+**Plot Name: \$Vertex Naame and \$color**
 
@@
 # Statnet
+
 ```{r STATNET:}
@@
 
-# Plotting: network data
-# Plotting: attribute data
+## Plotting: network data
+
+```{r PLOT: Find strong components}
+library(statnet)
+library(sna)
+cd <- component.dist(
+  snEL,
+  connected="strong")
+cd$membership              #Who's in what component?
+cd$csize                   #What are the component sizes?
+                           #Plot the size distribution
+plot(1:length(cd$cdist),
+     cd$cdist/sum(cd$cdist),
+     ylim=c(0,1),
+     type="h")
+
+lgc<- #Get largest component
+  component.largest(snEL,
+                    connected="strong")
+
+#Plot g, with component membership
+gplot(snEL,
+      vertex.col=2+lgc)
+
+#Plot largest component itself 
+gplot(component.largest(
+  snEL,
+  connected="strong",
+  result="graph"))
+
+```
+
+```{r STATNET: PLOT: Find weak components}
+
+library(statnet)
+library(sna)
+cd<-component.dist(snEL,connected="weak")
+cd$membership              #Who's in what component?
+cd$csize                   #What are the component sizes?
+                           #Plot the size distribution
+plot(1:length(cd$cdist),cd$cdist/sum(cd$cdist),ylim=c(0,1),type="h")  
+lgc<-component.largest(snEL,connected="weak")  #Get largest component
+gplot(snEL,vertex.col=2+lgc)  #Plot g, with component membership
+                           #Plot largest component itself 
+gplot(component.largest(snEL,connected="weak",result="graph"))
+```
+
+```{r}
+
+```
+
+## Plotting: attribute data
+
+## Plotting:  Path Length and Geodesic Distance
+
+```{r STATNET:Path: Geodesic number & lengths}
+library(statnet)
+library(sna)
+
+gplot(geodist(snEL, 
+        inf.replace=Inf, 
+        count.paths=TRUE, 
+        predecessors=FALSE,
+        ignore.eval=FALSE, 
+        na.omit=FALSE)
+        )
+```

### 2022-03-02 docs/3. SNA - Assignments/sna_Week3/DRAFT-week3-Assignment.Rmd

@@
 ## Smuggler's Index: Network Attributes
-  - Edgelist
-  - unweghted
-  - undirected
-
-Network attributes:
-
-*statnet*
-  vertices = 274
-  directed = TRUE
-  hyper = FALSE
-  loops = FALSE
-  multiple = FALSE
-  bipartite = FALSE
- total edges = 671 
-   missing edges = 0 
-   non-missing edges = 0 
- density = 0
-
-Edge attributes:
-[1]ingTyp:
-   character valued attribute
-
-Attribute summary:
-  the 10 most common values are:
-  JUICE     RUM   SYRUP LIQUEUR BITTERS    SODA   SPICE     GIN  BRANDY   FRUIT 
-    135     125     115      84      54      28      19      12       9       7
 
@@
 ###   STATNET:   Network Description
- *statnet*
-  vertices = 274
-  directed = TRUE
-  hyper = FALSE
-  loops = FALSE
-  multiple = FALSE
-  bipartite = FALSE
- total edges = 671 
-   missing edges = 0 
-   non-missing edges = 0 
- density = 0
 
-Edge attributes:
-
- ingTyp:
-   character valued attribute
-   attribute summary:
-   the 10 most common values are:
-  JUICE     RUM   SYRUP LIQUEUR BITTERS    SODA   SPICE     GIN  BRANDY   FRUIT 
-    135     125     115      84      54      28      19      12       9       7 
 ```{r statnet: Network Summary & Attribute info, echo=TRUE}
@@
 
-component.dist(
+cd_snEL<- component.dist(
   snEL, 
-  connected= c("unilateral")) # c("strong","weak","unilateral","recursive"))
+  connected= c("strong")) # c("strong","weak","unilateral","recursive"))
+  summary(cd_snEL)    
+  View(cd_snEL)
 
-component.largest(
+  gplot.layout.circle(cd_snEL)
+
+cl_snEL <- component.largest(
   snEL, 
-  connected = c("unilateral"), #=c("strong","weak","unilateral" "recursive")
+  connected = c("strong"), #=c("strong","weak","unilateral" "recursive")
   result = c("graph"), #c("membership", "graph") 
   return.as.edgelist = FALSE)
+
+  view(summary(cl_snEL))
+  View(cl_snEL)
+
+gplot(cl_snEL)
 
@@
 
+```{r STATNET: Plot: Geodesic: Numbers and Lengths }
+library(statnet)
+library(sna)
+
+  gd_snEL <- geodist(
+    snEL, 
+    inf.replace=Inf, 
+    count.paths=TRUE, 
+    predecessors=FALSE,
+    ignore.eval=TRUE, 
+    na.omit=TRUE)
+
+   summary(gd_snEL)
+  gplot(gd_snEL)
+
+  #Examine the number of geodesics
+snEL_gdCounts <- gd_snEL$counts
+
+#Examine the geodesic distances
+snEL_gdist  <- gd_snEL$gdist
+
+```
+
 ```{r STATNET:Path: Reachability}
@@
 library(sna)
+
+  reachability(
+    snEL,
+    geodist.precomp=NULL,
+    return.as.edgelist=FALSE,
+    na.omit=FALSE)
 
@@
         )
+
+#Examine the number of geodesics
+gd_snEL$counts
+
+#Examine the geodesic distances
+gd_snEL$gdist
+
+  summary(gd_snEL)
+  gplot(gd_snEL)
+
 ```
@@
 
-# Head
-head(V(igEL)$name,10)
-head(E(igEL)$ingTyp, 10)
-
-#Tail
-tail(V(igEL)$name,10)
-tail(E(igEL)$ingTyp, 10)
-
 ```
-
-  # 20 Vertex Names
-
-      Head, 10 + Tail, 10
- [1] "AKU AKU"                    
- [2] "(1-INCH-SQUARE) CHUNKS PINEAPPLE"    
- [3] "MINT LEAVES"                
- [4] "LIME JUICE"    
- [5] "DEMERARA SYRUP"             
- [6] "PEACH LIQUEUR (SUCH AS MATHILDE, COMBIER, OR GIFFARD)"
- [7] "BLENDED LIGHTLY AGED RUM"   
- [8] "PUPULE" 
- [9] "ORANGE JUICE"               
- [10] "CINNAMON SYRUP"
- [1] "SINGAPORE SLING"                     
-      "BENEDICTINE"
-      "HONDO HATTIE'S JUNGLE PUNCH!"    
-  [4] "KAHIKO PUNCH"
-      "PASSION FRUIT HONEY"                 
-      "TRIUMVIRATE PUNCH"   
-  [7] "EUREKA PUNCH"                         
-      "YULETIDAL WAVE"
-      "RUMBUSTION PUNCH"                
- [10] "PUKA PUNCH"
 
@@
 library(igraph)
+# Head
+list(
+  head(V(igEL)$name,10),
+  tail(V(igEL)$name,10)
+  )
 
@@
 
-all_shortest_paths(igEL,
+aku_Sing <- all_shortest_paths(igEL,
                      "AKU AKU" ,
@@
 
-all_shortest_paths(igEL,
+aku_Hondo <- all_shortest_paths(igEL,
                    "AKU AKU",
@@
 
-all_shortest_paths(igEL,
+aku_Kahiko <- all_shortest_paths(igEL,
                    "AKU AKU",
                    "KAHIKO PUNCH",
-                   weights=NA)$res
+                   weights=NA)
 
-all_shortest_paths(igEL,
+aku_PFhoney <- all_shortest_paths(igEL,
                      "AKU AKU", 
@@
 
-all_shortest_paths(igEL,
+aku_Trium <- all_shortest_paths(igEL,
                    "AKU AKU",
@@
 
-  all_shortest_paths(igEL,"AKU AKU",
+aku_Eureka <- all_shortest_paths(igEL,"AKU AKU",
                      "EUREKA PUNCH",
@@
 
-  all_shortest_paths(igEL,"AKU AKU", 
+aku_YuleTide <- all_shortest_paths(igEL,"AKU AKU", 
                      "YULETIDAL WAVE" ,
@@
 
-  all_shortest_paths(igEL,
+aku_Rumbustion <-   all_shortest_paths(igEL,
                      "AKU AKU" ,
@@
 
-  all_shortest_paths(igEL,
+aku_Puka <-   all_shortest_paths(igEL,
                      "AKU AKU" ,
@@
 ```
-
-6.  *triads or transitivity,*
 
@@
 
-```{r statnet: Dyad Census , echo=TRUE}
-library(statnet)
-    sna::dyad.census(snEL)
-
-```
 ```{r iGraph: Dyad Census, echo=TRUE}
@@
 dyad.census(igEL)
+
+```
+
+```{r iGraph: Directed: GRAPH: Dyad Census, echo=TRUE}
+
+graph.density(igEL)
+    ## Density captures, at the macro-level, the proportion of dyads that are present over the possible total number of dyads in the network
+
+      # Generating a random graph for comparison
+# ?erdos.renyi.game
+      ## In an erdos.renyi.graph, each edge has the same probability of being created.
+We determine the probability and it returns a random graph with a density that equals (in expectation) this probability.
+
+igELNod <- vcount(igEL)
+
+igELDen <- graph.density(igEL)
+
+smugEL_DigRandoG <- 
+  erdos.renyi.game(
+    n = igELNod, 
+    p.or.m = igELDen, 
+    directed = T) 
+      # where n is the number of nodes, 
+      # p.or.m is the probability of drawing an edge, 
+      #directed is whether the network is directed or not
+
+#**plot(smugEL_DigRandoG, ...** in .R notebook  
+     # vertex.size = 5, 
+     # vertex.label = 1, 
+     # edge.curved = .1, 
+     # vertex.color = "tomato", 
+     # edge.arrow.size = .1, 
+     # edge.width = .5, 
+     # edge.color = "grey60")
+
+```
+
+```{r statnet: Dyad Census , echo=TRUE}
+library(statnet)
+
+  sna::dyad.census(snEL)
+
+  network.dyadcount(snEL)
+
+```
+
+```{r statnet: grecip: dyadic reciprocity & Mutuality, echo=TRUE}
+library(statnet)
+library(sna)
+
+#  the number of complete dyads (i.e., i<->j)
+mutuality(snEL)
+
+  grecip(snEL)
+
+    #proportion of symmetric dyads
+  grecip(snEL, 
+         measure = "dyadic")
+
+      # returns the ratio of mutuals to non-null dyads.
+  grecip(snEL, 
+         measure = "dyadic.nonnull")
+
+      # the proportion of edges which are reciprocated
+  grecip(snEL, 
+         measure = "edgewise")
+
+      # returns the log of the ratio of the edgewise reciprocity to the density
+  grecip(snEL, 
+         measure = "edgewise.lrr")
+
+  # The correlation measure may be interpreted as the net tendency for edges of similar relative value (with respect to the mean edge value) to occur within the same dyads.
+
+  grecip(snEL, 
+         measure = "correlation")
 
@@
 #     total number of all four triad types returned by triad census
-   sum(
+snEL_sumTCensus  <- sum(
   sna::triad.census(
     snEL,
-       mode="graph")
-     )
+    mode="graph"))
 
@@
 
-   sna::triad.classify(
+list(   sna::triad.classify(
      snEL,
@@
      mode==c("digraph")
-   )
+   ))
   #Classify the triads (1,2,3) and (2,3,4)
 
-   triad.classify(snEL,tri=c(1:14))
-   gplot(snEL,c[1:14])
+   triad.classify(snEL,tri=c(1:5))
+   gplot(snEL,c[1:5])
 
@@
 #Classify all Triad in the network
-     igraph::triad_census(igEL)
+list(igraph::triad_census(igEL))
 
@@
 #     network transitivity:
+summary(
   transitivity(igEL)
+)
 
-#     weighted network transitivity:
-#   igraph::transivity(igEL)
+summary(
+igEL_guTrans <- transitivity(igEL,
+             type = c("globalundirected"),
+             vids = NULL, #  all vertices are considered.
+             weights = NULL,
+             isolates = c("NaN", "zero"))
+)
+
+summary(
+  transitivity(igEL,
+             type = c(
+               "average"),
+             vids = NULL, #  all vertices are considered.
+             weights = NULL,
+             isolates = c("NaN", "zero"))
+)
+
+#   c("undirected", "global", "globalundirected", "localundirected", "local","average", "localaverage","localaverageundirected", "barrat", "weighted")
 
@@
 
-## Local Transivity or Clustering
+## Ego Network Transivity or Clustering
 `Local transitivity` (local clustering coefficient), is a technical description of the density of an ego network.
 
+, "KAHIKO PUNCH", "TRIUMVIRATE PUNCH", "EUREKA PUNCH", 
+                "YULETIDAL WAVE",
+                "RUMBUSTION PUNCH",
+                "PUKA PUNCH"
 ```{r iGraph:Local transitivity, echo=TRUE}
-
-#     Retrive a list of the vertices we are interested
-    V(igEL)[c("" ,
-                "", 
-                "Medici",
-                "")]
-
-#     check ego network transitivity
-transitivity(igEL,
-             type="local", 
-             vids=V(igEL)
-             [c("",
-                "", 
-                "Medici",
-                "")]) 
 #     get global clustering cofficient
@@
 
+#     check ego network transitivity
+transitivity(igEL,
+             type="local", 
+             vids=V(igEL)[c(
+               "AKU AKU", "SINGAPORE SLING", "HONDO HATTIE'S JUNGLE PUNCH!")]
+               )
 ```
 
-7.  *connectedness and.or component structure, etc.*
+## Component Structure and Membership
 
-> Distill is a publication format for scientific and technical writing, native to the web.
->
-> Learn more about using Distill for R Markdown at <https://rstudio.github.io/distill>.
-##
+### Statnet: Component STructure, Isolates, Density
+```{r Statnet: Isolates, echo=TRUE}
+
+              ## Isolates:
+
+ #List the isolates
+ isolates(snEL)
+
+ # Returns a list of the isolates in the graph or graph set
+ isolates(snEL, diag=FALSE)
+
+ # Is Ego an Isolate?
+ is.isolate(snEL, ego_exp, g=1, diag=FALSE)
+
+ # Adds n isolates to the graph (or graphs)
+ add.isolates(snEL, n_umber, return.as.edgelist = FALSE)
+
+```
+
+```{r Statnet: Network Density, echo=TRUE}
+
+            # get network density: with possible loops
+   network.density(snEL)
+          ##**WARNING: Network is multiplex - no general way to define density.**
+
+ # get network density **with** loops: statnet
+ gden(snEL, diag=F)
+
+```
+
+### Igraph: Component STructure, Isolates,
+```{r iGraph: Undirected: Component Structure, echo=TRUE}
+                ## Component Structure:
+
+    # Number of components
+ igraph::components(igEL)$no 
+      ##**NOTE:** $no prevents a list of components from being printed
+
+# Size of each component
+ igraph::components(igEL)$csize
+
+```
+
+```{r iGraph: Undirected: network density, echo=TRUE}
+
+    #get network density **with** loops
+ network.density(igEL)
+ class(igEL)
+          ##**NOTE** provides an incorrect density calculation 
+          ## as the default assumes that loops are not included but does not remove them
+
+```
+ **Igraph** provides an incorrect density calculation as the default assumes  that loops are not included but does not remove them.
+
+ Therefore, the default calculation includes the loops in the numerator but not the denominator of the density calculation.
+
+# Week 3:
+
+## Network Density
+
+ The density of a network is defined as the proportion of ties present out of all possible ties in a network.
+
+ **Note:**
+
+ the network density command ignores edge values at present.
+
+ If loops are present or there are multiple edges between two nodes, then the results may not make sense.
+
+```{r Statnet: Network Density, echo=TRUE}
+
+            # get network density: with possible loops
+   network.density(snEL)
+          ##**WARNING: Network is multiplex - no general way to define density.**
+
+ # get network density **with** loops: statnet
+
+  gden(snEL, diag=F)
+
+```
+
+ **Igraph** provides an incorrect density calculation as the default assumes  that loops are not included but does not remove them.
+
+```{r iGraph: edge density, echo=TRUE}
+library(igraph)
+    #get network density **with** loops
+edge_density(igEL, loops = FALSE)
+
+ class(igEL)
+          ##**NOTE** provides an incorrect density calculation 
+          ## as the default assumes that loops are not included but does not remove them
+
+```
+
+## Vertex Degree
+ **Vertex degree** is a description of an individual node; each vertex in a network may have a different node degree.
+
+ *Node Degree:*
+   node degree is one measure of node centrality or popularity; 
+ Node degree cis a count of the relationships that a node is involved in or the count of the edges that are incident to a vertex
+
+ **use the network degree command to:**
+   *  compute network summary statistics (such as average network degree);
+ *  graph the network degree distribution; or
+ *  identify particular nodes (such as the five nodes with the most contacts).
+
+```{r Statnet: Vertex Degree, echo=TRUE}
+library(statnet)
+library(sna)
+      # statnet: Calculate average network degree
+summary(sna::degree(snEL, 
+             g=1, 
+             nodes=NULL, 
+             gmode="digraph", #directed;
+             diag=FALSE, #excludes diagonals 
+             tmaxdev=FALSE, 
+             cmode="indegree", 
+             rescale=FALSE, 
+             ignore.eval=FALSE))
+          # ignores loops or self-nominations 
+summary(
+  snEL_vd <- sna::degree(snEL, 
+             g=1, 
+             nodes= NULL, 
+             gmode="graph", #undirected
+             diag=TRUE, #includes diagonals 
+             tmaxdev=F, 
+             cmode="freeman", 
+             rescale=F, #  scores rescaled to sum to 1.
+             ignore.eval=FALSE))
+plot(snEL_vd)
+#**cmode=* degree centrality being computed. 
+#*"indegree"
+#*"outdegree"
+#**DEFAULT*"freeman" refer to the indegree, outdegree, 
+#*total (Freeman) degree measures, respectively. 
+```
+
+```{r iGraph: Undirected: Vertex Degree, echo=TRUE}
+# igraph: Calculate average network degree
+ # provides node name along with node degree
+
+ # includes loops
+  plot(igraph::degree(igEL))
+
+```
+
+## Network Degree Summary Statistics
+
+```{r Statnet: , echo=TRUE}
+library(statnet)
+library(sna)   
+   # Basic R: get summary statistics for node attributes
+
+summary(snEL_Deg <- 
+           sna::degree(snEL))
+    plot(snEL_Deg)
+
+      # provides range, mean, median and standard deviation of a vector.
+
+ # get summary statistics for node degree for the binary network degree
+
+snEL_degVtx <- data.frame(
+   name=snEL%v%"vertex.names",
+   totdegree=sna::degree(snEL),
+   indegree=sna::degree(snEL, cmode="indegree"),
+   outdegree=sna::degree(snEL, cmode="outdegree"))
+gplot(snEL_degDF)
+
+snEL_degVtx <- data.frame(
+   name=snEL%v%"vertex.names",
+   totdegree=sna::degree(snEL))
+
+   gplot(snEL_degDF)
+  summary(snEL_degVNme)
+
+snEL_degVNme <- data.frame(
+   name=snEL%v%"Aku Aku",
+    outdegree=sna::degree(snEL, cmode="outdegree"))
+   gplot(snEL_degVNme)
+    summary(snEL_degVNme)
+
+snEL_degVNme <- data.frame(
+   name=snEL%v%"(1-INCH-SQUARE) CHUNKS PINEAPPLE",
+   indegree=sna::degree(snEL, cmode="indegree"))
+
+gplot(snEL_degVNme)
+summary(snEL_degVNme)
+
+snEL_degVNme <- data.frame(
+   name=snEL%v%"MINT LEAVES",
+   outdegree=sna::degree(snEL, cmode="outdegree"))
+
+gplot(snEL_degVNme)
+summary(snEL_degVNme)
+
+snEL_degVNme <- data.frame(
+   name=snEL%v%"DEMERARA SYRUP",
+   outdegree=sna::degree(snEL, cmode="outdegree"))
+
+gplot(snEL_degVNme)
+summary(snEL_degVNme)
+
+odeg_peachLqr <- data.frame(
+   name=snEL%v%"PEACH LIQUEUR (SUCH AS MATHILDE, COMBIER, OR GIFFARD)",
+   outdegree=sna::degree(snEL, cmode="outdegree"))
+gplot(odeg_peachLqr)
+summary(odeg_peachLqr)
+
+odeg_blaRum <- data.frame(
+   name=snEL%v%" BLENDED LIGHTLY AGED RUM",
+   outdegree=sna::degree(snEL, cmode="outdegree"))
+gplot(out_blaRum)
+summary(out_blaRum)
+
+odeg_val3 <- data.frame(
+
+   outdegree=sna::degree(snEL, cmode="outdegree"))
+
+```
+
+ 6/274 vertices, named, from 1bfe0b4:
+[1] (1-INCH-SQUARE) CHUNKS PINEAPPLE                     
+[2] MINT LEAVES                                          
+[3] LIME JUICE                                           
+[4] DEMERARA SYRUP                                       
+[5] PEACH LIQUEUR (SUCH AS MATHILDE, COMBIER, OR GIFFARD)
+[6] BLENDED LIGHTLY AGED RUM
+
+## Centrilization
+
+```{r iGraph: Undirected: DEGREE CENTRALITY: dnkIng}
+library(igraph)
+library(tidyverse)
+
+plot(centr_degree(igEL)$res)
+
+summary(
+  centr_degree(igEL,
+  mode = c("all"),
+  loops = TRUE,
+  normalized = TRUE)$res)
+
+plot(
+  centr_degree(igEL,mode = c("all"))$res)
+
+summary(
+centr_degree(igEL,
+  mode = c("all"),
+  loops = TRUE,
+  normalized = TRUE)$centralization
+)
+
+summary(
+centr_degree(igEL,
+  mode = c("all"),
+  loops = TRUE,
+  normalized = TRUE)$theoretical_max
+)
+
+```
+
+## Degree Centrality
+We can break large social networks down into their constituent parts.
+These constituent parts are referred to as “motifs”.
+The most basic motif consists of two nodes and is called a dyad.
+Edges in a network signify the presence or absence of dyadic relations.
+It follows that a dyad in an undirected network can have two unique configurations: connected or disconnected; and three unique configurations in a directed network (mutual, assymetric, and null
+
+```{r iGraph: Directed: GRAPH: Dyad Census, echo=TRUE}
+
+graph.density(igEL)
+    ## Density captures, at the macro-level, the proportion of dyads that are present over the possible total number of dyads in the network
+
+      # Generating a random graph for comparison
+# ?erdos.renyi.game
+      ## In an erdos.renyi.graph, each edge has the same probability of being created.
+We determine the probability and it returns a random graph with a density that equals (in expectation) this probability.
+
+igELNod <- vcount(igEL)
+
+igELDen <- graph.density(igEL)
+
+smugEL_DigRandoG <- 
+  erdos.renyi.game(
+    n = igELNod, 
+    p.or.m = igELDen, 
+    directed = T) 
+      # where n is the number of nodes, 
+      # p.or.m is the probability of drawing an edge, 
+      #directed is whether the network is directed or not
+
+#**plot(smugEL_DigRandoG, ...** in .R notebook  
+     # vertex.size = 5, 
+     # vertex.label = 1, 
+     # edge.curved = .1, 
+     # vertex.color = "tomato", 
+     # edge.arrow.size = .1, 
+     # edge.width = .5, 
+     # edge.color = "grey60")
+
+```
+
+```{r iGraph: Directed: Degree Centrality}
+# Degree centrality is calculated using the degree function in R. It returns how many edges each node has.
+view(degree(igEL))
+
+ingT_deg <- igEL
+V(ingT_deg)$degree <- degree(ingT_deg) # assignment
+
+# plot(ingT_deg, 
+#     vertex.label.cex = .6, 
+#     vertex.label.color = "black", 
+#     vertex.size = V(igEL)$degree, 
+#     vertex.label.cex = .2) # sized by degree
+
+```
+
+```{r iGraph: Directed: Betweenness Centrality}
+
+view(betweenness(igEL, directed = FALSE))
+
+# view(betweenness(igEL, directed = TRUE))
+              # Yeilds 0
+
+ingTypEL_Between <- igEL
+# We can again assign the output of betweenness() to a variable in the network and size the nodes according to it.
+
+V(ingTypEL_Between)$betweenness <- 
+  betweenness(ingTypEL_Between, 
+              directed = F)
+
+# plot(ingTypEL_Between, 
+#     vertex.label.cex = .6, 
+#     vertex.label.color = "black", 
+#     vertex.size = V(ingTypEL_Between)$betweenness) # sized by betweenness
+
+```
+
+```{r iGraph: UnDirected:  Closeness Centrality}
+
+view(closeness(igEL))
+
+  # We assign it to a node variable and plot the network, adjusting node size by closeness.
+ingTyp_Cent <- igEL #**UNDIRECTED **
+
+V(ingTyp_Cent)$closeness <- closeness(ingTyp_Cent)
+
+View(ingTyp_Cent)
+
+# plot(ingTyp_Cent,
+#     vertex.label.cex = .6, 
+#     vertex.label.color = "black", 
+#     vertex.size = V(ingTyp_Cent)$closeness/max(V(ingTyp_Cent)$closeness) * 20)
+
+```
+
+Degree centrality only takes into account the number of edges for each node, but it leaves out information about ego’s alters
+```{r iGraph: Directed: Eigenvector Centrality}
+
+view(evcent(igEL)$vector)
+# view(evcent(igEL)$vector)
+ingTyp_Vector <- igEL
+V(ingTyp_Vector)$eigenvector <- evcent(ingTyp_Vector)$vector
+
+# plot(ingTyp_Vector,
+#     vertex.label.cex = .6, 
+#     vertex.label.color = "black", 
+#     vertex.size = V(ingTyp_Vector)$eigenvector/max(V(ingTyp_Vector)$eigenvector) * 20)
+```
+
+```{r iGraph: Directed: Bonacich Centrality}
+
+ingTyp_Cent <- igEL
+
+V(ingTyp_Cent)$bonacich <- 
+  power_centrality(ingTyp_Cent, exponent = -2, rescale = T)
+
+V(ingTyp_Cent)$bonacich <- 
+  ifelse(V(ingTyp_Cent)$bonacich < 0, 0, V(ingTyp_Cent)$bonacich)
+```
+
+```{r iGraph: Directed: Page Rank}
+
+ingTyp_Cent <- igEL
+
+V(ingTyp_Cent)$page_rank <- page_rank(ingTyp_Cent, directed = TRUE)$vector
+
+```
+
+ plot(ingTyp_Cent,
+     vertex.label.cex = .6, 
+     vertex.label.color = "black", 
+     vertex.size = V(ingTyp_Cent)$page_rank/max(V(ingTyp_Cent)$page_rank) * 20)

### 2022-03-02 docs/3. SNA - Assignments/sna_Week3/Week3_Notebook.Rmd

--- 2022-02-25 docs/3. SNA - Assignments/sna_Week3/Week3_Notebook.Rmd
@@
 output: html_notebook
+--
+
+#   Project Varriables
+
+    Raw Data:
+  indx_SmugglerCove_recip
+
+    DataFrame:
+  smugCovIdx
+            "dnkNam" "ingNam" "dnkIng" "ingTyp"
+  network_nodes <- smugCovIdx << "dnkNam"
+
+    Matrix:
+
+    Network Objects: EDGE LIST
 
@@
 ```
+
+smugEL_sn
+
+[1] "network"
+
+Network attributes:
+  vertices = 274 
+  directed = TRUE 
+  hyper = FALSE 
+  loops = FALSE 
+  multiple = TRUE 
+  bipartite = FALSE 
+  total edges= 672 
+    missing edges= 0 
+    non-missing edges= 672
+
+ Vertex attribute names: 
+    dnkNam vertex.names
+
+ Edge attribute names: 
+    dnkIng ingTyp
 
@@
 
+gtrans(smugEL_sn)
+proportion of transitive triads
+
+symmetrize( smugEL_sn, rule = "weak") 
+symmetrize so i<->j iff i->j OR i<-j
+
+symmetrize( smugEL_sn, rule = "strong") 
+symmetrize so i<->j iff i->j OR i<-j
+
+dyad.census(smugEL_sn) 
+MAN dyad census
+
+triad.census(smugEL_sn) 
+standard directed triad census
+
 ```{r igraph: Network Description, echo=TRUE}

### 2022-03-02 docs/3. SNA - Assignments/sna_Week3/week3_Plots/Scripts_week3_Plots.Rmd

@@
+#: Visualization: ggplot2
+```{r Visualization: ggplot2}
+
+# Dependencies
+ library(network)
+ library(sna)
+ library(ggplot2)
+
+library(visNetwork)
+library(threejs)
+ library(networkD3)
+ library(ndtv)
+ # ggnetwork - This package allows to pass network objects to ggplot2 and provides geometries to plot their elements.
+
+ library(ggnetwork)
+
+  # visualize your network graphs 
+ library(GGally)
+
+## [network visualization with ggplot2]
+
+```
+
+# graph the SMUG network
+
+smug_attributes <- smugCovIdx
+smug_edj <- smugCovIdx[2:3]
+View(smug_edj)
+#V1: dnkIng
+#V2: ingTyp
+
+smugNet <- 
+  graph.edgelist(as.matrix(smug_edj), directed = T)
+
+V(smugNet)$dnkIng <- 
+  smug_attributes$dnkIng[match(V(smugNet)$name, smug_attributes$ingTyp)]
+
+V(smugNet)$dnkNam <- 
+  smug_attributes$dnkNam[
+    match(V(
+      smugNet)$name,
+      smug_attributes$dnkIng)
+    ]
+summary(smugNet)
+
+###**PLOT** in .R Doc
+
 # IGRAPH

### 2022-03-04 docs/3. SNA - Assignments/sna_Week3/DRAFT-week3-Assignment.Rmd
3.2.22 I'm not sure what day it is, and does it really matter?

@@
 ## Smuggler's Index: Network Attributes 
+```{r Network Size}
+
+  print(snEL)
+  print(igEL)
+
+  summary(snEL)
+  summary(igEL)
+
+```
 
@@
 - Edge Attribute Names: [1] "ingTyp"
-```{r igraph: Network Description, echo=TRUE}
+```{r igraph: Network & Attribute Descripions, echo=TRUE}
 
-summary(igEL)
+## Network Size
 #     Count Vertices
     vcount(igEL)
-
 #     Count Edges
     ecount(igEL)
+
+## Network Attributes
 
@@
 
+# vertex attribute names
+  igraph::vertex_attr_names(igEL)
+
+#   edge attributes  names
+  igraph::edge_attr_names(igEL)
+
+#   summarize numeric network attribute
+#**summary(E(igEL)$weight)*
+
 ```
 
-```{r igraph: Vertex & Attribute info, echo=TRUE}
+```{r igraph: Vetex & Edge Names, echo=TRUE}
 library(igraph)
@@
 #     access vertex attribute 
-  head(V(igEL)$name,20)
-#     Generate a list the names of vertex attributes
-  print(igraph::vertex_attr_names(igEL))
+  head(
+    V(igEL)$name,20)
 
@@
   head(E(igEL)$ingTyp, 20)
-
-#   Generate a list the names of edge attributes  
-  igraph::edge_attr_names(igEL)
-
-#   summarize numeric network attribute
-  summary(E(igEL)$weight)
 
@@
 ```{r statnet: Network Summary & Attribute info, echo=TRUE}
+print(snEL)
 
-summary(snEL)
-print(snEL)
-#     access vertex attributes
- head(snEL %v% "vertex.names")
+print(summary(snEL))
 
@@
   network::list.vertex.attributes(snEL)
-
-#     access edge attribute
-  head(snEL%e% "ingTyp")
-
 #  Generate a list the names of edge attributes
@@
 #   summarize numeric network attribute
-  summary(snEL  %v% "name")
+  summary(snEL%v%"name")
+  summary(snEL%v%"ingNam")
+  summary(snEL%v%"dnkNam")
+  summary(snEL%e%"ingTyp")
+
+#     access vertex & edge attribute names
+ head(snEL %v% "vertex.names")
+#     access edge attribute
+  head(snEL%e%"ingTyp")
 
 ```
-
-```{r STATNET: Component Size Distribution}
-library(statnet)
-library(sna)
-
-cd_snEL<- component.dist(
-  snEL, 
-  connected= c("strong")) # c("strong","weak","unilateral","recursive"))
-  summary(cd_snEL)    
-  View(cd_snEL)
-
-  gplot.layout.circle(cd_snEL)
-
-cl_snEL <- component.largest(
-  snEL, 
-  connected = c("strong"), #=c("strong","weak","unilateral" "recursive")
-  result = c("graph"), #c("membership", "graph") 
-  return.as.edgelist = FALSE)
-
-  view(summary(cl_snEL))
-  View(cl_snEL)
-
-gplot(cl_snEL)
-
-```
-
-##### Details: Component Size Distribution 
-Components are maximal sets of mutually connected vertices; depending on the definition of “connected” one employs, one can arrive at several types of components.
-Those supported here are as follows (in increasing order of restrictiveness):
-
-weak: v_1 is connected to v_2 iff there exists a semi-path from v_1 to v_2 (i.e., a path in the weakly symmetrized graph)
-
-unilateral: v_1 is connected to v_2 iff there exists a directed path from v_1 to v_2 or a directed path from v_2 to v_1
-
-strong: v_1 is connected to v_2 iff there exists a directed path from v_1 to v_2 and a directed path from v_2 to v_1
-
-recursive: v_1 is connected to v_2 iff there exists a vertex sequence v_a,...,v_z such that v_1,v_a,...,v_z,v_2 and v_2,v_z,...,v_a,v_1 are directed paths
 
@@
 dyad.census(igEL)
+print("Undirected graph, $asym is 0")
 
@@
 library(statnet)
+library(sna)
 
     sna::dyad.census(snEL)
+  print("statnet thinks it's an undirected network, so there are no mutual ties because it's an undirected network and the 'names' and 'ingredients' in a recipie do not have a reciprocal relationship.
+If anything the 'flow of info' moves from 'Drink Name' to 'Drink Ingredient' to 'Ingredient type'.
+The Drink name determines the recipie ingredients, but we're unable to identify a drink by calling on individual ingredients in a recipie")
 
@@
 ```
+
+gplot(sna::dyad.census(snEL))
 
@@
 # Week 3:
+
+```{r STATNET: Component Size Distribution}
+library(statnet)
+library(sna)
+
+cd_snEL<- component.dist(
+  snEL, 
+  connected= c("strong")) # c("strong","weak","unilateral","recursive"))
+  summary(cd_snEL)    
+  View(cd_snEL)
+
+  gplot.layout.circle(cd_snEL)
+
+cl_snEL <- component.largest(
+  snEL, 
+  connected = c("strong"), #=c("strong","weak","unilateral" "recursive")
+  result = c("graph"), #c("membership", "graph") 
+  return.as.edgelist = FALSE)
+
+  view(summary(cl_snEL))
+  View(cl_snEL)
+
+gplot(cl_snEL)
+
+```
+
+##### Details: Component Size Distribution 
+Components are maximal sets of mutually connected vertices; depending on the definition of “connected” one employs, one can arrive at several types of components.
+Those supported here are as follows (in increasing order of restrictiveness):
+
+weak: v_1 is connected to v_2 iff there exists a semi-path from v_1 to v_2 (i.e., a path in the weakly symmetrized graph)
+
+unilateral: v_1 is connected to v_2 iff there exists a directed path from v_1 to v_2 or a directed path from v_2 to v_1
+
+strong: v_1 is connected to v_2 iff there exists a directed path from v_1 to v_2 and a directed path from v_2 to v_1
+
+recursive: v_1 is connected to v_2 iff there exists a vertex sequence v_a,...,v_z such that v_1,v_a,...,v_z,v_2 and v_2,v_z,...,v_a,v_1 are directed paths
 

### 2022-03-04 docs/3. SNA - Assignments/sna_Week3/DRAFT-week3-Assignment.Rmd
3.4.22

@@
 # Week 2: Scripts
+
 ## Smuggler's Index: Network Attributes 
@@
 
+## Dyad Census
+
+Classifies all dyads in the network as:
+- Mutual - Reciprocal (mutual) 
+- Asymmetric -  (non-mutual), 
+- Null - Absent
+
+```{r iGraph: Dyad Census, echo=TRUE}
+library(igraph)
+
+dyad.census(igEL)
+print("Undirected graph, $asym is 0")
+
+```
+
+```{r iGraph: Dyad: Graph Density / Edge Density, echo=TRUE}
+library(igraph)
+
+  graph.density(igEL)
+
+summary(
+  graph.density(igEL)
+)
+
+    ## Density captures, at the macro-level, the proportion of dyads that are present over the possible total number of dyads in the network
+
+  edge_density(igEL)
+
+summary(
+   edge_density(igEL)
+)
+
+      # Generating a random graph for comparison
+# erdos.renyi.game
+      ## In an erdos.renyi.graph, each edge has the same probability of being created.
+We determine the probability and it returns a random graph with a density that equals (in expectation) this probability.
+
+igEL_Nod <- vcount(igEL)
+
+igEL_Den <- graph.density(igEL)
+
+ igEL_randoGraph <- erdos.renyi.game(
+    n = igEL_Nod, 
+    p.or.m = igEL_Den, 
+    directed = T) 
+      # where n is the number of nodes, 
+      # p.or.m is the probability of drawing an edge, 
+      #directed is whether the network is directed or not
+ class(igEL_randoGraph)
+ summary(igEL_randoGraph)
+
+ print_all(igEL_randoGraph)
+
+```
+
+plot(igEL_randoGraph,
+      vertex.size = 5, 
+      vertex.label = NA, 
+      edge.curved = .1, 
+      vertex.color = "tomato", 
+      edge.arrow.size = .1, 
+      edge.width = .5, 
+     edge.color = "grey60")
+
+```{r statnet: Dyad Count / Dyad Census , echo=TRUE}
+library(statnet)
+library(sna)
+
+ network.dyadcount(snEL)
+ sna::dyad.census(snEL)
+
+     print("statnet thinks it's a directed network, so there are no mutual ties because it's an undirected network and the 'names' and 'ingredients' in a recipie do not have a reciprocal relationship.
+If anything the 'flow of info' moves from 'Drink Name' to 'Drink Ingredient' to 'Ingredient type'.
+The Drink name determines the recipie ingredients, but we're unable to identify a drink by calling on individual ingredients in a recipie")
+
+```
+
+gplot(sna::dyad.census(snEL))
+
+```{r statnet: GRecip / Mutuality, echo=TRUE}
+library(statnet)
+library(sna)
+
+#  the number of complete dyads (i.e., i<->j)
+mutuality(snEL)
+
+  grecip(snEL)
+
+    #proportion of symmetric dyads
+  grecip(snEL, 
+         measure = "dyadic")
+
+      # returns the ratio of mutuals to non-null dyads.
+  grecip(snEL, 
+         measure = "dyadic.nonnull")
+
+      # the proportion of edges which are reciprocated
+  grecip(snEL, 
+         measure = "edgewise")
+
+      # returns the log of the ratio of the edgewise reciprocity to the density
+  grecip(snEL, 
+         measure = "edgewise.lrr")
+
+  # The correlation measure may be interpreted as the net tendency for edges of similar relative value (with respect to the mean edge value) to occur within the same dyads.
+
+    grecip(snEL, 
+         measure = "correlation") 
+```
+
+## Triad Census
+
+Classifies all triads in the network.
+
+```{r iGraph: Triad Census, echo=TRUE}
+library(igraph)
+#Classify all Triad in the network
+
+sum(
+  triad_census(igEL)
+)
+
+list(
+  triad_census(igEL)
+)
+
+```
+plot(
+  triad_census(igEL)
+)
+
+```{r statnet: Triad Census / Triad Classify, echo=TRUE}
+library(sna)
+
+#     total number of all four triad types returned by triad census
+sum(
+  sna::triad.census(
+    snEL,
+    mode="graph"))
+
+#     Classify all Triad in the network: Undirected Network
+ sna::triad.census(
+     snEL,
+     mode="graph")
+
+#Davis and Leinhardt classification of the triad classification scheme 
+   # describes each triad by a string of four elements: 
+   # the number of mutual (complete) dyads within the triad; 
+   # the number of asymmetric dyads within the triad; 
+   # the number of null (empty) dyads within the triad; 
+   #and a configuration code for the triads which are not uniquely distinguished by the first three distinctions.
+
+sna::triad.classify(
+     snEL,
+     tri=c(1,2,3),
+     mode==c("graph")
+   )
+
+```
+
+## Transitivity or Global Clustering
+
+Perportion of connected triads to complete triads
+
+```{r iGraph: Transitivity Network, echo=TRUE}
+library(igraph)
+
+# Calculate the maximal (weakly or strongly) connected components of a graph
+igraph::cluster.distribution()
+
+#     network transitivity:
+ transitivity(igEL)
+
+ summary(  
+  transitivity(
+   igEL,
+   type = c("undirected"),
+   vids = NULL, #  all vertices are considered.
+   weights = NULL,
+   isolates = c("NaN", "zero"))
+)
+
+summary( 
+ transitivity(igEL,
+             type = c("globalundirected"),
+             vids = NULL, #  all vertices are considered.
+             weights = NULL,
+             isolates = c("NaN", "zero"))
+)
+
+summary(
+  transitivity(igEL,
+             type = c("localundirected"),
+             vids = NULL, #  all vertices are considered.
+             weights = NULL,
+              isolates = c("NaN", "zero"))
+)
+#   c("undirected", "global", "globalundirected", "localundirected", "local","average", "localaverage","localaverageundirected", "barrat", "weighted")
+
+```
+plot(
+  transitivity(igEL,
+             type = c("localundirected"),
+             vids = NULL, #  all vertices are considered.
+             weights = NULL,
+              isolates = c("NaN", "zero"))
+)
+```{r statnet: Transitivity:, echo=FALSE}
+library(statnet)
+library(sna)
+
+#   Networks transitivity:
+print("Networks transitivity:")  
+print("Note: where missing values prevent the assessment of whether a triple is transitive, that triple is omitted.")
+
+print("use.adjacency=FALSE -> 0: completely intransitive ")        
+  gtrans(snEL,
+         mode="digraph", #"digraph" for triads 
+         use.adjacency=FALSE)
+
+print("use.adjacency=TRUE -> 1: completely transitive")
+  gtrans(snEL, 
+         mode="graph", # No triads
+         use.adjacency=TRUE)
+
+# Unaffected by mode=digrag/graph, diag(nal)=F/T
+
+#   measure = 
+  ## c("weak", "strong", "weakcensus", "strongcensus", "rank", "correlation"),
+
+print("Weak Ties: fraction of potentially intransitive triads returned")
+  ## Weak Ties
+  gtrans(
+    snEL,
+    g=NULL,
+    mode="graph", 
+    measure = c("weak"),
+    use.adjacency=FALSE)
+
+  gtrans(
+    snEL,
+    g=NULL,
+    mode="graph", 
+    measure = c("weak"),
+     use.adjacency=TRUE)
+
+print("weak census: total number of transitive triads is computed")  
+  ## "weakcensus"
+  gtrans(
+    snEL,
+    g=NULL,
+    mode="graph", 
+    measure = c("weakcensus"),
+    use.adjacency=TRUE)
+
+  gtrans(
+    snEL,
+    g=NULL,
+    mode="graph", 
+    measure = c("weakcensus"),
+    use.adjacency=FALSE)
+
+print("strong ties")  
+  ## Strong Ties
+  gtrans(
+    snEL,
+    g=NULL,
+    mode="graph", 
+    measure = c("strong"),
+    use.adjacency=TRUE)
+
+  gtrans(
+    snEL,
+    g=NULL,
+    mode="graph", 
+    measure = c("strong"),
+    use.adjacency=FALSE)
+
+print("strongcensus: total number of all (in/transitive) triad sets considered")
+  ## "strongcensus"
+gtrans(
+    snEL,
+    g=NULL,
+    mode="graph", 
+    measure = c("strongcensus"),
+    use.adjacency=FALSE)
+
+  gtrans(
+    snEL,
+    g=NULL,
+    mode="graph", 
+    measure = c("strongcensus"),
+    use.adjacency=TRUE)
+
+print("rank")  
+  ##  "rank"
+gtrans(
+    snEL,
+    g=NULL,
+    mode="graph", 
+    measure = c( "rank"),
+    use.adjacency=FALSE)
+
+  gtrans(
+    snEL,
+    g=NULL,
+    mode="graph", 
+    measure = c( "rank"),
+    use.adjacency=TRUE)
+
+  ## "correlation"
+print("correlation: the matrix correlation of the valued adjacency matrix A with its second power (i.e., A^2), omitting diagonal entries where inapplicable.")
+
+  gtrans(
+    snEL,
+    g=NULL,
+    mode="graph", 
+    measure = c("correlation"),
+    use.adjacency=TRUE)
+
+```
+
+## Ego Network Transivity or Local Clustering
+
+`Local transitivity` (local clustering coefficient), is a technical description of the density of an ego network.
+
+```{r iGraph: Local / Ego Network Transitivity, echo=TRUE}
+#     get global clustering cofficient
+  transitivity(igEL,
+               type="global")
+
+#     get average local clustering coefficient
+  transitivity(igEL,
+               type="average")
+
+#     check ego network transitivity
+transitivity(igEL,
+             type="undirected",
+             vids=V(igEL)[c(
+               "AKU AKU", 
+               "SINGAPORE SLING",
+               "HONDO HATTIE'S JUNGLE PUNCH!")])
+
+```
+
+```{r statnet: Local / Ego Network Transitivity}
+library(statnet)
+library(sna)
+print("Ego Network Transitivity")
+
+print("use.adjacency=TRUE -> 1: completely transitive")
+gtrans(
+    snEL,
+    g=snEL%v%"AKU AKU",
+    use.adjacency=T)
+
+gtrans(
+    snEL,
+    g=snEL%v%"LIME JUICE",
+    use.adjacency=T)
+
+print("use.adjacency=FALSE -> 0: completely intransitive ")        
+gtrans(
+    snEL,
+    g=snEL%v%"AKU AKU",
+    use.adjacency=FALSE)
+
+gtrans(
+    snEL,
+    g=snEL%v%"LIME JUICE",
+    use.adjacency=FALSE)
+
+#   measure = 
+  ## c("weak", "strong", "weakcensus", "strongcensus", "rank", "correlation"),
+
+print("strong ties")  
+  ## Strong Ties
+  gtrans(
+    snEL,
+      g=snEL%v%"AKU AKU",
+    mode="digraph", 
+    measure = c("strong"),
+    use.adjacency=FALSE)
+
+  gtrans(
+    snEL,
+    g=snEL[c(
+      "AKU AKU,KAHIKO PUNCH", "TRIUMVIRATE PUNCH", "EUREKA PUNCH",
+      "YULETIDAL WAVE","RUMBUSTION PUNCH", "PUKA PUNCH")],
+    mode="graph", 
+    measure = c("strong"),
+    use.adjacency=FALSE)
+
+  gtrans(
+    snEL,
+    g=snEL%v%"LIME JUICE",
+    mode="graph", 
+    measure = c("strong"),
+    use.adjacency=F)
+
+ gtrans(
+    snEL,
+     g=snEL[c(
+       "LIME JUICE","2:1 SIMPLE SYRUP","ALLSPICE BERRIES",
+       "APPLE BRANDY"  ,"ABSINTHE BLANC","AQUAVIT","AMARO AVERNA")],
+    mode="graph", 
+    measure = c("strong"),
+    use.adjacency=F)
+
+print("strongcensus: total number of all (in/transitive) triad sets considered")
+
+print("strongcensus")
+    ## "strongcensus"
+  gtrans(
+    snEL,
+      g=snEL%v%"AKU AKU",
+    mode="graph", 
+    measure = c("strongcensus"))
+
+gtrans(
+    snEL,
+    g=snEL[c(
+      "AKU AKU,KAHIKO PUNCH", "TRIUMVIRATE PUNCH", "EUREKA PUNCH",
+      "YULETIDAL WAVE","RUMBUSTION PUNCH", "PUKA PUNCH")],
+    mode="graph", 
+    measure = c("strongcensus"))
+
+gtrans(
+    snEL,
+   g=snEL%v%"LIME JUICE",
+    mode="graph", 
+    measure = c("strongcensus"))
+
+  gtrans(
+    snEL,
+     g=snEL[c("LIME JUICE","2:1 SIMPLE SYRUP","ALLSPICE BERRIES","APPLE BRANDY"  ,"ABSINTHE BLANC","AQUAVIT","AMARO AVERNA")],
+    mode="graph", 
+    measure = c("strongcensus"))
+
+```
+
 ##  Path Length and Geodesic Distance
@@
 
+#uses a BFS to find the number and lengths of geodesics between all nodes
+
  gd_snEL <- geodist(
     snEL, 
-    inf.replace=Inf, 
+    inf.replace=.5, #geodesics do not exist, substitute value
     count.paths=TRUE, 
-    predecessors=FALSE,
-    ignore.eval=TRUE, 
-    na.omit=TRUE)
+    predecessors=T, # return predecessor list
+    ignore.eval=F, # ignore edge values
+    na.omit=F) # remove NA values
 
 summary(gd_snEL)
-  gplot(gd_snEL)
+view(
+  list(gd_snEL))
 
@@
 ```
+gplot(gd_snEL)
+gplot(snEL_gdist)
 
@@
 
+summary(
   reachability(
@@
     na.omit=FALSE)
-
+)
 ```
@@
 ```{r iGraph:Nodes: Path: Length, echo=TRUE}
+
 library(igraph)
@@
 
-## Dyad Census
-
-Classifies all dyads in the network as:
-- Mutual - Reciprocal (mutual) 
-- Asymmetric -  (non-mutual), 
-- Null - Absent
-
-```{r iGraph: Dyad Census, echo=TRUE}
-library(igraph)
-
-dyad.census(igEL)
-print("Undirected graph, $asym is 0")
-
-```
-
-```{r iGraph: Directed: GRAPH: Dyad Census, echo=TRUE}
-
-graph.density(igEL)
-    ## Density captures, at the macro-level, the proportion of dyads that are present over the possible total number of dyads in the network
-
-      # Generating a random graph for comparison
-# ?erdos.renyi.game
-      ## In an erdos.renyi.graph, each edge has the same probability of being created.
-We determine the probability and it returns a random graph with a density that equals (in expectation) this probability.
-
-igELNod <- vcount(igEL)
-
-igELDen <- graph.density(igEL)
-
-smugEL_DigRandoG <- 
-  erdos.renyi.game(
-    n = igELNod, 
-    p.or.m = igELDen, 
-    directed = T) 
-      # where n is the number of nodes, 
-      # p.or.m is the probability of drawing an edge, 
-      #directed is whether the network is directed or not
-
-#**plot(smugEL_DigRandoG, ...** in .R notebook  
-     # vertex.size = 5, 
-     # vertex.label = 1, 
-     # edge.curved = .1, 
-     # vertex.color = "tomato", 
-     # edge.arrow.size = .1, 
-     # edge.width = .5, 
-     # edge.color = "grey60")
-
-```
-
-```{r statnet: Dyad Census , echo=TRUE}
-library(statnet)
-library(sna)
-
-    sna::dyad.census(snEL)
-  print("statnet thinks it's an undirected network, so there are no mutual ties because it's an undirected network and the 'names' and 'ingredients' in a recipie do not have a reciprocal relationship.
-If anything the 'flow of info' moves from 'Drink Name' to 'Drink Ingredient' to 'Ingredient type'.
-The Drink name determines the recipie ingredients, but we're unable to identify a drink by calling on individual ingredients in a recipie")
-
-    network.dyadcount(snEL)
-
-```
-
-gplot(sna::dyad.census(snEL))
-
-```{r statnet: grecip: dyadic reciprocity & Mutuality, echo=TRUE}
-library(statnet)
-library(sna)
-
-#  the number of complete dyads (i.e., i<->j)
-mutuality(snEL)
-
-  grecip(snEL)
-
-    #proportion of symmetric dyads
-  grecip(snEL, 
-         measure = "dyadic")
-
-      # returns the ratio of mutuals to non-null dyads.
-  grecip(snEL, 
-         measure = "dyadic.nonnull")
-
-      # the proportion of edges which are reciprocated
-  grecip(snEL, 
-         measure = "edgewise")
-
-      # returns the log of the ratio of the edgewise reciprocity to the density
-  grecip(snEL, 
-         measure = "edgewise.lrr")
-
-  # The correlation measure may be interpreted as the net tendency for edges of similar relative value (with respect to the mean edge value) to occur within the same dyads.
-
-  grecip(snEL, 
-         measure = "correlation")
-
-```
-
-## Triad Census
-
-Classifies all triads in the network.
-
-```{r statnet: Triad Census, echo=TRUE}
-library(sna)
-#     Classify all Triad in the network:
-
-#Directed Network
-#**triad.census(snEL, mode="digraph")*
-
-#     Classify all Triad in the network: Undirected Network
- sna::triad.census(
-     snEL,
-     mode="graph")
-
-#     total number of all four triad types returned by triad census
-snEL_sumTCensus  <- sum(
-  sna::triad.census(
-    snEL,
-    mode="graph"))
-
-#Davis and Leinhardt classification of the triad classification scheme 
-   # describes each triad by a string of four elements: 
-   # the number of mutual (complete) dyads within the triad; 
-   # the number of asymmetric dyads within the triad; 
-   # the number of null (empty) dyads within the triad; 
-   #and a configuration code for the triads which are not uniquely distinguished by the first three distinctions.
-
-list(   sna::triad.classify(
-     snEL,
-     tri=c(1,2,3),
-     mode==c("digraph")
-   ))
-  #Classify the triads (1,2,3) and (2,3,4)
-
-   triad.classify(snEL,tri=c(1:5))
-   gplot(snEL,c[1:5])
-
-```
-
-```{r iGraph: Triad Census, echo=TRUE}
-library(igraph)
-#Classify all Triad in the network
-list(igraph::triad_census(igEL))
-
-```
-
-## Transitivity or Global Clustering
-
-```{r iGraph: weighted/ network transitivity, echo=TRUE}
-
-#     network transitivity:
-summary(
-  transitivity(igEL)
-)
-
-summary(
-igEL_guTrans <- transitivity(igEL,
-             type = c("globalundirected"),
-             vids = NULL, #  all vertices are considered.
-             weights = NULL,
-             isolates = c("NaN", "zero"))
-)
-
-summary(
-  transitivity(igEL,
-             type = c(
-               "average"),
-             vids = NULL, #  all vertices are considered.
-             weights = NULL,
-             isolates = c("NaN", "zero"))
-)
-
-#   c("undirected", "global", "globalundirected", "localundirected", "local","average", "localaverage","localaverageundirected", "barrat", "weighted")
-
-```
-
-```{r statnet: weighted/ directed network transitivity, echo=TRUE}
-
-#     Directed Networks transitivity:
-  gtrans(snEL)
-
-#   methods for weighted networks, rank and correlation, along with the relevant references.
-#  sna::gtrans()
-
-```
-
-## Ego Network Transivity or Clustering
-`Local transitivity` (local clustering coefficient), is a technical description of the density of an ego network.
-
-, "KAHIKO PUNCH", "TRIUMVIRATE PUNCH", "EUREKA PUNCH", 
-                "YULETIDAL WAVE",
-                "RUMBUSTION PUNCH",
-                "PUKA PUNCH"
-```{r iGraph:Local transitivity, echo=TRUE}
-#     get global clustering cofficient
-  transitivity(igEL, type="global")
-
-#     get average local clustering coefficient
-  transitivity(igEL, type="average")
-
-#     check ego network transitivity
-transitivity(igEL,
-             type="local", 
-             vids=V(igEL)[c(
-               "AKU AKU", "SINGAPORE SLING", "HONDO HATTIE'S JUNGLE PUNCH!")]
-               )
-```
-
-## Component Structure and Membership
-
 ### Statnet: Component STructure, Isolates, Density
@@
  Therefore, the default calculation includes the loops in the numerator but not the denominator of the density calculation.
+
+## Component Structure and Membership
 

### 2022-03-05 docs/3. SNA - Assignments/sna_Week3/DRAFT-week3-Assignment.Rmd
3.5.22

@@
 ## Smuggler's Index: Network Attributes
+
 ```{r Network Size}
@@
 ```
+plot.network(snEL)
+igraph::plot.igraph(igEL)
 
@@
 
+```{r iGraph: Undirected: network density, echo=TRUE}
+
+    #get network density **with** loops
+ igraph::graph.density(igEL)
+ edge_density(igEL)
+          ##**NOTE** provides an incorrect density calculation 
+          ## as the default assumes that loops are not included but does not remove them
+
+```
+
 ###   STATNET:   Network Description
+
+```{r Statnet: Network Density, echo=TRUE}
+
+            # get network density: with possible loops
+   network.density(snEL)
+          ##**WARNING: Network is multiplex - no general way to define density.**
+
+ # get network density **with** loops: statnet
+ gden(snEL, diag=F)
+
+```
 
@@
 
-list(
+igEL_triList <- 
   triad_census(igEL)
-)
-
-```
-plot(
-  triad_census(igEL)
-)
+
+```
+plot(igEL_triList)
 
@@
 #     total number of all four triad types returned by triad census
-sum(
+
+#     Classify all Triad in the network
+
   sna::triad.census(
     snEL,
-    mode="graph"))
-
-#     Classify all Triad in the network: Undirected Network
+    mode="graph")
+
+view(
  sna::triad.census(
      snEL,
-     mode="graph")
+     mode="digraph")
+))
 
@@
      tri=c(1,2,3),
-     mode==c("graph")
-   )
-
-```
+     mode==c("graph"))
+
+sna::triad.classify(
+     snEL,
+     tri=c(1:16),
+     mode==c("digraph"))
+
+```
+plot(view(
+ sna::triad.census(
+     snEL,
+     mode="digraph")
+))
+
+plot(view(
+sna::triad.census(snEL,mode="graph")))
 
@@
    weights = NULL,
-   isolates = c("NaN", "zero"))
+   isolates = c("zero"))
 )
@@
              weights = NULL,
-             isolates = c("NaN", "zero"))
+             isolates = c("zero"))
 )
@@
              weights = NULL,
-              isolates = c("NaN", "zero"))
+              isolates = c("zero"))
 )
@@
 ```
-plot(
-  transitivity(igEL,
-             type = c("localundirected"),
-             vids = NULL, #  all vertices are considered.
-             weights = NULL,
-              isolates = c("NaN", "zero"))
-)
-```{r statnet: Transitivity:, echo=FALSE}
+
+```{r statnet: PLOT: Transitivity:, echo=FALSE}
 library(statnet)
@@
 
-###  Statnet:   Path Length and Geodesic Distance
+###  Statnet:   Path Length and Geodesic Distance: Networks
 
@@
 
+View(
+geodist(snEL))
+
  gd_snEL <- geodist(
     snEL, 
-    inf.replace=.5, #geodesics do not exist, substitute value
+    inf.replace=.25, #geodesics do not exist, substitute value
     count.paths=TRUE, 
-    predecessors=T, # return predecessor list
-    ignore.eval=F, # ignore edge values
-    na.omit=F) # remove NA values
-
-summary(gd_snEL)
-view(
-  list(gd_snEL))
+    predecessors=F, # return predecessor list
+    ignore.eval=T, # ignore edge values
+    na.omit=T) # remove NA values
 
@@
 snEL_gdCounts <- gd_snEL$counts
+  sum(snEL_gdCounts)
+  log_mean_exp(snEL_gdCounts)
+  log_sum_exp(snEL_gdCounts)
 
@@
 
-```
-gplot(gd_snEL)
+  sum(snEL_gdist)
+  log_mean_exp(snEL_gdist)
+  log_sum_exp(snEL_gdist)
+
+```
+gplot(gd_snEL) in 
 gplot(snEL_gdist)
@@
     snEL,
-    geodist.precomp=NULL,
-    return.as.edgelist=FALSE,
-    na.omit=FALSE)
-)
-```
-
-```{r STATNET:Path: Geodesic number & lengths}
+    geodist.precomp= gd_snEL,
+    return.as.edgelist=F,
+    na.omit=F)
+)
+```
+
+```{r STATNET:PLOT: Reachability}
 library(statnet)
@@
 
-summary(geodist(snEL, 
-        inf.replace=Inf, 
-        count.paths=TRUE, # include geodesics 
-        predecessors=FALSE,# include predecessor list
-        ignore.eval=FALSE, # ignore edge values
-        na.omit=FALSE) # remove NA-values edges
-        )
-
-#Examine the number of geodesics
-gd_snEL$counts
-
-#Examine the geodesic distances
-gd_snEL$gdist
-
-  summary(gd_snEL)
-  gplot(gd_snEL)
-
-```
+gplot(
+  reachability(
+    snEL,
+    geodist.precomp= gd_snEL,
+    return.as.edgelist=F,
+    na.omit=F)
+)
+```
+
+    K-Path Census
+- Aggregate counts of paths/cycles by length (i.e., k).
+
+- Counts of paths/cycles to which each vertex belongs (when tabulate.byvertex==TRUE).
+
+- Counts of path/cycle co-memberships, potentially disaggregated by length (when the appropriate co-membership argument is set to bylength).
+
+- For path.census, counts of the total number of paths from each vertex to each other vertex, possibly disaggregated by length (if dyadic.tabulation=="bylength").
 
@@
              mode = "graph",
-             tabulate.by.vertex = TRUE, 
-             path.comembership = c("none"), # c("none", "sum","bylength"), 
-             dyadic.tabulation = c("none") # c("none", "sum", "bylength"))
+             tabulate.by.vertex = T, 
+             path.comembership = c("sum"), # c("none", "sum","bylength"),
+             dyadic.tabulation = c("sum") # c("none", "sum", "bylength"))
 ))
@@
              ##**"none"* disables this computation.
-
-```
-- Aggregate counts of paths/cycles by length (i.e., k).
-
-- Counts of paths/cycles to which each vertex belongs (when tabulate.byvertex==TRUE).
-
-- Counts of path/cycle co-memberships, potentially disaggregated by length (when the appropriate co-membership argument is set to bylength).
-
-- For path.census, counts of the total number of paths from each vertex to each other vertex, possibly disaggregated by length (if dyadic.tabulation=="bylength").
-
-###  IGRAPH:   Path Length and Geodesic Distance
-
-```{r iGraph:Nodes: Path: Length, echo=TRUE}
+```
+
+```{r STATNET: PLOT: k Path Census}
+library(statnet)
+library(sna)
+
+gplot(kpath.census(snEL, 
+             maxlen = 10, 
+             mode = "graph",
+             tabulate.by.vertex = T, 
+             path.comembership = c("bylength"), # c("none", "sum","bylength"),
+             dyadic.tabulation = c("sum") # c("none", "sum", "bylength"))
+))
+              ##**"sum"* returns a vertex by vertex matrix of source/destination path counts
+             ##**"bylength"* disaggregates these counts by path length. 
+             ##**"none"* disables this computation.
+
+```
+
+###  IGRAPH:    Path Length and Geodesic Distance: Networks & Nodes
+
+  The shortest path to describe the overall network structure 
+```{r iGraph: Path: Network & Nodes, echo=TRUE}
 library(igraph)
 
-```
-
-  The shortest path to describe the overall network structure 
-```{r iGraph:Network: Path: Shortest, echo=TRUE}
-
 #     find average shortest path for network
-    average.path.length(igEL,directed=F)
-
-```
-
-```{r iGraph:Nodes: Path: Length, echo=TRUE}
-
+    average.path.length(igEL,
+                        directed=F,
+                       ig_histPath)
+
+    igraph::path.length.hist(igEL)$no
+
+#  shortest_paths calculates one shortest path (the path itself, and not just its length) from or to the given vertex.
+
+  shortest_paths(
+  igEL,
+  from=1,
+  to = V(igEL),
+  mode = c("all"),
+  weights = NULL,
+  output = c("epath"), #c("vpath", "epath", "both")
+  predecessors = FALSE,
+  inbound.edges = FALSE)$no
+
+    all_shortest_paths(
+      igEL,
+      from = 1, # Vertex ID: AkuAku
+      to = V(igEL),
+      mode = c("all"),
+      weights = NULL)$no
+
+##**From=(vertex id)*	
+    ##Numeric constant, the vertex from or to the shortest paths
+
+##**mode=c("out", "all", "in")*
+
+##**output= *	
+    ## defines how to report the shortest paths. 
+  #**“vpath”* the vertices along the paths are reported, this form was used prior to igraph version 0.6. 
+  #**“epath”* edges along the paths are reported. 
+  #*“both”* both forms are returned, in a named list with components “vpath” and “epath”.
+
+```
+
+```{r iGraph: PLOT: PATH: Network & Nodes, echo=TRUE}
 library(igraph)
-# Head
-list(
-  head(V(igEL)$name,10),
-  tail(V(igEL)$name,10)
-  )
-
-#     Calculate distance between two nodes using unweighted edges
+
+ ig_histPath <-
+view(
+    igraph::path.length.hist(igEL)
+)
+#  shortest_paths calculates one shortest path (the path itself, and not just its length) from or to the given vertex.
+
+ig_ShortPath <-
+  shortest_paths(
+  igEL,
+  from=1,
+  to = V(igEL),
+  mode = c("all"),
+  weights = NULL,
+  output = c("epath"), #c("vpath", "epath", "both")
+  predecessors = FALSE,
+  inbound.edges = FALSE)
+
+ig_AllShort <- 
+    all_shortest_paths(
+      igEL,
+      from = 1, # Vertex ID: AkuAku
+      to = V(igEL),
+      mode = c("all"),
+      weights = NULL)$res
+
+##**From=(vertex id)*	
+    ##Numeric constant, the vertex from or to the shortest paths
+
+##**mode=c("out", "all", "in")*
+
+##**output= *	
+    ## defines how to report the shortest paths. 
+  #**“vpath”* the vertices along the paths are reported, this form was used prior to igraph version 0.6. 
+  #**“epath”* edges along the paths are reported. 
+  #*“both”* both forms are returned, in a named list with components “vpath” and “epath”.
+
+ class(ig_histPath)
+  class(ig_ShortPath)
+  class(ig_AllShort)
+```   
+  Distance between two or more Nodes
+```{r iGraph: Distances: Network & Nodes, echo=TRUE}
+
+library(igraph)
+# distances calculates the length of all the shortest paths from or to the vertices in the network.
+
+ mean_distance(igEL, directed = F, unconnected = TRUE)
+
+view(
+  distance_table(igEL, directed = F)
+)
+
+view(
+  igraph::distances(igEL)
+)
+
+### distances between specific nodes
 
@@
     distances(igEL,"AKU AKU" ,"KAHIKO PUNCH" ,weights=NA)
-    distances(igEL,"AKU AKU" , "PASSION FRUIT HONEY"   ,weights=NA)
+    distances(igEL,"AKU AKU" , "JET PILOT"   ,weights=NA)
     distances(igEL,"AKU AKU" , "TRIUMVIRATE PUNCH"   ,weights=NA)
@@
 
+```{r iGraph:Nodes: GRAPH:  Length between Nodes, echo=TRUE}
+library(igraph)
+
+class(aku_Puka)
+
+View(
+  list(
+    aku_Sing,
+    aku_Hondo,
+    aku_Kahiko,
+    aku_JetPilot,
+    aku_Trium,
+    aku_Eureka,
+    aku_YuleTide,
+    aku_Rumbustion,
+    aku_Puka)
+  )
+
+```
+
 Find *all* of the shortest paths between two specific nodes in this network.
 
-```{r iGraph:Nodes: Path: Shortest, echo=TRUE}
+```{r iGraph:Nodes & Network: Path: Shortest , echo=TRUE}
+
+# shortest_paths calculates one shortest path (the path itself, and not just its length) from or to the given vertex.
+view(
+  igraph::shortest.paths(igEL)
+  )
 
 #     isolating the distances between specific node
-
 ## Note: manually tell igraph to ignore edge weights.
@@
 
-aku_PFhoney <- all_shortest_paths(igEL,
+aku_JetPilot <- all_shortest_paths(igEL,
                      "AKU AKU", 
-                     "PASSION FRUIT HONEY",
+                     "JET PILOT",
                      weights=NA)$res
@@
                      weights=NA)$res
-```
-
-### Statnet: Component STructure, Isolates, Density
+
+View(list(
+  aku_Sing,
+  aku_Hondo,
+  aku_Kahiko,
+  aku_JetPilot,
+  aku_Trium,
+  aku_Eureka,
+  aku_YuleTide,
+  aku_Rumbustion,
+  aku_Puka)
+)
+
+```
+
+```{r iGraph:Nodes: GRAPH: Shortest between Nodes, echo=TRUE}
+library(igraph)
+
+class(aku_Puka)
+
+View(
+  list(
+    aku_Sing,
+    aku_Hondo,
+    aku_Kahiko,
+    aku_JetPilot,
+    aku_Trium,
+    aku_Eureka,
+    aku_YuleTide,
+    aku_Rumbustion,
+    aku_Puka)
+  )
+
+```
+
+## Component Structure and Membership
+
+### Igraph: Component Structure, Isolates,
+
+```{r iGraph: network density, echo=TRUE}
+
+    #get network density **with** loops
+ igraph::graph.density(igEL)
+ edge_density(igEL)
+          ##**NOTE** provides an incorrect density calculation 
+          ## as the default assumes that loops are not included but does not remove them
+```
+
+```{r iGraph: Component Structure & Isolates, echo=TRUE}
+
+## Component Structure:
+
+# Number of Components in a Graph
+  count_components(igEL)
+
+# Connected components ?
+ igraph::is_connected(igEL)
+
+# Calculate the maximal (weakly or strongly) connected components of a graph
+
+ component_distribution(igEL, 
+                       cumulative =F, # relative frequency) is calculated
+                       mul.size = F) # multiplied by cluster sizes
+                       #**mode= c("strong"/"weak"))*
+
+# a list with: membership by node, size of each component, and the total number of components.
+
+ igraph::components(igEL)$no # mode = c("weak", "strong"))
+      ##**NOTE:** $no prevents a list of components from being printed
+summary(
+  igraph::components(igEL,
+                     mode = c("weak"))
+)
+
+summary(
+  igraph::components(igEL,
+                     mode = c("strong"))
+)
+ # Size of each component
+
+ igraph::components(igEL)$csize
+
+ # Membership of each component 
+summary(  
+igraph::components(igEL)$membership
+)
+
+```
+
+components are all the same size, so no interesting plots
+
+### Statnet: Isolates & Component Structure
 ```{r Statnet: Isolates, echo=TRUE}
-
+library(statnet)
+library(sna)
               ## Isolates:
@@
  # Is Ego an Isolate?
- is.isolate(snEL, ego_exp, g=1, diag=FALSE)
+ is.isolate(snEL,
+            1,# vertex index number (or a vector of vertices)
+            g=1, 
+            diag=FALSE) #diagonals (i.e., loops) contain meaningful data
 
  # Adds n isolates to the graph (or graphs)
- add.isolates(snEL, n_umber, return.as.edgelist = FALSE)
-
-```
-
-```{r Statnet: Network Density, echo=TRUE}
-
-            # get network density: with possible loops
-   network.density(snEL)
-          ##**WARNING: Network is multiplex - no general way to define density.**
-
- # get network density **with** loops: statnet
- gden(snEL, diag=F)
-
-```
-
-### Igraph: Component STructure, Isolates,
-```{r iGraph: Undirected: Component Structure, echo=TRUE}
-                ## Component Structure:
-
-    # Number of components
- igraph::components(igEL)$no 
-      ##**NOTE:** $no prevents a list of components from being printed
-
-# Size of each component
- igraph::components(igEL)$csize
-
-```
-
-```{r iGraph: Undirected: network density, echo=TRUE}
-
-    #get network density **with** loops
- network.density(igEL)
- class(igEL)
-          ##**NOTE** provides an incorrect density calculation 
-          ## as the default assumes that loops are not included but does not remove them
-
-```
- **Igraph** provides an incorrect density calculation as the default assumes  that loops are not included but does not remove them.
-
- Therefore, the default calculation includes the loops in the numerator but not the denominator of the density calculation.
-
-## Component Structure and Membership
+ ##**add.isolates(snEL, n_umber, return.as.edgelist = FALSE)*
+
+ #subset vertex.names attribute to get names of isolates
+  ##**as.vector(SOURCE.stat%v%'vertex.names')[c(isolates(SOURCE.stat))]*
+
+```
+
+```{r Statnet: Component Structure: Component Size Distribution of a Graph, echo=TRUE}
+library(statnet)
+library(sna)
+
+# Number of Compnents
+sna::components(snEL)
+
+# returns a list of vectors: the number of components of graph according to size, length, and membership
+summary(
+component.dist(snEL)
+)
+
+summary(
+component.dist(snEL,
+               connected=c("unilateral"))
+)
+
+summary(
+component.dist(
+ snEL,
+  connected=c("unilateral"))$csize
+)
+
+summary(
+component.dist(
+ snEL,
+  connected=c("unilateral"))$cdist 
+)
+
+# identifies the component(s) of maximum order within graph
+summary(
+component.largest(snEL)
+)
+
+summary(
+component.largest(
+ snEL, 
+  connected=c("weak"),
+  result = c("membership"), # "membership", "graph")
+  return.as.edgelist = T)
+)
+
+#  computes the component structure of the input network, and returns a vector
+
+summary(
+component.size.byvertex(snEL)
+)
+
+summary(
+component.size.byvertex(
+ snEL, 
+  connected = c("unilateral")) # "strong", "weak", "unilateral", "recursive"
+)
+
+```
 

### 2022-03-06 docs/3. SNA - Assignments/DRAFT_Week3-Distill-Blog_Degree-and-Centrality.Rmd
3.6.22

@@
 
+Smuggler's Bay Drink Recipe Book Index
+
+:   Is an edge-list with one edge attribute:
+
+    Vertices:
+
+    -   Drink Name
+
+    -   Drink Ingredient
+
+    Edge Attribute:
+
+    -   Drink Ingredient Type
+
+Network Description
+
+:   Nodes:
+
+    Edges:
+
+    Ties: Are a connection between Drink Names and
+    Drink Ingredients. The network is undirected
+    and unweighted. Undirected: because the
+    relationship between Drink Names and Drink
+    Ingredients lacks any sort of power dynamic.
+    Edge weights could be added by including the
+    amount of each ingredient required for each
+    drink recipe.
+
+    -   Statnet: number, directed, unweighted
+
+    -   igraph: number, udirected, unweighted
+
+    Smuggler's Bay Edglist is long but
+    uncomplicated: which means there are few ways
+    to subset data to help answer our research
+    question: ***what sort of relationships exist
+    between the components ?*** Which makes Drink
+    Ingredient Type edge attribute very useful.
+
+- Whether or not there are edge attributes
+
+that might be used to:
+
+- subset data, or
+
+- stack multiple networks.
+
 ## \*Provide at least two or three noteworthy
@@
     1.  **What do you make of network density and
-        centralization measures?\
-        **
-
-        +---+---+---+---+
-        | A | s | i | P |
-        | n | t | g | l |
-        | a | a | r | o |
-        | l | t | a | t |
-        | y | n | p |   |
-        | s | e | h |   |
-        | i | t |   |   |
-        h       | s|    |   |  |
-        +====+===+===+===+
-        | D | M | 0 | y |
-        | y | u | . | e |
-        | a | t |   | s |
-        | d | u | 0 |   |
-      |  yC | a | 1 |  |
-        | e n| l | 7 |   |
-        | n | : | 9 |   |
-        | s | 1 |   |  | 
-        |       | u |
-  |   |   |           s | A |   |   |
-          | | s |1 7| 9  
-        |
-  | y |   |   |           | | m |s y| m m
-        |   |     | |   |
-        |
-  | e |   |   |           | | t |t r| i c
-        |   | r |     | |
-        |
-  | i |   |   |           | | c |   |   |
-        |   | a |   |   |
-        |   | l |     | |
-        |
-  | : |   |   |           | | 6 |   |    
-        |   | 7 |     | |
-        |
-  | 0 |   |   |           | |   |   |   |
- |      |     N |   |   |
-        |
-  | u |   |   |           | | l |u l| l :
-        |   | l |     | |
-        |
-  | : |   |   |           | | 3 |6 7| 3 0
-        |   | 6 |   |   |
-        |   | 7 |   |   |
-        |   | 3 |     | |
-        |
-  | 0 |   |   +-----------+-+---+---+---+
-        | T | 0 | \ |   |
-        | r | : | | |   |
-        | C e n s i | 3 | l |   |
-        | a | 2 |   |   |
-        | d | 1 |       |
-|
-        C | 6 |   |       |       e | 3 |   |    
-        |       | n | 9 |   |   |
-     |    s | 1 |   |  | 1 : 7 8   |u |   |   |    
-        | s | 1 |   |   |
-        | : | : |  |
-   |
-     | A    | 7 |   | |  \|        |  | 8 |   |    
-        |   | \ |  |
-   |
-     +------| | |   |--+-----------+--+---+---+| \| l \| l \| 9 \| \| \| \| T \|
-        0 \| \| \| \|\|\| r \| \| \|\
-        \| \| i \| 2 \| \| 2 \| a \| : \| \| \| \|
-        d \| 1 \| \| \| \| \|\| \| s \| \| \| \|
-        \| \|i\| 6 \| i 4 \|n 7\|\| \| \|
-
-|    \|\| N \| \| \| N
-|  \| \| e \| 4 \| 4 e \| \|\| t \| \| \| \| \| w \| \| 3 \| \|\| \| \| oo \| \| \|\| \| \|r\| r \| \| \|
-|      \|\| k \| \| \| \| k +---+---+-----+ \| T \|-- \| ( \| y \| \| r \| 3 \| u \| e \| \| i \| 9 \| n \| s \| \| a \| 1 \| d \| \| \| d \| 0 \| i \| \| \| C \| 2 \| r \| \| \| e \| 4 \| e \| \| \| \| cn \| \| \| \| n \| \|\|d g\| ss s t \| \| u \| \| e \| \| \| s \| \| d \| \| \| : \| \| g \| \| \| \|aph r \| t\| \| \| at \| \| \| \| \| \|\|\| \| \| \| p \| \| \| t \| t\| h \| \| \| )a \| \| \| l \| \| \| \| \| n \| \| [ \| \| \| u \| \| 1 \| \| mber \| m \| \| 2 \|
-
-] \| \| b \| \| 3 \| \|\| \|\|\
-\| e e 2 \| \| \| r \| \| 1 \|665\| 9 \| 6\| o \|
-\| \| \|\
-\| f\| \| 6 \| \| riad t \| \| \| a \|a \| 5 \| l
-\| \| 9\
-\| \| l \|\| \| \| ypes \| \| [ \| f \| [] \| \|
-\|\| 16\| o o \| 2 \| \| \| u \| \| ] \| \| \| r
-\| \| 1 \| \| \| t \| \| 6 \| \| \| r \| \| 6 \|
-\| \| i \| \| 4 \| \| \| a \| \| 8 \| \| \| d \|
-\| \| \| \|6 6 6 \| \|\| t \| t \|\
-\| y \| \| [ \| \| \| p \| \| 1 \| \| \| e \| \| 1
-\| \| \| s \| \| ] \| \| \| \| \|\| \| \|\
-\| [\|11]\| 8 \| \| 8 \| \| \| 7 \|\
-\| +-\|- \| \| \| \| +-- -+---+---+---+ \| T \| u
-\| U \| \| \| r \| n \| n \| \| \| a \| d \| d \|
-\| \| n \| i \| i \| \| \| s \| r \| r \| \| \| i
-\| e \| \|\
-e e \| e \| \| c t c \| t \| i \| t \| t \| \| \|
-v \| e \| e \| \| \| i \| d \| d \| \| \| t \|
-\|\| \|--\|\| \| y \|\| \| \|\| +---+---+---+L oal
----+ \| L \|L \| \| \| \| o \| \| \| c \| \| \| \|
-\| a \| \| \| \| \| \| \|l \| l \| \| \|t \| \| \|
-\| r \| \| \|ran s \| \| \| a \| \| a \| n \|\| \|
-\| \| \| \| \| \| \| \| i \| \| \| \| \| t \| \|
-\| \| \| i \| \| \| \| \| v \| \| \| \| \| i \| \|
-\| \| \| t \| \| \| \| \|\| \| \| \| \|\| \| \| \|
-: \| \| \| \| \| N \| \| \| \| \| o \| \| \| \| \|
-d \| \| \| \| \| e \| \| \| \| \| L \| \| \| \| \|
-i \| \| \|\
-\| \| \| \|\|\| s s \| s\
-&\| Eg\| t \| \| \| \|
-
-    & &  |
-
-& \| \|E\| \| \|\| \| \| g \| \| \| \| \| o \| \|
-\| \| \| N \| \| \| \| \| \| \| e \| \| \| w\|ork
-\| \| \| \| \| \|\| w \| \| w \| o \| \|\| \| \|
-\|\| \| \| r \| r\| \|\
-\|k \| \| \| \| +---+---+---+---+ \| I \| n \| \|
-\| \| s \| o \| \| \| \| o \| \| \| \| \| l \| \|
-\| \| \| a \| \| \| \| \| t \| \| \| \| \| e \|---
-\|\|---\| \| \| \| \| s\| \| \| +---+---+---+---+
-\| U \| \| n \| \| \| n \| \| u \| \| \| d \| \| m
-\| \| \| i \| \| b \| \| \| r \| \| e \| \| \| e
-\| \| r \| \| \| c \| \| : \| \| \| t \| \| 1 \|
-\| \| e \| \| \| \| \| d \| \| s \| \| \| : \| \|
-i \| \| \| \| \| zC \|C \| C \| \|\| \| o \|\| \|
-\|\| \| m \| \| : \| \| \| p \| \| 2 \| \| \| o \|
-\| 7 \| \| \| n \| \| 4 \| \| \| e \| \| \| \| n
-\|\| S \|\|tru\| \| \| \| t \|\| \| S \| \| \| \|
-\| t \| \| \| \| \| r \| \| \| \| \| u \| \|274 \|
-\| c \| \| c \| \| c \| \|
-
-    |t |   ||t
-    |    |        ||
-
-\| \| +- r \|\| \| \| \|\| e \| \| \| \|
-+---+---+rec + \| D \| \| i \| 0 \| y \| \| . \| e
-\|\| \| r \| \| 0 \| s \| \| e \| \| 1 \| \| \|
-6\|7 \| 6 c \| c \|\| \| d \| \| t \| \| 7 \| \|
-\|e e \| \| d \| 6 \| \| \| : \| \| 4 \| \| \| \|
-\| \| 2 G \| G 2 \| \|\| 2 R\| \|\| \| \| A \| \|
-\| \| \| P \| \| \| \| \| H \| \| \| \| \| : \| \|
-\| \| \| D \| \| \| \| \| y \| \| \| \| \| a \| \|
-\| \| \|\
-d \| C \| \| \| \| \| \| \|\| \| C \| \|\
-\| \|\| \| e \| \| \| \| \| \|\| \| s \| \| \| \|
-\| \| \| \| \| u \|\| \| s \| \| \| \|
-+---+---+---+---+ \| D \| \| \| y \| \| i \| \| \|
-e \| \| r \| \| \| s \| \| e \| \| \| \| \| \| \|
-c \| \|cy\| cs \|\| \| t \| \| \| t \|\
-\| \| \| \| d \| \| \| \| \| : \| \| \| \| \| D \|
-\| \| \| \| \| \| \|ee \| e\| \| g \| \| \| \| \|
-\| \| r \| \| e \| \| \| \| \| e \| \| \| \| \| C
-\| \| \| \| \| e \| \| \| \| \| n \| \| \| \| \| t
-\| \| \| \| \| r \| \| \| \| \| a \| \| \| \| \| l
-\| \| \| \| \| i \| \| \| \| \| \| \| --- \| t \|
-\| \| \| y \| \| \|\| \| +---+---+rec + \| D \| \|
-i \| \| y \| \| \| e \|\| \| r \| \| \| s \| \| e
-\| \| \| \| \| \| \| c \| \|cy\| cs \|\| t \| \|
-\| \| e\
-\| \| \| \| d \| \| \| \| \| : \| \| \| \| \| B \|
-\| \| \| \| e \| \| \| \| \| t \| \| \| \|
-
-     w |       | | |
-
-\| \|\| \| \| \| \| e \| \| e \| \| \| \| \| n \|
-\| \| \| \| n \| \| \| \| \| e \| \| \| \|
-
-     s |       ||  |
-
-\| s \| \| \|\| \| \| C \| \| \| \| \| e \| \| \|
-\| \| n \| \| \| \| \| t \| \| \| \| \| \| \| \|\|
-rr \| \| \| a \| \| \| \| \| l \| \| \| \| \| i \|
-\| \| \| \| \|\| t +-\| --\|-\| \| yy \|\| \|+---
-+--+ ----+ --+---+ \| D \| \| y \| \| \| e \| \|
-\| r \| \| \| s \| \| e \| \| \| \| \| c \| \| \|
-y\| s \| \| \| tedt \| \| \| e \| \|\|\| \|\| \|
-\| \| \| \| d \|\
-d \| : \| \| \| \| \| E \| \| \| \| \| i \| \| \|
-\| \| g \| \| \| \| \| e \| \| \|\| \| \|\| n\| \|
-\| \| \| \| v \| \| \| \| \| e \| \| \| \| \| c \|
-\| \| \| \| t \| \| \| \|
-
-       o |   C||e |n||
-
-\| \| \| \|\| r \| \| C \| \| \| \| \| e \| \| \|
-\| \| n \| \| \| \| \| t \| \| \| \| \| r \| \| \|
-\| \| \| a \|\| \|\| \| \| \| \| \| l \| \| \|
-\|\| i \| i \| \|t + \|\|\| \|\|\| \| y \| \| \|
-\| +---+---+---+---+ \| D \| \| \| \| \| i \| \|
-\| \| \| r \| \| \| \| \| \| e \| e\| \| \| \| c
-\| \| \|\| \| t \| \| \| \| \| e \| \| \| \| \| d
-\| \| \| \| \| : \| \| \| \| \| B \| \| \| \| \| o
-\| \| \| \| \| n \| \| \| \| \| a \| \| \| \| \| c
-\| \| \| \| \| i \| \| \| \| \| c \| \| \| \| \| h
-\| \| \| \| \| C \| \| \| \| \| e \| \| \| \| \| n
-\| \| \| \| \| t \| \| \|\| \| \|\| r\| \| \| \|
-\| \| a \| \| \| \| \| l \| \| \| \| \| i \| \| \|
-\| \| t \| \| \| \|
-
-       y |    ||  | ||
-          | 
-          |   |   |
-
-} +---+---+---+ \| ------+ +--+ \|\| D \| \|\| i
-\| \| \|\| \| \| \| r \| \| \| \| \| \| \| \|\| e
-\| \| \| \| \| \| c \|c \|\| c \| \| \|t \| k \|t
-\| t \| \| \| \|e \| \| \| \| \| \| \| \| \| \|\|:
-\| \| \| \| \| P \| \| \| \| \| \| \| \|\
-a \| \| g \|\| \| \| \| \| \| e \| \| \| \| \| R
-\| \| \| \| \|a
-
-          | a |   || a||  |
-
-| \| n\| n\| \|n \| \| \| \| \|----- --+ \|
-
--
-
-    -   ++ + +-+---+ \|+- \| \| +-+ +> Dist+ill+
-        \| \| + is+ a publ+ic\| \| \|
-        +---+---+---+---+
+        centralization measures?**
 

### 2022-03-06 docs/3. SNA - Assignments/sna_Week3/DRAFT-week3-Assignment.Rmd
3.6.22

@@
 ## Briefly describe the dataset:
+
 1.  identify initial network format;
-2.   describe and identify the nodes 
-     including: 
-        *  how many nodes are in the dataset; 
-3.   what constitutes a tie or edge
-     including:
-        *  how many ties, 
-        *   whether ties are directed/undirected,
-        *   whether ties are weighted/binary, 
-        *   and how to interpret the value of the tie if any.
-        *   Whether or not there are edge attributes 
+
+2.  describe and identify the nodes including:
+
+    -   how many nodes are in the dataset;
+
+3.  what constitutes a tie or edge including:
+
+    -   how many ties,
+
+    -   whether ties are directed/undirected,
+
+    -   whether ties are weighted/binary,
+
+    -   and how to interpret the value of the tie
+        if any.
+
+    -   Whether or not there are edge attributes
         that might be used to:
-            *   subset data, or 
-            *   stack multiple networks.
+
+        -   subset data, or
+        -   stack multiple networks.
 
@@
 
-```{r Network Size}
+```{r Network Size & Info}
 
   print(snEL)
-  print(igEL)
-
   summary(snEL)
+  network::has.loops(snEL)
+  network::is.directed(snEL)
+  network::is.bipartite(snEL)
+  network::is.hyper(snEL) # hypergraphic edges allowed
+  network::is.multiplex(snEL) # multiplex edges allowed
+
+  print_all(igEL)
   summary(igEL)
-
-```
-plot.network(snEL)
-igraph::plot.igraph(igEL)
+  igraph::is_directed(igEL)
+  summary(
+  igraph::is.loop(igEL))
+
+```
+
+plot.network(snEL) igraph::plot.igraph(igEL)
 
 ### IGRAPH: Network Description
-*igraph*
-- Network Size
-  - Number Vertex: 274
-    - attr: name (v/c)
-  - Number Edges: 672
-    - attr: ingTyp (e/c)
-- Bipartite: FALSE
-- Directed: FALSE
+
+*igraph* - Network Size - Number Vertex: 274 -
+attr: name (v/c) - Number Edges: 672 - attr:
+ingTyp (e/c) - Bipartite: FALSE - Directed: FALSE
 - Weighted: FALSE
 
-Names
-- Vertex Names: view
-- Edge Attribute Names: [1] "ingTyp"
+Names - Vertex Names: view - Edge Attribute Names:
+[1] "ingTyp"
+
 ```{r igraph: Network & Attribute Descripions, echo=TRUE}
@@
 
-```{r iGraph: Undirected: network density, echo=TRUE}
-
-    #get network density **with** loops
- igraph::graph.density(igEL)
- edge_density(igEL)
-          ##**NOTE** provides an incorrect density calculation 
-          ## as the default assumes that loops are not included but does not remove them
-
-```
-
 ### STATNET: Network Description
 
-```{r Statnet: Network Density, echo=TRUE}
-
-            # get network density: with possible loops
-   network.density(snEL)
-          ##**WARNING: Network is multiplex - no general way to define density.**
-
- # get network density **with** loops: statnet
- gden(snEL, diag=F)
-
-```
-
 ```{r statnet: Network Summary & Attribute info, echo=TRUE}
-print(snEL)
 
@@
 
+  network::list.network.attributes(snEL)
 #      list the names of vertex attributes
@@
 
-Classifies all dyads in the network as:
-- Mutual - Reciprocal (mutual) 
-- Asymmetric -  (non-mutual), 
-- Null - Absent
+Classifies all dyads in the network as: - Mutual -
+Reciprocal (mutual) - Asymmetric - (non-mutual), -
+Null - Absent
 
@@
 
-plot(igEL_randoGraph,
+```{r iGraph: GRAPH: Dyad Census, echo=TRUE}
+
+plot(
+  igEL_randoGraph, 
   vertex.size = 5,
@@
   edge.curved = .1, 
-      vertex.color = "tomato", 
-      edge.arrow.size = .1, 
-      edge.width = .5, 
+  vertex.color= "tomato", 
+  edge.arrow.size = .1, edge.width = .5,
   edge.color = "grey60")
+
+graph.density(igEL)
+    ## Density captures, at the macro-level, the proportion of dyads that are present over the possible total number of dyads in the network
+
+      # Generating a random graph for comparison
+# ?erdos.renyi.game
+      ## In an erdos.renyi.graph, each edge has the same probability of being created.
+We determine the probability and it returns a random graph with a density that equals (in expectation) this probability.
+
+igELNod <- vcount(igEL)
+
+igELDen <- graph.density(igEL)
+
+smugEL_DigRandoG <- 
+  erdos.renyi.game(
+    n = igELNod, 
+    p.or.m = igELDen, 
+    directed = T) 
+      # where n is the number of nodes, 
+      # p.or.m is the probability of drawing an edge, 
+      #directed is whether the network is directed or not
+
+#**plot(smugEL_DigRandoG, ...** in .R notebook  
+     # vertex.size = 5, 
+     # vertex.label = 1, 
+     # edge.curved = .1, 
+     # vertex.color = "tomato", 
+     # edge.arrow.size = .1, 
+     # edge.width = .5, 
+     # edge.color = "grey60")
+
+```
 
@@
 ```
+
 plot(igEL_triList)
@@
 ```
-plot(view(
- sna::triad.census(
-     snEL,
-     mode="digraph")
-))
-
-plot(view(
-sna::triad.census(snEL,mode="graph")))
+
+plot(view( sna::triad.census( snEL,
+mode="digraph") ))
+
+plot(view( sna::triad.census(snEL,mode="graph")))
 
@@
 
-`Local transitivity` (local clustering coefficient), is a technical description of the density of an ego network.
+`Local transitivity` (local clustering
+coefficient), is a technical description of the
+density of an ego network.
 
@@
 -   Nodes:
+
     -   (v/c) Drink Names
     -   (v/c) Drink Ingredients
+
 -   Links:
+
     -   (e/c) Ingredient Type
@@
 ```
-gplot(gd_snEL) in 
-gplot(snEL_gdist)
+
+gplot(gd_snEL) in gplot(snEL_gdist)
 
@@
     K-Path Census
-- Aggregate counts of paths/cycles by length (i.e., k).
-
-- Counts of paths/cycles to which each vertex belongs (when tabulate.byvertex==TRUE).
-
-- Counts of path/cycle co-memberships, potentially disaggregated by length (when the appropriate co-membership argument is set to bylength).
-
-- For path.census, counts of the total number of paths from each vertex to each other vertex, possibly disaggregated by length (if dyadic.tabulation=="bylength").
+
+-   Aggregate counts of paths/cycles by length
+    (i.e., k).
+
+-   Counts of paths/cycles to which each vertex
+    belongs (when tabulate.byvertex==TRUE).
+
+-   Counts of path/cycle co-memberships,
+    potentially disaggregated by length (when the
+    appropriate co-membership argument is set to
+    bylength).
+
+-   For path.census, counts of the total number of
+    paths from each vertex to each other vertex,
+    possibly disaggregated by length (if
+    dyadic.tabulation=="bylength").
 
@@
 
-  The shortest path to describe the overall network structure 
+The shortest path to describe the overall network
+structure
+
 ```{r iGraph: Path: Network & Nodes, echo=TRUE}
@@
 ```
+
 Distance between two or more Nodes
+
 ```{r iGraph: Distances: Network & Nodes, echo=TRUE}
@@
 
-Find *all* of the shortest paths between two specific nodes in this network.
+Find *all* of the shortest paths between two
+specific nodes in this network.
 
@@
 
-components are all the same size, so no interesting plots
+components are all the same size, so no
+interesting plots
 
 ### Statnet: Isolates & Component Structure
+
 ```{r Statnet: Isolates, echo=TRUE}
@@
 
-# Week 3:
-
 ```{r STATNET: Component Size Distribution}
@@
 
+# Week 3:
+
 ##### Details: Component Size Distribution
-Components are maximal sets of mutually connected vertices; depending on the definition of “connected” one employs, one can arrive at several types of components.
-Those supported here are as follows (in increasing order of restrictiveness):
-
-weak: v_1 is connected to v_2 iff there exists a semi-path from v_1 to v_2 (i.e., a path in the weakly symmetrized graph)
-
-unilateral: v_1 is connected to v_2 iff there exists a directed path from v_1 to v_2 or a directed path from v_2 to v_1
-
-strong: v_1 is connected to v_2 iff there exists a directed path from v_1 to v_2 and a directed path from v_2 to v_1
-
-recursive: v_1 is connected to v_2 iff there exists a vertex sequence v_a,...,v_z such that v_1,v_a,...,v_z,v_2 and v_2,v_z,...,v_a,v_1 are directed paths
+
+Components are maximal sets of mutually connected
+vertices; depending on the definition of
+"connected" one employs, one can arrive at several
+types of components. Those supported here are as
+follows (in increasing order of restrictiveness):
+
+weak: v_1 is connected to v_2 iff there exists a
+semi-path from v_1 to v_2 (i.e., a path in the
+weakly symmetrized graph)
+
+unilateral: v_1 is connected to v_2 iff there
+exists a directed path from v_1 to v_2 or a
+directed path from v_2 to v_1
+
+strong: v_1 is connected to v_2 iff there exists a
+directed path from v_1 to v_2 and a directed path
+from v_2 to v_1
+
+recursive: v_1 is connected to v_2 iff there
+exists a vertex sequence v_a,...,v_z such that
+v_1,v_a,...,v_z,v_2 and v_2,v_z,...,v_a,v_1 are
+directed paths
 
@@
 
- The density of a network is defined as the proportion of ties present out of all possible ties in a network.
-
- **Note:**
-
- the network density command ignores edge values at present.
-
- If loops are present or there are multiple edges between two nodes, then the results may not make sense.
+The density of a network is defined as the
+proportion of ties present out of all possible
+ties in a network.
+
+**Note:** the network density command ignores edge
+values at present. If loops are present or there
+are multiple edges between two nodes, then the
+results may not make sense.
 
 ```{r Statnet: Network Density, echo=TRUE}
-
-            # get network density: with possible loops
+library(statnet)
+library(sna)
+
+  # computes network density
    network.density(snEL)
-          ##**WARNING: Network is multiplex - no general way to define density.**
-
- # get network density **with** loops: statnet
-
-  gden(snEL, diag=F)
-
-```
-
- **Igraph** provides an incorrect density calculation as the default assumes  that loops are not included but does not remove them.
-
-```{r iGraph: edge density, echo=TRUE}
+
+    network.density(
+     snEL, 
+     na.omit = T, # Exclude missing edges
+     discount.bipartite = FALSE)
+
+ # computes the density of  graphs and adjusts for the type of graph 
+  gden(snEL)
+
+  gden(
+    snEL, 
+       g=NULL, 
+       diag=FALSE, # Set to TRUE if graph contains loops
+       mode="graph", # digraph or graph
+       ignore.eval=FALSE)
+
+  network::is.bipartite(snEL)
+  network::has.loops(snEL)
+
+```
+
+**Igraph** provides an incorrect density
+calculation as the default assumes that loops are
+not included but does not remove them.
+
+```{r iGraph: network density / edge density, echo=TRUE}
+
 library(igraph)
+
     #get network density **with** loops
-edge_density(igEL, loops = FALSE)
-
- class(igEL)
+ igraph::graph.density(
+   igEL,
+   loops = F)
+
+ edge_density(igEL)
           ##**NOTE** provides an incorrect density calculation 
@@
 
-## Vertex Degree
- **Vertex degree** is a description of an individual node; each vertex in a network may have a different node degree.
-
- *Node Degree:*
-   node degree is one measure of node centrality or popularity; 
- Node degree cis a count of the relationships that a node is involved in or the count of the edges that are incident to a vertex
-
- **use the network degree command to:**
-   *  compute network summary statistics (such as average network degree);
- *  graph the network degree distribution; or
- *  identify particular nodes (such as the five nodes with the most contacts).
-
-```{r Statnet: Vertex Degree, echo=TRUE}
-library(statnet)
-library(sna)
+## Network & Vertex Degree
+
+### **use the network degree command to:**
+
+-   compute network summary statistics (such as
+    average network degree);
+-   graph the network degree distribution; or
+-   identify particular nodes (such as the five
+    nodes with the most contacts). ##\# **Vertex
+    degree** is a description of an individual
+    node; each vertex in a network may have a
+    different node degree.
+
+###*Node Degree:* node degree is one measure of
+node centrality or popularity; Node degree cis a
+count of the relationships that a node is involved
+in or the count of the edges that are incident to
+a vertex
+
+### Statnet: Network & Vertex Degree
+
+#### Network Degree
+```{r Statnet: Network Degree, echo=TRUE}
+library(statnet)
+library(sna)
+
  # statnet: Calculate average network degree
-summary(sna::degree(snEL, 
+summary(  
+  sna::degree(snEL))
+
+summary(
+  sna::degree(snEL, 
              g=1, 
@@
              gmode="digraph", #directed;
-             diag=FALSE, #excludes diagonals 
+             diag=FALSE, # contains loops
              tmaxdev=FALSE, 
@@
              rescale=FALSE, 
-             ignore.eval=FALSE))
-          # ignores loops or self-nominations 
+             ignore.eval=FALSE)) # ignores loops or self-nominations 
 summary(
@@
              ignore.eval=FALSE))
+
 plot(snEL_vd)
@@
 
-```{r iGraph: Undirected: Vertex Degree, echo=TRUE}
-# igraph: Calculate average network degree
- # provides node name along with node degree
-
- # includes loops
-  plot(igraph::degree(igEL))
-
-```
-
-## Network Degree Summary Statistics
-
-```{r Statnet: , echo=TRUE}
-library(statnet)
-library(sna)   
+```{r Statnet: PLOT: Network Degree, echo=TRUE}
+library(statnet)
+library(sna)
+
+ # statnet: Calculate average network degree
+
+summary( snEL_netDeg <-
+  sna::degree(snEL))
+
+summary( snEL_vdDig  <-
+ sna::degree(snEL, 
+             g=1, 
+             nodes=NULL, 
+             gmode="digraph", #directed;
+             diag=FALSE, # contains loops
+             tmaxdev=FALSE, 
+             cmode="indegree", 
+             rescale=FALSE, 
+             ignore.eval=FALSE)) # ignores loops or self-nominations 
+summary(
+  snEL_vdG <- sna::degree(snEL, 
+             g=1, 
+             nodes= NULL, 
+             gmode="graph", #undirected
+             diag=TRUE, #includes diagonals 
+             tmaxdev=F, 
+             cmode="freeman", 
+             rescale=F, #  scores rescaled to sum to 1.
+             ignore.eval=FALSE))
+
+plot(snEL_netDeg)
+plot(snEL_vdDig)
+plot(snEL_vdG)
+
+#**cmode=* degree centrality being computed. 
+#*"indegree"
+#*"outdegree"
+#**DEFAULT*"freeman" refer to the indegree, outdegree, 
+#*total (Freeman) degree measures, respectively. 
+```
+
+```{r Statnet: Vertex Degree (Directed Network), echo=TRUE}
+library(statnet)
+library(sna)
+
+     ## create a dataset of vertex names and degree:
+#####
+snEL_nDeg <- data.frame(
+  name=snEL%v%"vertex.names",
+  degree=sna::degree(snEL))
+
+snEL_nDegDig <-data.frame(
+    name=snEL%v%"vertex.names",
+    degree=sna::degree(snEL),
+    indegree=sna::degree(snEL,
+                         cmode="indegree"),
+    outdegree=sna::degree(snEL,
+                          cmode="outdegree"))
+
+snEL_nInDegDig <-data.frame(
+    name=snEL%v%"vertex.names",
+    indegree=sna::degree(snEL,
+                         cmode="indegree"))
+
+snEL_nOutDegDig <-data.frame(
+    name=snEL%v%"vertex.names",
+    outdegree=sna::degree(snEL,
+                          cmode="outdegree"))
+
+```
+
+#### Network Degree Summary Statistics
+
+```{r Statnet: Network Degree: Summary Stats, echo=TRUE}
+library(statnet)
+library(sna)
+
  # Basic R: get summary statistics for node attributes
-
-summary(snEL_Deg <- 
-           sna::degree(snEL))
-    plot(snEL_Deg)
-
  # provides range, mean, median and standard deviation of a vector.
+
+  summary(snEL_nDeg)
+  summary(snEL_nDegDig)
+```
+
+```{r Statnet: PLOT: Node Degree, echo=TRUE}
+library(statnet)
+library(sna)
 
@@
 
- 6/274 vertices, named, from 1bfe0b4:
-[1] (1-INCH-SQUARE) CHUNKS PINEAPPLE                     
-[2] MINT LEAVES                                          
-[3] LIME JUICE                                           
-[4] DEMERARA SYRUP                                       
-[5] PEACH LIQUEUR (SUCH AS MATHILDE, COMBIER, OR GIFFARD)
-[6] BLENDED LIGHTLY AGED RUM
-
-## Centrilization
-
-```{r iGraph: Undirected: DEGREE CENTRALITY: dnkIng}
+#### Network PLOT: Degree Distribution
+
+hist() is a basic R command that draws a histogram
+of vector of data
+
+```{r Statnet: HIST: Network Degree Distribution}
+
+library(statnet)
+library(sna)
+
+#create a histogram 
+hist(
+  snEL_nDegDig$degree, 
+  main="Smuggler's Bay: Drink Names & Ingredients: Degree Distribution", 
+  xlab="Nominations Received")
+
+hist(
+  snEL_nDegDig$indegree, 
+  main="Smuggler's Bay: Drink Names & Ingredients: In-degree Distribution"
+  , xlab="Nominations Received")
+
+hist(
+  snEL_nDegDig$outdegree, 
+     main="Smuggler's Bay: Drink Names & Ingredients: Out-degree Distribution ", 
+     xlab="Nominations made")
+
+```
+
+```{r Statnet: HIST: Node Degree Distribution, echo=TRUE}
+library(statnet)
+library(sna)
+
+ # get summary statistics for node degree for the binary network degree
+
+### AKU AKU   
+snEL_degVNme <- data.frame(
+   name=snEL%v%"Aku Aku",
+    outdegree=sna::degree(snEL, cmode="outdegree"),
+    indegree=sna::degree(snEL, cmode="indegree"))
+
+hist(
+  snEL_degVNme$outdegree, 
+  main="Drink Name:  Aku Aku: Out Degree Distribution", 
+  xlab="Nominations Received")
+
+hist(
+  snEL_degVNme$indegree, 
+  main="Drink Name:  Aku Aku: Out Degree Distribution", 
+  xlab="Nominations Received")
+
+## "(1-INCH-SQUARE) CHUNKS PINEAPPLE"
+snEL_degVNme <- data.frame(
+   name=snEL%v%"(1-INCH-SQUARE) CHUNKS PINEAPPLE",
+   indegree=sna::degree(snEL, cmode="indegree"),
+   outdegree=sna::degree(snEL, cmode="outdegree"))
+
+hist(
+  snEL_degVNme$outdegree, 
+  main="Drink Ingredient: (1-INCH-SQUARE) CHUNKS PINEAPPLE Out Degree Distribution", 
+  xlab="Nominations Received")
+
+hist(
+  snEL_degVNme$indegree, 
+  main="Drink Ingredient: Drink Ingredient: (1-INCH-SQUARE) CHUNKS PINEAPPLE in Degree Distribution", 
+  xlab="Nominations Received")
+
+## Mint Leaves 
+snEL_degVNme <- data.frame(
+   name=snEL%v%"MINT LEAVES",
+   indegree=sna::degree(snEL, cmode="indegree"),
+   outdegree=sna::degree(snEL, cmode="outdegree"))
+
+hist(
+  snEL_degVNme$outdegree, 
+  main="Out Degree: Drink Ingredient: ", 
+  xlab="Nominations Received")
+
+hist(
+  snEL_degVNme$indegree, 
+  main="In Degree: Drink Ingredient: " , 
+  xlab="Nominations Received")
+
+## "DEMERARA SYRUP"
+snEL_degVNme <- data.frame(
+   name=snEL%v%"DEMERARA SYRUP",
+   indegree=sna::degree(snEL, cmode="indegree"),
+   outdegree=sna::degree(snEL, cmode="outdegree"))
+
+hist(
+  snEL_degVNme$outdegree, 
+  main="Out Degree: Drink Ingredient: DEMERARA SYRUP", 
+  xlab="Nominations Received")
+
+hist(
+  snEL_degVNme$indegree, 
+  main="In Degree: Drink Ingredient:  DEMERARA SYRUP", 
+  xlab="Nominations Received")
+
+## Peach Liqueur
+odeg_peachLqr <- data.frame(
+   name=snEL%v%"PEACH LIQUEUR (SUCH AS MATHILDE, COMBIER, OR GIFFARD)",
+   indegree=sna::degree(snEL, cmode="indegree"),
+   outdegree=sna::degree(snEL, cmode="outdegree"))
+
+hist(
+  snEL_degVNme$outdegree, 
+  main="Out Degree: Drink Ingredient: PEACH LIQUEUR", 
+  xlab="Nominations Received")
+
+hist(
+  snEL_degVNme$indegree, 
+  main="In Degree: Drink Ingredient: PEACH LIQUEUR" , 
+  xlab="Nominations Received")
+
+## " BLENDED LIGHTLY AGED RUM"
+odeg_blaRum <- data.frame(
+   name=snEL%v%"BLENDED LIGHTLY AGED RUM",
+   indegree=sna::degree(snEL, cmode="indegree"),
+   outdegree=sna::degree(snEL, cmode="outdegree"))
+
+hist(
+  snEL_degVNme$outdegree, 
+  main="Out Degree: Drink Ingredient: BLENDED LIGHTLY AGED RUM ", 
+  xlab="Nominations Received")
+
+hist(
+  snEL_degVNme$indegree, 
+  main="In Degree: Drink Ingredient: BLENDED LIGHTLY AGED RUM " , 
+  xlab="Nominations Received")
+
+```
+
+### iGraph: Vertex Degree
+
+```{r iGraph: Vertex Degree, echo=TRUE}
+# igraph: Calculate average network degree
+ # provides node name along with node degree
+
+ # includes loops
+  plot(igraph::degree(igEL))
+
+```
+
+## Network degree Centrilization
+### Degree Centrality
+
+We can break large social networks down into their
+constituent parts. These constituent parts are
+referred to as "motifs". The most basic motif
+consists of two nodes and is called a dyad. Edges
+in a network signify the presence or absence of
+dyadic relations. It follows that a dyad in an
+undirected network can have two unique
+configurations: connected or disconnected; and
+three unique configurations in a directed network
+(mutual, assymetric, and null
+
+### Statnet: Degree Centraility: In/Out
+
+```{r Statnet: Network Degree centralization, eval=FALSE, include=FALSE}
+library(statnet)
+library(sna)
+
+#get network centralization score:
+
+# centralization(snEL, degree, cmode="indegree")
+
+```
+
+```{r Statmet: Netweork Centrality:  low & high degree nodes}
+
+#sort to find 5 highest and lowest degree nodes in trade100
+
+network::list.edge.attributes(snEL)
+
+snEL_nodeHeadTail <-data.frame(
+  name=snEL%v%"vertex.names",
+  indegree=sna::degree(snEL, cmode="indegree"),
+  outdegree=sna::degree(snEL, cmode="outdegree"))
+
+snEL_nodeHeadTail%>%
+  arrange(desc(indegree))%>%
+  slice(1:10)
+
+snEL_nodeHeadTail%>%
+  arrange(indegree)%>%
+  slice(1:10)
+
+snEL_nodeHeadTail%>%
+  arrange(desc(outdegree))%>%
+  slice(1:10)
+
+snEL_nodeHeadTail%>%
+  arrange(outdegree)%>%
+  slice(1:10)
+
+view(snEL_nodeHeadTail)
+
+```
+
+### Igraph: Degree Centrality
+
+```{r iGraph: DEGREE CENTRALITY}
 library(igraph)
@@
 
-plot(centr_degree(igEL)$res)
+#get network centralization score:
+
+summary(
+  centr_degree(igEL)$res)
+
+  centr_degree(igEL)$centralization
+
+summary(
+  centr_degree(igEL)$centralizatio)
+
+  centr_degree(igEL)$theoretical_max
+
+#get network centralization score: in
+
+  centr_degree(
+    igEL, 
+    loops = FALSE, 
+    mode="in")$centralization
+
+summary(
+  centr_degree(
+    igEL, 
+    loops = FALSE, 
+    mode="in")$centralization)
+
+  centr_degree(
+    igEL, 
+    mode ="in")$theoretical_max
+
+#get network centralization score: out
+
+  centr_degree(
+    igEL, 
+    loops = FALSE, 
+    mode="out")$centralization
+
+summary(
+  centr_degree(
+    igEL, 
+    loops = FALSE, 
+    mode="out")$centralization)
+
+  centr_degree(
+    igEL,
+    mode ="out")$theoretical_max
+
+## get network centralization score: ALL
 
@@
 
-plot(
-  centr_degree(igEL,mode = c("all"))$res)
-
-summary(
 centr_degree(igEL,
@@
   normalized = TRUE)$centralization
-)
-
-summary(
+
 centr_degree(igEL,
@@
   normalized = TRUE)$theoretical_max
-)
-
-```
-
-## Degree Centrality
-We can break large social networks down into their constituent parts.
-These constituent parts are referred to as “motifs”.
-The most basic motif consists of two nodes and is called a dyad.
-Edges in a network signify the presence or absence of dyadic relations.
-It follows that a dyad in an undirected network can have two unique configurations: connected or disconnected; and three unique configurations in a directed network (mutual, assymetric, and null
-
-```{r iGraph: Directed: GRAPH: Dyad Census, echo=TRUE}
-
-graph.density(igEL)
-    ## Density captures, at the macro-level, the proportion of dyads that are present over the possible total number of dyads in the network
-
-      # Generating a random graph for comparison
-# ?erdos.renyi.game
-      ## In an erdos.renyi.graph, each edge has the same probability of being created.
-We determine the probability and it returns a random graph with a density that equals (in expectation) this probability.
-
-igELNod <- vcount(igEL)
-
-igELDen <- graph.density(igEL)
-
-smugEL_DigRandoG <- 
-  erdos.renyi.game(
-    n = igELNod, 
-    p.or.m = igELDen, 
-    directed = T) 
-      # where n is the number of nodes, 
-      # p.or.m is the probability of drawing an edge, 
-      #directed is whether the network is directed or not
-
-#**plot(smugEL_DigRandoG, ...** in .R notebook  
-     # vertex.size = 5, 
-     # vertex.label = 1, 
-     # edge.curved = .1, 
-     # vertex.color = "tomato", 
-     # edge.arrow.size = .1, 
-     # edge.width = .5, 
-     # edge.color = "grey60")
-
-```
-
-```{r iGraph: Directed: Degree Centrality}
+
+```
+
+```{r iGraph: PLOT: DEGREE CENTRALITY}
+library(igraph)
+library(tidyverse)
+
+# network centralization score: 
+plot(
+  centr_degree(igEL)$res)
+
+hist(
+  centr_degree(igEL)$res
+)
+
+#get network centralization score: in
+
+hist(
+  centr_degree(igEL,mode = c("in"))$res)
+
+  centr_degree(
+    igEL, 
+    loops = FALSE, 
+    mode="in")$centralization
+
+  centr_degree(igEL,
+               mode ="in")$theoretical_max
+#get network centralization score: out
+
+  centr_degree(
+    igEL, 
+    loops = FALSE, 
+    mode="out")$centralization
+
+  centr_degree(
+    igEL,
+    mode ="out")$theoretical_max
+
+  ##
+summary(
+  centr_degree(
+    igEL, 
+    loops = FALSE, 
+    mode="out")$centralization)
+
+summary(
+  centr_degree(igEL,
+  mode = c("all"),
+  loops = TRUE,
+  normalized = TRUE)$res)
+
+plot(
+  centr_degree(igEL,mode = c("all"))$res)
+
+summary(
+centr_degree(igEL,
+  mode = c("all"),
+  loops = TRUE,
+  normalized = TRUE)$centralization
+)
+
+summary(
+centr_degree(igEL,
+  mode = c("all"),
+  loops = TRUE,
+  normalized = TRUE)$theoretical_max
+)
+
+```
+
+```{r iGraph: PLOT: Degree Centrality}
 # Degree centrality is calculated using the degree function in R. It returns how many edges each node has.
@@
 
-# plot(ingT_deg, 
-#     vertex.label.cex = .6, 
-#     vertex.label.color = "black", 
-#     vertex.size = V(igEL)$degree, 
-#     vertex.label.cex = .2) # sized by degree
-
-```
-
+plot(ingT_deg, 
+     vertex.label.cex = .6, 
+     vertex.label.color = "black", 
+     vertex.size = V(igEL)$degree, 
+     vertex.label.cex = .2) # sized by degree
+
+```
+
+# WEEK4
 ```{r iGraph: Directed: Betweenness Centrality}
@@
 
-Degree centrality only takes into account the number of edges for each node, but it leaves out information about ego’s alters
+Degree centrality only takes into account the
+number of edges for each node, but it leaves out
+information about ego's alters
+
 ```{r iGraph: Directed: Eigenvector Centrality}
@@
 
- plot(ingTyp_Cent,
-     vertex.label.cex = .6, 
-     vertex.label.color = "black", 
-     vertex.size = V(ingTyp_Cent)$page_rank/max(V(ingTyp_Cent)$page_rank) * 20)
+plot(ingTyp_Cent, vertex.label.cex = .6,
+vertex.label.color = "black", vertex.size =
+V(ingTyp_Cent)$page_rank/max(V(ingTyp_Cent)$page_rank)
+\* 20)

### 2022-03-06 docs/3. SNA - Assignments/DRAFT_Week3-Distill-Blog_Degree-and-Centrality.Rmd
3.6.22 time for a walk

@@
 ```
-
-![](https://media.giphy.com/media/3ornkcUTDQyU4E6kRa/giphy.gif)
-
-![](https://media.giphy.com/media/3ornjK3aalyWAEhxDi/giphy.gif)
-
-![](https://media.giphy.com/media/3o6Yg4Hgd2bt4802xW/giphy.gif)
 
@@
 
+![](https://media.giphy.com/media/3ornjK3aalyWAEhxDi/giphy.gif)
+
 # ## \*Write up your results briefly: \*
@@
 
-Smuggler's Bay Drink Recipe Book Index
+Network Description: Smuggler's Bay Drink Recipes
 
@@
 
-    Vertices:
+    Vertex Attributes
 
-    -   Drink Name
+    vertices = 274
 
-    -   Drink Ingredient
+    -   Nodes:
+
+        Drink Name
+
+        Drink Ingredient
+
+    -   total edges= 671
+
+        missing edges= 0
+
+        non-missing edges= 0
 
@@
 
-Network Description
-
-:   Nodes:
-
-    Edges:
-
-    Ties: Are a connection between Drink Names and
+:   Ties: Are a connection between Drink Names and
     Drink Ingredients. The network is undirected
@@
     question: ***what sort of relationships exist
-    between the components ?*** Which makes Drink
-    Ingredient Type edge attribute very useful.
+    between the components ?***
 
-- Whether or not there are edge attributes
-
-that might be used to:
-
-- subset data, or
-
-- stack multiple networks.
+    Which makes the edge attribute really useful
+    because subsetting network data by Drink
+    Ingredient Type allows us to look at the
+    ingredients in rum-based cocktails vs those in
+    gin-based cocktails.
 
@@
 
-results\*, including:
+![](https://media.giphy.com/media/3ornkcUTDQyU4E6kRa/giphy.gif)
 
-1\. the relevant statistics and interpretation.
+**Network & Ego Network**
 
-For example, explaining which node(s) are most
-central and which are least central.
+-   Network Transitivity: 1 or 0
 
-2\. Discuss (with any related evidence) whether or
-not the node(s) behavior is in line with or
-violates expectations based on the degree
-centrality measure.
+```{=html}
+<!-- -->
+```
+-   Reach-ability:
 
-3\. What do you make of network density and
-centralization measures?
+    -   Network: K Path Census
 
-4\. What about differences in the binary 100
-million threshold network vs valued trade flows
-network.
+    -   Ego Network: Path / Distance
 
-5.  Check tutorial for other ideas of results to
-    discuss.
+**Network stats VS Individual Node stats**
 
-    *Provide at least two or three noteworthy
-    results*, including:
+-   Network Density
 
-<!-- -->
+-   Degree: Network vs Node
 
-1.  the relevant statistics and interpretation.
+-   Degree Centrality: Network vs Node
 
-    -   For example, explaining which **node(s)
-        are most central and which are least
-        central.**
+    -   Most Central Nodes
 
-2.  Discuss (with any related evidence) whether or
-    not the **node(s) behavior is in line with or
-    violates expectations based on the degree
-    centrality measure.**
+    -   Least Central Nodes
 
-    1.  **What do you make of network density and
-        centralization measures?**
+    -   Centralization Score Break Down
+
+    -   <div>
+
+        -   \$res
+
+        -   \$centralization
+
+        -   \$theoretical_max
+
+        </div>
+
+**2. Node Behavior:** Degree Centrality Meastures
+
+Is node(s) behavior in line with or violates
+expectations based on the degree centrality
+measure.
+
+![](https://media.giphy.com/media/3o6Yg4Hgd2bt4802xW/giphy.gif)
 

### 2022-03-08 docs/3. SNA - Assignments/DRAFT_Week3-Distill-Blog_Degree-and-Centrality.Rmd
3.6.22

@@
 
-## To start:
-
-### I'm curious to see what sort of relationships exist between the components of [Smuggler's Cove](https://www.smugglerscovesf.com/#about-section) Tiki Cocktail Recipies?
+### Which drink ingredients in [Smuggler's Cove](https://www.smugglerscovesf.com/#about-section)'s have the most connections and are the most central in this network of Tiki Cocktail Recipes?
 
@@
 
-    vertices = 274
+    -   Nodes = 274
 
-    -   Nodes:
+        -   Drink Name
 
-        Drink Name
-
-        Drink Ingredient
+        -   Drink Ingredient
 
@@
 
+    Edge attributes: Ingredient Type
+
+    > 10 most common values are:
+    >
+    > JUICE : 135 , RUM: 125, SYRUP: 115, LIQUEUR
+    > : 84 , BITTERS: 54 ,
+    >
+    > SODA : 28 , SPICE: 19, GIN: 12, BRANDY: 9,
+    > FRUIT: 7
+
 ## \*Provide at least two or three noteworthy
@@
 
-```{=html}
-<!-- -->
-```
+    Network Transitivity is either 1 or 0. Statnet
+    read in the edgelist as "directed", which
+    igraph is "undirected" .
+
+    According to statnet the network is entirely
+    transitive because the graph is composed
+    entirely of dyads and potential traids
+
+    Igraph: Transitivity is near 0 (0.018) because
+    network is composed of 627 mutual ties, no
+    Asymetic ties, and 36,729 null ties.
+
+    statnet: 0 mutual, 671 asymetric, 36,730
+    potential ties
+
 -   Reach-ability:
@@
 
--   Network Density
+1 component in graph
 
--   Degree: Network vs Node
+all components are connected
 
--   Degree Centrality: Network vs Node
+### Network Density: Low Transitivity == Low Density
+
+*The density of a network is defined as the
+proportion of ties present out of all possible
+ties in a network.*
+
+statnet:
+
+-   Network Density: 0
+
+-   gDen() - Edgelist Network Density: 0.0089
+
+igraph:
+
+-   Graph Density: 0.0179
+
+-   Edge Density: 0.0179
+
+### Degree: Network vs Vertex
+
+\*\*Vertex Degree\*\* measures an individual
+node's centrality o; each vertex in a network may
+have a different node degree.
+
+#### Degree: Network vs Node
+
+[Network Degree Summary Stats]{.ul}
+
++-----+---+------+---+------+---+
+| deg |   | inde |   | o    |   |
+| ree |   | gree |   | utde |   |
+|     |   |      |   | gree |   |
++=====+===+======+===+======+===+
+| M   | 0 | Min. | 0 | Min. | 0 |
+| in. |   |      | . |      |   |
+|     |   |      | 0 |      |   |
+|     |   |      | 0 |      |   |
+|     |   |      | 0 |      |   |
++-----+---+------+---+------+---+
+| 1st | 0 | 1st  | 0 | 1st  | 0 |
+| Qu. |   | Qu.  |   | Qu.  |   |
++-----+---+------+---+------+---+
+| Med | 1 | Me   | 1 | Me   | 0 |
+| ian |   | dian |   | dian |   |
++-----+---+------+---+------+---+
+| M   | 2 | Mean | 2 | Mean | 2 |
+| ean | . |      | . |      | . |
+|     | 4 |      | 4 |      | 4 |
+|     | 5 |      | 4 |      | 4 |
+|     |   |      | 9 |      | 9 |
++-----+---+------+---+------+---+
+| 3rd | 2 | 3rd  | 2 | 3rd  | 5 |
+| Qu. |   | Qu.  |   | Qu.  |   |
++-----+---+------+---+------+---+
+| M   | 6 | Max. | 6 | Max. | 1 |
+| ax. | 2 |      | 2 |      | 1 |
++-----+---+------+---+------+---+
+|     |   |      |   |      |   |
++-----+---+------+---+------+---+
+
+[Vertex Degree Summary Stats]{.ul}
+
++-----------+-------------+-----------------+
+| degree    | indegree    | outdegree       |
++===========+=============+=================+
+| Min:      | Min: 0.000  | Min: 0.000      |
+| 1.000     |             |                 |
++-----------+-------------+-----------------+
+| 1st Qu:   | 1st Qu:     | 1st Qu: 0.000   |
+| 1.000     | 0.000       |                 |
++-----------+-------------+-----------------+
+| Median:   | Median:     | Median: 0.000   |
+| 4.000     | 1.000       |                 |
++-----------+-------------+-----------------+
+| Mean:     | Mean: 2.449 | Mean: 2.449     |
+| 4.898     |             |                 |
++-----------+-------------+-----------------+
+| 3rd Qu:   | 3rd Qu:     | 3rd Qu: 5.000   |
+| 6.000     | 2.000       |                 |
++-----------+-------------+-----------------+
+| Max:      | Max: 62.000 | Max: 11.000     |
+| 62.000    |             |                 |
++-----------+-------------+-----------------+
+
+[Network Degree Distribution Graphs]{.ul}
+
+#### Degree Centrality: Network vs Node
+
+Vertex Degree Centrality:
 

### 2022-03-08 docs/3. SNA - Assignments/sna_Week3/DRAFT-week3-Assignment.Rmd
3.6.22 time for a walk
3.6.22

@@
 #   summarize numeric network attribute
-  summary(snEL%v%"name")
-  summary(snEL%v%"ingNam")
-  summary(snEL%v%"dnkNam")
-  summary(snEL%e%"ingTyp")
+  summary(snEL%v%"vertex.name")
+  #summary(snEL%v%"ingNam")
+  #summary(snEL%v%"dnkNam")
+  #summary(snEL%e%"ingTyp")
 
@@
 
-summary(
-  graph.density(igEL)
-)
-
     ## Density captures, at the macro-level, the proportion of dyads that are present over the possible total number of dyads in the network
@@
   edge_density(igEL)
-
-summary(
-   edge_density(igEL)
-)
 
@@
  class(igEL_randoGraph)
- summary(igEL_randoGraph)
-
- print_all(igEL_randoGraph)
-
-```
-
+
+ graph.density(igEL_randoGraph)
+ edge_density(igEL_randoGraph)
+
+```
 ```{r iGraph: GRAPH: Dyad Census, echo=TRUE}
@@
 #Classify all Triad in the network
+igEL_triList <- triad_census(igEL)
+igEL_triList
 
@@
 )
-
-igEL_triList <- 
-  triad_census(igEL)
+summary(igEL_triList)
 
@@
 
-View(
+summary(
 geodist(snEL))
@@
 
-summary(
+view(
   reachability(
@@
 gplot(kpath.census(snEL, 
-             maxlen = 10, 
+             maxlen = 5, 
              mode = "graph",
@@
 
-view(
   distance_table(igEL, directed = F)
-)
 
@@
 
+# Size of each component
+
+ igraph::components(igEL)$csize
+
+ # Membership of each component 
+summary(  
+igraph::components(igEL)$membership
+)
+
 # Connected components ?
@@
 
- igraph::components(igEL)$no # mode = c("weak", "strong"))
+ igraph::components(igEL)$no# mode = c("weak", "strong"))
       ##**NOTE:** $no prevents a list of components from being printed
@@
                      mode = c("strong"))
-)
- # Size of each component
-
- igraph::components(igEL)$csize
-
- # Membership of each component 
-summary(  
-igraph::components(igEL)$membership
 )
@@
 
-summary(
 component.largest(
@@
   result = c("membership"), # "membership", "graph")
-  return.as.edgelist = T)
-)
+  return.as.edgelist =FALSE)
 
 #  computes the component structure of the input network, and returns a vector 
-
-summary(
+sum(
 component.size.byvertex(snEL)
@@
 
-summary(
+sum(
 component.size.byvertex(
@@
 
-  view(summary(cl_snEL))
-  View(cl_snEL)
-
+# View(cl_snEL)
+
+```
 gplot(cl_snEL)
-
-```
-
-# Week 3:
 
@@
 
+# Week 3:
+
 ## Network Density
@@
 
+network::is.bipartite(snEL)
+network::has.loops(snEL)
+
   # computes network density
@@
      na.omit = T, # Exclude missing edges
-     discount.bipartite = FALSE)
+     discount.bipartite=F)
 
  # computes the density of  graphs and adjusts for the type of graph 
-  gden(snEL)
+  gden(snEL,
+       diag = F)
 
@@
        g=NULL, 
-       diag=FALSE, # Set to TRUE if graph contains loops
+       diag=T, # Set to TRUE if graph contains loops
        mode="graph", # digraph or graph
@@
 
-  network::is.bipartite(snEL)
-  network::has.loops(snEL)
+ gden(snEL,
+      diag = T,
+      mode = "digraph")
 
@@
 
-## Network & Vertex Degree
-
+## Degree: Network & Vertex
 ### **use the network degree command to:**
@@
 -   identify particular nodes (such as the five
-    nodes with the most contacts). ##\# **Vertex
-    degree** is a description of an individual
+    nodes with the most contacts). 
+    **Vertex degree** is a description of an individual
     node; each vertex in a network may have a
@@
 
-###*Node Degree:* node degree is one measure of
+*Node Degree:* node degree is one measure of
 node centrality or popularity; Node degree cis a
@@
 ### Statnet: Network & Vertex Degree
-
-#### Network Degree
+#### Statnet: Network Degree
 ```{r Statnet: Network Degree, echo=TRUE}
@@
  # statnet: Calculate average network degree
-summary(  
-  sna::degree(snEL))
+
+  sna::degree(snEL)$no
+summary(
+  snEL_vd <- sna::degree(snEL, 
+             g=1, 
+             nodes= NULL, 
+             gmode="graph", #undirected
+             diag=TRUE, #includes diagonals 
+             tmaxdev=F, 
+             cmode="freeman", 
+             rescale=F, #  scores rescaled to sum to 1.
+             ignore.eval=FALSE))
 
@@
              ignore.eval=FALSE)) # ignores loops or self-nominations
-summary(
-  snEL_vd <- sna::degree(snEL, 
+
+summary(
+  sna::degree(snEL, 
              g=1, 
-             nodes= NULL, 
-             gmode="graph", #undirected
-             diag=TRUE, #includes diagonals 
-             tmaxdev=F, 
-             cmode="freeman", 
-             rescale=F, #  scores rescaled to sum to 1.
-             ignore.eval=FALSE))
+             nodes=NULL, 
+             gmode="digraph", #directed;
+             diag=FALSE, # contains loops
+             tmaxdev=FALSE, 
+             cmode="outdegree", 
+             rescale=FALSE, 
+             ignore.eval=FALSE)) # ignores loops or self-nominations
 
@@
 ```
+
+hist() is a basic R command that draws a histogram
+of vector of data
 
@@
 
+```{r Statnet: HIST: Network Degree Distribution}
+
+library(statnet)
+library(sna)
+
+#create a histogram 
+hist(
+  snEL_nDegDig$degree, 
+  main="Smuggler's Bay: Drink Names & Ingredients: Degree Distribution", 
+  xlab="Nominations Received")
+
+hist(
+  snEL_nDegDig$indegree, 
+  main="Smuggler's Bay: Drink Names & Ingredients: In-degree Distribution"
+  , xlab="Nominations Received")
+
+hist(
+  snEL_nDegDig$outdegree, 
+     main="Smuggler's Bay: Drink Names & Ingredients: Out-degree Distribution ", 
+     xlab="Nominations made")
+
+```
+
+```{r Statnet: Network Degree: Summary Stats, echo=TRUE}
+library(statnet)
+library(sna)
+
+```
+
+#### Statnet: Vertex Degree
 ```{r Statnet: Vertex Degree (Directed Network), echo=TRUE}
@@
 #####
-snEL_nDeg <- data.frame(
-  name=snEL%v%"vertex.names",
-  degree=sna::degree(snEL))
 
@@
 
+snEL_nDeg <- data.frame(
+  name=snEL%v%"vertex.names",
+  degree=sna::degree(snEL))
+
 snEL_nInDegDig <-data.frame(
@@
                           cmode="outdegree"))
-
-```
-
-#### Network Degree Summary Statistics
-
-```{r Statnet: Network Degree: Summary Stats, echo=TRUE}
-library(statnet)
-library(sna)
 
@@
 
-#### Network PLOT: Degree Distribution
-
-hist() is a basic R command that draws a histogram
-of vector of data
-
-```{r Statnet: HIST: Network Degree Distribution}
-
-library(statnet)
-library(sna)
-
-#create a histogram 
-hist(
-  snEL_nDegDig$degree, 
-  main="Smuggler's Bay: Drink Names & Ingredients: Degree Distribution", 
-  xlab="Nominations Received")
-
-hist(
-  snEL_nDegDig$indegree, 
-  main="Smuggler's Bay: Drink Names & Ingredients: In-degree Distribution"
-  , xlab="Nominations Received")
-
-hist(
-  snEL_nDegDig$outdegree, 
-     main="Smuggler's Bay: Drink Names & Ingredients: Out-degree Distribution ", 
-     xlab="Nominations made")
-
-```
-
 ```{r Statnet: HIST: Node Degree Distribution, echo=TRUE}
@@
 # igraph: Calculate average network degree
+
  # provides node name along with node degree
+summary(igraph::degree(igEL))
 
@@
 
-We can break large social networks down into their
-constituent parts. These constituent parts are
-referred to as "motifs". The most basic motif
-consists of two nodes and is called a dyad. Edges
-in a network signify the presence or absence of
-dyadic relations. It follows that a dyad in an
-undirected network can have two unique
-configurations: connected or disconnected; and
-three unique configurations in a directed network
+A dyad in an undirected network can have two unique configurations: connected or disconnected; 
+and three unique configurations in a directed network
 (mutual, assymetric, and null
@@
 summary(
-  centr_degree(igEL)$centralizatio)
+  centr_degree(igEL)$centralization)
 

### 2022-04-19 docs/3. SNA - Assignments/DRAFT_Week3-Distill-Blog_Degree-and-Centrality.Rmd
4.12.22

@@
     > JUICE : 135 , RUM: 125, SYRUP: 115, LIQUEUR
+    >
     > :   84 , BITTERS: 54 ,
@@
 
+centr_degree(igEL)\$theoretical_max: 74802
+
 [Network Degree Summary Stats]{.ul}
 
-+-----+---+------+---+------+---+
-| deg |   | inde |   | o    |   |
-| ree |   | gree |   | utde |   |
-|     |   |      |   | gree |   |
-+=====+===+======+===+======+===+
-| M   | 0 | Min. | 0 | Min. | 0 |
-| in. |   |      | . |      |   |
-|     |   |      | 0 |      |   |
-|     |   |      | 0 |      |   |
-|     |   |      | 0 |      |   |
-+-----+---+------+---+------+---+
-| 1st | 0 | 1st  | 0 | 1st  | 0 |
-| Qu. |   | Qu.  |   | Qu.  |   |
-+-----+---+------+---+------+---+
-| Med | 1 | Me   | 1 | Me   | 0 |
-| ian |   | dian |   | dian |   |
-+-----+---+------+---+------+---+
-| M   | 2 | Mean | 2 | Mean | 2 |
-| ean | . |      | . |      | . |
-|     | 4 |      | 4 |      | 4 |
-|     | 5 |      | 4 |      | 4 |
-|     |   |      | 9 |      | 9 |
-+-----+---+------+---+------+---+
-| 3rd | 2 | 3rd  | 2 | 3rd  | 5 |
-| Qu. |   | Qu.  |   | Qu.  |   |
-+-----+---+------+---+------+---+
-| M   | 6 | Max. | 6 | Max. | 1 |
-| ax. | 2 |      | 2 |      | 1 |
-+-----+---+------+---+------+---+
+| deg ree |         | inde gree |           | o utde gree |           |
+|---------|---------|-----------|-----------|-------------|-----------|
+| M in.   | 0       | Min.      | 0 . 0 0 0 | Min.        | 0         |
+| 1st Qu. | 0       | 1st Qu.   | 0         | 1st Qu.     | 0         |
+| Med ian | 1       | Me dian   | 1         | Me dian     | 0         |
+| M ean   | 2 . 4 5 | Mean      | 2 . 4 4 9 | Mean        | 2 . 4 4 9 |
+| 3rd Qu. | 2       | 3rd Qu.   | 2         | 3rd Qu.     | 5         |
+| M ax.   | 6 2     | Max.      | 6 2       | Max.        | 1 1       |
 |         |         |           |           |             |           |
-+-----+---+------+---+------+---+
 
@@
 
-+-----------+-------------+-----------------+
 | degree        | indegree      | outdegree     |
-+===========+=============+=================+
-| Min:      | Min: 0.000  | Min: 0.000      |
-| 1.000     |             |                 |
-+-----------+-------------+-----------------+
-| 1st Qu:   | 1st Qu:     | 1st Qu: 0.000   |
-| 1.000     | 0.000       |                 |
-+-----------+-------------+-----------------+
-| Median:   | Median:     | Median: 0.000   |
-| 4.000     | 1.000       |                 |
-+-----------+-------------+-----------------+
-| Mean:     | Mean: 2.449 | Mean: 2.449     |
-| 4.898     |             |                 |
-+-----------+-------------+-----------------+
-| 3rd Qu:   | 3rd Qu:     | 3rd Qu: 5.000   |
-| 6.000     | 2.000       |                 |
-+-----------+-------------+-----------------+
-| Max:      | Max: 62.000 | Max: 11.000     |
-| 62.000    |             |                 |
-+-----------+-------------+-----------------+
+|---------------|---------------|---------------|
+| Min: 1.000    | Min: 0.000    | Min: 0.000    |
+| 1st Qu: 1.000 | 1st Qu: 0.000 | 1st Qu: 0.000 |
+| Median: 4.000 | Median: 1.000 | Median: 0.000 |
+| Mean: 4.898   | Mean: 2.449   | Mean: 2.449   |
+| 3rd Qu: 6.000 | 3rd Qu: 2.000 | 3rd Qu: 5.000 |
+| Max: 62.000   | Max: 62.000   | Max: 11.000   |
 
@@
 
-#### Degree Centrality: Network vs Node
+#### Vetwork Degree Centrality: In's & Out's
+
+Centralization Score Break Down
+
+-   Stat: Overall Network Centrality
+
+-   Stats: 10 most Popular In's & Out's
 
@@
 
--   Centralization Score Break Down
+-
 

### 2022-04-19 docs/3. SNA - Assignments/sna_Week3/DRAFT-week3-Assignment.Rmd
4.12.22

@@
 
-```{r Statmet: Netweork Centrality:  low & high degree nodes}
-
+```{r Statnet:Centrality: High Degree Nodes}
+library(statnet)
+library(sna)
 #sort to find 5 highest and lowest degree nodes in trade100
 
-network::list.edge.attributes(snEL)
-
-snEL_nodeHeadTail <-data.frame(
+snel_HiStatus<-data.frame(
   name=snEL%v%"vertex.names",
+  sna::degree(snEL),
   indegree=sna::degree(snEL, cmode="indegree"),
@@
 
-snEL_nodeHeadTail%>%
+temp_in <- temp%>%
   arrange(desc(indegree))%>%
   slice(1:10)
-
-snEL_nodeHeadTail%>%
+temp%>%
   arrange(indegree)%>%
@@
 
-snEL_nodeHeadTail%>%
+temp_out <- temp%>%
   arrange(desc(outdegree))%>%
   slice(1:10)
-
-snEL_nodeHeadTail%>%
+temp%>%
   arrange(outdegree)%>%
@@
 
-view(snEL_nodeHeadTail)
+  summary(temp)
+  summary(temp_in)
+  summary(temp_out)
+
+```
+
+```{r Statnet: Centrality: Low Degree Nodes}
+library(statnet)
+library(sna)
+#sort to find 5 highest and lowest degree nodes in trade100
+
+temp <-data.frame(
+  name=snEL%v%"vertex.names",
+  sna::degree(snEL),
+  indegree=sna::degree(snEL, cmode="indegree"),
+  outdegree=sna::degree(snEL, cmode="outdegree"))
+
+low_in <- temp%>%
+  arrange(tail(indegree))%>%
+  slice(1:10)
+temp%>%
+  arrange(indegree)%>%
+  slice(1:10)
+
+low_out <- temp%>%
+  arrange(tail(outdegree))%>%
+  slice(1:10)
+temp%>%
+  arrange(outdegree)%>%
+  slice(1:10)
+
+  summary(temp)
+  summary(low_in)
+  summary(low_out)
 
